### 2020-02-16 Paper/ms.tex
Add manuscript files

\documentclass[twocolumn]{aastex63}
\usepackage{apjfonts}

\usepackage{lipsum}

%\received{\today}
%\revised{\today}
%\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the argument.
%\submitjournal{AJ}

%\topmargin 0.6in

\usepackage{multirow}

%\usepackage{deluxetable}
%\usepackage{color}
%\usepackage[usenames, dvipsnames]{color}
%\definecolor{citeRGB}{rgb}{0,0.1,0.7}
%\usepackage[hyperfootnotes=true,naturalnames=true,letterpaper,pdfstartview=FitH,pdfpagemode=UseNone,colorlinks=true,citecolor=citeRGB]{hyperref}

\gdef\HST{\textit{HST}}
\gdef\Spitzer{\textit{Spitzer}}
\gdef\fluxcgs{\mathrm{erg~s^{-1}~cm^{-2}}}
\gdef\micront{$\mu$m}
\gdef\micronm{\mu\mathrm{m}}
\gdef\aXe{\texttt{aXe}}
\gdef\flux_radius{\textsc{flux\_radius}}
\gdef\epers{\textit{e}$^{-}$ s$^{-1}$}

\gdef\logOH{12 + \log \left(\mathrm{O/H}\right)}
\gdef\SFRuvir{SFR_\mathrm{UV+IR}}
\gdef\peryr{\mathrm{yr}^{-1}}
\gdef\kms{km\,s$^{-1}$}
\gdef\mum{$\mu\mathrm{m}$}
\gdef\24mum{$24\,\mu\mathrm{m}$}
\gdef\arcsec{^{\prime\prime}}
\gdef\UDFj{UDFj-39546284}
\gdef\compareID{UDF-40106456}
\gdef\Lya{\mathrm{Ly}\alpha}
\gdef\Halpha{\mathrm{H}\alpha}
\gdef\Hbeta{\mathrm{H}\beta}

\newcommand\xxx{{\textcolor{red}{\bf xxx}}}
\newcommand\xref[1]{{\textcolor{red}{\bf (REF #1)}}}
\newcommand\XXX[1]{{\textcolor{red}{xxx #1}}}

\gdef\HAWKI{\mbox{HAWK-I}}

\gdef\sncode{\mbox{ABC}}

\shortauthors{Brammer et al.}
\shorttitle{CHArGE}
% \setwatermarkfontsize{50pt} 
%\citestyle{aa}
\begin{document}

\title{SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.9$}

% \footnotetext[*]{Based on observations made with the NASA/ESA \textit{Hubble
% Space Telescope}, programs GO-11640, 12177 and 12328, obtained at the
% Space Telescope Science Institute, which is operated by the Association of
% Universities for Research in Astronomy, Inc., under NASA contract NAS
% 5-26555.}

\correspondingauthor{Gabriel Brammer}
\email{gabriel.brammer@nbi.ku.dk}

\author[0000-0003-2680-005X]{Gabriel Brammer}
\affiliation{The Cosmic Dawn Center, University of Copenhagen, Vibenshuset, Lyngbyvej 2, DK-2100 Copenhagen, Denmark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

We report the discovery of a gravitationally-lensed, multiply-imaged transient source with a likely host at $z=1.905$, observed in archival \textit{Hubble Space Telescope} near-infrared imaging observations.

\end{abstract}
\keywords{supernovae: individual SN-\sncode --- gravitational lensing: strong --- galaxies: evolution --- galaxies: high-redshift}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{s:introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Archival data summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Observations}
\label{s:observations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Lens model
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Strong Lensing Analysis}
\label{s:lensing}

\subsection{Multiple images}
\label{ss:images}

\subsection{Time delay}
\label{ss:timedelay}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  SN Classification
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transient Classification}
\label{s:classifiation}

\subsection{Light curve analysis}
\label{ss:lightcurve}

\subsection{Host galaxy properties}
\label{ss:host}

Discussion from \cite{Newman2018a} and \cite{Newman2018b}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Discussion & Conclusions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}
\label{s:discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  End things
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments

\bibliography{ms}{}
\bibliographystyle{aasjournal}

Software acknowledgements: astropy, scipy, matplotlib, sep, astroquery, shapely

The Cosmic Dawn Center (DAWN) is funded by the Danish National Research Foundation under grant No. 140.

\end{document}

### 2020-02-16 Analysis/mrg/bcg.py

@@ -138,3 +138,12 @@ def bcg_surface_brightness():
     fig.tight_layout(pad=0.5)
     
     fig.savefig('sn_image_{0}_mu.png'.format(img))
+
+def ellipse_fit():
+    pass
+    
+def _ellipse(R, q, phi):
+    xp = R*np.cos(theta)*np.cos(phi) - R*q*np.sin(theta)*np.sin(phi)
+    yp = R*np.cos(theta)*np.sin(phi) + R*q*np.sin(theta)*np.cos(phi)
+    return xp, yp
+    

### 2020-02-16 Paper/ms.tex
First push from overleaf

@@
 
-\shortauthors{Brammer et al.}
+\shortauthors{XXX et al.}
 \shorttitle{CHArGE}
@@
 
-\title{SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.9$}
+\title{SN-\sncode: A Gravitationally-Lensed Type Ia Supernova Candidate at $z=1.95$}
 
@@
 
+\author[0000-0003-3631-7176]{Sune Toft}
+\affiliation{The Cosmic Dawn Center, University of Copenhagen, Vibenshuset, Lyngbyvej 2, DK-2100 Copenhagen, Denmark}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We report the discovery of a gravitationally-lensed, multiply-imaged transient source with a likely host at $z=1.905$, observed in archival \textit{Hubble Space Telescope} near-infrared imaging observations.
+We report the discovery of a gravitationally-lensed, multiply-imaged transient source with a likely host at $z=1.9459$, observed in archival \textit{Hubble Space Telescope} near-infrared imaging observations.
 

### 2020-02-16 Analysis/mrg/irac.py
add IRAC script

@@ -1,0 +1,79 @@
+"""
+IRAC imaging of the cluster field taken before and after the SN discovery 
+epoch
+
+Nothing obviously there, though difference imaging doesn't work very well for
+the rotated IRAC PSF
+
+"""
+
+import os
+import glob
+
+import numpy as np
+
+import astropy.io.fits as pyfits 
+import astropy.wcs as pywcs
+
+AORS = ['r58289152', 'r58785536']
+
+def sync():
+    for aor in AORS:
+        os.system(f'aws s3 sync s3://grizli-v1/IRAC/AORS/{aor}/ ./{aor}/')
+        
+def mosaic():
+    
+    from grizli import utils
+    from drizzlepac.astrodrizzle import ablot 
+    
+    head, outputwcs = utils.make_wcsheader(ra=24.51568758, dec=-21.92554133, size=240, pixscale=1.0, get_hdu=False, theta=0)
+    
+    files = {}
+    drz = {}
+    
+    for ch in ['ch1', 'ch2']:
+        files[ch] = {}
+        drz[ch] = {}
+        
+        for aor in AORS:
+            files[ch][aor] = glob.glob(f'{aor}/{ch}/*/*fits.gz')
+            files[ch][aor].sort()
+            
+            sci_list = [pyfits.open(file)['CBCD'].data for file in files[ch][aor]]
+            unc_list = [pyfits.open(file)['CBUNC'].data for file in files[ch][aor]]
+            N = len(sci_list)
+            wht_list = [1/unc**2 for unc in unc_list]
+            bcd_headers = [pyfits.open(file)['CBCD'].header for file in files[ch][aor]]
+
+            headers = [pyfits.open(file)['WCS'].header for file in files[ch][aor]]
+            wcs_list = [pywcs.WCS(head, relax=True) for head in headers]
+
+            for i in range(N):
+                mask = (unc_list[i] == 0) | (~np.isfinite(sci_list[i]))
+                mask |= (~np.isfinite(unc_list[i]))
+                
+                sci_list[i] -= headers[i]['PEDESTAL']
+                sci_list[i][mask] = 0
+                wht_list[i][mask] = 0
+                wcs_list[i].pscale = utils.get_wcs_pscale(wcs_list[i])
+                
+            _drz = utils.drizzle_array_groups(sci_list, wht_list, wcs_list, outputwcs=outputwcs, kernel='square', pixfrac=0., verbose=True)
+            
[…]

### 2020-02-16 Analysis/mrg/irac.py
add decam

@@ -58,9 +58,13 @@ def mosaic():
                 wcs_list[i].pscale = utils.get_wcs_pscale(wcs_list[i])
                 
             _drz = utils.drizzle_array_groups(sci_list, wht_list, wcs_list, outputwcs=outputwcs, kernel='square', pixfrac=0., verbose=True)
-            
+                        
             for iter in range(2):
                 cr_wht = [wht*1 for wht in wht_list]
+            
+                exptime = 0
+                ndrizim = 0
+                
                 # CR rejection
                 for i in range(N):
                     _blt = ablot.do_blot(_drz[0], _drz[4], wcs_list[i], 1., coeffs=True, interp='poly5')
@@ -68,7 +72,14 @@ def mosaic():
                     cr &= (_blt != 0)
                     cr_wht[i] *= (cr == 0)
                     
+                    if (_blt != 0).sum() > 10:
+                        exptime += bcd_headers[9]['EXPTIME']
+                        ndrizim += 1
+                        
                 _drz = utils.drizzle_array_groups(sci_list, cr_wht, wcs_list, outputwcs=outputwcs, kernel='square', pixfrac=0., verbose=True)
+            
+            _drz[3]['EXPTIME'] = exptime
+            _drz[3]['NDRIZIM'] = ndrizim
             
             for k in ['DATE_OBS', 'MJD_OBS', 'INSTRUME', 'CHNLNUM']:
                 _drz[3][k] = bcd_headers[0][k]

### 2020-02-28 Analysis/mrg/fig1.py
add layout figure

@@ -1,0 +1,120 @@
+"""
+Discovery figure, Fig. 1
+"""
+
+def rgb():
+    
+    from grizli.pipeline import auto_script
+    from mastquery import overlaps
+    import astropy.io.fits as pyfits
+    import astropy.wcs as pywcs
+    import numpy as np      
+    
+    root = 'j013804m2156'
+
+    x0, y0= 2465, 1740
+    
+    NY = 200
+    NX = 200
+
+    slx = slice(x0-NX, x0+NX)
+    sly = slice(y0-NY, y0+NY)
+    
+    mi = -0.01
+    
+    si = 4.8
+    
+    _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si))
+
+    _rgb = auto_script.field_rgb(root=root, filters=['f110w','f125w','f140w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', rgb_scl=[1.06,1,1.02], suffix='.off', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si))
+    
+    im = pyfits.open(f'{root}-f160w_drz_sci.fits')
+    wcs = pywcs.WCS(im[0].header, relax=True)
+    wsl = wcs.slice((sly, slx))
+    
+    coo = utils.read_catalog('coords.txt')
+    N, inter = 10, 0.5
+    
+    N, inter = 20, 1.0
+    
+    xy = np.cast[int](np.round(wcs.all_world2pix(coo['ra'], coo['dec'], 0))).T
+    
+    for i in [4,5,6]:
+        
+        xi, yi = xy[i]
+        slx = slice(xi-N, xi+N)
+        sly = slice(yi-N, yi+N)
+        
+        _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
+
[…]

### 2020-02-28 Paper/ms.tex
Push updates

@@
 \documentclass[twocolumn]{aastex63}
-\usepackage{apjfonts}
 
-\usepackage{lipsum}
+\input{Paper/preamble}
 
-%\received{\today}
-%\revised{\today}
-%\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the argument.
-%\submitjournal{AJ}
-
-%\topmargin 0.6in
-
-\usepackage{multirow}
-
-%\usepackage{deluxetable}
-%\usepackage{color}
-%\usepackage[usenames, dvipsnames]{color}
-%\definecolor{citeRGB}{rgb}{0,0.1,0.7}
-%\usepackage[hyperfootnotes=true,naturalnames=true,letterpaper,pdfstartview=FitH,pdfpagemode=UseNone,colorlinks=true,citecolor=citeRGB]{hyperref}
-
-\gdef\HST{\textit{HST}}
-\gdef\Spitzer{\textit{Spitzer}}
-\gdef\fluxcgs{\mathrm{erg~s^{-1}~cm^{-2}}}
-\gdef\micront{$\mu$m}
-\gdef\micronm{\mu\mathrm{m}}
-\gdef\aXe{\texttt{aXe}}
-\gdef\flux_radius{\textsc{flux\_radius}}
-\gdef\epers{\textit{e}$^{-}$ s$^{-1}$}
-
-\gdef\logOH{12 + \log \left(\mathrm{O/H}\right)}
-\gdef\SFRuvir{SFR_\mathrm{UV+IR}}
-\gdef\peryr{\mathrm{yr}^{-1}}
-\gdef\kms{km\,s$^{-1}$}
-\gdef\mum{$\mu\mathrm{m}$}
-\gdef\24mum{$24\,\mu\mathrm{m}$}
-\gdef\arcsec{^{\prime\prime}}
-\gdef\UDFj{UDFj-39546284}
-\gdef\compareID{UDF-40106456}
-\gdef\Lya{\mathrm{Ly}\alpha}
-\gdef\Halpha{\mathrm{H}\alpha}
-\gdef\Hbeta{\mathrm{H}\beta}
-
-\newcommand\xxx{{\textcolor{red}{\bf xxx}}}
-\newcommand\xref[1]{{\textcolor{red}{\bf (REF #1)}}}
-\newcommand\XXX[1]{{\textcolor{red}{xxx #1}}}
-
-\gdef\HAWKI{\mbox{HAWK-I}}
-
-\gdef\sncode{\mbox{ABC}}
-
-\shortauthors{XXX et al.}
-\shorttitle{CHArGE}
-% \setwatermarkfontsize{50pt} 
-%\citestyle{aa}
 \begin{document}
@@
 \email{gabriel.brammer@nbi.ku.dk}
+
+%%%%%%%%%%%%%%%%% NOT ANYTHING LIKE THE FINAL LIST!!
 
@@
 
+\begin{deluxetable*}{ccccccr}
+    \tablecaption{Additional archival data}
+
+    \tablehead{\colhead{Telescope} & \colhead{Instrument} & \colhead{$\lambda_\mathrm{obs}$} & \colhead{Observation date} & \colhead{MJD} & \colhead{Exp. time (s)}}
+\startdata
+\textit{Spitzer} & IRAC & $3.6\,\mu\mathrm{m}$ & 2016-10-13 14:35:13 & 57674.6078 & 468 \\ % AOR r58289152
+\textit{Spitzer} & IRAC & $4.5\,\mu\mathrm{m}$ & 2016-10-13 14:35:13 & 57674.6078 & 581 \\
+\textit{Spitzer} & IRAC & $3.6\,\mu\mathrm{m}$ & 2016-03-15 03:44:04 & 57462.1556 & 212 \\ % AOR r58785536
+\textit{Spitzer} & IRAC & $4.5\,\mu\mathrm{m}$ & 2016-03-15 03:44:04 & 57462.1556 & 241 \\
+\textit{VLT}     & MUSE & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 & 2649  \\
+\enddata
+\end{deluxetable*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsection{Light curve analysis}
-\label{ss:lightcurve}
+To evaluate the age of each transient image (and therefore constrain the lensing time delay between images), it is valuable to have a firm determination of the transient's class.
+The range of possible transients is broad, encompassing normal SNe, superluminous SNe \citep{galyam_luminous_2019}, fast transients \citep{berger_fast_2013, drout_rapidly_2014}, and even gravitational microlensing events \citep{rodney_two_2018,kelly_extreme_2018}.
+Identifying the transient type makes it possible to use the well-developed library of spectrophotometric SN models \citep[e.g.][]{kessler_models_2019} for the time delay measurement.
+ The first-order distinction that is most important is between a Type Ia SN--understood to be the explosion of a white dwarf star in a binary system--and core collapse SN (CCSN)--the end-point of a star with mass $\gtrsim 10$M$_{\odot}$.
+Given the limited data available for this transient, we will
+
+ \SR{Add to bib file: Gal-Yam SLSN review 2019ARAA..57..305G;
+ \href{https://ui.adsabs.harvard.edu/abs/2013ApJ...779...18B/abstract}{berger 2013};
+\href{https://ui.adsabs.harvard.edu/abs/2014ApJ...794...23D/abstract}{Drout Fast transients};
+Rodney 2018;  Kelly 2018
+ }}
 
@@
 
-Discussion from \cite{Newman2018a} and \cite{Newman2018b}.
+We first seek to classify this SN {\it circumstantially}, using measured properties of the host galaxy's stellar population to infer the SN's type.
+Although Type Ia SNe \citep{mannucci_rates_2005,foley_classifying_2013}.
+
+\SR{TODO:  explain and cite host-based classifications, e.g. Mannucci et al. 2005,   Galsnid:  Foley and Mandel}
+
+Discussion from Newman et al. \cite{newman_resolving_2018,newman_resolving_2018-1}.
+
+Conclusion: the host is a red-dead elliptical. It is most likely a Type Ia SN.
+
+\subsection{Light curve analysis}
+\label{ss:lightcurve}
+
+\SR{TODO: describe color-mag based classification checks}
+Figure~\ref{fig:colormag} shows the location of \SNABC in color-magnitude space, comparing the de-magnified apparent F160W magnitude against the observed F105W-F160W color.
+
+\SR{TODO: describe the interpretation of possible source-plane or lens-plane extinction}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.45\textwidth]{Images/color_mag_contours_all.pdf}
+    \includegraphics[width=0.45\textwidth]{Images/color_mag_contours_image2.pdf}
+    \caption{Classification information for \SNABC based on its position in color-magnitude space.
+Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
+These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
+Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
+    The left-hand plot includes time samples ranging from a rest-frame time of 20 days prior to 100 days after peak brightness.
+The right-hand plot limits this range to $-5<t<5$ rest-frame days.
+\SR{Kyle: did the sims for these plots include some dust extinction assumption, or range of Av values?
+Yes they used host dust w Rv drawn normally around 3.1, sigma 0.5, then the Av assigned using your Ia and CC pAv distributions from Rodney et al 2014a; I have updated images on evernote w a lens plane dust vector but going to hold off on putting those in until I talk to you to make sure what I did made sense there}  The observed photometry from each SN image appears with a cluster of 6 points in the plot: black markers show the observed (uncorrected) color-magnitude values, and colored markers show the demagnified value---after removing the magnification values inferred from each of the five lens model variants.
+Colored markers are slightly offset from the observed F105W-F160W color value for clarity.
+The right-hand plot shows only the photometry for image 2, which is most strongly consistent with a Type Ia SN near peak brightness.
+Red vectors in each diagram show the impact that $A_V=1$ magnitude of dust extinction would have on the observed photometry of \SNABC.
+    }
+    \label{fig:colormag}
+\end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%  Time Delay Constraints
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SN Age and Time Delays}
+\label{s:age_and_timedelays}
+
+In this section, we constrain the relative time delays of \SNABC by using two separate methods to estimate the age of the SN at each image during the single observed epoch.
+The preferred method of SN time delay measurements involves measuring the time of peak brightness for the SN at each image by fitting the light curves, and taking the difference between each measurement as the relative time delay \citep[e.g.][]{pierel_turning_2019,dhawan_magnification_2019,huber_strongly_2019}.
+With only a single observed epoch, this method is impossible due to model parameter degeneracies, and we must rely on age constraints using color (section \ref{s:colorcurves}) and brightness (section \ref{s:lightcurves}) to estimate relative time delays.
+The final time delay measurements are presented in section \ref{s:timedelays}.
+
+\begin{deluxetable*}{crrrrrrr}
+    \tablecaption{\label{tab:model_evidence}Model Preferences}
+
+    \tablehead{\colhead{Model} & \colhead{$\mu_1$} & \colhead{$\mu_2$} & \colhead{$\mu_3$}  &\colhead{$t_2-t_1$} & \colhead{$t_3-t_1$}& \colhead{$t_4-t_1$} & \colhead{Bayesian Evidence}}
+\startdata
+\textit{C} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-15.18\pm0.33$ \\
+\textit{D} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-13.46\pm0.31$ \\
+\textit{E} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-8.91\pm0.27$ \\
+\textit{F} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-9.67\pm0.28$ \\
+\enddata
+
+\end{deluxetable*}
+
+\subsection{Color Curve Age Constraints}
+\label{s:colorcurves}
+
+The color of a Type Ia SN evolves substantially over its lifetime, as the photosphere expands and cools, revealing different layers of the expanding shell and driving episodes of recombination \citep{woosley_type_2007,kasen_type_2009}.
+Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model.
+One important caveat to this principle is that {\it microlensing} effects are not generally achromatic, because the microlensing caustics may cause differential magnification on the scale of the SN radius \citep{goldstein_precise_2018,foxley-marrable_impact_2018,bonvin_impact_2019}.
+Hence, if the expanding SN shell has a color gradient then microlensing may introduce spurious features in the observed colors of the SN \SR{citations: vernardos, kochanek, etc}.
+Goldstein et al.
+\cite{goldstein_precise_2018} found that such chromatic microlensing is most likely not present for lensed Type Ia SNe in the period up to about 25 rest-frame days after explosion ($\sim$15 observer days after peak brightness for \SNABC).
+Only image 2 is likely in the achromatic microlensing phase, but Goldstein et al.
+\cite{goldstein_precise_2018} found extremely small deviations in the rest-frame $U-V$ color curve due to microlensing at the 68\% confidence interval, and up to a $\sim0.2-0.4$ mag difference with 99\% confidence.
+While such extreme microlensing could alter the results for images 1 and 3, it would not alter the measurement of image 2 as it is likely in the achromatic phase.
+
+We use version 2 of the SuperNova Time Delays (SNTD) package\footnote{Link to version 2} both in this section and section \ref{s:lightcurves}, which has several improvements over the original SNTD package \citep{pierel_turning_2019}.
+The SNTD package employs a nested sampling algorithm within three separate methods to measure time delays, and is designed to fully utilize the information present in SN light curve templates \citep[e.g.][]{hsiao_k_2007,kessler_results_2010,pierel_extending_2018} to reduce the impacts of microlensing and make more accurate measurements.
+
+We first obtain a constraint on the time delay from the SN color (F110W-F160W) at each image, which is completely independent from the lens model and relatively insensitive to microlensing.
+We use the "color" method present in SNTD, which attempts to reconstruct the intrinsic color curve using the SALT2 model as a template \citep{guy_salt2:_2007}.
+This method fits the age of each image simultaneously, while also varying the SN model parameters.
+Joint and marginalized posterior distributions
+from SNTD for SALT2 parameters and measured ages for each image are shown in the appendix.
+The result of this process is seen in figure \ref{fig:colorcurve2} for image 2 (and in the appendix for images 1 and 3).
+As the measured colors intersect the model at two distinct locations there are two plausible ages for image 2 of \SNABC, causing a double peaked posterior distribution.
+This is caused by a model parameter degeneracy that could be broken if a sufficiently precise light curve of image 4 is obtained in the future (see section \ref{s:discussion} and the appendix).
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image2.pdf}
+    \caption{Color-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:colorcurves}.
+The upper panel shows the posterior for the age of image 2 from SNTD, using a prior on the SALT2 color parameter (c) based on known population characteristics of SNIa.
+The effect of adding this prior is slight, with no significant deviation from the best-fit value of c ($0.02\pm0.05$).
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 color curve, with the median model shown as a solid line.
+The magenta shaded region shows the 1$\sigma$ range of the measured F105W-F160W color, which corresponds to a $U-V$ color in the rest-frame.}
+    \label{fig:colorcurve2}
+\end{figure}
+
+\subsection{Light Curve Age Constraints}
+\label{s:lightcurves}
+
+To help break the age degeneracies in the color-based constraints, we need to use some information about the relative brightnesses of the \SNABC images.
+For this step we can no longer be independent of the lens models, as we must use the lens-model-predicted magnification values to de-amplify the observed magnitudes for comparison to SN models.
+We expect future improvements of the lens model will further improve the constraints outlined in this section.
+
+For the four lens models described in section \ref{s:lensing}, we correct the observed magnitude of each image using the predicted lensing magnification ($\mu$).
+Next we employ SNTD's "series" method, as it is most effective for sparse sampling, to attempt a reconstruction of the intrinsic SN light curve \citep{pierel_turning_2019}.
+Once again the age of each image is constrained simultaneously, while also varying the SN model parameters (see the appendix for joint and marginalized posterior distributions).
+At this stage we adopt priors on the intrinsic SNIa luminosity \citep{rodney_type_2014} and SNIa color \citep{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Figure \ref{fig:lightcurve2}, and see the appendix for images 1 \& 3).
+
+After repeating this process for each of the four lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
+We find significant preference for models E and F over models C and D (at $\gtrsim15\sigma$), and some preference for model E over model F (at $\sim2.8\sigma$).
+We therefore adopt model E as our preferred model, and use the model E light curve constraints to obtain joint posterior distributions with the lens-independent result from section \ref{s:colorcurves} (Figure \ref{fig:lightcurve2}).
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image2.pdf}
+    \caption{Light-curve-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:lightcurves}.
+The upper panel shows the posterior distributions from SNTD for the age of image 2 from section \ref{s:colorcurves} (magenta), section \ref{s:lightcurves} (light blue), and the combination of both methods (orange).
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 light curve, with the median model shown as a solid line.
+The orange shaded region shows the 1$\sigma$ range of the measured (lens-model-corrected, see table \ref{tab:time_delays}) F160W magnitude, which corresponds to a V band magnitude in the rest-frame.
+}
+    \label{fig:lightcurve2}
+\end{figure}
+
+\begin{deluxetable*}{crrrrr}
+    \tablecaption{\label{tab:time_delays}Time Delays \JP{check/fix these uncertainties.}}
+
+    \tablehead{\colhead{Image} & \colhead{$\mu_E$} &\colhead{$F110W_\rm{corr}$}  & \colhead{$F160W_\rm{corr}$} &  \colhead{Age}&\colhead{$t_i-t_2$}}
+\startdata
+\textit{1} & $8.94\pm1.61$  & $ 28.48\pm 0.24$&$26.71\pm 0.21$ &$79.10^{+45.56}_{-11.76}$&$91.31^{+62.49}_{-23.36}$ \\
+\textit{2} & $18.48\pm3.78$ &  $26.00\pm0.22$&$25.58\pm0.22$ &$-16.67^{+19.14}_{13.10}$&-- \ \ \ \ \ \ \ \ \  \\
+\textit{3} &$13.26\pm2.71$  &  $28.50\pm 0.24$&$26.46 \pm0.23$ &$80.46^{+20.10}_{-9.84}$&$92.60^{+37.28}_{-21.76}$ \\
+\enddata
+
+\end{deluxetable*}
+
+\subsection{Inferred Time Delays}
+\label{s:timedelays}
+As discussed at the end of section \ref{s:lightcurves}, our final age constraints for each SN image are a joint posterior between the parameter estimates from sections \ref{s:colorcurves} and \ref{s:lightcurves} (see appendix for final joint and marginalized posteriors).
+We use image 2 as the reference image because of its likely insensitivity to chromatic microlensing,  resulting in the final time delays and uncertainties reported in table \ref{tab:time_delays}.
+These constraints represent an upper limit on the age (and therefore time delay) uncertainties, but they would still deliver an uncertainty of $\sim0.3\%$ on the $\sim6000$ day time delay expected by lens model E (Table \ref{tab:model_evidence}).
+While already dwarfed by the expected lens model uncertainty, constraints on the intrinsic SN light curve parameters gained from the future fourth image of \SNABC could improve this even further.
+The final posterior distribution for image 2 is bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (see appendix).
+If this degeneracy can be broken with the exquisite photometry expected for the final image of \SNABC, then the expected age of image 2 becomes $-31.51^{+2.23}_{-2.01}$, producing a time delay uncertainty for image 4 of $\sim0.04\%$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Discussion}
+\section{Discussion}
 \label{s:discussion}
@@
 \acknowledgments
-
-\bibliography{ms}{}
-\bibliographystyle{aasjournal}
-
 Software acknowledgements: astropy, scipy, matplotlib, sep, astroquery, shapely
@@
 
+\pagebreak
+
+\bibliographystyle{naturemag}
+
+\bibliography{Paper/references}
+
+\pagebreak
+
+\appendix
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image1.pdf}
+    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image3.pdf}
+    \caption{Color-based age constraints for \SNABC image 1 and image 3, as in Fig~\ref{fig:colorcurve2}.}
+    \label{fig:colorcurve13}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image1.pdf}
+    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image3.pdf}
+    \caption{Light-curve-based age constraints for \SNABC images 1 and 3.}
+    \label{fig:lightcurve13}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/corner_color_curve_fit_with_c_prior.pdf}
+    \caption{Corner plot for color curve nested sampling with prior on c.}
+    \label{fig:corner_cfit}
+\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/corner_model_E.pdf}
+    \caption{Corner plot for light curve nested sampling using model E.}
+    \label{fig:corner_modelE}
+\end{figure*}
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Images/corner_combined_lc_color_model_E.pdf}
+    \caption{Corner plot for combined color curve and model E light curve nested sampling.}
+    \label{fig:corner_combined}
+\end{figure*}
+
 \end{document}

### 2020-03-08 Paper/ms.tex
text updates

@@
 \begin{deluxetable*}{ccccccr}
-    \tablecaption{Additional archival data}
+    \tablecaption{MACSJ0138 Observation Log}
 
-    \tablehead{\colhead{Telescope} & \colhead{Instrument} & \colhead{$\lambda_\mathrm{obs}$} & \colhead{Observation date} & \colhead{MJD} & \colhead{Exp. time (s)}}
+    \tablehead{\colhead{Telescope} & \colhead{Instrument} & \colhead{$\lambda_\mathrm{obs}$} & \colhead{Observation date} & \colhead{MJD} & \colhead{SN} & \colhead{Exp. time (s)}}
 \startdata
-\textit{Spitzer} & IRAC & $3.6\,\mu\mathrm{m}$ & 2016-10-13 14:35:13 & 57674.6078 & 468 \\ % AOR r58289152
-\textit{Spitzer} & IRAC & $4.5\,\mu\mathrm{m}$ & 2016-10-13 14:35:13 & 57674.6078 & 581 \\
-\textit{Spitzer} & IRAC & $3.6\,\mu\mathrm{m}$ & 2016-03-15 03:44:04 & 57462.1556 & 212 \\ % AOR r58785536
-\textit{Spitzer} & IRAC & $4.5\,\mu\mathrm{m}$ & 2016-03-15 03:44:04 & 57462.1556 & 241 \\
-\textit{VLT}     & MUSE & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 & 2649  \\
+\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 212 \\ % AOR r58785536
+\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 241 \\
+\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 000        &   & 5214 \\
+\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 000        & + & 1611 \\
+\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 000        & + & 3611 \\ 
+\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 468 \\ % AOR r58289152
+\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 581 \\
+\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 000        &   & 706 \\ 
+\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 000        &   & 353 \\ 
+\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 000        &   & 706 \\ 
+\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 000        &   & 912 \\ 
+\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 000        &   & 1272 \\ 
+\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 000        &   & 353 \\ 
+\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 &   & 2649  \\
 \enddata
 \end{deluxetable*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
+    \caption{Overview of the field around the center of the MACSJ0138 cluster field and the locations of the lensed host (H1--4) and \SNABC (SN1--3) images.
+The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
+Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
+The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.
+All panels use the late-epoch F125W imaging for the green channel.
+Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use in \S\ref{s:colorcurves} below to constrain the transient classification as a likely Ia supernova explosion.}
+
+    \label{fig:layout}
+\end{figure*}
 
@@
 \label{ss:images}
+
+\XXX{Would an empirical estimate of the relative magnifications from the host images help?  Images 2&3 are blobbed together, but could possibly come up with a number like $\mu_1:(\mu_2 + \mu_3)$.}
 
@@
  The first-order distinction that is most important is between a Type Ia SN--understood to be the explosion of a white dwarf star in a binary system--and core collapse SN (CCSN)--the end-point of a star with mass $\gtrsim 10$M$_{\odot}$.
-Given the limited data available for this transient, we will
+Given the limited data available for this transient, we will not attempt a more fine-grained classification, though in principle that could be achieved with spectroscopy and multi-band photometry upon arrival of the final image.
 
- \SR{Add to bib file: Gal-Yam SLSN review 2019ARAA..57..305G;
- \href{https://ui.adsabs.harvard.edu/abs/2013ApJ...779...18B/abstract}{berger 2013};
-\href{https://ui.adsabs.harvard.edu/abs/2014ApJ...794...23D/abstract}{Drout Fast transients};
-Rodney 2018;  Kelly 2018
- }}
+As a first step, we can use inferences from the lens model to establish a strong prior against any of the various rapidly evolving and low-luminosity stellar transient classes.  
+The expected time delays between the images are $\sim100$ observer-frame days, 
+but we see that three images of the transient are visible simultaneously.
+From this we can infer that the visibility time of the transient in the $z=1.95$ rest-frame must be at least $\sim$30 days. 
+Similarly, with expected magnifications in the vicinity of $\mu\sim10$, the measured apparent magnitudes near 23 AB mag translate to a rest-frame absolute magnitude near $M_B \sim-19.5$ mag (too bright to be a nova, luminous blue variable, or other low-luminosity stellar transient).
+Taken together, these indicators strongly suggest that the transient is a supernova (SN).
+
+Although we have invoked the lens model in this analysis, note that the inferences are not strongly dependent on the specific lens model predictions.
+To make the observed transient images consistent with a fast or low-luminosity transient, the time delays and/or magnifications would have to be changed by more than a factor of 2.
+In the analysis to follow, we will work under the assumption that the transient is a SN.
 
@@
 
-We first seek to classify this SN {\it circumstantially}, using measured properties of the host galaxy's stellar population to infer the SN's type.
-Although Type Ia SNe \citep{mannucci_rates_2005,foley_classifying_2013}.
+We first seek to classify this transient {\it circumstantially}, using measured properties of the host galaxy stellar population to infer the type.
+Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.
+We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \citep{mannucci_rates_2005,foley_classifying_2013}.
+In the case of the host galaxy MRG0138, we have very stringent limits on the star formation rate.
+This galaxy is a high-mass but very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.
+The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr,  making it highly unlikely that MRG0138 retains any significant population of massive stars \SR{this should be revised, b/c of total mass.
+Focus instead on the relative probability.
+as discussed on telecon}
 
-\SR{TODO:  explain and cite host-based classifications, e.g. Mannucci et al. 2005,   Galsnid:  Foley and Mandel}
-
-Discussion from Newman et al. \cite{newman_resolving_2018,newman_resolving_2018-1}.
+Discussion from Newman et al. \citep{newman_resolving_2018-1}.
 

### 2020-03-09 Paper/ms.tex

@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{Paper/Figures/snrequiem_w0wa_compared_to_lsst_wfirst.pdf}
+    \caption{The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$).
+Contours show the 1$\sigma$ confidence region for a typical sample of lensed SN time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta).
+Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation.
+In order to isolate the $w_0, w_a$ dependence, all contours are constructed assuming perfect knowledge of $H_0$, $\Omega_{m,0}$ and $\Omega_{\rm de,0}$.
+SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$).
+\SR{TBD: make the contours actually reflect realistic confidence regions for LSST, WFIRST and SN Requiem}.
+}
+    \label{fig:my_label}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-09 Paper/Nature/main.tex

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\title{Scientific Reports Title to see here}

\author[1,*]{Gabriel Brammer}
\author[2]{Steven Rodney}
\author[2]{Justin Roberts-Pierel}
\author[2]{Kyle O'Connor}
\author[3]{Johan Richard}
\author[1]{Sune Toft}
\author[4]{Mohammad Akhshik}
\author[4]{Katherine Whitaker}
\affil[1]{Affiliation, department, city, postcode, country}
\affil[2]{Affiliation, department, city, postcode, country}
\affil[3]{Affiliation, department, city, postcode, country}
\affil[4]{Affiliation, department, city, postcode, country}

\affil[*]{gabriel.brammer@nbi.ku.dk}

%\affil[+]{these authors contributed equally to this work}

%\keywords{Keyword1, Keyword2, Keyword3}

\begin{abstract}
Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations. Example Abstract. Abstract must not include subheadings or citations.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
%
%  Click the title above to edit the author information and abstract
%
\thispagestyle{empty}

\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.

\section*{Introduction}

The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.

\section*{Results}

Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.

\subsection*{Subsection}

Example text under a subsection. Bulleted lists may be used where appropriate, e.g.

\begin{itemize}
\item First item
\item Second item
\end{itemize}

\subsubsection*{Third-level section}

Topical subheadings are allowed.

\section*{Discussion}

The Discussion should be succinct and must not contain subheadings.

\section*{Methods}

Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.

\bibliography{sample}

\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu. Use the cite command for an inline citation, e.g.  \cite{Hao:gidmaps:2014}.

For data citations of datasets uploaded to e.g. \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

\section*{Author contributions statement}

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

\section*{Additional information}

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{../Figures/fig1_layout.pdf}
    \caption{Overview of the field around the center of the MACSJ0138 cluster field and the locations of the lensed host (H1--4) and \SNABC (SN1--3) images. The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.  All panels use the late-epoch F125W imaging for the green channel.  Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use in \S\ref{s:colorcurves} below to constrain the transient classification as a likely Ia supernova explosion.}

    \label{fig:layout}
\end{figure*}

% \begin{figure}[ht]
% \centering
% \includegraphics[width=\linewidth]{stream}
% \caption{Legend (350 words max). Example legend text.}
% \label{fig:stream}
% \end{figure}

% \begin{table}[ht]
% \centering
% \begin{tabular}{|l|l|l|}
% \hline
% Condition & n & p \\
% \hline
% A & 5 & 0.1 \\
% \hline
% B & 10 & 0.01 \\
% \hline
% \end{tabular}
% \caption{\label{tab:example}Legend (350 words max). Example legend text.}
% \end{table}

Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.

\end{document}

### 2020-03-27 Paper/Nature/main.tex
Updates from Overleaf

@@
 \usepackage[T1]{fontenc}
-\title{Scientific Reports Title to see here}
+
+\input{Paper/preamble}
+
+\title{Three views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
 
@@
 \author[2]{Steven Rodney}
-\author[2]{Justin Roberts-Pierel}
+\author[2]{Justin Pierel}
 \author[2]{Kyle O'Connor}
@@
 \author[4]{Katherine Whitaker}
-\affil[1]{Affiliation, department, city, postcode, country}
-\affil[2]{Affiliation, department, city, postcode, country}
-\affil[3]{Affiliation, department, city, postcode, country}
-\affil[4]{Affiliation, department, city, postcode, country}
+\affil[1]{Cosmic Dawn Center, Niels Bohr Institute, K{\o}benhavns Universitet}
+\affil[2]{University of South Carolina}
+\affil[3]{Universit\'e Claude Bernard Lyon}
+\affil[4]{University of Massachusetts, Amherst}
 
@@
 \begin{abstract}
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
-Example Abstract.
-Abstract must not include subheadings or citations.
+% https://www.nature.com/documents/nature-summary-paragraph.pdf
+%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline
+The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe. 
+%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
+The observed brightness of distant type Ia supernova explosions has played a key role in  mapping the expansion history and to the discovery of dark energy driving the accelerating expansion rate.
+Determining the nature of dark energy and how it may evolve over time is a primary goal for major current and planned large-scale cosmology experiments.
+%One sentence clearly stating the general problem being addressed by this particular study
+One promising method for determining the dark energy equation of state and its evolution  is through time delays of gravitational lens systems, which for a given lens potential provide a geometric measurement of the relative angular diameter distances to the foreground lens and background source.
+%One sentence summarising the main result (with the words “here we show” or their equivalent).
+Here we report the discovery of a Type Ia supernova explosion in an evolved galaxy at $z=1.95$ gravitationally lensed by a massive foreground galaxy cluster that will provide a time delay precision of <1\%.
+%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+With three lensed images of the supernova detected in existing observations from the \textit{Hubble Space Telescope} with time delays of order 50 days, this is the most distant multiply-imaged supernova yet discovered.
+A fourth image in the component closest to the cluster core is predicted to appear in the year 2035$\pm$2.
+Monitoring that future image will provide a time delay precision of $\approx 7$ days over an unprecedented baseline of nearly 20 years.
+This single source will therefore provide a similar precision and complementary cosmological constraints to an ensemble of dozens or hundreds of time delay measurements expected at somewhat lower redshifts and shorter timescales from the planned ground-based LSST and WFIRST space telescope missions.
+If we suppose that cosmological parameters such as the local expansion rate ($H_0$) and dominant energy densities $\Omega_m$ and $\Omega_\Lambda$ will be well established in 2035, the combined time delay measurements will constrain the dark energy equation of state ($w_0$) to better than 10\%.
+%One or two sentences to put the results into a more general context. 
+% Considering this observation in the context of
+% Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion.
+
 \end{abstract}
@@
 \maketitle
-% * <john.hammersley@gmail.com> 2015-02-09T12:07:31.197Z:
+
 %
@@
 %
-\thispagestyle{empty}
 
-\noindent Please note: Abbreviations should be introduced at the first mention in the main text – no abbreviations lists. Suggested structure of main text (not enforced) is provided below.
+% \thispagestyle{empty}
 
-\section*{Introduction}
+% \section*{Introduction}
 
-The Introduction section, of referenced text\cite{Figueredo:2009dg} expands on the background of the work (some overlap with the Abstract is acceptable).
-The introduction should not include subheadings.
+% \section*{Results}
 
-\section*{Results}
+%Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.
 
-Up to three levels of \textbf{subheading} are permitted. Subheadings should not be numbered.
+%\subsection*{Subsection}
 
-\subsection*{Subsection}
+% Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
 
-Example text under a subsection. Bulleted lists may be used where appropriate, e.g.
+% \begin{itemize}
+% \item First item
+% \item Second item
+% \end{itemize}
 
-\begin{itemize}
-\item First item
-\item Second item
-\end{itemize}
+% \subsubsection*{Third-level section}
 
-\subsubsection*{Third-level section}
+% Topical subheadings are allowed.
 
-Topical subheadings are allowed.
+% \section*{Discussion}
 
-\section*{Discussion}
+% The Discussion should be succinct and must not contain subheadings.
 
-The Discussion should be succinct and must not contain subheadings.
+% \section*{Methods}
 
-\section*{Methods}
+% Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.
 
-Topical subheadings are allowed. Authors must ensure that their Methods section includes adequate experimental and characterization data necessary for others in the field to reproduce their work.
+% \bibliography{sample}
 
-\bibliography{sample}
-
-\noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
+% \noindent LaTeX formats citations and references automatically using the bibliography records in your .bib file, which you can edit via the project menu.
 Use the cite command for an inline citation, e.g.
@@
 
-For data citations of datasets uploaded to e.g.
+% For data citations of datasets uploaded to e.g.
 \emph{figshare}, please use the \verb|howpublished| option in the bib entry to specify the platform and the link, as in the \verb|Hao:gidmaps:2014| example in the sample bibliography file.
 
-\section*{Acknowledgements (not compulsory)}
+% \section*{Acknowledgements (not compulsory)}
 
-Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
+% Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
 
-\section*{Author contributions statement}
+% \section*{Author contributions statement}
 
-Must include all authors, identified by initials, for example:
-A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.
+% Must include all authors, identified by initials, for example: A.A.
+conceived the experiment(s),  A.A.
+and B.A.
+conducted the experiment(s), C.A.
+and D.A.
+analysed the results.
+All authors reviewed the manuscript.
 
-\section*{Additional information}
+% \section*{Additional information}
 
-To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).
+% To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing interests} (mandatory statement).
 
-The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper.
+% The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing interests statement} on behalf of all authors of the paper.
 This statement must be included in the submitted article file.
@@
     \caption{Overview of the field around the center of the MACSJ0138 cluster field and the locations of the lensed host (H1--4) and \SNABC (SN1--3) images. 
-The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
-Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
-The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.
-All panels use the late-epoch F125W imaging for the green channel.
-Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use in \S\ref{s:colorcurves} below to constrain the transient classification as a likely Ia supernova explosion.}
-
+    %The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  
+    Three-color images are generated from the \textit{Hubble} WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.
+It is immediately clear that the SN2 image is substantially bluer than the other two, which helps constrain the transient classification as a likely Ia supernova explosion.}
     \label{fig:layout}
 \end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
+    \caption{Classification information for \SNABC based on its position in color-magnitude space.
+(left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
+These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
+Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
+Open markers show the observed photometry of the SN.
+Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.
+(right) The evolution of a Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.
+White diamonds correspond to the labels on the colorbar at right, showing the time relative to maximum brightness in the observer frame.
+An interactive 3-D version of this figure is available online at \url{https://plot.ly/~jpierel/6/#/}
+    }
+    \label{fig:colormag}
+\end{figure*}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=0.5\textwidth]{../Figures/combined_lightcurve.pdf}
+%     \caption{Color and magnitude evolution from the multiple images of the SN.
+Panel $a)$ shows the direct measurements for the three SN images, where the $H_{160}$-band magnitude has been corrected for the (achromatic) gravitational lensing magnification derived from the lens model.
+The evolution in both color and magnitude is fully consistent with a Type Ia template (gray curve) where the SN2 image is observed just before peak brightness and the other two images show the SN approximately 30 rest-frame days after the peak.
+These time delays inferred from the lightcurve are consistent with the estimates from the lens model, shown in the filled regions at lower right.}
+%     \label{fig:my_label}
+% \end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{../Figures/snrequiem_w0wa_compared_to_lsst_wfirst.pdf}
+    \caption{The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$).
+Contours show the 1$\sigma$ confidence region for a typical sample of lensed SN time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta).
+Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation.
+In order to isolate the $w_0, w_a$ dependence, all contours are constructed assuming perfect knowledge of $H_0$, $\Omega_{m,0}$ and $\Omega_{\rm de,0}$.
+SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$).
+\SR{TBD: make the contours actually reflect realistic confidence regions for LSST, WFIRST and SN Requiem}.
+}
+    \label{fig:my_label}
+\end{figure}
 
@@
 
-Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
+% Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
 

### 2020-03-27 Paper/ms.tex
Updates from Overleaf

@@
 \input{Paper/preamble}
+\usepackage{apjfonts}
 
@@
 
-\author[0000-0003-3631-7176]{Sune Toft}
-\affiliation{The Cosmic Dawn Center, University of Copenhagen, Vibenshuset, Lyngbyvej 2, DK-2100 Copenhagen, Denmark}
+% \author[0000-0003-3631-7176]{Sune Toft}
+% \affiliation{The Cosmic Dawn Center, University of Copenhagen, Vibenshuset, Lyngbyvej 2, DK-2100 Copenhagen, Denmark}
 
@@
 \XXX{Would an empirical estimate of the relative magnifications from the host images help?  Images 2&3 are blobbed together, but could possibly come up with a number like $\mu_1:(\mu_2 + \mu_3)$.}
+\SR{This sounds like a useful validity check 
+for a lens model.  Worth doing, but not an essential piece of info for this paper}
 
@@
 
-\subsection{Light curve analysis}
+\subsection{Classification from Color and Brightness}
 \label{ss:lightcurve}
 
-\SR{TODO: describe color-mag based classification checks}
 Figure~\ref{fig:colormag} shows the location of \SNABC in color-magnitude space, comparing the de-magnified apparent F160W magnitude against the observed F105W-F160W color.  
+For a source at $z=1.95$ the F160W band is centered near 5400 \AA, approximately corresponding to the Bessell V bandpass, while the F105W-F160W color approximates a U-V color. 
+As shown in Figure~\ref{fig:colormag}, the observed photometry for \SNABC is fully consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~\ref{tab:model_evidence}.
+The magnification-corrected photometry is inconsistent with Type II SNe, which are fainter and more blue.
+\SNABC is marginally consistent with the CCSN Type Ib/Ic sub-class, although the image 2 point falls outside of the 95\% confidence region for that population.
 
-\SR{TODO: describe the interpretation of possible source-plane or lens-plane extinction}
+The right panel in Figure~\ref{fig:colormag} shows that the three data points are also consistent with the expected time-dependence  of a Type Ia SN in this color-magnitude space.
+Visualizing the changing color and brightness of a SNIa at $z=1.95$ in the F105W and F160W bands, we see that it  would intersect image 2 near peak brightness and approach the image 1 and 3 photometry at roughly 80 observer-frame days after peak.
+
+Taken together, this evidence reinforces the conclusion that \SNABC is most likely a Type Ia SN.  Although we have to adopt a magnification correction 
+from a lens model, this conclusion is not sensitive to the choice of lens model.
+Every lens model we have evaluated locates \SNABC's un-magnified position squarely within the Type Ia region of color-magnitude space.
+Dust is also not a confounding factor here.
+The simulations used to generate the contours in Figure~\ref{fig:colormag} include dust extinction at the source plane.
+If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC requiem points upward and leftward on this plot, causing it to be even more strongly associated with the Type Ia region.
+
+\SR{TODO: add an appendix explaining the sims}
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{Images/color_mag_contours_all.pdf}
-    \includegraphics[width=0.45\textwidth]{Images/color_mag_contours_image2.pdf}
+    \includegraphics[width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
     \caption{Classification information for \SNABC based on its position in color-magnitude space.
-Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
+(left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
 These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
 Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
-    The left-hand plot includes time samples ranging from a rest-frame time of 20 days prior to 100 days after peak brightness.
-The right-hand plot limits this range to $-5<t<5$ rest-frame days.
-\SR{Kyle: did the sims for these plots include some dust extinction assumption, or range of Av values?
-Yes they used host dust w Rv drawn normally around 3.1, sigma 0.5, then the Av assigned using your Ia and CC pAv distributions from Rodney et al 2014a; I have updated images on evernote w a lens plane dust vector but going to hold off on putting those in until I talk to you to make sure what I did made sense there}  The observed photometry from each SN image appears with a cluster of 6 points in the plot: black markers show the observed (uncorrected) color-magnitude values, and colored markers show the demagnified value---after removing the magnification values inferred from each of the five lens model variants.
-Colored markers are slightly offset from the observed F105W-F160W color value for clarity.
-The right-hand plot shows only the photometry for image 2, which is most strongly consistent with a Type Ia SN near peak brightness.
-Red vectors in each diagram show the impact that $A_V=1$ magnitude of dust extinction would have on the observed photometry of \SNABC.
+Open markers show the observed photometry of the SN.
+Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.
+(right) The evolution of a Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.
+White diamonds correspond to the times labeled on the colorbar at right.
+An interactive 3-D version of this figure is available online at \url{https://plot.ly/~jpierel/6/#/}
     }

### 2020-03-28 Paper/Nature/main.tex

@@
 
-\title{Three views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
+\title{Three magnified views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
 
@@
 \author[4]{Mohammad Akhshik}
-\author[4]{Katherine Whitaker}
+\author[5]{Katherine Whitaker}
 \affil[1]{Cosmic Dawn Center, Niels Bohr Institute, K{\o}benhavns Universitet}
@@
 \affil[3]{Universit\'e Claude Bernard Lyon}
-\affil[4]{University of Massachusetts, Amherst}
+\affil[4]{University of Connecticut}
+\affil[5]{University of Massachusetts, Amherst}
 
@@
 %Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
-The observed brightness of distant type Ia supernova explosions has played a key role in  mapping the expansion history and to the discovery of dark energy driving the accelerating expansion rate.
-Determining the nature of dark energy and how it may evolve over time is a primary goal for major current and planned large-scale cosmology experiments.
+The observed brightness of distant Type Ia supernova (SN) explosions has played a key role in mapping the expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate.
+Determining the nature of dark energy and how it may evolve over time is a primary goal for current and planned large-scale cosmology experiments.
 %One sentence clearly stating the general problem being addressed by this particular study
-One promising method for determining the dark energy equation of state and its evolution  is through time delays of gravitational lens systems, which for a given lens potential provide a geometric measurement of the relative angular diameter distances to the foreground lens and background source.
+One promising method for determining the dark energy equation of state and its evolution  is through time delays of gravitational lens systems, which for a given lens potential provide a measurement of the ratio of the angular diameter distances to the foreground lens and background source.
 %One sentence summarising the main result (with the words “here we show” or their equivalent).
-Here we report the discovery of a Type Ia supernova explosion in an evolved galaxy at $z=1.95$ gravitationally lensed by a massive foreground galaxy cluster that will provide a time delay precision of <1\%.
+Here we report the discovery of a strongly-lensed Type Ia SN explosion that will provide a time delay precision of $<1\%$.
+The SN is in an evolved galaxy at $z=1.95$ gravitationally lensed by a massive foreground galaxy cluster.
 %Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
@@
 A fourth image in the component closest to the cluster core is predicted to appear in the year 2035$\pm$2.
-Monitoring that future image will provide a time delay precision of $\approx 7$ days over an unprecedented baseline of nearly 20 years.
-This single source will therefore provide a similar precision and complementary cosmological constraints to an ensemble of dozens or hundreds of time delay measurements expected at somewhat lower redshifts and shorter timescales from the planned ground-based LSST and WFIRST space telescope missions.
+Observing the lightcurve of that future image will provide a time delay precision of $\approx 7$ days over an unprecedented baseline of nearly 20 years.
+This single source will therefore provide a similar precision and complementary cosmological constraints to an ensemble of dozens of time delay measurements expected at somewhat lower redshifts and shorter timescales from the planned ground-based LSST and WFIRST space telescope missions.
 If we suppose that cosmological parameters such as the local expansion rate ($H_0$) and dominant energy densities $\Omega_m$ and $\Omega_\Lambda$ will be well established in 2035, the combined time delay measurements will constrain the dark energy equation of state ($w_0$) to better than 10\%.
@@
     Three-color images are generated from the \textit{Hubble} WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.
-It is immediately clear that the SN2 image is substantially bluer than the other two, which helps constrain the transient classification as a likely Ia supernova explosion.}
+It is immediately clear that the SN2 image is substantially bluer than the other two, which helps constrain the transient classification as a likely Ia supernova explosion.
+\textbf{The lens model that predicts time delays of the first three images consistent with the evolution of the Ia lightcurve predicts that the SN image in H4 will appear in 2035.} }
     \label{fig:layout}
@@
 White diamonds correspond to the labels on the colorbar at right, showing the time relative to maximum brightness in the observer frame.
-An interactive 3-D version of this figure is available online at \url{https://plot.ly/~jpierel/6/#/}
+An interactive 3-D version of this figure is available online \href{https://plot.ly/~jpierel/6/#/}{here}.
     }
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{../Figures/snrequiem_w0wa_compared_to_lsst_wfirst.pdf}
+    \includegraphics[width=0.7\textwidth]{../Figures/snrequiem_w0wa_compared_to_lsst_wfirst.pdf}
     \caption{The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$).
-Contours show the 1$\sigma$ confidence region for a typical sample of lensed SN time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta).
+Contours show the 1$\sigma$ confidence region for a typical sample of lensed SNIa time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta).
 Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation.
@@
 SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$).
-\SR{TBD: make the contours actually reflect realistic confidence regions for LSST, WFIRST and SN Requiem}.
-}
+This single SN could deliver constraints on dark energy equation of state parameters comparable to several dozen SNe with shorter and less precise  time delays.}
     \label{fig:my_label}

### 2020-03-28 Paper/Nature/main.tex
Presubmission to Nature

@@
 %One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline
-The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe. 
+The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe\footnote{Penzias \& Wilson 1965, ApJL, 142, 419}. 
 %Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
-The observed brightness of distant Type Ia supernova (SN) explosions has played a key role in mapping the expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate.
-Determining the nature of dark energy and how it may evolve over time is a primary goal for current and planned large-scale cosmology experiments.
+The observed brightness of distant Type Ia supernova (SN) explosions has played a key role in mapping the expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate\footnote{Riess et al.
+1998, AJ, 116, 1009; Perlmutter et al.
+1999, ApJ, 517, 565; Riess et al.
+2007, ApJ, 659, 98}.
+Determining the nature of dark energy and how it may evolve over time is a primary goal for current and planned large-scale cosmology experiments\footnote{Amendola et al.
+2013, Living Reviews in Relativity, Volume 16, Issue 1, article id.
+6, 270 pp.; Ivezic et al.
+2019, ApJ, 873, 111}.
 %One sentence clearly stating the general problem being addressed by this particular study
-One promising method for determining the dark energy equation of state and its evolution  is through time delays of gravitational lens systems, which for a given lens potential provide a measurement of the ratio of the angular diameter distances to the foreground lens and background source.
+One promising method for determining the dark energy equation of state and its evolution  is through time delays of gravitational lens systems, which for a given lens potential provide a measurement of the ratio of the angular diameter distances to the foreground lens and background source\footnote{Coe \& Moustakas, 2009, Apj 706, 45; Suyu 2010, ApJ, 711, 201}.
 %One sentence summarising the main result (with the words “here we show” or their equivalent).
@@
 This single source will therefore provide a similar precision and complementary cosmological constraints to an ensemble of dozens of time delay measurements expected at somewhat lower redshifts and shorter timescales from the planned ground-based LSST and WFIRST space telescope missions.
-If we suppose that cosmological parameters such as the local expansion rate ($H_0$) and dominant energy densities $\Omega_m$ and $\Omega_\Lambda$ will be well established in 2035, the combined time delay measurements will constrain the dark energy equation of state ($w_0$) to better than 10\%.
+If we suppose that cosmological parameters such as the local expansion rate ($H_0$) and dominant energy densities $\Omega_m$ and $\Omega_\Lambda$ will be well established in 2035, the combined time delay measurements will constrain the dark energy equation of state ($w_0$) to a precision of 20\%.
 %One or two sentences to put the results into a more general context. 
@@
     \caption{The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$).
-Contours show the 1$\sigma$ confidence region for a typical sample of lensed SNIa time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta).
+Contours show the 1$\sigma$ confidence region for a typical sample of lensed SNIa time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta), which is shown for assumed uncertainties on the lens potential of 5\% and 2\%.
 Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation.

### 2020-06-17 Paper/Science/main.tex
Updates from Overleaf

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt,dvipsnames]{article}

%extra packages added during drafting, remove for submission
\usepackage{todonotes}
\usepackage{hyperref}
\usepackage{booktabs}

% Simple little macros to hide and highlight some text:
%\newcommand{\highlight}[1]{{\bf \textcolor{Maroon}{#1}}}
\newcommand{\highlight}[1]{{\bf {#1}}}

%\usepackage{ifthen}
\newif\ifshowoutline
%\showoutlinetrue
\showoutlinefalse
\ifshowoutline
    \newcommand{\outline}[1]{\textcolor{blue}{#1}}
\else
    \newcommand{\outline}[1]{}
\fi

\usepackage{amssymb}
\usepackage{xspace}

\gdef\arcsec{$^{\prime\prime}$}
\def\SNABC{SN Requiem\xspace}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

% Include your paper's title here

%\title{Requiem for a 10 billion year old supernova } 
\title{A Gravitationally Lensed Supernova with an Observable Decade-long Time Delay}
%\title{A Strongly Lensed Type Ia Supernova with a Decade-Long Time Delay}
%\title{SN Requiem: A Strongly Lensed Type Ia Supernova with a Decade-Long Time Delay}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

%%%%%%%fill in once decided
% \author
% {John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
% \\
% \normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
% \normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
% \normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
% \\
% \normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
% }

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
%   The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe\footnote{Penzias \& Wilson 1965, ApJL, 142, 419}.

  We report the discovery of a quadruply-lensed Type Ia supernova (SN) explosion that will produce a time delay measurement uncertainty of $<1\%$. This unprecedented scenario will enable a unique and highly precise measurement of the Hubble constant from a single lensed SN.  The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACSJ0138. With three lensed images of the supernova detected in existing observations from the \textit{Hubble Space Telescope} with time delays of order 50 days, this is the most distant multiply-imaged supernova yet discovered.  A fourth image in the component closest to the cluster core is predicted to appear in the year 2035$\pm$2.  Observing the light curve of that future image will provide a time delay precision of $\approx 7$ days over an extraordinary baseline of nearly 20 years.

\end{sciabstract}

% In setting up this template for *Science* papers, we've used both
% the \section* command and the \paragraph* command for topical
% divisions.  Which you use will of course depend on the type of paper
% you're writing.  Review Articles tend to have displayed headings, for
% which \section* is more appropriate; Research Articles, when they have
% formal topical divisions at all, tend to signal them with bold text
% that runs into the paragraph, for which \paragraph* is the right
% choice.  Either way, use the asterisk (*) modifier, as shown, to
% suppress numbering.

%\section*{Introduction}

%\todo[inline]{JP: Can edit intro} SN1a play a special role in cosmology, they are standard candles -> led to discovery of DE. High redshift SN-1a provide particularly strong constraints.
%\newline

Observations of Type Ia supernova (SN) explosions have played a key role in mapping the cosmic expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate\cite{riess_observational_1998,perlmutter_measurements_1999, Riess_large_2019}.  Determining the nature of dark energy and how it may evolve over time is a primary goal for the large-scale cosmology experiments of the 2020s \cite{amendola_cosmology_2013,spergel_wide_2015,Ivezic_lsst_2019}.
A series of recent investigations into the expansion rate of the universe (the Hubble-LeM\^aitre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background (CMB) radiation \cite{Riess_large_2019,aghanim_planck_2018}.  Resolving this tension in $H_0$ measurements may reveal new physics from the early universe \textcolor{red}{Citation here?}, and to do so requires multiple 
independent cosmological probes.

One promising method uses %time delays of 
gravitational lens systems in which a background
source appears as multiple images that arrive to the observer with relative delays \cite{einstein_lens_1936}.
%, which %for a given lens potential 
When such a strongly-lensed source is variable, one can measure the time delay between any pair of lensed images and derive a ratio of angular diameter distances to the foreground lens and background source. 
This distance ratio is sensitive to cosmological parameters, such as 
%the expansion rate of the universe, 
$H_0$  and the dark energy equation of state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
In recent years this method has been very successfully applied to lensed
quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}. As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosological_2018}.

Gravitationally lensed SN with multiple images present an attractive new addition to this field. Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---a contrast to the stochastic variation of quasars.  However, the exploration of lensed SN time delay cosmography has been hindered by their rarity.  To date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}. The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_SNRefsdal_2016}. The second, {\it SN iPTF16geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2020}. Here we present the discovery 
of a third lensed SN resolved into multiple images: SN Requiem.

\todo[inline]{put in precise UT dates for HST data and double check newman proposal \href{https://archive.stsci.edu/hst/abstract.html}{(this one?)}}

We discovered SN Requiem using data from the Hubble Space Telescope (HST) program {\it Resolved Quiescent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik). This project targets rare examples of quiescent galaxies that have been magnified by strong gravitational lensing. %These are typically too faint and compact to be resolved even with Hubble, but due to lensing are magnified. This provides a unique opportunity to  understand the still mysterious quenching mechnism. 
The brightest and most spectacular galaxy targeted by REQUIEM
is MRG-M0138, first discovered as a massive red galaxy (MRG) at $z=1.95$ \cite{newman_resolving_2018} behind the massive galaxy cluster MACS J0138.0-2155 \cite{ebeling_macs_2001}.
MRG-M0138 is quadruply lensed by the foreground cluster, which is at $z=0.338$.  
During analysis of REQUIEM observations obtained July 2019 we discovered three point 
sources that were present in archival HST images from July 2016, part of the program 
that originally discovered the MRG-M0138 galaxy (HST-GO-14496; PI:Newman). 
Each point source is within 5 arcseconds of one of the four MRG-M0138 images.  None of the
three point sources are present in the REQUIEM HST data in 2019 (Fig \ref{fig:layout}). We infer that 
the point sources are multiple images of a single astrophysical 
transient in MRG-M0138, most likely a SN. Hereafter we call this multiply-imaged transient {\it SN Requiem}.

To construct a lens model for the MACS J0138.0-2155 cluster we used the publicly available {\tt Lenstool} software \cite{jullo_bayesian_2007, kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster scale and multiple galaxy scale potentials.  To avoid unintended bias, we kept the lens model development completely separate from the analysis of the SN.  Only upon independent completion of both were the results combined for the analysis described here.  The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the central light peak and the SN location in each image) as well as a multiply-imaged background 
galaxy at $z=0.766$, both having secure spectroscopic redshifts.  
From this model we derive estimates for the lensing magnification and time delay of each of the SN images, including the predicted fourth image (Tab 1).
The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in 20XX+/-X., with a magnification of X. A fifth image will also appear in 20XX+/- but this will be demagnified and likely not observable.

%The range of possible transients for Requiem is broad, encompassing normal SNe, superluminous SNe (galyam luminous 2019), fast transients (berger fast 2013, drout rapidly 2014), and even gravitational microlensing events (rodney two 2018, kelly extreme 2018). 
To realize the cosmological promise of SN Requiem 
we need to estimate the age of each SN image, which in turn constrains the lensing time delays. For this
goal, it is valuable to have a firm determination of the transient’s class. Expected time delays and magnifications from the lens model exclude any of the various rapidly evolving and low-luminosity stellar transient classes, strongly suggesting that it is a SN. The first-order SN distinction remaining is between a Type Ia SN---the explosion of a white dwarf star in a binary system---and a core collapse SN (CCSN)---the end-point of a star with mass $\gtrsim 10 M_{\odot}$. 
The properties of the host galaxy can inform this classification because CCSN are limited to galaxies with young stellar populations. Limits on the specific star formation rate and age for this host, MRG-M0138, show it to be a high-mass but very quiescent and evolved galaxy, %($\log(M_*/M_\odot)=11.7\pm0.2; )$ , 
unlikely to retain any significant population of high-mass stars \cite{newman_resolving_2018}. Based on observed properties of the host galaxy alone, we find a 75\% probability that Requiem is a Type Ia SN (see supplementary text). Adopting the lens model magnifications for the three observed SN images (Table S2) the position of each SN image in color-magnitude space (Fig \ref{fig:class}) provides more classification leverage, yielding p(Ia)=\textcolor{red}{XX}. By also including the measured time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=\textcolor{Orange}{YY} (Fig \ref{fig:class}).
%This is corroborated by the limited data available for the transient. In color -magnitude space it displays best agreement with the Type Ia population (Fig 1). 
An improved classification can be achieved with spectroscopy and multi-band photometry upon arrival of the fourth image.

%The galaxy has very low SFR=XX and based on stellar ages stopped forming stars ~X.X Gyr earlier. This is a proto typical early type galaxy progenitor.

%%%%%% ORIGINAL Classification text
% To evaluate the age of each transient image (and therefore constrain the lensing time delay between images), it is valuable to have a firm determination of the transient's class.  The range of possible transients is broad, encompassing normal SNe, superluminous SNe \citep{galyam_luminous_2019}, fast transients \citep{berger_fast_2013, drout_rapidly_2014}, and even gravitational microlensing events \citep{rodney_two_2018,kelly_extreme_2018}.  Identifying the transient type makes it possible to use the well-developed library of spectrophotometric SN models \citep[e.g.][]{kessler_models_2019} for the time delay measurement. 
%  The first-order distinction that is most important is between a Type Ia SN--understood to be the explosion of a white dwarf star in a binary system--and core collapse SN (CCSN)--the end-point of a star with mass $\gtrsim 10$M$_{\odot}$.  Given the limited data available for this transient, we will not attempt a more fine-grained classification, though in principle that could be achieved with spectroscopy and multi-band photometry upon arrival of the final image.

% As a first step, we can use inferences from the lens model to establish a strong prior against any of the various rapidly evolving and low-luminosity stellar transient classes.  
% The expected time delays between the images are $\sim100$ observer-frame days, 
% but we see that three images of the transient are visible simultaneously.
% From this we can infer that the visibility time of the transient in the $z=1.95$ rest-frame must be at least $\sim$30 days. 
% Similarly, with expected magnifications in the vicinity of $\mu\sim10$, the measured apparent magnitudes near 23 AB mag translate to a rest-frame absolute magnitude near $M_B \sim-19.5$ mag (too bright to be a nova, luminous blue variable, or other low-luminosity stellar transient).
% Taken together, these indicators strongly suggest that the transient is a supernova (SN).

% Although we have invoked the lens model in this analysis, note that the inferences are not strongly dependent on the specific lens model predictions.  To make the observed transient images consistent with a fast or low-luminosity transient, the time delays and/or magnifications would have to be changed by more than a factor of 2.  In the analysis to follow, we will work under the assumption that the transient is a SN.

% \subsection{Host galaxy properties}
% \label{ss:host}

% We first seek to classify this transient {\it circumstantially}, using measured properties of the host galaxy stellar population to infer the type. Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.  We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \citep{mannucci_rates_2005,foley_classifying_2013}.  In the case of the host galaxy MRG0138, we have very stringent limits on the star formation rate. This galaxy is a high-mass but very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.  The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr,  making it highly unlikely that MRG0138 retains any significant population of massive stars \SR{this should be revised, b/c of total mass.  Focus instead on the relative probability. as discussed on telecon}

% Discussion from Newman et al. \citep{newman_resolving_2018-1}.

% Conclusion: the host is a red-dead elliptical. It is most likely a Type Ia SN.

% \subsection{Classification from Color and Brightness}
% \label{ss:lightcurve}

% Figure~\ref{fig:colormag} shows the location of \SNABC in color-magnitude space, comparing the de-magnified apparent F160W magnitude against the observed F105W-F160W color.  
% For a source at $z=1.95$ the F160W band is centered near 5400 \AA, approximately corresponding to the Bessell V bandpass, while the F105W-F160W color approximates a U-V color. 
% As shown in Figure~\ref{fig:colormag}, the observed photometry for \SNABC is fully consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~\ref{tab:model_evidence}.  The magnification-corrected photometry is inconsistent with Type II SNe, which are fainter and more blue. \SNABC is marginally consistent with the CCSN Type Ib/Ic sub-class, although the image 2 point falls outside of the 95\% confidence region for that population.

% The right panel in Figure~\ref{fig:colormag} shows that the three data points are also consistent with the expected time-dependence  of a Type Ia SN in this color-magnitude space. Visualizing the changing color and brightness of a SNIa at $z=1.95$ in the F105W and F160W bands, we see that it  would intersect image 2 near peak brightness and approach the image 1 and 3 photometry at roughly 80 observer-frame days after peak.

% Taken together, this evidence reinforces the conclusion that \SNABC is most likely a Type Ia SN.  Although we have to adopt a magnification correction 
% from a lens model, this conclusion is not sensitive to the choice of lens model.  Every lens model we have evaluated locates \SNABC's un-magnified position squarely within the Type Ia region of color-magnitude space.  
% Dust is also not a confounding factor here.  The simulations used to generate the contours in Figure~\ref{fig:colormag} include dust extinction at the source plane.  If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC requiem points upward and leftward on this plot, causing it to be even more strongly associated with the Type Ia region.

% \SR{TODO: add an appendix explaining the sims}

\outline{
Multiple lensed transient or varying sources can be used to constrain cosmology, through timedelay measurements.  Many quasars lensed by galaxies known, provide some of the most accurate measurements of H0.  Possibly in dissagremment with CMB }
\newline
\newline
\outline{
Refsdal proposed multiple lensed SN as means of constraining cosmology. A few have been observed (list), most famously the Refsdal SN, a Type II at z=1.5 lensed by a cluster, missed one image, observed 2 and predicted a fourth that was later observed
}\newline
\newline
\outline{
Requiem is a hubble project that target rare examples of quiescent galaxies, that have been magnified by gravitational lensing. These are typically too faint and compact to be resolved even with Hubble, but due to lensing are magnified. This provides a unique opportunity to  understand the still mysterious quenching mechnism. 
The brightest and most spectacular target of REQUIEM, first discovered by Newman in 2016 is RGM0138, is a z=2.X, logM=XX quiescent galaxy quadruply lensed by a cluster at z=0.X. The galaxy has very low SFR=XX and based on stellar ages stopped forming stars ~X.X Gyr earlier. This is a proto typical early type galaxy progenitor.
}
\newline
\newline
\outline{
During analysis of the REQUIEM observations obtained  July 2019 we discovered a new pointsource close to three of the four images, which was not there in the original Hubble images taken in July 2016 (PI Newman), when the system was first discovered (Fig \ref{fig:layout}). 
}
\newline
\newline

\outline{
\todo[inline]{JP: I'll fill this in from the old text, then SR and/or KO work on this classification section} The SN has different colors and brightness in the three observed images. This is expected as SN evolve in brightness and color with time, and the three images represent different times on the supernova light curve, due to the different time delays of the different images. Fig \ref{fig:class} shows the colors and magnitudes expected for different types of SN lightcurves. The observations classify the explosion as a Type Ia, when the magnifications from the lensing model is taken into account. This is consistent with the host galaxy being an evolved early type (void of O and B stars). Using the absolute magnitude, $M_K$, and color, $B-K$, of the host, there is about 75 percent probability that the object is of type Ia (citation to https://arxiv.org/pdf/1309.2630.pdf).
}
\newline
\newline
\outline{
\todo[inline]{JP: Need Johan to fill in this section, or give details for us to fill it in} The lensing model is derived using the lenstool software, constrained by XX spectroscopically confirmed lensed images, and scaling relation for the cluster galaxies, as well as local pertubers .... (johan)
}
\newline
\newline
\outline{
\todo[inline]{JP: I'll fill this in + Johan lens model stuff, this will include time delay/magnification constraints from SNTD} In addition to the relative magnifications of the individual images, the lensing model predicts relative timdelays between the images. These are are XXX in a greement with the observed colors evolution in Fig 2 providing confidence in the accuracy of the lensing model. The lensing model predicts that the SN should appear in the fourth image in 20XX+/-X., with a magnification of X. A fifth image will also appear in 20XX+/- but this will be demagnified and likely not observable.
}
\newline
\newline
\outline{
This is the second highest redshift SNIa, it is the first one that where we observe it from the appearance of the first image to the last (Refsdal had an image that appeared Xyears before it was first dicovered), and it it the one with the longest (predicted) timedelay.  Add here other properties that make the system unique.
}
\newline
\newline
\outline{
\todo[inline]{JP: Can edit time delay/cosmo section} Due to the long timedelay baseline, the sensitivity to cosmology is exceptional, and the precision with which cosmological parameters can be constrained is limited only by the precision of the lensing model. Assuming that H0 is determined from other methods when the fourth image appears in 20XX Fig 3 shows that this single system will have provide comparable (and complementary) constraints as those expectede from tens of lensed supernova in planned LSST and WFIRST cosmological surveys. At that time JWST will likely be in the past but we will have E-ELT, and XXX.. which will allow for cool science such as...
}

The color of a SNIa evolves substantially over its lifetime as the photosphere expands and cools, revealing different layers of the expanding shell and driving episodes of recombination \cite{woosley_type_2007,kasen_type_2009}. Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model.\todo{add a lens-model-independent precision statement?}  Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table 1. 
Remarkably, the ages of image 1 and 3 are constrained to better than $\pm$20 days, despite having only a single epoch of photometric data.   These uncertainties may be 
further reduced when the future fourth image is observed with high-precision, multi-epoch photometry.  Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images.
%These constraints represent an upper limit on the age (and therefore time delay) uncertainties, but they would still deliver an uncertainty of $\sim0.3\%$ on the predicted $\sim6000$ day delay. While already dwarfed by the expected lens model uncertainty, constraints on the intrinsic SN light curve parameters gained from exquisite photometry of the future fourth image of Requiem could improve this even further.

Future large scale surveys such as the Vera C. Rubin Observatory 
%Legacy Survey of Space and Time (LSST) 
and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their duration \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}. However, many of these lensed SN will require follow-up resources and all will have significantly shorter delays (and therefore higher relative uncertainties) than SN Requiem. In Figure \ref{fig:cosmo} we imagine a scenario in which scarce follow-up resources could be used to observe $\sim5$ objects. We compare the cosmological constraints obtainable from small samples of SN representative of those expected from the Rubin Observatory and the Roman Space Telescope, with ``Requiem-Like'' SN.

Because of the unusually large ratio of source to lens redshift, the constraints on dark energy equation of state parameters ($w_0$, $w_a$) from the Requiem-like sample are nicely complementary to the samples accessible to the wide-area Rubin Observatory and Roman Space Telescope surveys. The extraordinarily long time delays of cluster-lensed SNe like SN Requiem also deliver significantly better time delay precision, with comparable observational cost.  
Such a sample could be developed with regular monitoring of cluster-scale lenses.  As SN Requiem has shown, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.

% Your references go at the end of the main text, and before the
% figures.  For this document we've used BibTeX, the .bib file
% scibib.bib, and the .bst file Science.bst.  The package scicite.sty
% was included to format the reference numbers according to *Science*
% style.

%BibTeX users: After compilation, comment out the following two lines and paste in
% the generated .bbl file. 
\clearpage
\begin{figure*}
    \centering
    \includegraphics[width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
    \caption{Overview of the field around the center of the MACSJ0138 cluster field and the locations of the lensed host (H1--4) and \SNABC (SN1--3) images. The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.  Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.  The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.  All panels use the late-epoch F125W imaging for the green channel.  Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion.}

    \label{fig:layout}
\end{figure*}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
    \caption{Classification information for \SNABC based on its position in color-magnitude space. (left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).  These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.  Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time. Open markers show the observed photometry of the SN. Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.  (right) The evolution of a Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.  White diamonds correspond to the times labeled on the colorbar at right. An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6/#/}{https://plot.ly/~jpierel/6/#/}
    \label{fig:class}
    }
\end{figure}

\clearpage
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../Figures/snrequiem_hw_w0wa_apples_to_lsst_ngrst.pdf}
    \caption{ \todo[inline]{replace caption for new figure}The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$). Contours show the 1$\sigma$ confidence region for a typical sample of lensed SNIa time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta), which is shown for assumed uncertainties on the lens potential of 5\% and 2\%. Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation. In order to isolate the $w_0, w_a$ dependence, all contours are constructed assuming perfect knowledge of $H_0$, $\Omega_{m,0}$ and $\Omega_{\rm de,0}$.  SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$). This single SN could deliver constraints on dark energy equation of state parameters comparable to several dozen SNe with shorter and less precise  time delays.}
    \label{fig:cosmo}
\end{figure}

\clearpage

\begin{table}
\centering
\begin{tabular}{crr|rrrr}
    \multicolumn{1}{c}{}&
    \multicolumn{2}{c}{\textbf{Photometry}}&\multicolumn{2}{c}{\textbf{Lens Model}}\\
    %\multicolumn{1}{c}{}&\multicolumn{1}{c}{}\\
    \multicolumn{1}{c}{\textbf{Image}} &\multicolumn{1}{c}{\textbf{Age}} &\multicolumn{1}{c}{$\mathbf{t_i-t_2}$}&\multicolumn{1}{c}{$\mathbf{\mu}$}
    &\multicolumn{1}{c}{$\mathbf{t_i-t_2}$}\\

\midrule

\textit{1}  &$79.10^{+45.56}_{-11.76}$&$91.31^{+62.49}_{-23.36}$ &8.942&103.6\\
\textit{2} & $-16.67^{+19.14}_{-13.10}$&-- \ \ \ \ \ \ \ \ \  & 18.48&-- \ \ \ \ \\
\textit{3} &$80.46^{+20.10}_{-9.84}$&$92.60^{+37.28}_{-21.76}$ & 13.257&153.8\\
\textit{4} &-- \ \ \ \ \ \ \ \ \ &-- \ \ \ \ \ \ \ \ \ &1.137&5980.4\\

\end{tabular}
\caption{\label{tab:time_delays}Time Delays}
\end{table}

\bibliography{references}

\bibliographystyle{Science}

\section*{Acknowledgments}

The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No. 140.

%Here you should list the contents of your Supplementary Materials -- below is an example. 
%You should include a list of Supplementary figures, Tables, and any references that appear only in the SM. 
%Note that the reference numbering continues from the main text to the SM.
% In the example below, Refs. 4-10 were cited only in the SM.

\clearpage
\section*{Supplementary materials}
Materials and Methods\\
Supplementary Text\\
Figs. S1 to S10\\
Tables S1 to S2\\
References \textit{(4-10)}
\clearpage
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
% For your review copy (i.e., the file you initially send in for
% evaluation), you can use the {figure} environment and the
% \includegraphics command to stream your figures into the text, placing
% all figures at the end.  For the final, revised manuscript for
% acceptance and production, however, PostScript or other graphics
% should not be streamed into your compliled file.  Instead, set
% captions as simple paragraphs (with a \noindent tag), setting them
% off from the rest of the text with a \clearpage as shown  below, and
% submit figures as separate files according to the Art Department's
% instructions.

\section*{Materials and Methods}
%\todo[inline]{I'm not really sure what this section is for, or if we need it (commented out is the description from science about what this should be)}
% The materials and methods section should provide sufficient information to allow replication of the study. It should be cited at relevant points in the text using a citation number that refers to a note in the reference list that reads “Materials and methods are available as supplementary materials at the Science website.” Study design should be described in detail and descriptions of reagents and equipment should facilitate replication (for example source and purity of reagents should be specified, there should be evidence that antibodies have been validated, and cell lines should be authenticated). Clinical and preclinical studies should include a section titled Experimental Design at the beginning of materials and methods in which the objectives and design of the study, as well as prespecified components, are described. Statistical methods must be described with enough detail to enable a knowledgeable reader with access to the original data to verify the results. The values for N, P, and the specific statistical test performed for each experiment should be included in the appropriate figure legend or main text.  Please see our editorial policies for additional guidelines for specific types of studies as well as further details on reporting of statistical analysis. For papers in the life sciences that involve a method that would benefit from the publication of a step-by-step protocol, we encourage authors to consider submitting a detailed protocol to our collaborative partner Bio-protocol.

\subsection*{Observations of the SN and Lensing System}

The observations of MRG0138 used in this work are  summarized in Table \ref{tab:observations}.   For this work, all HST observations were processed using the {\tt Drizzlepac} software utilities \cite{gonzaga_drizzlepac_2012}, aligned to a common astrometric reference frame and resampled to a pixel scale of 0.1 arcseconds per pixel.  We then identified isolated and unsaturated stars in each image and used them to create an effective point spread function (ePSF) with $4\times$ oversampling, using the {\tt photutils} package from the {\tt astropy} software suite \cite{astropy_citation_needed}.   To measure the SN photometry we followed two tracks.  As our primary method we performed ePSF-fitting directly on the F105W and F160W images where the SN was apparent.  This ePSF fitting allowed for a fixed background flux to account for both the sky brightness and the background light of the cluster and host galaxy.  
As a second approach, we created ``pseudo-difference images'' by rescaling the later F110W and F140W images collected in 2019 (in which the SN is not present).  The transmission functions of the F110W and F140W filters are broader than F105W and F160W, and do not strictly overlap in wavelength.  The optimal scaling factor to produce a clean subtraction therefore depends on the spectral energy distribution of the source.  We set the scaling to 0.62 and 1.17 for F110W-to-F105W and F140W-to-F160W, respectively.  These values produced visually clean subtractions of the SN host galaxy MRG0138---meaning that they minimize the residual flux from MRG0138 left behind in the pseudo-difference images.  We then performed ePSF fitting on the SN in each pseudo-difference image, using the same ePSF model as before.   Both sets of photometry agree to within one standard deviation.  The reported photometry in Table~\ref{tab:photometry} are the first  measurements, collected directly from the unsubtracted images.

\begin{table}[h]
\centering
\begin{tabular}{ccccccr}
    \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{Observation Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp. Time (s)}\\

\midrule
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 212 \\ % AOR r58785536
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 241 \\
\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 57542.9102 &   & 5214 \\
\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 57587.9686 & + & 1611 \\
\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 57588.0304 & + & 3611 \\ 
\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 468 \\ % AOR r58289152
\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 581 \\
\midrule
\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 58677.8703 &   & 706 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 58678.9278 &   & 353 \\ 
\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 58683.8941 &   & 706 \\ 
\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 58685.7853 &   & 912 \\ 
\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 58685.7924 &   & 1272 \\ 
\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 58685.9461 &   & 353 \\ 
\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 &   & 2649  \\
\end{tabular}
\caption{Record of MACSJ0138 observations used in this work.  
The two observations from which three images of the SN were detected are marked with a '+' in column six.
\label{tab:observations}
}
\caption{}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{ccc}
Obs. Date (MJD) & Filter & Flux density ($\mu$Jy) \\
\midrule
57588.03 & F105W & 0.09  $\pm$ 0.02 \\
57588.03 & F105W & 2.35  $\pm$ 0.02 \\
57588.03 & F105W & 0.18  $\pm$ 0.02 \\
57587.97 & F160W & 0.61  $\pm$ 0.04 \\
57587.97 & F160W & 3.57  $\pm$ 0.05 \\
57587.97 & F160W & 1.13  $\pm$ 0.04 \\
\end{tabular}
\caption{Photometry of the SN in MRG0138.
\label{tab:photometry}}
\end{table}

\subsection{VLT Spectroscopy}
\label{sec:vltmuse}

We make use of integral field spectroscopic data obtained on the cluster core of MRG0138 with VLT/MUSE, publicly 
available as part of the program 0103.A-0777(A) (PI: Edge). Three exposures of 970 sec each were taken with a small dithering offset and 90 degree rotations in between. This dataset was reduced and analysed using the MUSE data reduction pipeline v.2.7 (\cite{}) for basic calibration (bias, flat-field, wavelength, LSF, geometry) as well as flux calibration, sky subtraction and astrometry. We  also make use of the self-calibration technique \cite{bacon_muse_2017}  to remove illumination systematics, specifically tuned for the case of crowded fields in the central region of galaxy clusters (Richard et al. in prep.). The combined datacube is then processed through {\tt ZAP} \cite{soto_zap_2016} which applies a PCA technique to remove sky subtraction residuals. The final datacube covers the central 1x1 arcmin$^2$ around the cluster center with 0.2\arcsec$\times$0.2\arcsec$\times$1.25\AA\ pixels.

We have extracted spectra for each HST detected source and inspected them for redshift measurements. In addition, we have run the {\tt muselet} software (publicly available as part of the MPDAF package \cite{piqueras_mpdaf_2019}\footnote{\url{https://mpdaf.readthedocs.io/en/latest/muselet.html}}) to search for line emitters not directly associated with HST sources (see also Mahler et al. 2018, Lagattuta et al. 2019). Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.776$.

\subsection*{Lens Modeling}
%\todo[inline]{Fill in details of lens models here.}

In order to correctly estimate the magnification factors, time delays, and predict the appearance of the future images of MRG0138-SN we need to precisely model the mass distribution in the MRG0138 cluster core. To do so we make use of the latest version of Lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and error on each parameter of the mass distribution.

The strong-lensing constraints used are the locations of multiple images found in HST and MUSE/VLT. More specifically we group them into 3 systems: (1) the 4 images of the quiescent galaxy hosting MRG0138-SN, (2) the 3 observed images of MRG0138-SN assumed at the same redshift, and (3) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see Sect.~\ref{sec:vltmuse}). The locations and redshifts used in the lens model are summarised in Table \ref{tab:mulimages}.

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c}
     ID &   R.A. & Dec. & $z$ \\
1.1 & 24.50990183 & -21.92601304 & 1.95 \\
1.2 & 24.51320906 & -21.92990322 & 1.95 \\
1.3 & 24.51641380 & -21.93031720 & 1.95 \\
1.4 & 24.51761179 & -21.92334337 & 1.95 \\
2.1 & 24.51007534 & -21.92734181 & 1.95 \\
2.2 & 24.51231984 & -21.92978758 & 1.95 \\
2.3 & 24.51512533 & -21.93066599 & 1.95 \\
3.1 & 24.5169659 & -21.9234814 & 0.7663 \\
3.2 & 24.5161061 & -21.9231225 & 0.7663 \\
3.3 & 24.5184361 & -21.9264250 & 0.7663 \\
3.4 & 24.5146833 & -21.9261020 & 0.7663 \\
    \end{tabular}
    \caption{Multiple images used as constraints in our parametric model. From left to right: image ID, right ascension, declination, spectroscopic redshift}
    \label{tab:mulimages}
\end{table}

The cluster mass modelling is performed similarly to other massive strong lensing clusters observed with HST \cite{richard_mass_2014}. In summary, the total mass distribution is parametrised as a combination of multiple dPIE (double Pseudo Isothermal Elliptical) profiles describing both cluster-scale and galaxy-scale dark matter haloes. dPIE are elliptical isothermal profiles with both a core and a cut radius where the density flattens and drops respectively. In the case of MRG0138 the mass distribution is dominated by a single mass concentration centered on its Brightest Cluster Galaxy (BCG), therefore we use a single cluster-scale halo at a fixed cut radius of 1 Mpc. We add multiple galaxy-scale haloes on cluster members where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15 kpc). Cluster members were identified by the combination of red sequence selection (based on the F814W-F160W color) and MUSE spectroscopy.

The majority of cluster members are elliptical galaxies selected from the red sequence, and to reduce the number of parameters we assume they follow the scaling relations: $\sigma=\sigma^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/4)}$ for the velocity dispersion, and $r_{\rm cut}=r_{\rm cut}^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/2)}$, assuming the Faber-Jackson relation and a constant M/L ratio respectively. $\sigma^*$ and $r_\rm{cut}^*$ are model parameters for a cluster member at the characteristic luminosity $L^*$, following the discussion in \cite{richard_locuss_2010} we fix $\sigma^*=158$ km/s and $r_{\rm cut}^*$=45 kpc.

We individually optimise the $\sigma$ and $r_{\rm cut}$ parameters for 4 specific galaxies which are not expected to follow the abovementioned scaling relations: the BCG and three pertubators P1 to P3. These pertubators are either blue gas-stripped galaxies infalling into the cluster core, and/or located very close to the images of the quiescent galaxy, perturbing its morphology. This choice of perturbators is similar to the ones used in the model by \cite{newman_resolving_2018}.

Lenstool optimises the parameters of the model by minimising the overall rms between the predicted and observed locations of the multiple images. The best fit parameters of each mass components are provided in Table~\ref{tab:massmodel}. The error bars are derived from the MCMC models sampling their posterior probability distribution.

The best model reproduces all multiple systems with an rms of 0.15\arcsec. We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs. This model is then used to predict the magnification and time delays for the 3 observed images of MRG0138-SN, as well as the location of the two additional images which are still to appear. As the lens model reproduces the location of the supernova images within a small uncertainty, these predictions are computed with Lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position. We summarise these predictions in Table \ref{tab:snpred}.

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c|c|c|c|c|c|}
    Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpcs] & [kpc] \\
\hline
Cluster-DM & $ -0.7^{+  0.4}_{ -0.4}$ & $ -1.2^{+  0.4}_{ -0.4}$ & $ 0.81^{+ 0.02}_{-0.13}$ & $114.9^{+  2.0}_{ -4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
\hline
    \end{tabular}
    \caption{Best fit model parameters for the mass distribution. From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius.}
    \label{tab:massmodel}
\end{table}

\begin{table}[]
    \centering
    \begin{tabular}{c|c|c}
    Image     & $\alpha$ & $\delta$ & $\mu$ & $\Delta T$ \\
    & & [days] \\
\hline 
SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
SN.2 & & & 7.381$\pm$3.044 & 101.4 \\
SN.3 & & & 5.020$\pm$1.217 &  19.3 \\
SN.4 & & & 0.377$\pm$0.187 & 7761.0 \\
SN.5 & & & & \\
\hline 
\end{tabular}
    \caption{Magnification and time delays estimated at the location of each supernova image.}
    \label{tab:snpred}
\end{table}

\section*{Supplementary Text}

\subsection*{SN Classification from Photometry}
The lens modeled time delays between the images are $\sim100$ observer-frame days, 
but we see that three images of the transient are visible simultaneously.
From this we can infer that the visibility time of the transient in the $z=1.95$ rest-frame must be at least $\sim$30 days. 
Similarly, with expected magnifications in the vicinity of $\mu\sim10$, the measured apparent magnitudes near 23 AB mag translate to a rest-frame absolute magnitude near $M_B \sim-19.5$ mag (too bright to be a nova, luminous blue variable, or other low-luminosity stellar transient).
Taken together, these indicators strongly suggest that the transient is a supernova (SN).

Although we have invoked the lens model in this analysis, note that the inferences are not strongly dependent on the specific lens model predictions.  To make the observed transient images consistent with a fast or low-luminosity transient, the time delays and/or magnifications would have to be changed by more than a factor of 2.  In the analysis to follow, we will work under the assumption that the transient is a SN.

\todo[inline]{Do we want another figure here? We can't really effectively reference main text figures in the supp. materials}
The observed photometry for SN Requiem is fully consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~S2.  The magnification-corrected photometry is inconsistent with Type II SNe, which are fainter and more blue. SN Requiem is marginally consistent with the CCSN Type Ib/Ic sub-class, although the image 2 point falls outside of the 95\% confidence region for that population. The three SN Requiem data points are also consistent with the expected time-dependence  of a Type Ia SN in color-magnitude space. Visualizing the changing color and brightness of a SNIa at $z=1.95$ in the F105W and F160W bands, we see that it  would intersect image 2 near peak brightness and approach the image 1 and 3 photometry at roughly 80 observer-frame days after peak (see main text Fig \ref{fig:class}).  
\missingfigure[]{Something showing more about classification process/results.\label{fig:quant_class}}
Taken together, this evidence reinforces the conclusion that SN Requiem is most likely a Type Ia SN.  Although we have to adopt a magnification correction 
from a lens model, this conclusion is not sensitive to the choices we can reasonably make for modeling the lens.  Every  {\tt LensTool} model we have evaluated locates Requiem's de-magnified position squarely within the Type Ia region of color-magnitude space. Dust is also not a confounding factor here. 
\todo[inline]{Reference whatever figure ends up here correctly in this section}
The simulations used to generate the contours in Fig \ref{fig:quant_class} include dust extinction at the source plane.  If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC requiem points upward and leftward on this plot, causing it to be even more strongly associated with the Type Ia region.

\subsection*{Classification Based on Host Galaxy}
Once this transient was identified as a SN (tentatively Ia), we  seek to use only measured properties of the host galaxy stellar population to {\it circumstantially} infer the type. This inference is fully independent of lens model, helping to reduce any bias associated with a lens model-dependent classification.

Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.  We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \cite{mannucci_rates_2005,foley_classifying_2013}.  In the case of the host galaxy MRG0138, we have very stringent limits on the star formation rate. This galaxy is a high-mass but very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.  The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr (\textcolor{red}{citation?}),  making it highly unlikely that MRG0138 retains any significant population of massive stars. To derive a quantitative classification probability, we used the host galaxy's rest-frame $B-K$ color and absolute magnitude, $M_K$, which serve as proxies for the stellar population age and have been empirically calibrated with SN rates in the local universe  \cite{foley_classifying_2013}.  This 
results in a $75\%$ probability that Requiem is Type Ia.
\todo[inline]{Anything more quantitative/technical to say here? Any figures?}

\subsection*{Light Curve Age Constraints}
We constrain the relative time delays of SN Requiem by using two separate methods to estimate the age of the SN at each image during the single observed epoch. The preferred method of SN time delay measurements involves measuring the time of peak brightness for the SN at each image by fitting the light curves, and taking the difference between each measurement as the relative time delay \cite{pierel_turning_2019,dhawan_magnification_2019,huber_strongly_2019}. With only a single observed epoch, this method is impossible due to model parameter degeneracies, and we must rely on color and brightness to constrain the age of each image of the SN. Each of these images stems from the same SN explosion, so the difference between the measured age of each image is also a measure of the relative time delay.

We first attempt to constrain the relative time delays using the color of each observed image, which is independent of the lens model and possible because the scenario of gravitation lensing is generally achromatic. One important caveat to this principle is that {\it microlensing} effects are not generally achromatic, because the microlensing caustics may cause differential magnification on the scale of the SN radius \cite{goldstein_precise_2018,foxley-marrable_impact_2018,bonvin_impact_2019}.  Hence, if the expanding SN shell has a color gradient then microlensing may introduce spurious features in the observed colors of the SN \cite{kochanek_quantitative_2004,vernardos_joint_2018}.   Goldstein et al. \cite{goldstein_precise_2018} found that such chromatic microlensing is most likely not present for lensed Type Ia SNe in the period up to about 25 rest-frame days after explosion ($\sim$15 observer days after peak brightness for \SNABC). Only image 2 is likely in the achromatic microlensing phase, but Goldstein et al. \cite{goldstein_precise_2018} found extremely small deviations in the rest-frame $U-V$ color curve due to microlensing at the 68\% confidence interval, and up to a $\sim0.2-0.4$ mag difference with 99\% confidence. While such extreme microlensing could alter the results for images 1 and 3, it would not alter the measurement of image 2 as it is likely in the achromatic phase.

We use version 2 of the SuperNova Time Delays (SNTD) package\footnote{Link to version 2}, which has several improvements over the original SNTD package \cite{pierel_turning_2019}. The SNTD package employs a nested sampling algorithm within three separate methods to measure time delays, and is designed to fully utilize the information present in SN light curve templates \cite{hsiao_k_2007,guy_salt2:_2007,kessler_results_2010,pierel_extending_2018} to reduce the impacts of microlensing and make more accurate measurements.

We first obtain a constraint on the time delay from the SN color (F110W-F160W) at each image, which is completely independent from the lens model and relatively insensitive to microlensing. We use the "color" method present in SNTD, which attempts to reconstruct the intrinsic color curve using the SALT2 model as a template \cite{guy_salt2:_2007}. This method fits the age of each image simultaneously, while also varying the SN model parameters. Joint and marginalized posterior distributions
from SNTD for SALT2 parameters and measured ages for each image are shown in Fig \ref{fig:corner_cfit}. The result of this process is seen in Figs \ref{fig:colorcurve1}-\ref{fig:colorcurve3}. The measured colors intersect the model at two distinct locations for image 2 of Requiem, meaning there are two plausible ages that cause a double peaked posterior distribution (Fig \ref{fig:corner_cfit}). This is caused by a model parameter degeneracy that could be broken in a way independent of lens model if a sufficiently precise light curve of image 4 is obtained in the future.

To help break the age degeneracies in the color-based constraints without this precise photometry, we need to use some information about the relative brightnesses of the SN Requiem images.  For this step we can no longer be independent of the lens models, as we must use the lens-model-predicted magnification values to de-magnify the observed magnitudes for comparison to SN models.

For the four lens models described above, we correct the observed magnitude of each image using the predicted lensing magnification ($\mu$). Next we employ SNTD's "series" method, as it is most effective for sparse sampling, to attempt a reconstruction of the intrinsic SN light curve \cite{pierel_turning_2019}. Once again the age of each image is constrained simultaneously, while also varying the SN model parameters. At this stage we adopt priors on the intrinsic SNIa luminosity \cite{rodney_type_2014} and SNIa color \cite{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Figs \ref{fig:lightcurve1}-\ref{fig:lightcurve3}).

After repeating this process for each of the four lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}). We find significant preference for models E and F over models C and D (at $\gtrsim15\sigma$), and some preference for model E over model F (at $\sim2.8\sigma$). We therefore adopt model E as our preferred model, and use the model E light curve constraints (Fig \ref{fig:corner_modelE}) to obtain joint posterior distributions with the lens-independent result from color-curve fitting (Figure \ref{fig:corner_combined}).

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image2.pdf}
    \caption{Light-curve-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:lightcurves}. The upper panel shows the posterior distributions from SNTD for the age of image 2 from section \ref{s:colorcurves} (magenta), section \ref{s:lightcurves} (light blue), and the combination of both methods (orange). The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 light curve, with the median model shown as a solid line. The orange shaded region shows the 1$\sigma$ range of the measured (lens-model-corrected, see table \ref{tab:time_delays}) F160W magnitude, which corresponds to a V band magnitude in the rest-frame. }
    \label{fig:lightcurve2}
\end{figure}

\begin{table}[h]
\begin{tabular}{crrrrrrr}

    \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
\midrule
\textit{C} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-15.18\pm0.33$ \\
\textit{D} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-13.46\pm0.31$ \\
\textit{E} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-8.91\pm0.27$ \\
\textit{F} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-9.67\pm0.28$ \\
\end{tabular}
\caption{\label{tab:model_evidence}Model Preferences}
\end{table}

\subsection*{Final Inferred Time Delays}

As discussed at the end of the previous section, our final age constraints for each SN image are a joint posterior between the parameter estimates from color-curve fitting (lens model independent) and light curve fitting (lens model dependent). We use image 2 as the reference image because of its likely insensitivity to chromatic microlensing,  resulting in the final time delays and uncertainties reported in table \ref{tab:time_delays} of the main text. Using these measured time delays, we can create a reconstructed form of the intrinsic light curve (Fig \ref{fig:full_lightcurve}) and color curve (Fig \ref{fig:full_colorcurve}) of SN Requiem.

The final posterior distribution for image 2 is bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for SN Requiem (Fig \ref{fig:corner_combined}). If this degeneracy can be broken with the exquisite photometry expected for the final image of Requiem, then the expected age of image 2 becomes $-31.51^{+2.23}_{-2.01}$, producing a time delay uncertainty for image 4 of $\sim0.04\%$.

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image1.pdf}
    \caption{Color-based age constraints for \SNABC image 1 and image 3, as in Fig~\ref{fig:colorcurve2}.}
    \label{fig:colorcurve1}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image3.pdf}
    \caption{Color-based age constraints for \SNABC image 1 and image 3, as in Fig~\ref{fig:colorcurve2}.}
    \label{fig:colorcurve3}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image1.pdf}
    \caption{Light-curve-based age constraints for \SNABC images 1 and 3.}
    \label{fig:lightcurve1}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image3.pdf}
    \caption{Light-curve-based age constraints for \SNABC images 1 and 3.}
    \label{fig:lightcurve3}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/corner_color_curve_fit_with_c_prior.pdf}
    \caption{Corner plot for color curve nested sampling with prior on c.}
    \label{fig:corner_cfit}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/corner_model_E.pdf}
    \caption{Corner plot for light curve nested sampling using model E.}
    \label{fig:corner_modelE}
\end{figure*}
\begin{figure*}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/corner_combined_lc_color_model_E.pdf}
    \caption{Corner plot for combined color curve and model E light curve nested sampling.}
    \label{fig:corner_combined}
\end{figure*}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{Paper/Figures/full_lightcurve_full.pdf}
    \caption{\label{fig:full_lightcurve}}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\textwidth]{Paper/Figures/full_colorcurve_total.pdf}
    \caption{\label{fig:full_colorcurve}}
\end{figure}
\clearpage
\section*{References}
\end{document}

### 2020-06-17 Paper/unused/main_backup.tex
Updates from Overleaf

--- 2020-03-28 Paper/Nature/main.tex
@@
 
-\title{Three magnified views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
+\title{96 ch. Three magnified views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
 
@@
 %One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline
-The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe\footnote{Penzias \& Wilson 1965, ApJL, 142, 419}. 
+125W: The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe\footnote{Penzias \& Wilson 1965, ApJL, 142, 419}.
 %Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
@@
 
-% \section*{Introduction}
+\section*{10 paragraphs - (total 2500 words including references, notes and captions}
+SN1a play a special role in cosmology, they are standard candles -> led to discovery of DE. High redshift SN-1a provide particularly strong constraints.
+\newline
+\newline
+Multiple lensed transient or varying sources can be used to constrain cosmology, through timedelay measurements.
+Many quasars lensed by galaxies known, provide some of the most accurate measurements of H0.
+Possibly in dissagremment with CMB
+\newline
+\newline
+Refsdal proposed multiple lensed SN as means of constraining cosmology.
+A few have been observed (list), most famously the Refsdal SN, a Type II at z=1.5 lensed by a cluster, missed one image, observed 2 and predicted a fourth that was later observed
+\newline
+\newline
+Requiem is a hubble project that target rare examples of quiescent galaxies, that have been magnified by gravitational lensing.
+These are typically too faint and compact to be resolved even with Hubble, but due to lensing are magnified.
+This provides a unique opportunity to  understand the still mysterious quenching mechnism.
+The brightest and most spectacular target of REQUIEM, first discovered by Newman in 2016 is RGM0138, is a z=2.X, logM=XX quiescent galaxy quadruply lensed by a cluster at z=0.X.
+The galaxy has very low SFR=XX and based on stellar ages stopped forming stars ~X.X Gyr earlier.
+This is a proto typical early type galaxy progenitor.
+\newline
+\newline
+During analysis of the REQUIEM observations obtained  July 2019 we discovered a new pointsource close to three of the four images, which was not there in the original Hubble images taken in July 2016 (PI Newman), when the system was first discovered (Fig 1).
+\newline
+\newline
+
+The SN has different colors and brightness in the three observed images.
+This is expected as SN evolve in brightness and color with time, and the three images represent different times on the supernova light curve, due to the different time delays of the different images.
+Fig 2 shows the colors and magnitudes expected for different types of SN lightcurves.
+The observations classify the explosion as a Type Ia, when the magnifications from the lensing model is taken into account.
+This is consistent with the host galaxy being an evolved early type (void of O and B stars)
+\newline
+\newline
+The lensing model is derived using the lenstool software, constrained by XX spectroscopically confirmed lensed images, and scaling relation for the cluster galaxies, as well as local pertubers ....
+(johan)
+\newline
+\newline
+In addition to the relative magnifications of the individual images, the lensing model predicts relative timdelays between the images.
+These are are XXX in a greement with the observed colors evolution in Fig 2 providing confidence in the accuracy of the lensing model.
+The lensing model predicts that the SN should appear in the fourth image in 20XX+/-X., with a magnification of X.
+A fifth image will also appear in 20XX+/- but this will be demagnified and likely not observable.
+\newline
+\newline
+This is the second highest redshift SNIa, it is the first one that where we observe it from the appearance of the first image to the last (Refsdal had an image that appeared Xyears before it was first dicovered), and it it the one with the longest (predicted) timedelay.
+Add here other properties that make the system unique.
+\newline
+\newline
+Due to the long timedelay baseline, the sensitivity to cosmology is exceptional, and the precision with which cosmological parameters can be constrained is limited only by the precision of the lensing model.
+Assuming that H0 is determined from other methods when the fourth image appears in 20XX Fig 3 shows that this single system will have provide comparable (and complementary) constraints as those expectede from tens of lensed supernova in planned LSST and WFIRST cosmological surveys.
+At that time JWST will likely be in the past but we will have E-ELT, and XXX..
+which will allow for cool science such as...
 

### 2020-06-17 Paper/unused/main_old.tex
Updates from Overleaf

--- 2020-06-17 Paper/unused/main_backup.tex
@@
 
-\input{Paper/preamble}
+\usepackage{xspace}
+\usepackage{multirow}
+\usepackage[numbers]{natbib}
+\usepackage[colorinlistoftodos,textwidth=1.4in,textsize=small]{todonotes}
 
-\title{96 ch. Three magnified views of a supernova explosion 10 billion years ago, and a fourth that will reveal the nature of cosmological dark energy}
+% 96 characters including spaces
+\title{(Requiem for a supernova 10 billion years ago, which in 2030 will reveal the nature of dark energy}
 
-\author[1,*]{Gabriel Brammer}
-\author[2]{Steven Rodney}
-\author[2]{Justin Pierel}
-\author[2]{Kyle O'Connor}
-\author[3]{Johan Richard}
-\author[1]{Sune Toft}
-\author[4]{Mohammad Akhshik}
-\author[5]{Katherine Whitaker}
-\affil[1]{Cosmic Dawn Center, Niels Bohr Institute, K{\o}benhavns Universitet}
-\affil[2]{University of South Carolina}
-\affil[3]{Universit\'e Claude Bernard Lyon}
-\affil[4]{University of Connecticut}
-\affil[5]{University of Massachusetts, Amherst}
+\author[1,2,*]{Gabriel Brammer}
+\author[3]{Steven Rodney}
+\author[4]{Justin Pierel}
+\author[4]{Kyle O'Connor}
+\author[4]{Johan Richard}
+\author[1,2]{Sune Toft}
+\author[5]{Mohammad Akhshik}
+\author[6,1]{Katherine Whitaker}
+\affil[1]{Cosmic Dawn Center (DAWN)}
+\affil[2]{ Niels Bohr Institute, University of Copenhagen, Denmark}
+\affil[3]{University of South Carolina}
+\affil[5]{Universit\'e Claude Bernard Lyon}
+\affil[6]{University of Connecticut}
+\affil[6]{University of Massachusetts, Amherst}
 
@@
 %\keywords{Keyword1, Keyword2, Keyword3}
+
+%https://www.sciencemag.org/authors/instructions-preparing-initial-manuscript
+
+%a sentence giving a broad introduction to the field comprehensible to the general reader,
+
+%a sentence of more detailed background specific to your study.
+
+%an explanation of the OBJECTIVES/METHODS, and then the RESULTS
+
+%The final sentence should outline the main CONCLUSIONS of the study, in terms that will be comprehensible to all our readers
 
@@
 \end{abstract}
+
 \begin{document}
+\listoftodos
 
@@
 \section*{10 paragraphs - (total 2500 words including references, notes and captions}
-SN1a play a special role in cosmology, they are standard candles -> led to discovery of DE. High redshift SN-1a provide particularly strong constraints.
+\todo[inline]{JP: Can edit intro} SN1a play a special role in cosmology, they are standard candles -> led to discovery of DE. High redshift SN-1a provide particularly strong constraints.
 \newline
@@
 
-The SN has different colors and brightness in the three observed images.
+\todo[inline]{JP: I'll fill this in from the old text, then SR and/or KO work on this classification section} The SN has different colors and brightness in the three observed images.
 This is expected as SN evolve in brightness and color with time, and the three images represent different times on the supernova light curve, due to the different time delays of the different images.
@@
 The observations classify the explosion as a Type Ia, when the magnifications from the lensing model is taken into account.
-This is consistent with the host galaxy being an evolved early type (void of O and B stars)
+This is consistent with the host galaxy being an evolved early type (void of O and B stars).
+Using the absolute magnitude, $M_K$, and color, $B-K$, of the host, there is about 75 percent probability that the object is of type Ia (citation to https://arxiv.org/pdf/1309.2630.pdf).
 \newline
 \newline
-The lensing model is derived using the lenstool software, constrained by XX spectroscopically confirmed lensed images, and scaling relation for the cluster galaxies, as well as local pertubers ....
+\todo[inline]{JP: Need Johan to fill in this section, or give details for us to fill it in} The lensing model is derived using the lenstool software, constrained by XX spectroscopically confirmed lensed images, and scaling relation for the cluster galaxies, as well as local pertubers ....
 (johan)
@@
 \newline
-In addition to the relative magnifications of the individual images, the lensing model predicts relative timdelays between the images.
+\todo[inline]{JP: I'll fill this in + Johan lens model stuff, this will include time delay/magnification constraints from SNTD} In addition to the relative magnifications of the individual images, the lensing model predicts relative timdelays between the images.
 These are are XXX in a greement with the observed colors evolution in Fig 2 providing confidence in the accuracy of the lensing model.
@@
 \newline
-Due to the long timedelay baseline, the sensitivity to cosmology is exceptional, and the precision with which cosmological parameters can be constrained is limited only by the precision of the lensing model.
+\todo[inline]{JP: Can edit time delay/cosmo section} Due to the long timedelay baseline, the sensitivity to cosmology is exceptional, and the precision with which cosmological parameters can be constrained is limited only by the precision of the lensing model.
 Assuming that H0 is determined from other methods when the fourth image appears in 20XX Fig 3 shows that this single system will have provide comparable (and complementary) constraints as those expectede from tens of lensed supernova in planned LSST and WFIRST cosmological surveys.
@@
 % Figures and tables can be referenced in LaTeX using the ref command, e.g. Figure \ref{fig:stream} and Table \ref{tab:example}.
-
+\pagebreak
+\citep{jha_improved_2007}
+\bibliographystyle{plainnat}
+\bibliography{Paper/references}
 \end{document}

### 2020-06-17 Paper/unused/ms.tex
Updates from Overleaf

--- 2020-03-27 Paper/ms.tex
@@
 
-\correspondingauthor{Gabriel Brammer}
-\email{gabriel.brammer@nbi.ku.dk}
+\correspondingauthor{TBD}
+\email{tbd@aol.com}
 
@@
 Identifying the transient type makes it possible to use the well-developed library of spectrophotometric SN models \citep[e.g.][]{kessler_models_2019} for the time delay measurement.
- The first-order distinction that is most important is between a Type Ia SN--understood to be the explosion of a white dwarf star in a binary system--and core collapse SN (CCSN)--the end-point of a star with mass $\gtrsim 10$M$_{\odot}$.
-Given the limited data available for this transient, we will not attempt a more fine-grained classification, though in principle that could be achieved with spectroscopy and multi-band photometry upon arrival of the final image.
 

### 2020-06-22 Analysis/mrg/fig1.py
rename images 1 and 3

@@ -2,6 +2,35 @@
 Discovery figure, Fig. 1
 """
 
+def for_present():
+
+    from grizli.pipeline import auto_script
+    from mastquery import overlaps
+    import astropy.io.fits as pyfits
+    import astropy.wcs as pywcs
+    import numpy as np      
+    
+    root = 'j013804m2156'
+
+    x0, y0= 2465, 1740
+    
+    NY = 400
+    NX = 400
+
+    slx = slice(x0-NX, x0+NX)
+    sly = slice(y0-NY, y0+NY)
+    
+    mi = -0.01
+    
+    si = 4.8*NX/200
+    
+    _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.xon', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si), tickparams={'axis': 'both', 'colors': 'w', 'which': 'both', 'length':0})
+    
+    rgb_scl = np.array([1.06,1.03,1.03])/1.03
+    
+    _rgb = auto_script.field_rgb(root=root, filters=['f110w','f125w','f140w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', rgb_scl=rgb_scl, suffix='.xoff', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si), tickparams={'axis': 'both', 'colors': 'w', 'which': 'both', 'length':0})
+    
+    
 def rgb():
     
     from grizli.pipeline import auto_script
@@ -9,6 +38,8 @@ def rgb():
     import astropy.io.fits as pyfits
     import astropy.wcs as pywcs
     import numpy as np      
+    
+    from grizli import utils
     
     root = 'j013804m2156'
 
@@ -54,8 +85,8 @@ def rgb():
     from matplotlib.gridspec import GridSpec
     
     # Label offsets
-    dx = [-14, 0, 0, -8, 0, 0, 0, 0]
-    dy = [0, 8, 8, 5, 10, 10, 10]
+    dx = [-20, 10, 0, -10, 0, 0, -38]
+    dy = [0, 14, 10, 5, 10, 10, -15]
     
     fig = plt.figure(figsize=(8,3./5*8))
     gs = GridSpec(3, 5, figure=fig)

### 2020-06-22 Paper/Science/main.tex

@@
 \def\SNABC{SN Requiem\xspace}
+\def\reqlike{Requiem-like\xspace}
+\def\lenstool{{\tt LENSTOOL}\xspace}
 
@@
 %\title{Requiem for a 10 billion year old supernova } 
-\title{A Gravitationally Lensed Supernova with an Observable Decade-long Time Delay}
+\title{A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
 %\title{A Strongly Lensed Type Ia Supernova with a Decade-Long Time Delay}
@@
 
-  We report the discovery of a quadruply-lensed Type Ia supernova (SN) explosion that will produce a time delay measurement uncertainty of $<1\%$.
-This unprecedented scenario will enable a unique and highly precise measurement of the Hubble constant from a single lensed SN.
+  We report the discovery of a quadruply-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
+This unprecedented scenario will enable a rare and highly precise measurement of the Hubble constant from a single lensed SN.
 The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACSJ0138.
-With three lensed images of the supernova detected in existing observations from the \textit{Hubble Space Telescope} with time delays of order 50 days, this is the most distant multiply-imaged supernova yet discovered.
-A fourth image in the component closest to the cluster core is predicted to appear in the year 2035$\pm$2.
-Observing the light curve of that future image will provide a time delay precision of $\approx 7$ days over an extraordinary baseline of nearly 20 years.
+ This is the most distant multiply-imaged supernova yet discovered, and we find it is classified as a Type Ia with {$>90\%$} probability.
+  Three lensed images of the SN are detected in existing observations from the \textit{Hubble Space Telescope} with relative time delays of $<$200 days.
+A fourth image in the component closest to the cluster core is predicted to appear in the year 2037$\pm$2.
+Observing the light curve of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary baseline of nearly 20 years.
 
@@
 A series of recent investigations into the expansion rate of the universe (the Hubble-LeM\^aitre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background (CMB) radiation \cite{Riess_large_2019,aghanim_planck_2018}.
-Resolving this tension in $H_0$ measurements may reveal new physics from the early universe \textcolor{red}{Citation here?}, and to do so requires multiple
-independent cosmological probes.
+Resolving this tension in $H_0$ measurements may reveal new physics from the early universe, and to do so requires multiple
+independent cosmological probes \cite{verde_tensions_2019}.
 
@@
 The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_SNRefsdal_2016}.
-The second, {\it SN iPTF16geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2020}.
+The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2020}.
 Here we present the discovery
-of a third lensed SN resolved into multiple images: SN Requiem.
+of a third lensed SN resolved into multiple images: \SNABC.
 
-\todo[inline]{put in precise UT dates for HST data and double check newman proposal \href{https://archive.stsci.edu/hst/abstract.html}{(this one?)}}
-
-We discovered SN Requiem using data from the Hubble Space Telescope (HST) program {\it Resolved Quiescent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
+We discovered SN Requiem using data from the Hubble Space Telescope (HST) program {\it REsolved QUIEscent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
 This project targets rare examples of quiescent galaxies that have been magnified by strong gravitational lensing.
@@
 MRG-M0138 is quadruply lensed by the foreground cluster, which is at $z=0.338$.  
-During analysis of REQUIEM observations obtained July 2019 we discovered three point 
-sources that were present in archival HST images from July 2016, part of the program 
-that originally discovered the MRG-M0138 galaxy (HST-GO-14496; PI:Newman). 
+During analysis of REQUIEM observations obtained 13-14 July 2019 \cite{materials_methods_2020} we discovered three point 
+sources that were present in archival HST images from 18-19 July 2016, part of the program 
+that first confirmed the MRG-M0138 galaxy as a strongly-lensed object (HST-GO-14496; PI:Newman). 
 Each point source is within 5 arcseconds of one of the four MRG-M0138 images.  None of the
@@
 the point sources are multiple images of a single astrophysical 
-transient in MRG-M0138, most likely a SN. Hereafter we call this multiply-imaged transient {\it SN Requiem}.
+transient in MRG-M0138, most likely a SN. Hereafter we call this multiply-imaged transient \SNABC.
 
-To construct a lens model for the MACS J0138.0-2155 cluster we used the publicly available {\tt Lenstool} software \cite{jullo_bayesian_2007, kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster scale and multiple galaxy scale potentials.
+To construct a lens model for the MACS J0138.0-2155 cluster we used the publicly available \lenstool software \cite{jullo_bayesian_2007, kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster scale and multiple galaxy scale potentials \cite{materials_methods_2020}.
 To avoid unintended bias, we kept the lens model development completely separate from the analysis of the SN.
@@
 The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the central light peak and the SN location in each image) as well as a multiply-imaged background
-galaxy at $z=0.766$, both having secure spectroscopic redshifts.  
-From this model we derive estimates for the lensing magnification and time delay of each of the SN images, including the predicted fourth image (Tab 1).
-The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in 20XX+/-X., with a magnification of X.
-A fifth image will also appear in 20XX+/- but this will be demagnified and likely not observable.
+galaxy at $z=0.766$, both having secure spectroscopic redshifts \cite{materials_methods_2020}.  
+From this model we derive estimates for the lensing magnification and time delay of each of the SN images, including the predicted fourth image (Table \ref{tab:time_delays}).
+The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$1.5, demagnified with $\mu=0.4\pm0.2$.
+A fifth image will also appear at a later date, located very near the center of the cluster and much more significantly demagnified, so therefore likely not observable.
 
@@
 The properties of the host galaxy can inform this classification because CCSN are limited to galaxies with young stellar populations.
-Limits on the specific star formation rate and age for this host, MRG-M0138, show it to be a high-mass but very quiescent and evolved galaxy, %($\log(M_*/M_\odot)=11.7\pm0.2; )$ ,
+Limits on the specific star formation rate and age for this host, MRG-M0138, show it to be a massive but very quiescent and evolved galaxy, %($\log(M_*/M_\odot)=11.7\pm0.2; )$ ,
 unlikely to retain any significant population of high-mass stars \cite{newman_resolving_2018}.
-Based on observed properties of the host galaxy alone, we find a 75\% probability that Requiem is a Type Ia SN (see supplementary text).
-Adopting the lens model magnifications for the three observed SN images (Table S2) the position of each SN image in color-magnitude space (Fig \ref{fig:class}) provides more classification leverage, yielding p(Ia)=\textcolor{red}{XX}.
-By also including the measured time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=\textcolor{Orange}{YY} (Fig \ref{fig:class}).
+Based on observed properties of the host galaxy alone, we find a 62-75\% probability that \SNABC is a Type Ia SN \cite{materials_methods_2020}.
+Adopting the lens model magnifications for the three observed SN images (Table \ref{tab:time_delays}) the position of each SN image in color-magnitude space (Figure \ref{fig:class}) provides more classification leverage, yielding p(Ia)=95\% \cite{materials_methods_2020}.
+By also including the model-predicted time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=94\% \cite{materials_methods_2020}.
 %This is corroborated by the limited data available for the transient. In color -magnitude space it displays best agreement with the Type Ia population (Fig 1). 
@@
 
-\outline{
-Multiple lensed transient or varying sources can be used to constrain cosmology, through timedelay measurements.
-Many quasars lensed by galaxies known, provide some of the most accurate measurements of H0.
-Possibly in dissagremment with CMB }
-\newline
-\newline
-\outline{
-Refsdal proposed multiple lensed SN as means of constraining cosmology.
-A few have been observed (list), most famously the Refsdal SN, a Type II at z=1.5 lensed by a cluster, missed one image, observed 2 and predicted a fourth that was later observed
-}\newline
-\newline
-\outline{
-Requiem is a hubble project that target rare examples of quiescent galaxies, that have been magnified by gravitational lensing.
-These are typically too faint and compact to be resolved even with Hubble, but due to lensing are magnified.
-This provides a unique opportunity to  understand the still mysterious quenching mechnism.
-The brightest and most spectacular target of REQUIEM, first discovered by Newman in 2016 is RGM0138, is a z=2.X, logM=XX quiescent galaxy quadruply lensed by a cluster at z=0.X.
-The galaxy has very low SFR=XX and based on stellar ages stopped forming stars ~X.X Gyr earlier.
-This is a proto typical early type galaxy progenitor.
-}
-\newline
-\newline
-\outline{
-During analysis of the REQUIEM observations obtained  July 2019 we discovered a new pointsource close to three of the four images, which was not there in the original Hubble images taken in July 2016 (PI Newman), when the system was first discovered (Fig \ref{fig:layout}).
-}
-\newline
-\newline
-
-\outline{
-\todo[inline]{JP: I'll fill this in from the old text, then SR and/or KO work on this classification section} The SN has different colors and brightness in the three observed images.
-This is expected as SN evolve in brightness and color with time, and the three images represent different times on the supernova light curve, due to the different time delays of the different images.
-Fig \ref{fig:class} shows the colors and magnitudes expected for different types of SN lightcurves.
-The observations classify the explosion as a Type Ia, when the magnifications from the lensing model is taken into account.
-This is consistent with the host galaxy being an evolved early type (void of O and B stars).
-Using the absolute magnitude, $M_K$, and color, $B-K$, of the host, there is about 75 percent probability that the object is of type Ia (citation to https://arxiv.org/pdf/1309.2630.pdf).
-}
-\newline
-\newline
-\outline{
-\todo[inline]{JP: Need Johan to fill in this section, or give details for us to fill it in} The lensing model is derived using the lenstool software, constrained by XX spectroscopically confirmed lensed images, and scaling relation for the cluster galaxies, as well as local pertubers ....
-(johan)
-}
-\newline
-\newline
-\outline{
-\todo[inline]{JP: I'll fill this in + Johan lens model stuff, this will include time delay/magnification constraints from SNTD} In addition to the relative magnifications of the individual images, the lensing model predicts relative timdelays between the images.
-These are are XXX in a greement with the observed colors evolution in Fig 2 providing confidence in the accuracy of the lensing model.
-The lensing model predicts that the SN should appear in the fourth image in 20XX+/-X., with a magnification of X.
-A fifth image will also appear in 20XX+/- but this will be demagnified and likely not observable.
-}
-\newline
-\newline
-\outline{
-This is the second highest redshift SNIa, it is the first one that where we observe it from the appearance of the first image to the last (Refsdal had an image that appeared Xyears before it was first dicovered), and it it the one with the longest (predicted) timedelay.
-Add here other properties that make the system unique.
-}
-\newline
-\newline
-\outline{
-\todo[inline]{JP: Can edit time delay/cosmo section} Due to the long timedelay baseline, the sensitivity to cosmology is exceptional, and the precision with which cosmological parameters can be constrained is limited only by the precision of the lensing model.
-Assuming that H0 is determined from other methods when the fourth image appears in 20XX Fig 3 shows that this single system will have provide comparable (and complementary) constraints as those expectede from tens of lensed supernova in planned LSST and WFIRST cosmological surveys.
-At that time JWST will likely be in the past but we will have E-ELT, and XXX..
-which will allow for cool science such as...
-}
-
 The color of a SNIa evolves substantially over its lifetime as the photosphere expands and cools, revealing different layers of the expanding shell and driving episodes of recombination \cite{woosley_type_2007,kasen_type_2009}.
-Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model.\todo{add a lens-model-independent precision statement?}  Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table 1.
+Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model \cite{materials_methods_2020}.
+Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table \ref{tab:time_delays} \cite{materials_methods_2020}.
 Remarkably, the ages of image 1 and 3 are constrained to better than $\pm$20 days, despite having only a single epoch of photometric data.    These uncertainties may be 
 further reduced when the future fourth image is observed with high-precision, multi-epoch photometry.
-Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images.
+Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images, and break remaining parameter degeneracies (see supplemental materials).
 %These constraints represent an upper limit on the age (and therefore time delay) uncertainties, but they would still deliver an uncertainty of $\sim0.3\%$ on the predicted $\sim6000$ day delay.
@@
 
-Future large scale surveys such as the Vera C. Rubin Observatory 
+Future large-scale surveys such as the Vera C. Rubin Observatory 
 %Legacy Survey of Space and Time (LSST) 
 and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their duration \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
-However, many of these lensed SN will require follow-up resources and all will have significantly shorter delays (and therefore higher relative uncertainties) than SN Requiem.
-In Figure \ref{fig:cosmo} we imagine a scenario in which scarce follow-up resources could be used to observe $\sim5$ objects.
-We compare the cosmological constraints obtainable from small samples of SN representative of those expected from the Rubin Observatory and the Roman Space Telescope, with ``Requiem-Like'' SN.
+However, many of these lensed SN will require substantial follow-up resources to be cosmologically useful.
+Furthermore, almost all will have significantly shorter
+delays (of order 10-100 days) and therefore higher relative uncertainties than SN Requiem.  Since it is the {\it fractional} time delay uncertainty that 
+propagates through to any time delay distance measurement, the extraordinarily long time delays of cluster-lensed SNe like SN Requiem can deliver significantly better time delay precision, with comparable observational cost.
+In fact, the long time baseline of lensed SN like \SNABC effectively insures that their cosmological precision is not limited by the time delay measurement errors.
 
-Because of the unusually large ratio of source to lens redshift, the constraints on dark energy equation of state parameters ($w_0$, $w_a$) from the Requiem-like sample are nicely complementary to the samples accessible to the wide-area Rubin Observatory and Roman Space Telescope surveys.
-The extraordinarily long time delays of cluster-lensed SNe like SN Requiem also deliver significantly better time delay precision, with comparable observational cost.
-Such a sample could be developed with regular monitoring of cluster-scale lenses.
-As SN Requiem has shown, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
+In Figure \ref{fig:cosmo} we illustrate the cosmological value of time delay cosmography with objects like \SNABC  by considering a small sample of 5 ``\reqlike'' SN.
+For a comparison on equal footing, we evaluate equal-sized lensed SN samples
+that mimic those expected from the Rubin Observatory and  the Roman Space Telescope.  Differences in the 
+ratio of source to lens redshift account for the different cosmological parameter covariances, reflected in the orientations of the contours in these plots.
+Because of the unusually large redshift ratio of SN Requiem, the constraints
+%on dark energy equation of state parameters ($w_0$, $w_a$) 
+from the \reqlike sample are nicely complementary to the low-$z$ Rubin Observatory and high-$z$ Roman Space Telescope samples. 
+Furthermore, when we assume that the lens modeling uncertainty is equal for each sample (amounting to a 5\% uncertainty in each time delay distance), the \reqlike sample has leverage that is comparable to the same number of lensed SN from the wide-field surveys.
+However, if we improve  the lensing constraints to 2\% precision, the \reqlike contours tighten dramatically, reflecting the fact that these long-time-baseline events are limited only by the lens modeling uncertainty.
+
+To achieve these cosmological constraints in practice, such a sample could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered.
+As \SNABC has shown, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
+After that, all we need is patience.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
-    \caption{Overview of the field around the center of the MACSJ0138 cluster field and the locations of the lensed host (H1--4) and \SNABC (SN1--3) images.
+    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
+    \caption{Overview of the MACSJ0138 cluster field and the locations of the SN Requiem (SN1--3) images and its multiply-imaged host galaxy (H1--4).
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
@@
 All panels use the late-epoch F125W imaging for the green channel.
-Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion.}
+Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion and to constrain the relative age of each SN image.}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
-    \caption{Classification information for \SNABC based on its position in color-magnitude space.
+    \includegraphics[draft=False, width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
+    \caption{Classification information for SN Requiem based on its position in color-magnitude space.
 (left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
@@
 Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.
-(right) The evolution of a Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.
+(right) The evolution of a typical Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.
 White diamonds correspond to the times labeled on the colorbar at right.
+Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}.
 An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6/#/}{https://plot.ly/~jpierel/6/#/}
@@
     \centering
-    \includegraphics[width=\textwidth]{../Figures/snrequiem_hw_w0wa_apples_to_lsst_ngrst.pdf}
-    \caption{ \todo[inline]{replace caption for new figure}The unusual sensitivity of SN Requiem to dark energy equation of state parameters ($w_0, w_a$).
-Contours show the 1$\sigma$ confidence region for a typical sample of lensed SNIa time delays from LSST (blue) and WFIRST (red) compared to SN Requiem (magenta), which is shown for assumed uncertainties on the lens potential of 5\% and 2\%.
-Dashed lines and the white marker show the input values of $w_0=-1$, $w_a=0$ that were used for this simulation.
-In order to isolate the $w_0, w_a$ dependence, all contours are constructed assuming perfect knowledge of $H_0$, $\Omega_{m,0}$ and $\Omega_{\rm de,0}$.
-SN Requiem could be highly complementary to the LSST+WFIRST lensed SN sample, due to its unusual combination of a relatively low-redshift lens ($z=0.338$) and high-redshift source ($z=1.95$).
-This single SN could deliver constraints on dark energy equation of state parameters comparable to several dozen SNe with shorter and less precise  time delays.}
+    \includegraphics[draft=False,trim={2cm, 3cm, 3cm, 4cm},clip,width=\textwidth]{Paper/Figures/snrequiem_hw_w0wa_apples_to_lsst_ngrst_4panel.pdf}
+    \caption{  
+    The sensitivity of SN Requiem to the expansion rate of the universe ($H_0$) and dark energy equation of state parameters ($w_0, w_a$).
+Dashed lines and the white marker show the input values (upper right of the top panels) that were used for this simulation.
+Contours show the 1$\sigma$ confidence region for a projected sample of 5 lensed SNIa time delays from the Rubin Observatory (blue) and the Roman Space Telescope (red) compared to 5 events like \SNABC (black).
+The left and right columns assume a 5\% and 2\% contribution to the distance uncertainty from modeling the lens potential, respectively.
+Improving the lens modeling tightens the cosmological constraints for all three samples, but the improvement for the \SNABC-like sample is the most significant.
+This is simply because the long time delay baseline for \SNABC makes the time delay uncertainty negligible, raising the ceiling for cosmological improvement with tighter lens modeling constraints.
+In order to isolate the plotted parameters, all contours are constructed assuming perfect knowledge of the cosmological parameters that are not shown.
+    }
     \label{fig:cosmo}
@@
 \centering
-\begin{tabular}{crr|rrrr}
+\begin{tabular}{ccc|cc}
     \multicolumn{1}{c}{}&
-    \multicolumn{2}{c}{\textbf{Photometry}}&\multicolumn{2}{c}{\textbf{Lens Model}}\\
+    \multicolumn{2}{c}{\textbf{Inferred from Photometry}}&\multicolumn{2}{c}{\textbf{Lens Model Predictions}}\\
     %\multicolumn{1}{c}{}&\multicolumn{1}{c}{}\\
-    \multicolumn{1}{c}{\textbf{Image}} &\multicolumn{1}{c}{\textbf{Age}} &\multicolumn{1}{c}{$\mathbf{t_i-t_2}$}&\multicolumn{1}{c}{$\mathbf{\mu}$}
-    &\multicolumn{1}{c}{$\mathbf{t_i-t_2}$}\\
+    \multicolumn{1}{c}{\textbf{Image}} &\multicolumn{1}{c}{\textbf{Age}} &\multicolumn{1}{c}{$\mathbf{t_i-t_1}$}&\multicolumn{1}{c}{$\mathbf{\mu}$}
+    &\multicolumn{1}{c}{$\mathbf{t_i-t_1}$}\\
 
 \midrule
+\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
+\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & 101\pm62 \\
+\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & 19\pm34 \\
+\textit{4} & -- & -- & $0.4\pm0.2$ & 7761\pm541\\
 
-\textit{1}  &$79.10^{+45.56}_{-11.76}$&$91.31^{+62.49}_{-23.36}$ &8.942&103.6\\
-\textit{2} & $-16.67^{+19.14}_{-13.10}$&-- \ \ \ \ \ \ \ \ \  & 18.48&-- \ \ \ \ \\
-\textit{3} &$80.46^{+20.10}_{-9.84}$&$92.60^{+37.28}_{-21.76}$ & 13.257&153.8\\
-\textit{4} &-- \ \ \ \ \ \ \ \ \ &-- \ \ \ \ \ \ \ \ \ &1.137&5980.4\\
-
+% 2020.06.19  OLD DATA (prior to MODEL H) with time delays referenced to image 2.
+%\textit{1}  &$79.10^{+45.56}_{-11.76}$&$91.31^{+62.49}_{-23.36}$ &8.942&103.6\\
+%\textit{2} & $-16.67^{+19.14}_{-13.10}$&-- \ \ \ \ \ \ \ \ \  & 18.48&-- \ \ \ \ \\
+%\textit{3} &$80.46^{+20.10}_{-9.84}$&$92.60^{+37.28}_{-21.76}$ & 13.257&153.8\\
+%\textit{4} &-- \ \ \ \ \ \ \ \ \ &-- \ \ \ \ \ \ \ \ \ &1.137&5980.4\\
 \end{tabular}
-\caption{\label{tab:time_delays}Time Delays}
+\caption{\label{tab:time_delays}Time Delays.  The combination of the models for the light curve evolution and the lens time delays implies a date of $2037\pm2$ for the peak brightness of Image 4.}
 \end{table}
@@
 Supplementary Text\\
-Figs. S1 to S10\\
-Tables S1 to S2\\
+Figs. S1 to S9\\
+Tables S1 to S7\\
 References \textit{(4-10)}
@@
 For this work, all HST observations were processed using the {\tt Drizzlepac} software utilities \cite{gonzaga_drizzlepac_2012}, aligned to a common astrometric reference frame and resampled to a pixel scale of 0.1 arcseconds per pixel.
-We then identified isolated and unsaturated stars in each image and used them to create an effective point spread function (ePSF) with $4\times$ oversampling, using the {\tt photutils} package from the {\tt astropy} software suite \cite{astropy_citation_needed}.
+We then identified isolated and unsaturated stars in each image and used them to create an effective point spread function (ePSF) with $4\times$ oversampling, using the {\tt photutils} package from the {\tt astropy} software suite \cite{astropy_astropy_2013}.
+
 To measure the SN photometry we followed two tracks.
-As our primary method we performed ePSF-fitting directly on the F105W and F160W images where the SN was apparent.
-This ePSF fitting allowed for a fixed background flux to account for both the sky brightness and the background light of the cluster and host galaxy.
+As our primary method we performed ePSF fitting directly on the F105W (Y band) and F160W (H band) images where the SN was apparent.
+This ePSF fitting allowed for a constant background flux to account for both the sky brightness and the background light of the cluster and host galaxy.
 As a second approach, we created ``pseudo-difference images'' by rescaling the later F110W and F140W images collected in 2019 (in which the SN is not present).
@@
 Both sets of photometry agree to within one standard deviation.
-The reported photometry in Table~\ref{tab:photometry} are the first  measurements, collected directly from the unsubtracted images.
+The reported photometry in Table~\ref{tab:photometry} are the measurements from the first method (collected directly from the unsubtracted images).
 
@@
 }
-\caption{}
 \end{table}
@@
 \midrule
-57588.03 & F105W & 0.09  $\pm$ 0.02 \\
-57588.03 & F105W & 2.35  $\pm$ 0.02 \\
-57588.03 & F105W & 0.18  $\pm$ 0.02 \\
-57587.97 & F160W & 0.61  $\pm$ 0.04 \\
-57587.97 & F160W & 3.57  $\pm$ 0.05 \\
-57587.97 & F160W & 1.13  $\pm$ 0.04 \\
+57588.03 & F105W (Y) & 0.09  $\pm$ 0.02 \\
+57588.03 & F105W (Y) & 2.35  $\pm$ 0.02 \\
+57588.03 & F105W (Y) & 0.18  $\pm$ 0.02 \\
+57587.97 & F160W (H) & 0.61  $\pm$ 0.04 \\
+57587.97 & F160W (H) & 3.57  $\pm$ 0.05 \\
+57587.97 & F160W (H) & 1.13  $\pm$ 0.04 \\
 \end{tabular}
@@
 
-\subsection{VLT Spectroscopy}
+\subsection*{VLT Spectroscopy}
 \label{sec:vltmuse}
@@
 Three exposures of 970 sec each were taken with a small dithering offset and 90 degree rotations in between.
-This dataset was reduced and analysed using the MUSE data reduction pipeline v.2.7 (\cite{}) for basic calibration (bias, flat-field, wavelength, LSF, geometry) as well as flux calibration, sky subtraction and astrometry.
+This dataset was reduced and analysed using the MUSE data reduction pipeline v.2.7 \cite{weilbacher_data_2020} for basic calibration (bias, flat-field, wavelength, LSF, geometry) as well as flux calibration, sky subtraction and astrometry.
 We  also make use of the self-calibration technique \cite{bacon_muse_2017}  to remove illumination systematics, specifically tuned for the case of crowded fields in the central region of galaxy clusters (Richard et al.
@@
 We have extracted spectra for each HST detected source and inspected them for redshift measurements.
-In addition, we have run the {\tt muselet} software (publicly available as part of the MPDAF package \cite{piqueras_mpdaf_2019}\footnote{\url{https://mpdaf.readthedocs.io/en/latest/muselet.html}}) to search for line emitters not directly associated with HST sources (see also Mahler et al.
-2018, Lagattuta et al.
-2019).
+In addition, we have run the {\tt muselet} software (publicly available as part of the MPDAF package \cite{piqueras_mpdaf_2019}\footnote{\url{https://mpdaf.readthedocs.io/en/latest/muselet.html}}) to search for line emitters not directly associated with HST sources \cite{mahler_strong_2018,lagattuta_probing_2019}.
 Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.776$.
@@
 In order to correctly estimate the magnification factors, time delays, and predict the appearance of the future images of MRG0138-SN we need to precisely model the mass distribution in the MRG0138 cluster core.
-To do so we make use of the latest version of Lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and error on each parameter of the mass distribution.
+To do so we make use of the latest version of \lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and error on each parameter of the mass distribution.
 
 The strong-lensing constraints used are the locations of multiple images found in HST and MUSE/VLT.
-More specifically we group them into 3 systems: (1) the 4 images of the quiescent galaxy hosting MRG0138-SN, (2) the 3 observed images of MRG0138-SN assumed at the same redshift, and (3) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see Sect.~\ref{sec:vltmuse}).
+More specifically we group them into 3 systems: (1) the 4 images of the quiescent galaxy hosting MRG0138-SN, (2) the 3 observed images of MRG0138-SN assumed at the same redshift, and (3) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see previous section).
 The locations and redshifts used in the lens model are summarised in Table \ref{tab:mulimages}.
@@
 dPIE are elliptical isothermal profiles with both a core and a cut radius where the density flattens and drops respectively.
-In the case of MRG0138 the mass distribution is dominated by a single mass concentration centered on its Brightest Cluster Galaxy (BCG), therefore we use a single cluster-scale halo at a fixed cut radius of 1 Mpc.
-We add multiple galaxy-scale haloes on cluster members where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15 kpc).
+In the case of MRG0138 the mass distribution is dominated by a single mass concentration centered on its Brightest Cluster Galaxy (BCG).
+We therefore use a single cluster-scale halo at a fixed cut radius of 1 Mpc.
+We add a single galaxy-scale halo on each cluster member, where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15 kpc).
 Cluster members were identified by the combination of red sequence selection (based on the F814W-F160W color) and MUSE spectroscopy.
 
-The majority of cluster members are elliptical galaxies selected from the red sequence, and to reduce the number of parameters we assume they follow the scaling relations: $\sigma=\sigma^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/4)}$ for the velocity dispersion, and $r_{\rm cut}=r_{\rm cut}^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/2)}$, assuming the Faber-Jackson relation and a constant M/L ratio respectively.
-$\sigma^*$ and $r_\rm{cut}^*$ are model parameters for a cluster member at the characteristic luminosity $L^*$, following the discussion in \cite{richard_locuss_2010} we fix $\sigma^*=158$ km/s and $r_{\rm cut}^*$=45 kpc.
+The majority of cluster members are elliptical galaxies selected from the red sequence, and to reduce the number of parameters we assume they follow the scaling relations: $\sigma=\sigma^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/4)}$ for the velocity dispersion,
+and $r_{\rm cut}=r_{\rm cut}^*\ {\Big(\frac{L}{L^*}\Big)}^{(1/2)}$, assuming the Faber-Jackson relation and a constant M/L ratio respectively.
+$\sigma^*$ and $r^*_{\rm cut}$ are model parameters for a cluster member at the characteristic luminosity $L^*$.
+Following the discussion in \cite{richard_locuss_2010} we fix $\sigma^*=158$ km/s and $r_{\rm cut}^*$=45 kpc.
 
-We individually optimise the $\sigma$ and $r_{\rm cut}$ parameters for 4 specific galaxies which are not expected to follow the abovementioned scaling relations: the BCG and three pertubators P1 to P3.
-These pertubators are either blue gas-stripped galaxies infalling into the cluster core, and/or located very close to the images of the quiescent galaxy, perturbing its morphology.
-This choice of perturbators is similar to the ones used in the model by \cite{newman_resolving_2018}.
+We individually optimise the $\sigma$ and $r_{\rm cut}$ parameters for 4 specific galaxies which are not expected to follow the aforementioned scaling relations: the BCG and three perturbers P1 to P3.
+These perturbers are either blue gas-stripped galaxies infalling into the cluster core, and/or located very close to the images of the quiescent galaxy, perturbing its apparent morphology with additional lensing.
+This choice of perturbers is similar to the ones used in the model by \cite{newman_resolving_2018}.
 
-Lenstool optimises the parameters of the model by minimising the overall rms between the predicted and observed locations of the multiple images.
-The best fit parameters of each mass components are provided in Table~\ref{tab:massmodel}.
+\lenstool optimises the parameters of the model by minimising the overall root mean square dispersion (RMS) between the predicted and observed locations of the multiple images.
+The best fit parameters of each mass component are provided in Table~\ref{tab:massmodel}.
 The error bars are derived from the MCMC models sampling their posterior probability distribution.
 
-The best model reproduces all multiple systems with an rms of 0.15\arcsec.
+We developed five lens model variants blindly (i.e., without knowing the impact of each lens model variation on the transient classification or time delay inferences).
+Model A was the first viable model developed, which did not include additional perturbers, and did not include the additional lensed background source at $z=0.7763$.
+In Model B we allowed for the location of the main cluster dark matter halo to be free, with an offset from the reference position taken at the BCG center.
+Model C allowed the same central position offset and also relaxed the constraints on the BCG ($\sigma$ and $r_{\rm cut}$).
+Model D fixed the primary dark matter halo at the BCG center, but still relaxed the constraints on the BCG $\sigma$ and $r_{\rm cut}$.
+The final model, and the one selected as the preferred model prior to unblinding, is model E, which includes all four perturbers described above, and includes the additional background object at $z=0.7663$.
+
+The final \lenstool model E reproduces all multiple systems with an RMS of 0.15\arcsec.
 We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs.
-This model is then used to predict the magnification and time delays for the 3 observed images of MRG0138-SN, as well as the location of the two additional images which are still to appear.
-As the lens model reproduces the location of the supernova images within a small uncertainty, these predictions are computed with Lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position.
+This model is then used to predict the magnification and time delays for the 3 observed images of \SNABC, as well as the location of the fourth  image, which is still to appear.
+As the lens model reproduces the location of the SN images within a small uncertainty, these predictions are computed with \lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position.
 We summarise these predictions in Table \ref{tab:snpred}.
@@
     Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
-    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpcs] & [kpc] \\
+    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
 \hline
@@
     \caption{Best fit model parameters for the mass distribution.
-From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius.}
+From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius.
+The final row
+    is the generic galaxy mass at the characteristic luminosity L$^*$, which is scaled to match each of cluster member galaxies.
+Parameters in square brackets are fixed {\it a priori} in the final model (version E).
+}
+    }
     \label{tab:massmodel}
@@
     \centering
-    \begin{tabular}{c|c|c}
-    Image     & $\alpha$ & $\delta$ & $\mu$ & $\Delta T$ \\
-    & & [days] \\
+    \begin{tabular}{c|c|c|c|c|}
+    Image     & $\alpha$ & $\delta$ & $\mu$ & $\Delta t$ \\
+    & & & & [days] \\
 \hline 
-SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
-SN.2 & & & 7.381$\pm$3.044 & 101.4 \\
-SN.3 & & & 5.020$\pm$1.217 &  19.3 \\
-SN.4 & & & 0.377$\pm$0.187 & 7761.0 \\
-SN.5 & & & & \\
+SN1 & 1:38:02.4186     & -21:55:38.465         & 3.9$\pm$0.5   &   0.0 \\
+SN2 & 1:38:02.9568     & -21:55:47.263         & 7$\pm$3     & 101$\pm62$ \\
+SN3 & 1:38:03.6310     & -21:55:50.382         & 5$\pm$1     &  19$\pm34$\\
+SN4 & 1:38:04$\pm$0.36 & -21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760.0$\pm$540\\
+%SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
+%SN.2 & & & 7.381$\pm$3.044 & 101.4$\pm62$ \\
+%SN.3 & & & 5.020$\pm$1.217 &  19.3$\pm34$\\
+%SN.4 & -5.22$\pm$0.36 &6.99$\pm$0.43 & 0.377$\pm$0.187 & 7761.0$\pm$541\\
+%SN.5 & & & & \\
 \hline 
 \end{tabular}
-    \caption{Magnification and time delays estimated at the location of each supernova image.}
+    \caption{Magnifications and time delays predicted by the lens model at the location of each supernova image.
+Coordinates are given in the J2000 reference frame, as measured for images 1-3 and as predicted for image 4.
+Uncertainties in the predicted position of image 4 are in arcseconds.}
     \label{tab:snpred}
@@
 
-\section*{Supplementary Text}
-
-\subsection*{SN Classification from Photometry}
+\subsection*{Classification as a SN}
 The lens modeled time delays between the images are $\sim100$ observer-frame days, 
@@
 
-\todo[inline]{Do we want another figure here? We can't really effectively reference main text figures in the supp. materials}
-The observed photometry for SN Requiem is fully consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~S2.
+\subsection*{SN Sub-Classification Based on Host Galaxy}
+With this transient identified as a SN, we now seek to identify the most likely SN type, under the assumption that it belongs to one of the three most common sub-classes (Ia, II, Ib/c).
+We first use two methods that rely only on measured properties of the host galaxy to {\it circumstantially} infer the type.
+This inference is less strongly dependent on the lens model, helping to reduce any bias associated with a lens model-dependent classification.
+
+Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.
+We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \cite{mannucci_rates_2005}.
+In the case of the host galaxy MRG0138, we have a very well-constrained spectral energy distribution (SED) extending out to far-infrared wavelengths with Spitzer IRAC data \cite{newman_resolving_2018,newman_resolving_2018-1}.
+From the SED fitting we derived the host galaxy's 
+rest-frame $B-K$ color and absolute magnitude, $M_K$, which serve as proxies for the stellar population age and have been empirically calibrated with SN rates in the local universe \cite{foley_classifying_2013}.
+We adopt a lensing magnification correction using \lenstool model E to get $M_K$.
+The $B-K$ color is not affected by the foreground lens.
+Using the {\tt galsnid} method \cite{foley_classifying_2013} we 
+derive a $75\%$ probability that \SNABC is of Type Ia (row a of Table \ref{tab:classification}).
+
+As an alternative host galaxy classification constraint, we use the derived properties of the host galaxy stellar population directly,  rather than adopting color and magnitude proxies.
+The MRG-M0138 galaxy has high mass ($\log_{10}(M/M_{\odot})=11.7$) but is a very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.
+The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr \cite{smartt_progenitors_2009},  making it unlikely that CCSN progenitors make up a significant fraction of the MRG-M0138 stellar population---though the relatively high total stellar mass makes it possible that pockets of young stars are present.
+We define classification probabilities based on the projected SN rate for each SN sub-class, derived from the host galaxy's stellar mass and star formation rate \cite{li_rates_2012}.
+This yields a 62\% probability that \SNABC is of Type Ia (row b of Table~\ref{tab:classification}).
+
+\begin{table}[tb]
+    \centering
+    \begin{tabular}{lp{1.5in}cc|ccc}
+        \multicolumn{1}{c}{Method} & \multicolumn{1}{c}{Data} & Lens info & Priors & p(Ia) & p(II) & p(Ib/c) \\
+        \midrule
+        a. Host color-mag & Host galaxy rest-frame $M_K$, $B-K$ & $\mu_{\rm host}$ & - & 0.75 & 0.19 & 0.06\\
+        b. Host stellar pop. & Host galaxy mass, star form. rate & $\mu_{\rm host}$ & - & 0.62 & 0.27 & 0.09 \\
+        %SN color-mag^{*}$ & SN F105W-F160W color, $m_{\rm F160W}$ & SN magnification & Host: stellar pop. & $0.95\pm0.03$ & $0.01\pm0.01$ & $0.04\pm0.04$\\
+        c. SN color-mag & SN color (Y-H), $m_{\rm F160W}$ & $\mu_{\rm SN}$ & b & 0.95 & 0.01 & 0.04\\
+        d. SN light curve & SN light curves (Y and H) & $\mu_{\rm SN}$, $\Delta t_{\rm SN}$ & b & 0.94 & 0.06 & $<$0.01 \\
+    \end{tabular}
+    %\tablenote{*}{Reported uncertainties reflect the range of classification probabilities derived separately from the three SN images.}
+    \caption{SN classification probabilities. ``Lens info'' indicates the lensing information used to interpret or derive the 
+    observational data: $\mu_{\rm host}$ and $\mu_{\rm SN}$ are the magnifications of the host galaxy MRG0138 and the SN, respectively; $\Delta t_{\rm SN}$ refers to the time delays between SN images 1, 2 and 3.
+In all cases the preferred \lenstool model E is used.
+``Priors'' indicates the host galaxy classification probabilities that were adopted as priors for the subsequent classification using SN data.}
+    \label{tab:classification}
+\end{table}
+
+\subsection*{SN Sub-Classification Based on SN Photometry}
+
+\begin{figure}
+    \centering
+    \includegraphics{Paper/Figures/colormag_classification_supplement.pdf}
+    \caption{The position of \SNABC in color-magnitude space.
+    Colored points show simulated photometry for normal SNe of Type Ia (red), TypeIb/Ic (gold), and Type II (green), with 10,000 simulated SN in each sub-class (not all apparent on this plot).
+Histograms above and below show the marginalized distributions that have been rescaled to represent posterior probability density functions.
+They are normalized to integrate to unity, then multiplied by the SN sub-class priors based on the host galaxy stellar population (row b in Table~\ref{tab:classification}).
+Open markers show the observed photometry of the SN.
+Dotted vertical lines mark the magnification correction based on \lenstool model E, terminating in closed markers with error bars that show the magnitude uncertainty.
+Horizontal error bars in the upper panel indicate the observed uncertainty in
+    the SN color (not affected by lensing).
+The relevant SN photometry markers are repeated in the histogram side-panels with arbitrary vertical positions.
+All three SN images are located in regions of color-magnitude space that are expected to be dominated by Type Ia SN.}
+    \label{fig:colormag_classification_supplement}
+\end{figure}
+
+To improve the classification of the \SNABC sub-type, we now bring in observed photometry of the SN itself, and again we adopt two methods.
+The first method uses only magnification information from the lens model, and the second uses both the modeled magnification and time delay predictions.
+In both cases we adopt the stellar-population-based host galaxy classification probabilities as priors.
+
+Figure~\ref{fig:colormag_classification_supplement} illustrates the first approach.
+After applying the magnification corrections, each of the three images of the SN are mapped to color-magnitude space.
+We then treat each observed point (each SN image) separately, comparing their color-magnitude location to a simulated population of unlensed SNe.
+Our simulation uses the {\tt sncosmo} package \cite{barbary_sncosmo_2016}  to generate 10,000 SN for each of the three principal SN sub-classes (Ia, Ib/c, II), all at z=1.95.
+We then compute the number of simulated SN within a rectangular region around each observed point.
+The width of this sampling region is set to 3 times the observed color uncertainty, and the height is equal to the lens-modeling magnification uncertainty.
+We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
+Multiplying by the prior probabilities derived from host galaxy properties, we finally derive the probability that the SN is of Type Ia as $p(Ia)=0.95$, 0.98, and 0.92 from the three SN images SN1, SN2 and SN3, respectively.
+Row c of Table~\ref{tab:classification} reports the mean of our three classification probabilities for each sub-class.
+
+As a second photometric classification of this SN, we used the {\tt STARDUST2} Bayesian light curve classification tool \cite{rodney_type_2014}, which is also built on the underlying {\tt sncosmo} framework.
+Here we adopt both the predicted magnifications and time delays from the best lens model, which allows us to put the photometry from the three images together as a composite ``light curve'' and compare against simulated light curves.
+{\tt STARDUST2} uses the {\it SALT2-extended} model to represent Type Ia SN \cite{guy_salt2:_2007, pierel_extending_2018} and a collection of 42  spectrophotometric time series templates to represent CCSN (27 Type II and 15 Type Ib/c).
+These CCSN templates comprise all of the templates developed for the Supernova Analysis software {\tt SNANA} \cite{kessler_snana:_2009}, derived from the SN samples of the Sloan Digital Sky Survey \cite{frieman_sloan_2008,sako_sloan_2008, dandrea_type_2010}, Supernova Legacy Survey \cite{astier_supernova_2006}, and Carnegie Supernova Project \cite{hamuy_carnegie_2006, stritzinger_he-rich_2009, morrell_carnegie_2012}.
+With {\tt STARDUST2} we use a nested sampling algorithm to measure likelihoods over the SN simulation parameter space.
+Figure~\ref{fig:classification_lightcurves} shows the magnification- and time-delay-corrected photometry of \SNABC and the {\tt STARDUST2} maximum likelihood light curve fits from each of the three SN sub-classes considered (Ia, II, Ib/c).
+This figure shows that the limited photometric data can be reasonably well fit by at least one model from any of these three sub-classes.
+However, the range of model parameters that allow such a fit to the data is nuch more limited for the heterogeneous CCSN types than for the Type Ia class.
+To compute the posterior probability distribution we adopt priors for each of the three SN classes, again using the classification probabilities derived from the \SNABC host galaxy stellar population properties (row b of Table~\ref{tab:classification}).
+Marginalizing the posterior  probability distributions over all free parameters, we find a 94\% probability that \SNABC is of Type Ia (row d of Table~\ref{tab:classification}).
+
+%The observed photometry for SN Requiem is consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~S2.
 The magnification-corrected photometry is inconsistent with Type II SNe, which are fainter and more blue.
@@
 Visualizing the changing color and brightness of a SNIa at $z=1.95$ in the F105W and F160W bands, we see that it  would intersect image 2 near peak brightness and approach the image 1 and 3 photometry at roughly 80 observer-frame days after peak (see main text Fig \ref{fig:class}).
-\missingfigure[]{Something showing more about classification process/results.\label{fig:quant_class}}
-Taken together, this evidence reinforces the conclusion that SN Requiem is most likely a Type Ia SN.  Although we have to adopt a magnification correction 
-from a lens model, this conclusion is not sensitive to the choices we can reasonably make for modeling the lens.
-Every  {\tt LensTool} model we have evaluated locates Requiem's de-magnified position squarely within the Type Ia region of color-magnitude space.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=\textwidth]{Paper/Figures/snRequiem_stardust_classify_alltypes.pdf}
+    \caption{Maximum likelihood light curve fits for each of the three primary SN sub-classes (Type Ia, Ib/c, and II).
+The observed photometry, shown as black diamonds, has been corrected for magnification and shifted in time using the preferred \lenstool model E.
+In both panels the first data point is SN image 2, followed by image 1 and image 3.
+Plotted error bars include the measurement uncertainty and the lens modeling magnification uncertainty.
+The best-fitting Type Ia, Ib/c and II light curves are shown as solid, dashed, and dotted lines, respectively.
+    \label{fig:classification_lightcurves}
+    }
+\end{figure*}
+
+The combination of evidence from the derived host galaxy properties  and SN photometry supports the conclusion that \SNABC  is  a Type Ia SN with $>90\%$ confidence.
+Although we have adopted some lens modeling corrections for all of these methods, this conclusion is not sensitive to the choices we can reasonably make for modeling the lens.
+As shown in Figure~\ref{fig:colormag_classification_supplement}, every  \lenstool model we have evaluated locates the \SNABC  de-magnified position within the region of color-magnitude space dominated by Type Ia SN.
 Dust is also not a confounding factor here.
-\todo[inline]{Reference whatever figure ends up here correctly in this section}
-The simulations used to generate the contours in Fig \ref{fig:quant_class} include dust extinction at the source plane.
-If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC requiem points upward and leftward on this plot, causing it to be even more strongly associated with the Type Ia region.
+The simulations used in both SN-based classification methods (c and d in Table~\ref{tab:classification}) include dust extinction at the source plane.
+If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC points upward and leftward on Figure~\ref{fig:colormag_classification_supplement}, which would not shift it into the regions occupied by Type II and Ib/c SN.
 
-\subsection*{Classification Based on Host Galaxy}
-Once this transient was identified as a SN (tentatively Ia), we  seek to use only measured properties of the host galaxy stellar population to {\it circumstantially} infer the type.
-This inference is fully independent of lens model, helping to reduce any bias associated with a lens model-dependent classification.
-
-Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.
-We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \cite{mannucci_rates_2005,foley_classifying_2013}.
-In the case of the host galaxy MRG0138, we have very stringent limits on the star formation rate.
-This galaxy is a high-mass but very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.
-The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr (\textcolor{red}{citation?}),  making it highly unlikely that MRG0138 retains any significant population of massive stars.
-To derive a quantitative classification probability, we used the host galaxy's rest-frame $B-K$ color and absolute magnitude, $M_K$, which serve as proxies for the stellar population age and have been empirically calibrated with SN rates in the local universe  \cite{foley_classifying_2013}.
-This
-results in a $75\%$ probability that Requiem is Type Ia.
-\todo[inline]{Anything more quantitative/technical to say here? Any figures?}
-
-\subsection*{Light Curve Age Constraints}
-We constrain the relative time delays of SN Requiem by using two separate methods to estimate the age of the SN at each image during the single observed epoch.
+\subsection*{Measuring the Age of the SN for each Image}
+We constrain the relative time delays of \SNABC by using two separate methods to estimate the age of the SN at each image during the single observed epoch.
 The preferred method of SN time delay measurements involves measuring the time of peak brightness for the SN at each image by fitting the light curves, and taking the difference between each measurement as the relative time delay \cite{pierel_turning_2019,dhawan_magnification_2019,huber_strongly_2019}.
 With only a single observed epoch, this method is impossible due to model parameter degeneracies, and we must rely on color and brightness to constrain the age of each image of the SN.
+Such age estimates are sometimes referenced to the time of explosion, but in this case we use the observer's convention, setting age=0 as the time of peak brightness in the rest-frame B band ($\lambda\sim4500$ \AA).
 Each of these images stems from the same SN explosion, so the difference between the measured age of each image is also a measure of the relative time delay.
+
+\subsubsection*{Color Curve Age Constraints}
 
@@
 
-We use version 2 of the SuperNova Time Delays (SNTD) package\footnote{Link to version 2}, which has several improvements over the original SNTD package \cite{pierel_turning_2019}.
+We use version 2 of the SuperNova Time Delays (SNTD) package\footnote{The v2.0 release is at \href{https://github.com/jpierel14/sntd/releases/tag/2.0}{github.com/jpierel14/sntd/releases/tag/2.0} with documentation at
+\href{https://sntd.readthedocs.io/en/latest/}{sntd.readthedocs.io}}, which has several improvements over the original SNTD package \cite{pierel_turning_2019}.
 The SNTD package employs a nested sampling algorithm within three separate methods to measure time delays, and is designed to fully utilize the information present in SN light curve templates \cite{hsiao_k_2007,guy_salt2:_2007,kessler_results_2010,pierel_extending_2018} to reduce the impacts of microlensing and make more accurate measurements.
-
-We first obtain a constraint on the time delay from the SN color (F110W-F160W) at each image, which is completely independent from the lens model and relatively insensitive to microlensing.
 We use the "color" method present in SNTD, which attempts to reconstruct the intrinsic color curve using the SALT2 model as a template \cite{guy_salt2:_2007}.
 This method fits the age of each image simultaneously, while also varying the SN model parameters.
+The result of this process is seen in Figure \ref{fig:colorcurves}.
 Joint and marginalized posterior distributions
-from SNTD for SALT2 parameters and measured ages for each image are shown in Fig \ref{fig:corner_cfit}.
-The result of this process is seen in Figs \ref{fig:colorcurve1}-\ref{fig:colorcurve3}.
-The measured colors intersect the model at two distinct locations for image 2 of Requiem, meaning there are two plausible ages that cause a double peaked posterior distribution (Fig \ref{fig:corner_cfit}).
-This is caused by a model parameter degeneracy that could be broken in a way independent of lens model if a sufficiently precise light curve of image 4 is obtained in the future.
+from SNTD for SALT2 parameters and measured ages for each image are shown in Figure \ref{fig:corner_cfit}.
+The measured colors intersect the model at two distinct locations for images 1 and 2 of \SNABC, meaning there are two plausible ages that cause a double peaked posterior distribution (Figure \ref{fig:corner_cfit}).
+This is caused by a model parameter degeneracy that could be broken in a way independent of the lens model if a sufficiently precise light curve of image 4 is obtained in the future.
 
-To help break the age degeneracies in the color-based constraints without this precise photometry, we need to use some information about the relative brightnesses of the SN Requiem images.
+\subsubsection*{Light Curve + Lens Model Age Constraints}
+
+In order to break the age degeneracies in the color-based constraints today, we need to use some information about the relative brightnesses of the \SNABC images.
 For this step we can no longer be independent of the lens models, as we must use the lens-model-predicted magnification values to de-magnify the observed magnitudes for comparison to SN models.
 
-For the four lens models described above, we correct the observed magnitude of each image using the predicted lensing magnification ($\mu$).
-Next we employ SNTD's "series" method, as it is most effective for sparse sampling, to attempt a reconstruction of the intrinsic SN light curve \cite{pierel_turning_2019}.
+For the five lens models described above, we correct the observed magnitude of each image using the predicted lensing magnification ($\mu$).
+Next we employ SNTD's ``series'' method, as it is most effective for sparse sampling, to attempt a reconstruction of the intrinsic SN light curve \cite{pierel_turning_2019}.
 Once again the age of each image is constrained simultaneously, while also varying the SN model parameters.
-At this stage we adopt priors on the intrinsic SNIa luminosity \cite{rodney_type_2014} and SNIa color \cite{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Figs \ref{fig:lightcurve1}-\ref{fig:lightcurve3}).
+At this stage we adopt weak priors on the intrinsic SNIa luminosity \cite{wang_determination_2006} and SNIa color \cite{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Figure \ref{fig:lightcurves}).
 
-After repeating this process for each of the four lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
-We find significant preference for models E and F over models C and D (at $\gtrsim15\sigma$), and some preference for model E over model F (at $\sim2.8\sigma$).
+After repeating this process for each of the five lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
+Using a coarse sampling we find significant preference for models C and E over models A,B, and D (at $>3\sigma$), but no significant difference between models C and E (Table \ref{tab:model_evidence}).
+Using a finer sampling for these two models, we find that there is preference for model E over model C (at $\sim3.6\sigma$).
 We therefore adopt model E as our preferred model, and use the model E light curve constraints (Fig \ref{fig:corner_modelE}) to obtain joint posterior distributions with the lens-independent result from color-curve fitting (Figure \ref{fig:corner_combined}).
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image2.pdf}
-    \caption{Light-curve-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:lightcurves}.
+% \begin{figure}[h!]
+%     \centering
+%     \includegraphics[width=0.45\textwidth]{Images/lightcurve_image2.pdf}
+%     \caption{Light-curve-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:lightcurves}.
 The upper panel shows the posterior distributions from SNTD for the age of image 2 from section \ref{s:colorcurves} (magenta), section \ref{s:lightcurves} (light blue), and the combination of both methods (orange).
@@
 }
-    \label{fig:lightcurve2}
-\end{figure}
+%     \label{fig:lightcurve2}
+% \end{figure}
 
@@
 \midrule
-\textit{C} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-15.18\pm0.33$ \\
-\textit{D} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-13.46\pm0.31$ \\
-\textit{E} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-8.91\pm0.27$ \\
-\textit{F} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-9.67\pm0.28$ \\
+\textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
+\textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
+\textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
+\textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
+\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7761.0&$-6.95\pm0.2$ \\
 \end{tabular}
-\caption{\label{tab:model_evidence}Model Preferences}
+\caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work.
+The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D.
+We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=7.25\pm0.07, \ Z_E=7.00\pm0.06$).}
 \end{table}
 
-\subsection*{Final Inferred Time Delays}
+\section*{Supplementary Text}
 
-As discussed at the end of the previous section, our final age constraints for each SN image are a joint posterior between the parameter estimates from color-curve fitting (lens model independent) and light curve fitting (lens model dependent).
-We use image 2 as the reference image because of its likely insensitivity to chromatic microlensing,  resulting in the final time delays and uncertainties reported in table \ref{tab:time_delays} of the main text.
-Using these measured time delays, we can create a reconstructed form of the intrinsic light curve (Fig \ref{fig:full_lightcurve}) and color curve (Fig \ref{fig:full_colorcurve}) of SN Requiem.
+\subsection*{Final Inferred Time Delays and the \SNABC Light Curve}
 
-The final posterior distribution for image 2 is bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for SN Requiem (Fig \ref{fig:corner_combined}).
-If this degeneracy can be broken with the exquisite photometry expected for the final image of Requiem, then the expected age of image 2 becomes $-31.51^{+2.23}_{-2.01}$, producing a time delay uncertainty for image 4 of $\sim0.04\%$.
+Our final age constraints for each SN image are a joint posterior between the parameter estimates from color-curve fitting (lens model independent) and light curve fitting (lens model dependent), resulting in the final time delays and uncertainties reported in table \ref{tab:time_delays} of the main text.
+Using these measured time delays, we can create a reconstructed form of the intrinsic light curve (Figure \ref{fig:full_lightcurve}) and color curve (Figure \ref{fig:full_colorcurve}) of \SNABC.
+
+The final posterior distributions for images 1 and 2 are extremely bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (Figure \ref{fig:corner_combined}).
+If this degeneracy can be broken with the precise photometry expected for the final image of Requiem, then the final time delay uncertainty for \SNABC could be below $0.1\%$.
 
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image1.pdf}
-    \caption{Color-based age constraints for \SNABC image 1 and image 3, as in Fig~\ref{fig:colorcurve2}.}
-    \label{fig:colorcurve1}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/colorcurve_image1.pdf}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/colorcurve_image2.pdf}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/colorcurve_image3.pdf}
+    \caption{Color-based age constraints for \SNABC image 1 (upper right), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Color Curve Age Constraints} section.
+The upper panel of each figure shows the posterior for the age of each image from SNTD, using a prior on the SALT2 color parameter (c) based on known population characteristics of SNIa.
+The effect of adding this prior is slight, with no significant deviation from the best-fit value of c ($0.02^{+0.04}_{-0.05}$).
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 color curve, with the median model shown as a solid line.
+The magenta shaded region shows the 1$\sigma$ range of the measured F105W-F160W color, which corresponds to a $U-V$ color in the rest-frame.}
+    \label{fig:colorcurves}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{Images/colorcurve_image3.pdf}
-    \caption{Color-based age constraints for \SNABC image 1 and image 3, as in Fig~\ref{fig:colorcurve2}.}
-    \label{fig:colorcurve3}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/lightcurve_image1.pdf}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/lightcurve_image2.pdf}
+    \includegraphics[width=0.49\textwidth]{Paper/Figures/lightcurve_image3.pdf}
+    \caption{Light-curve-based age constraints for \SNABC image 1 (upper right), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Light Curve Age Constraints} section.
+The upper panel in each figure shows the posterior distributions from SNTD for the age of each image that is independent of the lens model (magenta, figure \ref{fig:colorcurves}), using lens model E (light blue), and the combination of both methods (orange).
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 light curve, with the median model shown as a solid line.
+The orange shaded region shows the 1$\sigma$ range of the measured (lens-model-corrected, see table \ref{tab:time_delays}) F160W magnitude, which corresponds to a V band magnitude in the rest-frame.}
+    \label{fig:lightcurves}
 \end{figure*}
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image1.pdf}
-    \caption{Light-curve-based age constraints for \SNABC images 1 and 3.}
-    \label{fig:lightcurve1}
-\end{figure*}
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.45\textwidth]{Images/lightcurve_image3.pdf}
-    \caption{Light-curve-based age constraints for \SNABC images 1 and 3.}
-    \label{fig:lightcurve3}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.75\textwidth]{Images/corner_color_curve_fit_with_c_prior.pdf}
-    \caption{Corner plot for color curve nested sampling with prior on c.}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner.pdf}
+%    corner_color_curve_fit_with_c_prior.pdf}
+    \caption{The marginalized and joint posterior distributions for the color curve age constraints measured in this analysis.
+We use a weak prior on the SALT2 color parameter ($c$), and set the SALT2 stretch parameter ($x_1$) to 0.
+This method is fully independent of lens modeling.
+}
     \label{fig:corner_cfit}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{Images/corner_model_E.pdf}
-    \caption{Corner plot for light curve nested sampling using model E.}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_corner.pdf}
+    \caption{The marginalized and joint posterior distributions for the light curve age constraints measured in this analysis.
+We use lens model E to de-magnify each image and fit the corrected apparent magnitudes.
+This fit includes weak priors on the absolute magnitude of a SNIa ($M_B$) and the SALT2 color parameter ($c$), and sets the SALT2 stretch parameter ($x_1$) to 0.}
     \label{fig:corner_modelE}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{Images/corner_combined_lc_color_model_E.pdf}
-    \caption{Corner plot for combined color curve and model E light curve nested sampling.}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner.pdf}
+    \caption{The marginalized and joint posterior distributions for the final age constraints measured in this analysis.
+We use the color curve posterior as the prior for light curve fitting with lens model E, and include weak priors on the absolute magnitude of a SNIa ($M_B$) and the SALT2 color parameter ($c$), and set the SALT2 stretch parameter ($x_1$) to 0.}
     \label{fig:corner_combined}
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/full_lightcurve_full.pdf}
-    \caption{\label{fig:full_lightcurve}}
+    \includegraphics[width=\textwidth]{Paper/Figures/full_lightcurve.pdf}
+    \caption{\label{fig:full_lightcurve}The reconstructed light curve for \SNABC.
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 color curve, with the median model shown as a solid line.
+Observed photometric data are shown as colored markers.
+The error bars on each data point represent the photometric +lens model magnification (y-dimension) and time delay (x-dimension) uncertainties.
+These constraints are obtained using the joint posterior of the color curve and light curve methods described above, and are dependent upon lens model E.}
 \end{figure}
@@
     \includegraphics[width=\textwidth]{Paper/Figures/full_colorcurve_total.pdf}
-    \caption{\label{fig:full_colorcurve}}
+    \caption{\label{fig:full_colorcurve} The reconstructed color curve for \SNABC, using best-fit lensing parameters.
+The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 color curve, with the median model shown as a solid line.
+Observed photometry is shown as colored markers.
+No magnification correction is needed to set the vertical position of each observed point, so error bars in the y direction represent only photometric uncertainty.
+The horizontal position is defined by the best-fit time delays reported in Table~1 of the main text, with error bars
+    representing the uncertainty in the final inferred time delays. }
 \end{figure}

### 2020-06-22 Paper/Science/main.tex
Updates from Overleaf

@@
 Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
-The three-color images are generated from the WFC3/IR filters as indicated; panels $b$--$d$ show the imaging from July 2016 where the SN was visible and $e$--$g$ show the later imaging from July 2019 where the the SN has faded away.
+The three-color images are generated from the WFC3/IR filters as indicated; panels $bcd$ show the imaging from July 2016 where the SN was visible and $efg$ show the later imaging from July 2019 where the the SN has faded away.
 All panels use the late-epoch F125W imaging for the green channel.
@@
 \textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
-\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & 101\pm62 \\
-\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & 19\pm34 \\
-\textit{4} & -- & -- & $0.4\pm0.2$ & 7761\pm541\\
+\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
+\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & $19\pm34$ \\
+\textit{4} & -- & -- & $0.4\pm0.2$ & $7761\pm541$\\
 
@@
 Cluster-DM & $ -0.7^{+  0.4}_{ -0.4}$ & $ -1.2^{+  0.4}_{ -0.4}$ & $ 0.81^{+ 0.02}_{-0.13}$ & $114.9^{+  2.0}_{ -4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
-BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
-P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
-P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
-P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
-L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
+BCG            & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $136^{+42}_{-32}$ & $[0.15]$ & $700^{+52}_{-57}$ \\
+P1             & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[25]$            & $[0.15]$ & $152^{+30}_{-57}$ \\
+P2             & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[12]$            & $[0.15]$ & $23^{+111}_{-29}$ \\
+P3             & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[6]$             & $[0.15]$ & $110^{+35}_{-32}$ \\
+L$^{*}$ galaxy &           &           &          &           & $[45]$            & $[0.15]$ & $[158]$\\            
+%BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
+%P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
+%P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
+%P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
+%L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
 \hline

### 2020-06-22 Analysis/mrg/fig1.py
revert labels in Fig. 1

@@ -85,8 +85,8 @@ def rgb():
     from matplotlib.gridspec import GridSpec
     
     # Label offsets
-    dx = [-20, 10, 0, -10, 0, 0, -38]
-    dy = [0, 14, 10, 5, 10, 10, -15]
+    dx = [-30, 10, 0, -10, 0, 0, -38]
+    dy = [-8, 14, 10, 5, 10, 10, -15]
     
     fig = plt.figure(figsize=(8,3./5*8))
     gs = GridSpec(3, 5, figure=fig)
@@ -107,7 +107,7 @@ def rgb():
     
     labels = 'bcdefg'
     
-    for j, i in enumerate([4,5,6]):
+    for j, i in enumerate([6,5,4]):
         ax = fig.add_subplot(gs[j,3])
         img = plt.imread('{0}.on{1}.png'.format(root, coo['label'][i]))
         ax.imshow(img, origin='upper')

### 2020-06-23 Analysis/mrg/fig1.py
fig1 with image 4

@@ -67,10 +67,12 @@ def rgb():
     N, inter = 10, 0.5
     
     N, inter = 20, 1.0
+
+    xy0 = np.array(wcs.all_world2pix(coo['ra'], coo['dec'], 0)).T
     
     xy = np.cast[int](np.round(wcs.all_world2pix(coo['ra'], coo['dec'], 0))).T
     
-    for i in [4,5,6]:
+    for i in [4,5,6,7]:
         
         xi, yi = xy[i]
         slx = slice(xi-N, xi+N)
@@ -85,36 +87,60 @@ def rgb():
     from matplotlib.gridspec import GridSpec
     
     # Label offsets
-    dx = [-30, 10, 0, -10, 0, 0, -38]
-    dy = [-8, 14, 10, 5, 10, 10, -15]
+    dx = [-30, 10, 0, -28, 0, 0, -38, -27]
+    dy = [-8, 14, 10, 0, 10, 10, -15, 10]
+        
+    ny = 3
+    ny = 4
     
-    fig = plt.figure(figsize=(8,3./5*8))
-    gs = GridSpec(3, 5, figure=fig)
+    if ny == 3:
+        fig = plt.figure(figsize=(8,3/5.*8))
+    else:
+        fig = plt.figure(figsize=(8,4/6.*8))
+        
+    gs = GridSpec(ny, 2+ny, figure=fig)
     
-    ax = fig.add_subplot(gs[:,:3])
+    ax = fig.add_subplot(gs[:,:ny])
     #ax.plot([0,1])
     img = plt.imread('j013804m2156.on.png')
     sh = img.shape
     xyi = (xy - np.array([x0-NX, y0-NY]))/np.array([NX, NY])/2*np.array(sh[:-1])
+    xyi0 = (xy0 - np.array([x0-NX, y0-NY]))/np.array([NX, NY])/2*np.array(sh[:-1])
     #dy = 20
+    pixgrow = sh[0]/2/NX
     
     ax.imshow(img, origin='upper')
     ax.axis('off')
     ax.text(0.03, 0.97, 'a)', ha='left', va='top', transform=ax.transAxes, color='w')
     
-    for j, i in enumerate(range(7)):#[4,5,6]):            
-        ax.text(xyi[i][0]+dx[i], sh[0]-xyi[i][1]+dy[i], coo['label'][i], ha='center', va='top', color='w', fontsize=8)
+    for j, i in enumerate(range(8)):#[4,5,6]):            
+        if i == 7:
[…]

### 2020-06-23 Paper/Science/main.tex
Updates from Overleaf

@@
 \gdef\arcsec{$^{\prime\prime}$}
-\def\SNABC{SN Requiem\xspace}
-\def\reqlike{Requiem-like\xspace}
+%\def\SNABC{SN Requiem\xspace}
+
+%\def\SNABC{AT 2016{\textcolor{red}{tbd}}\xspace}
+%\def\reqlike{16{\textcolor{red}{tbd}}-like\xspace}
+
+\def\SNABC{AT 2016{\textcolor{Gray}{tbd}}\xspace}
+\def\reqlike{16{\textcolor{Gray}{tbd}}-like\xspace}
 \def\lenstool{{\tt LENSTOOL}\xspace}
@@
 
-We discovered SN Requiem using data from the Hubble Space Telescope (HST) program {\it REsolved QUIEscent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
+We discovered \SNABC using data from the Hubble Space Telescope (HST) program {\it REsolved QUIEscent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
 This project targets rare examples of quiescent galaxies that have been magnified by strong gravitational lensing.
@@
 the point sources are multiple images of a single astrophysical 
-transient in MRG-M0138, most likely a SN. Hereafter we call this multiply-imaged transient \SNABC.
+transient in MRG-M0138, most likely a SN \cite{materials_methods_2020}.  
+%Hereafter we call this multiply-imaged transient \SNABC.
+The official designation for this multiply-imaged astrophysical transient is \SNABC.
 
@@
 The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$1.5, demagnified with $\mu=0.4\pm0.2$.
+The predicted location for this future image is $\alpha=01:38:04.15,\delta=-21:55:24.659$.
 A fifth image will also appear at a later date, located very near the center of the cluster and much more significantly demagnified, so therefore likely not observable.
@@
 %The range of possible transients for Requiem is broad, encompassing normal SNe, superluminous SNe (galyam luminous 2019), fast transients (berger fast 2013, drout rapidly 2014), and even gravitational microlensing events (rodney two 2018, kelly extreme 2018).
-To realize the cosmological promise of SN Requiem 
+To realize the cosmological promise of \SNABC 
 we need to estimate the age of each SN image, which in turn constrains the lensing time delays. For this
@@
 Furthermore, almost all will have significantly shorter
-delays (of order 10-100 days) and therefore higher relative uncertainties than SN Requiem.  Since it is the {\it fractional} time delay uncertainty that 
+delays (of order 10-100 days) and therefore higher relative uncertainties than \SNABC.  Since it is the {\it fractional} time delay uncertainty that 
 propagates through to any time delay distance measurement, the extraordinarily long time delays of cluster-lensed SNe like SN Requiem can deliver significantly better time delay precision, with comparable observational cost.
@@
 ratio of source to lens redshift account for the different cosmological parameter covariances, reflected in the orientations of the contours in these plots.
-Because of the unusually large redshift ratio of SN Requiem, the constraints
+Because of the unusually large redshift ratio of \SNABC, the constraints
 %on dark energy equation of state parameters ($w_0$, $w_a$) 
@@
 To achieve these cosmological constraints in practice, such a sample could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered.
-As \SNABC has shown, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
+As \SNABC shows, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
 After that, all we need is patience.
@@
     \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
-    \caption{Overview of the MACSJ0138 cluster field and the locations of the SN Requiem (SN1--3) images and its multiply-imaged host galaxy (H1--4).
+    \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4).
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
@@
     \caption{  
-    The sensitivity of SN Requiem to the expansion rate of the universe ($H_0$) and dark energy equation of state parameters ($w_0, w_a$).
+    The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation of state parameters ($w_0, w_a$).
 Dashed lines and the white marker show the input values (upper right of the top panels) that were used for this simulation.
@@
 \centering
-\begin{tabular}{ccc|cc}
+\begin{tabular}{crc|cc}
     \multicolumn{1}{c}{}&
@@
 \textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
-\textit{3} & $88\pm15$ & $16\pm19$ & $5\pm1$ & $19\pm34$ \\
+\textit{3} & $88^{+15}_{-15}$ & $16^{+19}_{-19}$ & $5\pm1$ & $19\pm34$ \\
 \textit{4} & -- & -- & $0.4\pm0.2$ & $7761\pm541$\\
@@
 In addition, we have run the {\tt muselet} software (publicly available as part of the MPDAF package \cite{piqueras_mpdaf_2019}\footnote{\url{https://mpdaf.readthedocs.io/en/latest/muselet.html}}) to search for line emitters not directly associated with HST sources \cite{mahler_strong_2018,lagattuta_probing_2019}.
-Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.776$.
+Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.766$.
 
@@
 The strong-lensing constraints used are the locations of multiple images found in HST and MUSE/VLT.
-More specifically we group them into 3 systems: (1) the 4 images of the quiescent galaxy hosting MRG0138-SN, (2) the 3 observed images of MRG0138-SN assumed at the same redshift, and (3) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see previous section).
+More specifically we group them into 3 systems: (a) the 4 images of the quiescent galaxy hosting MRG0138-SN, (b) the 3 observed images of MRG0138-SN assumed at the same redshift, and (c) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see previous section).
 The locations and redshifts used in the lens model are summarised in Table \ref{tab:mulimages}.
@@
      ID &   R.A. & Dec. & $z$ \\
+     \midrule
 1.1 & 24.50990183 & -21.92601304 & 1.95 \\
@@
     \end{tabular}
-    \caption{Multiple images used as constraints in our parametric model. From left to right: image ID, right ascension, declination, spectroscopic redshift}
+    \caption{Multiple images used as constraints in our parametric model.
+From left to right: image ID, right ascension, declination, spectroscopic redshift.
+Coordinates are in the J2000 reference frame.}
     \label{tab:mulimages}
@@
 We developed five lens model variants blindly (i.e., without knowing the impact of each lens model variation on the transient classification or time delay inferences).
-Model A was the first viable model developed, which did not include additional perturbers, and did not include the additional lensed background source at $z=0.7763$.
+Model A was the first viable model developed, which did not include additional perturbers, and did not include the additional lensed background source at $z=0.7663$.
 In Model B we allowed for the location of the main cluster dark matter halo to be free, with an offset from the reference position taken at the BCG center.
@@
 This model is then used to predict the magnification and time delays for the 3 observed images of \SNABC, as well as the location of the fourth  image, which is still to appear.
+The actual 1$\sigma$ uncertainty on this location is the ellipse overlayed on top of the bottom cutouts in Fig.~\ref{fig:layout}.
 As the lens model reproduces the location of the SN images within a small uncertainty, these predictions are computed with \lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position.
@@
 }
-    }
     \label{tab:massmodel}
@@
     \begin{tabular}{c|c|c|c|c|}
-    Image     & $\alpha$ & $\delta$ & $\mu$ & $\Delta t$ \\
+    Image     & R.A. & Dec. & $\mu$ & $\Delta t$ \\
     & & & & [days] \\
 \hline 
-SN1 & 1:38:02.4186     & -21:55:38.465         & 3.9$\pm$0.5   &   0.0 \\
-SN2 & 1:38:02.9568     & -21:55:47.263         & 7$\pm$3     & 101$\pm62$ \\
-SN3 & 1:38:03.6310     & -21:55:50.382         & 5$\pm$1     &  19$\pm34$\\
-SN4 & 1:38:04$\pm$0.36 & -21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760.0$\pm$540\\
+SN1 & 01:38:02.419     & -21:55:38.47         & 3.9$\pm$0.5   &   0.0 \\
+SN2 & 01:38:02.957     & -21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
+SN3 & 01:38:03.631     & -21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
+SN4 & 01:38:04.15$\pm$0.36 & -21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760.0$\pm$540\\
 %SN.1 & & & 3.907$\pm$0.534 &   0.0 \\

### 2020-06-23 Analysis/mrg/fig1.py
fig1

@@ -167,8 +167,8 @@ def rgb():
             ax.text(0.06+di, 0.18, '2019', ha='left', va='bottom', color='w',
                     transform=ax.transAxes)
     
+    # Error ellipse for SN4
     if 1:
-        # Error ellipse for SN4
         thet = np.linspace(0, 2*np.pi, 256)
         xt = np.cos(thet)*4.95*pixgrow
         yt = np.sin(thet)*1.14*pixgrow

### 2020-06-23 Analysis/mrg/fig1.py
figure with arc3

@@ -87,8 +87,8 @@ def rgb():
     from matplotlib.gridspec import GridSpec
     
     # Label offsets
-    dx = [-30, 10, 0, -28, 0, 0, -38, -27]
-    dy = [-8, 14, 10, 0, 10, 10, -15, 10]
+    dx = [-30, 10, 0, -28, 0, 0, -38, -27] + [0, 0, -18, 0]
+    dy = [-8, 14, 10, 0, 10, 10, -15, 10] + [15, 15, 0, 0]
         
     ny = 3
     ny = 4
@@ -113,13 +113,22 @@ def rgb():
     ax.axis('off')
     ax.text(0.03, 0.97, 'a)', ha='left', va='top', transform=ax.transAxes, color='w')
     
-    for j, i in enumerate(range(8)):#[4,5,6]):            
-        if i == 7:
-            col = 'pink'
-        else:
-            col = 'w'
+    colors = ['w']*7 + ['pink'] + ['w']*4
+
+    for j, i in enumerate(range(8+4)):#[4,5,6]):            
+        # if i == 7:
+        #     col = 'pink'
+        # elif i > 7:
+        #     col = '0.5'
+        # else:
+        #     col = 'w'
         
-        ax.text(xyi[i][0]+dx[i], sh[0]-xyi[i][1]+dy[i], coo['label'][i], ha='center', va='top', color=col, fontsize=8)
+        if i > 7:
+            fs = 6
+        else:
+            fs = 8
+            
+        ax.text(xyi[i][0]+dx[i], sh[0]-xyi[i][1]+dy[i], coo['label'][i], ha='center', va='top', color=colors[i], fontsize=fs)
     
     labels = 'bcdefghijk'
     
@@ -140,7 +149,7 @@ def rgb():
         ax.axis('off')
         
         ax.text(0.05, 0.95, '{0}): {1}'.format(labels[j], coo['label'][i]), 
-                ha='left', va='top', color=col, transform=ax.transAxes)
+                ha='left', va='top', color=colors[i], transform=ax.transAxes)
         
         di = 0.02
         if j == 2:
@@ -157,7 +166,7 @@ def rgb():
         ax.axis('off')
         
         ax.text(0.05, 0.95, '{0})'.format(labels[j+ny], coo['label'][i]), 
[…]

### 2020-06-23 Paper/Science/main.tex

@@
 quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}.
-As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosological_2018}.
+As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosmological_2018}.
 
@@
 To date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
-The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_SNRefsdal_2016}.
-The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2020}.
+The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_sn_2016}.
+The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2019}.
 Here we present the discovery
@@
     \centering
-    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
+    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout_sn4.pdf}
     \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4).
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
-Panels b--g) show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
-The three-color images are generated from the WFC3/IR filters as indicated; panels $bcd$ show the imaging from July 2016 where the SN was visible and $efg$ show the later imaging from July 2019 where the the SN has faded away.
-All panels use the late-epoch F125W imaging for the green channel.
-Nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which we use to constrain the transient classification as a likely Ia supernova explosion and to constrain the relative age of each SN image.}
+Panels \emph{b}--\emph{i} show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
+The three-color images are generated from the WFC3/IR filters as indicated; panels \emph{bcde} show the imaging from 2016 July where the SN was visible and \emph{fghi} show the later imaging from 2019 July where the the SN has faded away.
+Panels \emph{ei} indicate the location of the fourth image predicted to appear in $\approx$2037.
+All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.}
 
@@
 Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}.
-An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6/#/}{https://plot.ly/~jpierel/6/#/}
+An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
     \label{fig:class}
@@
 \textit{3} & $88^{+15}_{-15}$ & $16^{+19}_{-19}$ & $5\pm1$ & $19\pm34$ \\
-\textit{4} & -- & -- & $0.4\pm0.2$ & $7761\pm541$\\
+\textit{4} & -- & -- & $0.4\pm0.2$ & $7760\pm540$\\
 
@@
 
-The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No. 140.
+Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).
+Support for this work was provided by NASA through grant number HST-GO-15663 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
+under NASA contract NAS 5-26555.
+The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No.
+140.
 
@@
 \begin{tabular}{ccccccr}
-    \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{Observation Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp.
+    \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{UT Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp.
 Time (s)}\\
@@
 \midrule
-\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 212 \\ % AOR r58785536
-\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.1556 &   & 241 \\
-\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 57542.9102 &   & 5214 \\
-\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 57587.9686 & + & 1611 \\
-\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 57588.0304 & + & 3611 \\ 
-\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 468 \\ % AOR r58289152
-\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.6078 &   & 581 \\
+\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.156 &   & 212 \\ % AOR r58785536
+\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-03-15 03:44:04 & 57462.156 &   & 241 \\
+\textit{HST}     & ACS/WFC   & F555W                     & 2016-06-03 21:50:43 & 57542.910 &   & 5214 \\
+\textit{HST}     & WFC3/IR   & F160W                     & 2016-07-18 23:14:50 & 57587.969 & + & 1611 \\
+\textit{HST}     & WFC3/IR   & F105W                     & 2016-07-19 00:43:47 & 57588.030 & + & 3611 \\ 
+\textit{Spitzer} & IRAC      & $3.6\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.608 &   & 468 \\ % AOR r58289152
+\textit{Spitzer} & IRAC      & $4.5\,\mu\mathrm{m}$      & 2016-10-13 14:35:13 & 57674.608 &   & 581 \\
 \midrule
-\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 58677.8703 &   & 706 \\ 
-\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 58678.9278 &   & 353 \\ 
-\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 58683.8941 &   & 706 \\ 
-\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 58685.7853 &   & 912 \\ 
-\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 58685.7924 &   & 1272 \\ 
-\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 58685.9461 &   & 353 \\ 
-\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.1642 &   & 2649  \\
+\textit{HST}     & WFC3/IR   & F110w                     & 2019-07-13 20:53:16 & 58677.870 &   & 706 \\ 
+\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-14 22:16:01 & 58678.928 &   & 353 \\ 
+\textit{HST}     & WFC3/IR   & F125W                     & 2019-07-19 21:27:30 & 58683.894 &   & 706 \\ 
+\textit{HST}     & WFC3/UVIS & F814W                     & 2019-07-21 18:50:53 & 58685.785 &   & 912 \\ 
+\textit{HST}     & WFC3/UVIS & F390W                     & 2019-07-21 19:01:06 & 58685.792 &   & 1272 \\ 
+\textit{HST}     & WFC3/IR   & F140W                     & 2019-07-21 22:42:22 & 58685.946 &   & 353 \\ 
+\textit{VLT}     & MUSE      & 0.4--0.9$\,\mu\mathrm{m}$ & 2019-09-06 03:56:25 & 58732.164 &   & 2649  \\
 \end{tabular}
@@
 \centering
-\begin{tabular}{ccc}
-Obs. Date (MJD) & Filter & Flux density ($\mu$Jy) \\
+\begin{tabular}{cccc}
+Image & Obs. Date (MJD) & Filter & Flux density ($\mu$Jy) \\
 \midrule
-57588.03 & F105W (Y) & 0.09  $\pm$ 0.02 \\
-57588.03 & F105W (Y) & 2.35  $\pm$ 0.02 \\
-57588.03 & F105W (Y) & 0.18  $\pm$ 0.02 \\
-57587.97 & F160W (H) & 0.61  $\pm$ 0.04 \\
-57587.97 & F160W (H) & 3.57  $\pm$ 0.05 \\
-57587.97 & F160W (H) & 1.13  $\pm$ 0.04 \\
+SN1 & 57588.03 & F105W ($Y$) & 0.09  $\pm$ 0.02 \\
+SN2 & 57588.03 & F105W ($Y$) & 2.35  $\pm$ 0.02 \\
+SN3 & 57588.03 & F105W ($Y$) & 0.18  $\pm$ 0.02 \\
+SN1 & 57587.97 & F160W ($H$) & 0.61  $\pm$ 0.04 \\
+SN2 & 57587.97 & F160W ($H$) & 3.57  $\pm$ 0.05 \\
+SN3 & 57587.97 & F160W ($H$) & 1.13  $\pm$ 0.04 \\
+\midrule
+SN1 & 58677.87 & F110W ($Y$) & 0.01  $\pm$ 0.02 \\
+SN1 & 58678.93 & F140W ($H$) & 0.02  $\pm$ 0.02 \\
+SN1 & 58683.89 & F125W ($J$) & 0.02  $\pm$ 0.03 \\
 \end{tabular}
-\caption{Photometry of the SN in MRG0138.
+\caption{Photometry of the SN in MRG0138.  The final three rows indicate ``empty'' aperture flux densities measured at the position of SN1 in the 2019 \textit{HST} visits.
 \label{tab:photometry}}
@@
     \centering
-    \begin{tabular}{c|c|c|c}
-     ID &   R.A. & Dec. & $z$ \\
+    \begin{tabular}{rccl}
+     ID &   R.A. (deg) & Dec. (deg) & $z$ \\
      \midrule
-1.1 & 24.50990183 & -21.92601304 & 1.95 \\
-1.2 & 24.51320906 & -21.92990322 & 1.95 \\
-1.3 & 24.51641380 & -21.93031720 & 1.95 \\
-1.4 & 24.51761179 & -21.92334337 & 1.95 \\
-2.1 & 24.51007534 & -21.92734181 & 1.95 \\
-2.2 & 24.51231984 & -21.92978758 & 1.95 \\
-2.3 & 24.51512533 & -21.93066599 & 1.95 \\
-3.1 & 24.5169659 & -21.9234814 & 0.7663 \\
-3.2 & 24.5161061 & -21.9231225 & 0.7663 \\
-3.3 & 24.5184361 & -21.9264250 & 0.7663 \\
-3.4 & 24.5146833 & -21.9261020 & 0.7663 \\
+H1 & 24.5099018 & $-$21.9260130 & 1.95 \\
+H2 & 24.5132090 & $-$21.9299032 & 1.95 \\
+H3 & 24.5164138 & $-$21.9303172 & 1.95 \\
+H4 & 24.5176117 & $-$21.9233433 & 1.95 \\
+SN1 & 24.5100753 & $-$21.9273418 & 1.95 \\
+SN2 & 24.5123198 & $-$21.9297875 & 1.95 \\
+SN3 & 24.5151253 & $-$21.9306659 & 1.95 \\
+3.1 & 24.5169659 & $-$21.9234814 & 0.7663 \\
+3.2 & 24.5161061 & $-$21.9231225 & 0.7663 \\
+3.3 & 24.5184361 & $-$21.9264250 & 0.7663 \\
+3.4 & 24.5146833 & $-$21.9261020 & 0.7663 \\
     \end{tabular}
@@
     \centering
-    \begin{tabular}{c|c|c|c|c|}
+    \begin{tabular}{c|l|l|c|c|}
     Image     & R.A. & Dec. & $\mu$ & $\Delta t$ \\
@@
 \hline 
-SN1 & 01:38:02.419     & -21:55:38.47         & 3.9$\pm$0.5   &   0.0 \\
-SN2 & 01:38:02.957     & -21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
-SN3 & 01:38:03.631     & -21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
-SN4 & 01:38:04.15$\pm$0.36 & -21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760.0$\pm$540\\
+SN1 & 01:38:02.42     & $-$21:55:38.47         & 3.9$\pm$0.5   &   --- \\
+SN2 & 01:38:02.96     & $-$21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
+SN3 & 01:38:03.63     & $-$21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
+SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760$\pm$540\\
 %SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
@@
     \caption{Magnifications and time delays predicted by the lens model at the location of each supernova image.
-Coordinates are given in the J2000 reference frame, as measured for images 1-3 and as predicted for image 4.
-Uncertainties in the predicted position of image 4 are in arcseconds.}
+Coordinates are given in the J2000 reference frame, as measured for images 1--3 and as predicted for image 4.
+Uncertainties in the predicted position of image 4 are in arcseconds.
+Time delays are reported relative to SN1.}
     \label{tab:snpred}
@@
 \textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
-\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7761.0&$-6.95\pm0.2$ \\
+\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7760&$-6.95\pm0.2$ \\
 \end{tabular}

### 2020-06-23 Paper/Science/main.tex
Updates from Overleaf

@@
 MRG-M0138 is quadruply lensed by the foreground cluster, which is at $z=0.338$.  
-During analysis of REQUIEM observations obtained 13-14 July 2019 \cite{materials_methods_2020} we discovered three point 
-sources that were present in archival HST images from 18-19 July 2016, part of the program 
+During analysis of REQUIEM observations obtained 13--14 July 2019 \cite{materials_methods_2020} we discovered three point 
+sources that were present in archival HST images from 18--19 July 2016, part of the program 
 that first confirmed the MRG-M0138 galaxy as a strongly-lensed object (HST-GO-14496; PI:Newman). 
@@
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
+    %Labels marked 3.1--3.4 indicate the locations of a separate  multiply-imaged [O\textsc{ii}]-emitter at $z=0.77$ used to help constrain the lensing potential. 
     Panels \emph{b}--\emph{i} show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
@@
 3.1 & 24.5169659 & $-$21.9234814 & 0.7663 \\
-3.2 & 24.5161061 & $-$21.9231225 & 0.7663 \\
+3.2 & 24.5151039 & $-$21.9231406 & 0.7663 \\
 3.3 & 24.5184361 & $-$21.9264250 & 0.7663 \\

### 2020-06-24 Paper/Science/main.tex
Submitted version

@@
 
-\documentclass[12pt,dvipsnames]{article}
+\documentclass[12pt]{article}
 
 %extra packages added during drafting, remove for submission
-\usepackage{todonotes}
 \usepackage{hyperref}
@@
 
-% Simple little macros to hide and highlight some text:
-%\newcommand{\highlight}[1]{{\bf \textcolor{Maroon}{#1}}}
-\newcommand{\highlight}[1]{{\bf {#1}}}
-
-%\usepackage{ifthen}
-\newif\ifshowoutline
-%\showoutlinetrue
-\showoutlinefalse
-\ifshowoutline
-    \newcommand{\outline}[1]{\textcolor{blue}{#1}}
-\else
-    \newcommand{\outline}[1]{}
-\fi
-
-\usepackage{amssymb}
+%\usepackage{amssymb}
 \usepackage{xspace}
+\usepackage{graphicx}
 
 \gdef\arcsec{$^{\prime\prime}$}
+\def\TNSname{AT 2016tbd\xspace}
+\def\SNABC{AT 2016tbd\xspace}
 %\def\SNABC{SN Requiem\xspace}
-
-%\def\SNABC{AT 2016{\textcolor{red}{tbd}}\xspace}
-%\def\reqlike{16{\textcolor{red}{tbd}}-like\xspace}
-
-\def\SNABC{AT 2016{\textcolor{Gray}{tbd}}\xspace}
-\def\reqlike{16{\textcolor{Gray}{tbd}}-like\xspace}
+%\def\reqlike{Requiem-like\xspace}
+\def\reqlike{16tbd-like\xspace}
+
 \def\lenstool{{\tt LENSTOOL}\xspace}
@@
 
-%\title{Requiem for a 10 billion year old supernova } 
 \title{A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
-%\title{A Strongly Lensed Type Ia Supernova with a Decade-Long Time Delay}
-%\title{SN Requiem: A Strongly Lensed Type Ia Supernova with a Decade-Long Time Delay}
 
@@
 
-%%%%%%%fill in once decided
-% \author
-% {John Smith,$^{1\ast}$ Jane Doe,$^{1}$ Joe Scientist$^{2}$\\
-% \\
-% \normalsize{$^{1}$Department of Chemistry, University of Wherever,}\\
-% \normalsize{An Unknown Address, Wherever, ST 00000, USA}\\
-% \normalsize{$^{2}$Another Unknown Address, Palookaville, ST 99999, USA}\\
-% \\
-% \normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  jsmith@wherever.edu.}
-% }
+\author{
+ Steven A. Rodney$^{1\ast}$, 
+ Gabriel Brammer$^{2\ast}$,  
+ Justin D.\,R.~Pierel$^{1}$,\\ 
+ Johan Richard$^{3}$, 
+ Sune Toft$^{2}$,\\  
+ Kyle F. O'Connor$^{1}$, 
+ Mohammad Akhshik$^{4}$, 
+ Katherine E. Whitaker$^{2,4,5}$  
+\\
+\normalsize{$^{1}$Department of Physics \& Astronomy, University of South Carolina,}\\ \normalsize{ Columbia, SC 29208, USA}\\
+\normalsize{$^{2}$Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen,}\\ \normalsize{Lyngbyvej 2, Copenhagen \O\ 2100 Denmark}\\
+\normalsize{$^{3}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon}\\ \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
+\normalsize{$^{4}$Department of Physics, University of Connecticut,}\\ \normalsize{Storrs, CT 06269, USA}\\
+\normalsize{$^{5}$Department of Astronomy, University of Massachusetts,}\\ \normalsize{Amherst, MA 01003, USA}\\
+\normalsize{$^\ast$To whom correspondence should be addressed;}\\ \normalsize{E-mail:  srodney@sc.edu, gabriel.brammer@nbi.ku.dk}
+}
 
 % Include the date command, but leave its argument blank.
-
 \date{}
@@
 
+\paragraph*{One Sentence Summary:} A distant supernova has appeared as three images magnified by the gravity of a galaxy cluster, and will reappear in 20 years.
+
 % Place your abstract within the special {sciabstract} environment.
@@
 \begin{sciabstract}
-%   The expansion history of the Universe is one of the most fundamental observations leading to the hot big bang model for the origin of the Universe\footnote{Penzias \& Wilson 1965, ApJL, 142, 419}.
-
-  We report the discovery of a quadruply-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
+
+  We report the discovery of a strongly-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
 This unprecedented scenario will enable a rare and highly precise measurement of the Hubble constant from a single lensed SN.
-The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACSJ0138.
- This is the most distant multiply-imaged supernova yet discovered, and we find it is classified as a Type Ia with {$>90\%$} probability.
-  Three lensed images of the SN are detected in existing observations from the \textit{Hubble Space Telescope} with relative time delays of $<$200 days.
-A fourth image in the component closest to the cluster core is predicted to appear in the year 2037$\pm$2.
-Observing the light curve of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary baseline of nearly 20 years.
+The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACS J0138.0-2155.
+This is the most distant multiply-imaged supernova yet discovered.
+We classify the supernova as a Type Ia with {$>90\%$} probability based on archival imaging observations from the \textit{Hubble Space Telescope}.
+Three lensed images of the SN are detected with relative time delays of $<$200 days, and we predict that a fourth image in the component closest to the cluster core will appear in the year 2037$\pm$2.
+Observing the light curve of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline.
 
@@
 
-%\section*{Introduction}
-
-%\todo[inline]{JP: Can edit intro} SN1a play a special role in cosmology, they are standard candles -> led to discovery of DE. High redshift SN-1a provide particularly strong constraints.
-%\newline
+\section*{Main Text:}
 
@@
 
-One promising method uses %time delays of 
+One promising cosmological tool uses %time delays of 
 gravitational lens systems in which a background
@@
 %the expansion rate of the universe, 
-$H_0$  and the dark energy equation of state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
-In recent years this method has been very successfully applied to lensed
+$H_0$  and the dark energy equation-of-state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
+In recent years this method has been successfully applied to lensed
 quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}.
@@
 Gravitationally lensed SN with multiple images present an attractive new addition to this field.
-Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---a contrast to the stochastic variation of quasars.
-However, the exploration of lensed SN time delay cosmography has been hindered by their rarity.
-To date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
+Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---in contrast to the stochastic variation of quasars.
+However, despite the promise of lensed SN time delay cosmography as a cosmological distance probe, to date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
 The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_sn_2016}.
@@
 
-We discovered \SNABC using data from the Hubble Space Telescope (HST) program {\it REsolved QUIEscent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
-This project targets rare examples of quiescent galaxies that have been magnified by strong gravitational lensing.
+We discovered \SNABC ({\it AstroNotes citation})
+using data from the Hubble Space Telescope (HST) program {\it REsolved QUIEscent Magnified Galaxies} (REQUIEM, HST-GO-15663, PI:Akhshik).
+This project targets rare examples of massive galaxies with low specific star formation rates that have been magnified by strong gravitational lensing.
 %These are typically too faint and compact to be resolved even with Hubble, but due to lensing are magnified.
@@
 is MRG-M0138, first discovered as a massive red galaxy (MRG) at $z=1.95$ \cite{newman_resolving_2018} behind the massive galaxy cluster MACS J0138.0-2155 \cite{ebeling_macs_2001}.
-MRG-M0138 is quadruply lensed by the foreground cluster, which is at $z=0.338$.  
+MRG-M0138 is quadruply lensed by a foreground galaxy cluster at $z=0.338$.  
 During analysis of REQUIEM observations obtained 13--14 July 2019 \cite{materials_methods_2020} we discovered three point 
@@
 Each point source is within 5 arcseconds of one of the four MRG-M0138 images.  None of the
-three point sources are present in the REQUIEM HST data in 2019 (Fig \ref{fig:layout}). We infer that 
+three point sources are present in the REQUIEM HST data in 2019 (Fig. \ref{fig:layout}). We infer that 
 the point sources are multiple images of a single astrophysical 
 transient in MRG-M0138, most likely a SN \cite{materials_methods_2020}.  
-%Hereafter we call this multiply-imaged transient \SNABC.
-The official designation for this multiply-imaged astrophysical transient is \SNABC.
-
-To construct a lens model for the MACS J0138.0-2155 cluster we used the publicly available \lenstool software \cite{jullo_bayesian_2007, kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster scale and multiple galaxy scale potentials \cite{materials_methods_2020}.
+%The official designation for this multiply-imaged astrophysical transient is \TNSname. 
+%Formal designation as a SN requires spectroscopic confirmation, but with a high-confidence photometric classification we coin the name \SNABC for this unusual source.
+
+To construct a lens model for the MACS J0138.0-2155 cluster we use the \lenstool software \cite{jullo_bayesian_2007,kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster-scale and multiple galaxy-scale potentials \cite{materials_methods_2020}.
 To avoid unintended bias, we kept the lens model development completely separate from the analysis of the SN.
@@
 The predicted location for this future image is $\alpha=01:38:04.15,\delta=-21:55:24.659$.
-A fifth image will also appear at a later date, located very near the center of the cluster and much more significantly demagnified, so therefore likely not observable.
-
-%The range of possible transients for Requiem is broad, encompassing normal SNe, superluminous SNe (galyam luminous 2019), fast transients (berger fast 2013, drout rapidly 2014), and even gravitational microlensing events (rodney two 2018, kelly extreme 2018).
+A fifth image will also appear at date later still, located near the center of the cluster and much more significantly demagnified, so it will not be easily observable.
+
 To realize the cosmological promise of \SNABC 
 we need to estimate the age of each SN image, which in turn constrains the lensing time delays. For this
-goal, it is valuable to have a firm determination of the transient’s class.
+goal, it is necessary to have a firm determination of the transient’s class.
 Expected time delays and magnifications from the lens model exclude any of the various rapidly evolving and low-luminosity stellar transient classes, strongly suggesting that it is a SN.
-The first-order SN distinction remaining is between a Type Ia SN---the explosion of a white dwarf star in a binary system---and a core collapse SN (CCSN)---the end-point of a star with mass $\gtrsim 10 M_{\odot}$.
+The first-order SN distinction remaining is between a Type Ia SN---the explosion of a white dwarf star in a binary system---and a core collapse SN (CCSN)---the end-point of a star with mass $>10 M_{\odot}$.
 The properties of the host galaxy can inform this classification because CCSN are limited to galaxies with young stellar populations.
@@
 Based on observed properties of the host galaxy alone, we find a 62-75\% probability that \SNABC is a Type Ia SN \cite{materials_methods_2020}.
-Adopting the lens model magnifications for the three observed SN images (Table \ref{tab:time_delays}) the position of each SN image in color-magnitude space (Figure \ref{fig:class}) provides more classification leverage, yielding p(Ia)=95\% \cite{materials_methods_2020}.
+Adopting the lens model magnifications for the three observed SN images (Table \ref{tab:time_delays}) we can locate each SN image in color-magnitude space (Fig.
+\ref{fig:class}).
+This provides more classification leverage, yielding p(Ia)=95\% \cite{materials_methods_2020}.
 By also including the model-predicted time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=94\% \cite{materials_methods_2020}.
-%This is corroborated by the limited data available for the transient. In color -magnitude space it displays best agreement with the Type Ia population (Fig 1). 
 An improved classification can be achieved with spectroscopy and multi-band photometry upon arrival of the fourth image.
-
-%The galaxy has very low SFR=XX and based on stellar ages stopped forming stars ~X.X Gyr earlier. This is a proto typical early type galaxy progenitor.
-
-%%%%%% ORIGINAL Classification text
-% To evaluate the age of each transient image (and therefore constrain the lensing time delay between images), it is valuable to have a firm determination of the transient's class.
-The range of possible transients is broad, encompassing normal SNe, superluminous SNe \citep{galyam_luminous_2019}, fast transients \citep{berger_fast_2013, drout_rapidly_2014}, and even gravitational microlensing events \citep{rodney_two_2018,kelly_extreme_2018}.
-Identifying the transient type makes it possible to use the well-developed library of spectrophotometric SN models \citep[e.g.][]{kessler_models_2019} for the time delay measurement.
-%  The first-order distinction that is most important is between a Type Ia SN--understood to be the explosion of a white dwarf star in a binary system--and core collapse SN (CCSN)--the end-point of a star with mass $\gtrsim 10$M$_{\odot}$.
-Given the limited data available for this transient, we will not attempt a more fine-grained classification, though in principle that could be achieved with spectroscopy and multi-band photometry upon arrival of the final image.
-
-% As a first step, we can use inferences from the lens model to establish a strong prior against any of the various rapidly evolving and low-luminosity stellar transient classes.  
-% The expected time delays between the images are $\sim100$ observer-frame days, 
-% but we see that three images of the transient are visible simultaneously.
-% From this we can infer that the visibility time of the transient in the $z=1.95$ rest-frame must be at least $\sim$30 days. 
-% Similarly, with expected magnifications in the vicinity of $\mu\sim10$, the measured apparent magnitudes near 23 AB mag translate to a rest-frame absolute magnitude near $M_B \sim-19.5$ mag (too bright to be a nova, luminous blue variable, or other low-luminosity stellar transient).
-% Taken together, these indicators strongly suggest that the transient is a supernova (SN).
-
-% Although we have invoked the lens model in this analysis, note that the inferences are not strongly dependent on the specific lens model predictions.
-To make the observed transient images consistent with a fast or low-luminosity transient, the time delays and/or magnifications would have to be changed by more than a factor of 2.
-In the analysis to follow, we will work under the assumption that the transient is a SN.
-
-% \subsection{Host galaxy properties}
-% \label{ss:host}
-
-% We first seek to classify this transient {\it circumstantially}, using measured properties of the host galaxy stellar population to infer the type.
-Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.
-We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \citep{mannucci_rates_2005,foley_classifying_2013}.
-In the case of the host galaxy MRG0138, we have very stringent limits on the star formation rate.
-This galaxy is a high-mass but very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.
-The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr,  making it highly unlikely that MRG0138 retains any significant population of massive stars \SR{this should be revised, b/c of total mass.
-Focus instead on the relative probability.
-as discussed on telecon}
-
-% Discussion from Newman et al. \citep{newman_resolving_2018-1}.
-
-% Conclusion: the host is a red-dead elliptical. It is most likely a Type Ia SN.
-
-% \subsection{Classification from Color and Brightness}
-% \label{ss:lightcurve}
-
-% Figure~\ref{fig:colormag} shows the location of \SNABC in color-magnitude space, comparing the de-magnified apparent F160W magnitude against the observed F105W-F160W color.  
-% For a source at $z=1.95$ the F160W band is centered near 5400 \AA, approximately corresponding to the Bessell V bandpass, while the F105W-F160W color approximates a U-V color. 
-% As shown in Figure~\ref{fig:colormag}, the observed photometry for \SNABC is fully consistent with the expected color and magnitude of a Type Ia SN at $z=1.95$, after correcting for lensing magnification using the $\mu$ values from Table~\ref{tab:model_evidence}.
-The magnification-corrected photometry is inconsistent with Type II SNe, which are fainter and more blue.
-\SNABC is marginally consistent with the CCSN Type Ib/Ic sub-class, although the image 2 point falls outside of the 95\% confidence region for that population.
-
-% The right panel in Figure~\ref{fig:colormag} shows that the three data points are also consistent with the expected time-dependence  of a Type Ia SN in this color-magnitude space.
-Visualizing the changing color and brightness of a SNIa at $z=1.95$ in the F105W and F160W bands, we see that it  would intersect image 2 near peak brightness and approach the image 1 and 3 photometry at roughly 80 observer-frame days after peak.
-
-% Taken together, this evidence reinforces the conclusion that \SNABC is most likely a Type Ia SN.  Although we have to adopt a magnification correction 
-% from a lens model, this conclusion is not sensitive to the choice of lens model.
-Every lens model we have evaluated locates \SNABC's un-magnified position squarely within the Type Ia region of color-magnitude space.
-% Dust is also not a confounding factor here.
-The simulations used to generate the contours in Figure~\ref{fig:colormag} include dust extinction at the source plane.
-If a significant screen of dust exists in the lens plane, this would have the effect of making the SN appear dimmer and more red, so correcting for that extinction would move the \SNABC requiem points upward and leftward on this plot, causing it to be even more strongly associated with the Type Ia region.
-
-% \SR{TODO: add an appendix explaining the sims}
 
@@
 Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images, and break remaining parameter degeneracies (see supplemental materials).
-%These constraints represent an upper limit on the age (and therefore time delay) uncertainties, but they would still deliver an uncertainty of $\sim0.3\%$ on the predicted $\sim6000$ day delay.
-While already dwarfed by the expected lens model uncertainty, constraints on the intrinsic SN light curve parameters gained from exquisite photometry of the future fourth image of Requiem could improve this even further.
 
 Future large-scale surveys such as the Vera C. Rubin Observatory 
-%Legacy Survey of Space and Time (LSST) 
-and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their duration \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
-However, many of these lensed SN will require substantial follow-up resources to be cosmologically useful.
+and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
+However, many of these lensed SN will require substantial follow-up resources to be made cosmologically useful.
 Furthermore, almost all will have significantly shorter
-delays (of order 10-100 days) and therefore higher relative uncertainties than \SNABC.  Since it is the {\it fractional} time delay uncertainty that 
+delays (of order 10--100 days) and therefore higher relative uncertainties than \SNABC.  Since it is the {\it fractional} time delay uncertainty that 
 propagates through to any time delay distance measurement, the extraordinarily long time delays of cluster-lensed SNe like SN Requiem can deliver significantly better time delay precision, with comparable observational cost.
@@
 Because of the unusually large redshift ratio of \SNABC, the constraints
-%on dark energy equation of state parameters ($w_0$, $w_a$) 
 from the \reqlike sample are nicely complementary to the low-$z$ Rubin Observatory and high-$z$ Roman Space Telescope samples. 
@@
 As \SNABC shows, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
-After that, all we need is patience.
+%After that, all we need is patience.
+
+HST observations enabled us to find this SN.
+We anticipate that HST may be de-orbited and make its final plummet to Earth around the time of the reappearance of \TNSname, so we coin the name {\it SN  Requiem} as an ode to the vast new discovery space that HST continues to unveil.
 
@@
 
-%BibTeX users: After compilation, comment out the following two lines and paste in
-% the generated .bbl file. 
 \clearpage
@@
 Panels \emph{ei} indicate the location of the fourth image predicted to appear in $\approx$2037.
-All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.}
+All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.}
 
@@
 \clearpage
-\begin{figure}[h]
+\begin{figure}
   \centering
@@
     \caption{Classification information for SN Requiem based on its position in color-magnitude space.
-(left) Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green).
-These population contours are drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
+\emph{Left:} Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green), drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
 Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
 Open markers show the observed photometry of the SN.
-Dotted vertical lines mark the magnification correction based on the lens modeling, terminating in closed markers with error bars that show the magnitude uncertainty, which is dominated by the lens modeling uncertainty.
-(right) The evolution of a typical Type Ia SN at $z=1.95$ in observed color-mag space is shown by a colored line, with the color indicating SN age in observer-frame days relative to peak brightness.
+Dotted vertical lines mark the lensing magnification correction, terminating in closed markers and solid bars that indicate the magnification in our preferred lens model and its systematic uncertainty, respectively.
+\emph{Right:} The evolution of a typical Type Ia SN at $z=1.95$ in observed color-brightness space is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
 White diamonds correspond to the times labeled on the colorbar at right.
 Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}.
-An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
+    %An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
     \label{fig:class}
@@
     \caption{  
-    The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation of state parameters ($w_0, w_a$).
+    The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation-of-state parameters ($w_0, w_a$).
 Dashed lines and the white marker show the input values (upper right of the top panels) that were used for this simulation.
@@
 The left and right columns assume a 5\% and 2\% contribution to the distance uncertainty from modeling the lens potential, respectively.
-Improving the lens modeling tightens the cosmological constraints for all three samples, but the improvement for the \SNABC-like sample is the most significant.
-This is simply because the long time delay baseline for \SNABC makes the time delay uncertainty negligible, raising the ceiling for cosmological improvement with tighter lens modeling constraints.
     In order to isolate the plotted parameters, all contours are constructed assuming perfect knowledge of the cosmological parameters that are not shown. 
@@
 \midrule
-\textit{1}  & $112^{+20}_{-38}$ & -- & $3.9\pm0.5$ & --\\
-\textit{2} & $-27^{+26}_{-6}$ & $139^{+63}_{-23}$ & $7\pm3$ & $101\pm62$ \\
-\textit{3} & $88^{+15}_{-15}$ & $16^{+19}_{-19}$ & $5\pm1$ & $19\pm34$ \\
+\textit{1}  & $99^{+27}_{-29}$ & -- & $3.9\pm0.5$ & --\\
+\textit{2} & $-19^{+21}_{-13}$ & $114^{+39}_{-42}$ & $7\pm3$ & $101\pm62$ \\
+\textit{3} & $87^{+15}_{-13}$ & $11\pm23$ & $5\pm1$ & $19\pm34$ \\
 \textit{4} & -- & -- & $0.4\pm0.2$ & $7760\pm540$\\
@@
 
-\bibliography{references}
-
-\bibliographystyle{Science}
-
+%BibTeX users: After compilation, comment out the following two lines and paste in
+% the generated .bbl file. 
+%%%%%%%%%%%% Bibliography
+%\bibliography{references}
+%\bibliographystyle{Science}
+\begin{thebibliography}{10}
+
+\bibitem{riess_observational_1998}
+A.~G. Riess, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 116}, 1009
+  (1998).
+
+\bibitem{perlmutter_measurements_1999}
+S.~Perlmutter, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 517}, 565
+  (1999).
+
+\bibitem{Riess_large_2019}
+A.~G. Riess, S.~Casertano, W.~Yuan, L.~M. Macri, D.~Scolnic, {\it The
+  Astrophysical Journal\/} {\bf 876}, 85 (2019).
+
+\bibitem{amendola_cosmology_2013}
+L.~Amendola, {\it et~al.\/}, {\it Living Reviews in Relativity\/} {\bf 16}, 6
+  (2013).
+
+\bibitem{spergel_wide_2015}
+D.~Spergel, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:1503.03757}
+  (2015).
+
+\bibitem{Ivezic_lsst_2019}
+Ivezic, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 873}, 111
+  (2019).
+
+\bibitem{aghanim_planck_2018}
+{Planck Collaboration}, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf
+  arXiv:1807.06209} (2018).
+
+\bibitem{verde_tensions_2019}
+L.~Verde, T.~Treu, A.~G. Riess, {\it Nature Astronomy\/} {\bf 3}, 891 (2019).
+
+\bibitem{einstein_lens_1936}
+A.~Einstein, {\it Science\/} {\bf 84}, 506 (1936).
+
+\bibitem{refsdal_possibility_1964}
+S.~Refsdal, {\it Monthly Notices of the Royal Astronomical Society\/} {\bf
+  128}, 307 (1964).
+
+\bibitem{coe_cosmological_2009}
+D.~Coe, L.~A. Moustakas, {\it The Astrophysical Journal\/} {\bf 706}, 45
+  (2009).
+
+\bibitem{linder_lensing_2011}
+E.~V. Linder, {\it Physical Review D\/} {\bf 84}, 123529 (2011).
+
+\bibitem{suyu_cosmology_2014}
+S.~H. Suyu, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 788}, L35
+  (2014).
+
+\bibitem{bonvin_cosmograil_2019}
+V.~Bonvin, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 629}, A97
+  (2019).
+
+\bibitem{wong_h0licow_2019}
+K.~C. Wong, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:1907.04869}
+  (2019).
+
+\bibitem{suyu_cosmological_2018}
+S.~H. Suyu, T.-C. Chang, F.~Courbin, T.~Okumura, {\it Space Science Reviews\/}
+  {\bf 214}, 91 (2018).
+
+\bibitem{kelly_multiple_2015}
+P.~L. Kelly, {\it et~al.\/}, {\it Science\/} {\bf 347}, 1123 (2015).
+
+\bibitem{goobar_iptf16geu:_2017}
+A.~Goobar, {\it et~al.\/}, {\it Science\/} {\bf 356}, 291 (2017).
+
+\bibitem{kelly_sn_2016}
+P.~L. Kelly, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 831}, 205
+  (2016).
+
+\bibitem{dhawan_magnification_2019}
+S.~Dhawan, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
+  Society\/} 491, 2639 (2020).
+
+\bibitem{newman_resolving_2018}
+A.~B. Newman, S.~Belli, R.~S. Ellis, S.~G. Patel, {\it The Astrophysical
+  Journal\/} {\bf 862}, 126 (2018).
+
+\bibitem{ebeling_macs_2001}
+H.~Ebeling, A.~C. Edge, J.~P. Henry, {\it The Astrophysical Journal\/} {\bf
+  553}, 668 (2001).
+
+\bibitem{materials_methods_2020}
+Materials and methods are available as supplementary materials at the {Science}
+  website.
+
+\bibitem{jullo_bayesian_2007}
+E.~Jullo, {\it et~al.\/}, {\it New Journal of Physics\/} {\bf 9}, 447 (2007).
+
+\bibitem{kneib_lenstool_2011}
+J.-P. Kneib, {\it et~al.\/} LENSTOOL: A Gravitational Lensing Software for Modeling Mass Distribution of Galaxies and Clusters, ascl:1102.004 (2011).
+
+\bibitem{woosley_type_2007}
+S.~E. Woosley, D.~Kasen, S.~Blinnikov, E.~Sorokina, {\it The Astrophysical
+  Journal\/} {\bf 662}, 487 (2007).
+
+\bibitem{kasen_type_2009}
+D.~Kasen, S.~E. Woosley, {\it The Astrophysical Journal\/} {\bf 703}, 2205
+  (2009).
+
+\bibitem{oguri_gravitationally_2010}
+M.~Oguri, P.~J. Marshall, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 405}, 2579 (2010).
+
+\bibitem{goldstein_rates_2019}
+D.~A. Goldstein, P.~E. Nugent, A.~Goobar, {\it The Astrophysical Journal
+  Supplement Series\/} {\bf 243}, 6 (2019).
+
+\bibitem{wojtak_magnified_2019}
+R.~Wojtak, J.~Hjorth, C.~Gall, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 487}, 3342 (2019).
+
+\bibitem{wang_determination_2006}
+X.~Wang, L.~Wang, R.~Pain, X.~Zhou, Z.~Li, {\it The Astrophysical Journal\/}
+  {\bf 645}, 488 (2006).
+
+\bibitem{gonzaga_drizzlepac_2012}
+S.~Gonzaga, {et al.}, {\it The {DrizzlePac} handbook\/}, HST Data Handbook (2012).
+
+\bibitem{the_astropy_collaboration_astropy_2018}
+{The Astropy Collaboration}, {\it et~al.\/}, {\it The Astronomical Journal\/}
+  {\bf 156}, 123 (2018).
+
+\bibitem{weilbacher_data_2020}
+P.~M. Weilbacher, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:2006.08638}
+  (2020).
+
+\bibitem{bacon_muse_2017}
+R.~Bacon, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 608}, A1
+  (2017).
+
+\bibitem{soto_zap_2016}
+K.~T. Soto, S.~J. Lilly, R.~Bacon, J.~Richard, S.~Conseil, {\it Monthly Notices
+  of the Royal Astronomical Society\/} {\bf 458}, 3210 (2016).
+
+\bibitem{piqueras_mpdaf_2019}
+L.~Piqueras, {\it et~al.\/}, {\it Astronomical data analysis software and
+  systems {XXVI}\/}, M.~Molinaro, K.~Shortridge, F.~Pasian, eds. (2019), vol.
+  521 of {\it Astronomical society of the pacific conference series\/}, p. 545.
+
+\bibitem{mahler_strong_2018}
+G.~Mahler, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 473}, 663 (2018).
+
+\bibitem{lagattuta_probing_2019}
+D.~J. Lagattuta, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 485}, 3738 (2019).
+
+\bibitem{richard_mass_2014}
+J.~Richard, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 444}, 268 (2014).
+
+\bibitem{richard_locuss_2010}
+J.~Richard, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
+  Society\/} {\bf 404}, 325 (2010).
+
+\bibitem{mannucci_supernova_2005}
+F.~Mannucci, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 433}, 807
+  (2005).
+
+\bibitem{newman_resolving_2018-1}
+A.~B. Newman, S.~Belli, R.~S. Ellis, S.~G. Patel, {\it The Astrophysical
+  Journal\/} {\bf 862}, 125 (2018).
+
+\bibitem{foley_classifying_2013}
+R.~J. Foley, K.~Mandel, {\it The Astrophysical Journal\/} {\bf 778}, 167
+  (2013).
+
+\bibitem{smartt_progenitors_2009}
+S.~J. Smartt, {\it Annual Review of Astronomy and Astrophysics\/} {\bf 47}, 63
+  (2009).
+
+\bibitem{li_rates_2012}
+X.~Li, J.~Hjorth, J.~Richard, {\it Journal of Cosmology and Astroparticle
+  Physics\/} {\bf 2012}, 015 (2012).
+
+\bibitem{barbary_sncosmo_2016}
+K.~Barbary, {\it et~al.\/}, Sncosmo/{Sncosmo}: {V1}.4.0 (2016).
+
+\bibitem{rodney_type_2014}
+S.~A. Rodney, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 148}, 13
+  (2014).
+
+\bibitem{guy_salt2:_2007}
+J.~Guy, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 466}, 11 (2007).
+
+\bibitem{pierel_extending_2018}
+J.~D.~R. Pierel, {\it et~al.\/}, {\it Publications of the Astronomical Society
+  of the Pacific\/} {\bf 130}, 114504 (2018).
+
+\bibitem{kessler_snana:_2009}
+R.~Kessler, {\it et~al.\/}, {\it Publications of the Astronomical Society of
+  the Pacific\/} {\bf 121}, 1028 (2009).
+
+\bibitem{frieman_sloan_2008}
+J.~A. Frieman, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 135}, 338
+  (2008).
+
+\bibitem{sako_sloan_2008}
+M.~Sako, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 135}, 348
+  (2008).
+
+\bibitem{dandrea_type_2010}
+C.~B. D'Andrea, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 708},
+  661 (2010).
+
+\bibitem{astier_supernova_2006}
+P.~Astier, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 447}, 31
+  (2006).
+
+\bibitem{hamuy_carnegie_2006}
+M.~Hamuy, {\it et~al.\/}, {\it Publications of the Astronomical Society of the
+  Pacific\/} {\bf 118}, 2 (2006).
+
+\bibitem{stritzinger_he-rich_2009}
+M.~Stritzinger, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 696},
+  713 (2009).
+
+\bibitem{morrell_carnegie_2012}
+N.~I. Morrell, {\it Death of massive stars: {Supernovae} and gamma-ray
+  bursts\/}, P.~Roming, N.~Kawai, E.~Pian, eds. (2012), vol. 279 of {\it {IAU}
+  symposium\/}, pp. 361--362.
+
+\bibitem{pierel_turning_2019}
+J.~D.~R. Pierel, S.~Rodney, {\it The Astrophysical Journal\/} {\bf 876}, 107
+  (2019).
+
+\bibitem{huber_strongly_2019}
+S.~Huber, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 631}, A161
+  (2019).
+
+\bibitem{goldstein_precise_2018}
+D.~A. Goldstein, P.~E. Nugent, D.~N. Kasen, T.~E. Collett, {\it The
+  Astrophysical Journal\/} {\bf 855}, 22 (2018).
+
+\bibitem{foxley-marrable_impact_2018}
+M.~Foxley-Marrable, T.~E. Collett, G.~Vernardos, D.~A. Goldstein, D.~Bacon,
+  {\it Monthly Notices of the Royal Astronomical Society\/} {\bf 478}, 5081
+  (2018).
+
+\bibitem{bonvin_impact_2019}
+V.~Bonvin, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 621}, A55
+  (2019).
+
+\bibitem{kochanek_quantitative_2004}
+C.~S. Kochanek, {\it The Astrophysical Journal\/} {\bf 605}, 58 (2004).
+
+\bibitem{vernardos_joint_2018}
+G.~Vernardos, {\it Monthly Notices of the Royal Astronomical Society\/} {\bf
+  480}, 4675 (2018).
+
+\bibitem{hsiao_k_2007}
+E.~Y. Hsiao, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 663}, 1187
+  (2007).
+
+\bibitem{kessler_results_2010}
+R.~Kessler, {\it et~al.\/}, {\it Publications of the Astronomical Society of
+  the Pacific\/} {\bf 122}, 1415 (2010).
+
+\bibitem{mosher_cosmological_2014}
+J.~Mosher, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 793}, 16
+  (2014).
+
+\end{thebibliography}
+
+%%%%%%%%%%%% Acknowledgents
 \section*{Acknowledgments}
@@
 Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).
-Support for this work was provided by NASA through grant number HST-GO-15663 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
+{\bf Funding:} Support for this work was provided by NASA through grant numbers HST-GO-15663 and HST-AR-15050 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
 under NASA contract NAS 5-26555.
-The Cosmic Dawn Center of Excellence funded by the Danish National Research Foundation under grant No.
+The Cosmic Dawn Center of Excellence is funded by the Danish National Research Foundation under grant No.
 140.
+This work was supported by NASA Headquarters under the NASA Future Investigators in Earth and Space Science and Technology (FINESST) award 80NSSC19K1414.
+{\bf Author Contributions:} 
+Conceptualization, S.A.R., G.B., and S.T.; Methodology, S.A.R., J.D.R.P., J.R., and K.F.O.; Investigation, G.B., J.R., S.T., M.A., and K.E.W.; Writing - Original Draft, G.B.\ and S.T.; Writing - Review \& Editing, S.A.R., G.B., J.D.R.P., J.R., S.T., K.F.O., M.A., and K.E.W.; Visualization, S.A.R., G.B., J.D.R.P., J.R., K.F.O.; Supervision, G.B., S.T., and K.E.W.; Funding Acquisition, K.E.W.
+{\bf Competing Interests:} All authors declare no competing interests.
+{\bf Data and Materials Availability:} All HST images used in this work are available from the Mikulski Archive for Space Telescopes (mast.stsci.edu).
+All VLT MUSE spectroscopic data used in this work are available from  the ESO Archive Science Portal (archive.eso.org).
+All high-level science products (photometry, lens model inputs, etc.) are available in the main text or the supplementary materials.
+All software tools used for primary analysis tasks are publicly available, as indicated in the text.
 
@@
 Supplementary Text\\
-Figs. S1 to S9\\
+Figures S1 to S8\\
 Tables S1 to S7\\
-References \textit{(4-10)}
+References \textit{(32-68)}
 \clearpage
@@
 \renewcommand{\thefigure}{S\arabic{figure}}
+
+\setcounter{page}{1}
+
+\section*{Supplementary Materials for}
+{\bf \large A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
+
+\author{
+ Steven A. Rodney$^{1\ast}$, 
+ Gabriel Brammer$^{2\ast}$,  
+ Justin D.\,R.~Pierel$^{1}$, 
+ Johan Richard$^{3}$, 
+ Sune Toft$^{2}$,  
+ Kyle F. O'Connor$^{1}$, 
+ Mohammad Akhshik$^{4}$, 
+ Katherine E. Whitaker$^{2,4,5}$  \\
+\normalsize{$^{1}$Department of Physics \& Astronomy, University of South Carolina,} \normalsize{ Columbia, SC 29208, USA}\\
+\normalsize{$^{2}$Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen,} \normalsize{Lyngbyvej 2, Copenhagen \O\ 2100 Denmark}\\
+\normalsize{$^{3}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
+\normalsize{$^{4}$Department of Physics, University of Connecticut,} \normalsize{Storrs, CT 06269, USA}\\
+\normalsize{$^{5}$Department of Astronomy, University of Massachusetts,} \normalsize{Amherst, MA 01003, USA}\\
+\normalsize{$^\ast$To whom correspondence should be addressed;}\\ \normalsize{E-mail:  srodney@sc.edu, gabriel.brammer@nbi.ku.dk}
+}
+
+\subsection*{This PDF file includes:}
+
+Materials and Methods\\
+Supplementary Text\\
+Figures S1 to S8\\
+Tables S1 to S7\\
+References \textit{(32-68)}
+
+\clearpage
+
 % For your review copy (i.e., the file you initially send in for
@@
 \section*{Materials and Methods}
-%\todo[inline]{I'm not really sure what this section is for, or if we need it (commented out is the description from science about what this should be)}
-% The materials and methods section should provide sufficient information to allow replication of the study.
-It should be cited at relevant points in the text using a citation number that refers to a note in the reference list that reads “Materials and methods are available as supplementary materials at the Science website.” Study design should be described in detail and descriptions of reagents and equipment should facilitate replication (for example source and purity of reagents should be specified, there should be evidence that antibodies have been validated, and cell lines should be authenticated).
-Clinical and preclinical studies should include a section titled Experimental Design at the beginning of materials and methods in which the objectives and design of the study, as well as prespecified components, are described.
-Statistical methods must be described with enough detail to enable a knowledgeable reader with access to the original data to verify the results.
-The values for N, P, and the specific statistical test performed for each experiment should be included in the appropriate figure legend or main text.
-Please see our editorial policies for additional guidelines for specific types of studies as well as further details on reporting of statistical analysis.
-For papers in the life sciences that involve a method that would benefit from the publication of a step-by-step protocol, we encourage authors to consider submitting a detailed protocol to our collaborative partner Bio-protocol.
 
@@
 The observations of MRG0138 used in this work are  summarized in Table \ref{tab:observations}.
-For this work, all HST observations were processed using the {\tt Drizzlepac} software utilities \cite{gonzaga_drizzlepac_2012}, aligned to a common astrometric reference frame and resampled to a pixel scale of 0.1 arcseconds per pixel.
-We then identified isolated and unsaturated stars in each image and used them to create an effective point spread function (ePSF) with $4\times$ oversampling, using the {\tt photutils} package from the {\tt astropy} software suite \cite{astropy_astropy_2013}.
+We processed all HST observations using the {\tt Drizzlepac} software utilities \cite{gonzaga_drizzlepac_2012}, aligned to a common astrometric reference frame and resampled to a pixel scale of 0.1 arcseconds per pixel.
+We then identified isolated and unsaturated stars in each image and used them to create an effective point spread function (ePSF) with $4\times$ oversampling, using the {\tt photutils} package from the {\tt astropy} software suite \cite{the_astropy_collaboration_astropy_2018}.
 
 To measure the SN photometry we followed two tracks.
-As our primary method we performed ePSF fitting directly on the F105W (Y band) and F160W (H band) images where the SN was apparent.
+As our primary method we performed ePSF fitting directly on the F105W ($Y$ band) and F160W ($H$ band) images where the SN was apparent.
 This ePSF fitting allowed for a constant background flux to account for both the sky brightness and the background light of the cluster and host galaxy.
-As a second approach, we created ``pseudo-difference images'' by rescaling the later F110W and F140W images collected in 2019 (in which the SN is not present).
+As a second approach, we created ``pseudo-difference images'' by re-scaling the later F110W and F140W images collected in 2019 (in which the SN is not present).
 The transmission functions of the F110W and F140W filters are broader than F105W and F160W, and do not strictly overlap in wavelength.
@@
 Both sets of photometry agree to within one standard deviation.
-The reported photometry in Table~\ref{tab:photometry} are the measurements from the first method (collected directly from the unsubtracted images).
-
-\begin{table}[h]
+The reported photometry in Table~\ref{tab:photometry} are the measurements from the first method (collected directly from the un-subtracted images).
+Also reported in Table~\ref{tab:photometry} are flux densities and uncertainties measured within $D=0.^{\prime\prime}7$ circular apertures at the position of the SN1 image in the 2019 \textit{HST} visits where the SN has faded below the detection threshold.
+
+\begin{table}[ht]
 \centering
@@
     \multicolumn{1}{c}{Telescope} & \multicolumn{1}{c}{Instrument} & \multicolumn{1}{c}{$\lambda_\mathrm{obs}$} & \multicolumn{1}{c}{UT Date} & \multicolumn{1}{c}{MJD} & \multicolumn{1}{c}{SN} & \multicolumn{1}{c}{Exp.
-Time (s)}\\
-
+Time}\\
+ & & & & & & \multicolumn{1}{c}{[s]}\\
 \midrule
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 SN1 & 58677.87 & F110W ($Y$) & 0.01  $\pm$ 0.02 \\
-SN1 & 58678.93 & F140W ($H$) & 0.02  $\pm$ 0.02 \\
+SN1 & 58678.93 & F140W ($JH$) & 0.02  $\pm$ 0.02 \\
 SN1 & 58683.89 & F125W ($J$) & 0.02  $\pm$ 0.03 \\
@@
 available as part of the program 0103.A-0777(A) (PI: Edge).
-Three exposures of 970 sec each were taken with a small dithering offset and 90 degree rotations in between.
+Three exposures of 970\,sec each were taken with a small dithering offset and 90 degree rotations in between.
 This dataset was reduced and analysed using the MUSE data reduction pipeline v.2.7 \cite{weilbacher_data_2020} for basic calibration (bias, flat-field, wavelength, LSF, geometry) as well as flux calibration, sky subtraction and astrometry.
@@
 
-In order to correctly estimate the magnification factors, time delays, and predict the appearance of the future images of MRG0138-SN we need to precisely model the mass distribution in the MRG0138 cluster core.
+In order to correctly estimate the magnification factors, time delays, and predict the appearance of the future images of \SNABC we need to precisely model the mass distribution in the MACSJ0138 cluster core.
 To do so we make use of the latest version of \lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and error on each parameter of the mass distribution.
@@
 The strong-lensing constraints used are the locations of multiple images found in HST and MUSE/VLT.
-More specifically we group them into 3 systems: (a) the 4 images of the quiescent galaxy hosting MRG0138-SN, (b) the 3 observed images of MRG0138-SN assumed at the same redshift, and (c) the diffuse arc-like structure identified in HST and confirmed as an [OII] emitter in the VLT/MUSE data (see previous section).
-The locations and redshifts used in the lens model are summarised in Table \ref{tab:mulimages}.
-
-\begin{table}[]
-    \centering
-    \begin{tabular}{rccl}
+More specifically we group them into 3 systems: (a) the 4 images of the quiescent galaxy hosting MRG0138-SN, (b) the 3 observed images of \SNABC assumed to be at the same redshift, and (c) the diffuse arc-like structure identified in HST and confirmed as an [O\textsc{ii}]$\lambda$3727 emitter in the VLT/MUSE datacube (see previous section).
+The image coordinates and redshifts used in the lens model are summarised in Table \ref{tab:mulimages}.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabular}{cccl}
      ID &   R.A. (deg) & Dec. (deg) & $z$ \\
@@
 H4 & 24.5176117 & $-$21.9233433 & 1.95 \\
+     \midrule
 SN1 & 24.5100753 & $-$21.9273418 & 1.95 \\
@@
 SN3 & 24.5151253 & $-$21.9306659 & 1.95 \\
+     \midrule
 3.1 & 24.5169659 & $-$21.9234814 & 0.7663 \\
@@
 The cluster mass modelling is performed similarly to other massive strong lensing clusters observed with HST \cite{richard_mass_2014}.
-In summary, the total mass distribution is parametrised as a combination of multiple dPIE (double Pseudo Isothermal Elliptical) profiles describing both cluster-scale and galaxy-scale dark matter haloes.
+In summary, the total mass distribution is parametrized as a combination of multiple dPIE (double Pseudo Isothermal Elliptical) profiles describing both cluster-scale and galaxy-scale dark matter haloes.
 dPIE are elliptical isothermal profiles with both a core and a cut radius where the density flattens and drops respectively.
 In the case of MRG0138 the mass distribution is dominated by a single mass concentration centered on its Brightest Cluster Galaxy (BCG).
-We therefore use a single cluster-scale halo at a fixed cut radius of 1 Mpc.
-We add a single galaxy-scale halo on each cluster member, where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15 kpc).
-Cluster members were identified by the combination of red sequence selection (based on the F814W-F160W color) and MUSE spectroscopy.
+We therefore use a single cluster-scale halo at a fixed cut radius of 1\,Mpc.
+We add a single galaxy-scale halo on each cluster member, where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15\,kpc).
+Cluster members were identified by the combination of red sequence selection (based on the F814W$-$F160W color) and MUSE spectroscopy.
 
@@
 We individually optimise the $\sigma$ and $r_{\rm cut}$ parameters for 4 specific galaxies which are not expected to follow the aforementioned scaling relations: the BCG and three perturbers P1 to P3.
-These perturbers are either blue gas-stripped galaxies infalling into the cluster core, and/or located very close to the images of the quiescent galaxy, perturbing its apparent morphology with additional lensing.
+These perturbers are either blue gas-stripped galaxies infalling into the cluster core, and/or located very close to the images of the \SNABC host galaxy, perturbing its apparent morphology with additional lensing.
 This choice of perturbers is similar to the ones used in the model by \cite{newman_resolving_2018}.
@@
 
-\begin{table}[]
+\begin{table}[ht]
     \centering
@@
     Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
-    & [2000.0] & [2000.0] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
+    & [arcsec] & [arcsec] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
 \hline
@@
     \caption{Best fit model parameters for the mass distribution.
-From left to right: mass component, dPIE center and global shape (ellipticity and orientation), velocity dispersion, core and cut radius.
+From left to right: mass component, position relative to cluster center ($\Delta$R.A.
+and $\Delta$Dec.), dPIE shape (ellipticity and orientation), velocity dispersion, core and cut radius.
 The final row
@@
 
-\begin{table}[]
+\begin{table}[tb]
     \centering
@@
 
-Although we have invoked the lens model in this analysis, note that the inferences are not strongly dependent on the specific lens model predictions.
+Although we have invoked the lens model in this analysis, we note that the inferences are not strongly dependent on the specific lens model predictions.
 To make the observed transient images consistent with a fast or low-luminosity transient, the time delays and/or magnifications would have to be changed by more than a factor of 2.
-In the analysis to follow, we will work under the assumption that the transient is a SN.
+In the analysis to follow, we will work under the assumption that \SNABC is a SN.
 
@@
 Although Type Ia SNe are found in all types of galaxies, CCSNe are limited to galaxies with relatively young stellar populations.
-We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \cite{mannucci_rates_2005}.
-In the case of the host galaxy MRG0138, we have a very well-constrained spectral energy distribution (SED) extending out to far-infrared wavelengths with Spitzer IRAC data \cite{newman_resolving_2018,newman_resolving_2018-1}.
+We can therefore infer some information about the SN type using the observed host properties combined with knowledge of the relative rates of Type Ia and CCSNe in different stellar populations \cite{mannucci_supernova_2005}.
+In the case of the host galaxy MRG0138, we have a very well-constrained spectral energy distribution (SED) extending out to far-infrared wavelengths with \textit{Spitzer} IRAC data \cite{newman_resolving_2018,newman_resolving_2018-1}.
 From the SED fitting we derived the host galaxy's 
@@
 The MRG-M0138 galaxy has high mass ($\log_{10}(M/M_{\odot})=11.7$) but is a very quiescent galaxy, with a specific star formation rate of $\sim10^{-11.3}$ yr$^{-1}$  and a stellar population that is well-matched by an exponential star formation history with an age of $1.4$ Gyr \cite{newman_resolving_2018}.
-The massive stars that end as CCSN explosions have main-sequence lifetimes of $\lesssim 40$ Myr \cite{smartt_progenitors_2009},  making it unlikely that CCSN progenitors make up a significant fraction of the MRG-M0138 stellar population---though the relatively high total stellar mass makes it possible that pockets of young stars are present.
+The massive stars that end as CCSN explosions have main-sequence lifetimes of $<40$ Myr \cite{smartt_progenitors_2009},  making it unlikely that CCSN progenitors make up a significant fraction of the MRG-M0138 stellar population---though the high total stellar mass makes it possible that pockets of young stars are present.
 We define classification probabilities based on the projected SN rate for each SN sub-class, derived from the host galaxy's stellar mass and star formation rate \cite{li_rates_2012}.
@@
         a. Host color-mag & Host galaxy rest-frame $M_K$, $B-K$ & $\mu_{\rm host}$ & - & 0.75 & 0.19 & 0.06\\
-        b. Host stellar pop. & Host galaxy mass, star form. rate & $\mu_{\rm host}$ & - & 0.62 & 0.27 & 0.09 \\
+        b. Host stellar pop. & Host galaxy mass \& star formation rate & $\mu_{\rm host}$ & - & 0.62 & 0.27 & 0.09 \\
         %SN color-mag^{*}$ & SN F105W-F160W color, $m_{\rm F160W}$ & SN magnification & Host: stellar pop. & $0.95\pm0.03$ & $0.01\pm0.01$ & $0.04\pm0.04$\\
-        c. SN color-mag & SN color (Y-H), $m_{\rm F160W}$ & $\mu_{\rm SN}$ & b & 0.95 & 0.01 & 0.04\\
-        d. SN light curve & SN light curves (Y and H) & $\mu_{\rm SN}$, $\Delta t_{\rm SN}$ & b & 0.94 & 0.06 & $<$0.01 \\
+        c. SN color-mag & SN F105W-F160W color, $m_{\rm F160W}$ & $\mu_{\rm SN}$ & b & 0.95 & 0.01 & 0.04\\
+        d. SN light curve & F105W and F160W SN light curves & $\mu_{\rm SN}$, $\Delta t_{\rm SN}$ & b & 0.94 & 0.06 & $<$0.01 \\
     \end{tabular}
@@
     \centering
-    \includegraphics{Paper/Figures/colormag_classification_supplement.pdf}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/colormag_classification_supplement.pdf}
     \caption{The position of \SNABC in color-magnitude space.
@@
 This figure shows that the limited photometric data can be reasonably well fit by at least one model from any of these three sub-classes.
-However, the range of model parameters that allow such a fit to the data is nuch more limited for the heterogeneous CCSN types than for the Type Ia class.
+However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types than for the Type Ia class.
 To compute the posterior probability distribution we adopt priors for each of the three SN classes, again using the classification probabilities derived from the \SNABC host galaxy stellar population properties (row b of Table~\ref{tab:classification}).
@@
 
-We first attempt to constrain the relative time delays using the color of each observed image, which is independent of the lens model and possible because the scenario of gravitation lensing is generally achromatic.
+We first attempt to constrain the relative time delays using the color of each observed image, which is independent of the lens model and possible because the phenomenon of gravitational lensing is intrinsically achromatic.
 One important caveat to this principle is that {\it microlensing} effects are not generally achromatic, because the microlensing caustics may cause differential magnification on the scale of the SN radius \cite{goldstein_precise_2018,foxley-marrable_impact_2018,bonvin_impact_2019}.
@@
 This method fits the age of each image simultaneously, while also varying the SN model parameters.
-The result of this process is seen in Figure \ref{fig:colorcurves}.
-Joint and marginalized posterior distributions
-from SNTD for SALT2 parameters and measured ages for each image are shown in Figure \ref{fig:corner_cfit}.
-The measured colors intersect the model at two distinct locations for images 1 and 2 of \SNABC, meaning there are two plausible ages that cause a double peaked posterior distribution (Figure \ref{fig:corner_cfit}).
-This is caused by a model parameter degeneracy that could be broken in a way independent of the lens model if a sufficiently precise light curve of image 4 is obtained in the future.
+This means we are finding a single set of SN model parameters to describe the intrinsic photometric evolution of the SN, and also finding the age (time from peak brightness) for each of the three images.
+
+The result of this process is seen in Figure \ref{fig:colorcurves}.  Joint and marginalized posterior distributions
+from SNTD for the SALT2 SN model parameters and the measured ages for each image are shown in Figure \ref{fig:corner_cfit}.
+The measured colors intersect the model at two distinct locations for images 1 and 2 of \SNABC, meaning there are two plausible ages---resulting in a double peaked posterior distribution (Fig.
+\ref{fig:corner_cfit}).
+This is caused by a model parameter degeneracy that could be broken in a way independent of the lens model if a sufficiently precise color curve of image 4 is obtained in the future.
 
@@
 
-In order to break the age degeneracies in the color-based constraints today, we need to use some information about the relative brightnesses of the \SNABC images.
-For this step we can no longer be independent of the lens models, as we must use the lens-model-predicted magnification values to de-magnify the observed magnitudes for comparison to SN models.
-
-For the five lens models described above, we correct the observed magnitude of each image using the predicted lensing magnification ($\mu$).
+In order to break the age degeneracies in the color-based constraints using only data available today, we need to use some information about the relative brightnesses of the \SNABC images.
+For this step we can no longer be independent of the lens models, as we must use the lens-model-predicted magnification values to de-magnify the observed photometry for comparison to SN models (note, however, that we again do not use any time delay information from the lens model for this method).
+
+For the five lens models (A-E) described above, we correct the observed flux density of each image (in both F105W and F160W bands) using the predicted lensing magnification ($\mu$).
 Next we employ SNTD's ``series'' method, as it is most effective for sparse sampling, to attempt a reconstruction of the intrinsic SN light curve \cite{pierel_turning_2019}.
 Once again the age of each image is constrained simultaneously, while also varying the SN model parameters.
-At this stage we adopt weak priors on the intrinsic SNIa luminosity \cite{wang_determination_2006} and SNIa color \cite{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Figure \ref{fig:lightcurves}).
+At this stage we adopt weak priors on the intrinsic SNIa luminosity \cite{wang_determination_2006} and SNIa color \cite{mosher_cosmological_2014} to help break degeneracies in the light curve model, and obtain a second constraint on the age of each SN image (Fig.
+\ref{fig:lightcurves}).
 
@@
 Using a finer sampling for these two models, we find that there is preference for model E over model C (at $\sim3.6\sigma$).
-We therefore adopt model E as our preferred model, and use the model E light curve constraints (Fig \ref{fig:corner_modelE}) to obtain joint posterior distributions with the lens-independent result from color-curve fitting (Figure \ref{fig:corner_combined}).
+This was also the model selected as the optimal lens model before unblinding, so we have reinforced the justification to adopt model E as our preferred model.
+
+%Figure \ref{fig:corner_modelE} shows our final constraints on the age of each SN image based on these simultaneous light curve fits to the magnification-corrected fluxes in F105W and F160W.
+
+As our final method to incorporate the color and brightness information together, we use the color-based posterior probability distributions (Fig. \ref{fig:corner_cfit}) as the prior for 
+the light-curve based constraints.
+In this approach, we must use only a single photometric band for the light curve constraint, so that we are not ``double-counting'' the color information by simultaneously fitting to two bands together.
+We adopt F160W as the single band, since it is close to the rest-frame V band, where the SALT2 SNIa model is very well constrained.
+The joint posterior distributions from this method are shown in Figure \ref{fig:corner_combined}.
+%As expected, these match very closely with the two-band light-curve-based fitting (Fig. \ref{fig:corner_modelE}).
 
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \begin{tabular}{crrrrrrr}
@@
 Our final age constraints for each SN image are a joint posterior between the parameter estimates from color-curve fitting (lens model independent) and light curve fitting (lens model dependent), resulting in the final time delays and uncertainties reported in table \ref{tab:time_delays} of the main text.
-Using these measured time delays, we can create a reconstructed form of the intrinsic light curve (Figure \ref{fig:full_lightcurve}) and color curve (Figure \ref{fig:full_colorcurve}) of \SNABC.
-
-The final posterior distributions for images 1 and 2 are extremely bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (Figure \ref{fig:corner_combined}).
+Using these measured time delays, we can create a reconstructed form of the intrinsic light curve (Fig.
+\ref{fig:full_lightcurve}) and color curve (Fig.
+\ref{fig:full_colorcurve}) of \SNABC.
+
+The final posterior distributions for images 1 and 2 are extremely bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (Fig.
+\ref{fig:corner_combined}).
 If this degeneracy can be broken with the precise photometry expected for the final image of Requiem, then the final time delay uncertainty for \SNABC could be below $0.1\%$.
@@
 \end{figure*}
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/corner_color_curve_fit_with_c_prior_labels.pdf}
+%    corner_color_curve_fit_with_c_prior.pdf}
+    \caption{The marginalized and joint posterior distributions for the color curve age constraints measured in this analysis.
+We use a weak prior on the SALT2 color parameter ($c$), and set the SALT2 stretch parameter ($x_1$) to 0.
+This method is fully independent of lens modeling.
+The table in the upper right lists all
+    priors, observations, and lens model information
+    used for SN age estimates in this work.  
+    Only the highlighted 
+    components were used for the constraints shown here.}
+    \label{fig:corner_cfit}
+\end{figure*}
+
 \begin{figure*}
@@
 
+%\begin{figure*}
+%    \centering
+%    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_corner_labels.pdf}
+%    \caption{The marginalized and joint posterior distributions for the light curve age constraints measured in this analysis.
+We use lens model E to de-magnify each image and fit the corrected apparent magnitudes.
+This fit includes weak priors on the absolute magnitude of a SNIa ($M_B$) and the SALT2 color parameter ($c$), and sets the SALT2 stretch parameter ($x_1$) to 0.
+%     The table in the upper right lists all 
+%    priors, observations, and lens model information
+%    used for SN age estimates in this work.  
+%    Only the highlighted 
+%    components were used for the constraints shown here.
+%    }
+%    \label{fig:corner_modelE}
+%\end{figure*}
 \begin{figure*}
     \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner.pdf}
-%    corner_color_curve_fit_with_c_prior.pdf}
-    \caption{The marginalized and joint posterior distributions for the color curve age constraints measured in this analysis.
-We use a weak prior on the SALT2 color parameter ($c$), and set the SALT2 stretch parameter ($x_1$) to 0.
-This method is fully independent of lens modeling.
-}
-    \label{fig:corner_cfit}
-\end{figure*}
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_corner.pdf}
-    \caption{The marginalized and joint posterior distributions for the light curve age constraints measured in this analysis.
-We use lens model E to de-magnify each image and fit the corrected apparent magnitudes.
-This fit includes weak priors on the absolute magnitude of a SNIa ($M_B$) and the SALT2 color parameter ($c$), and sets the SALT2 stretch parameter ($x_1$) to 0.}
-    \label{fig:corner_modelE}
-\end{figure*}
-\begin{figure*}
-    \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner.pdf}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner_labels.pdf}
     \caption{The marginalized and joint posterior distributions for the final age constraints measured in this analysis.
@@
 
-\begin{figure}[h!]
+\begin{figure}[htp]
     \centering
@@
 \end{figure}
-\begin{figure}[h!]
+\begin{figure}[hbp]
     \centering
@@
 \end{figure}
-\clearpage
-\section*{References}
+
+%\clearpage
+%\section*{References}
+
 \end{document}

### 2021-01-12 Analysis/Classification/mrg0138_sn_photometry.tex
adding some local txt files long un-committed * sn coordinates  - not sure if this is used anywhere * lensing_modelH.txt no longer called model H ?

#
# Preference for now for psf_flux fluxes from ePSF fitting, with uncertainty
# fluxerr.  The `bkgflux` is a local background that has already been 
# subtracted from the R=0.3" aperture `flux`.
# The magnification estimates `mu` have not been applied to the photometry
#
# time   band psf_flux apcorr flux fluxerr bkgflux zp zpsys id img mu muerr dtA dtB dtC
57588.03 F105W 0.0877 1.192 0.1311 0.0165 0.1902 23.9 ab 0 1.1 6.3 1.2 0 0 0
57588.03 F105W 2.3471 1.192 2.6767 0.0160 0.2033 23.9 ab 1 1.2 11.4 4.9 242 280 160
57588.03 F105W 0.1748 1.192 0.1922 0.0157 0.2776 23.9 ab 2 1.3 7.1 1.1 137 160 83
57587.97 F160W 0.6113 1.262 0.6702 0.0433 0.7207 23.9 ab 0 1.1 6.3 1.2 0 0 0
57587.97 F160W 3.5715 1.262 3.9274 0.0453 0.7528 23.9 ab 1 1.2 11.4 4.9 242 280 160
57587.97 F160W 1.1265 1.262 1.2476 0.0442 1.2159 23.9 ab 2 1.3 7.1 1.1 137 160 83

### 2021-01-15 Analysis/Classification/plot_util.py
creating classification figures

@@ -1,0 +1,418 @@
+import matplotlib.pyplot as plt
+from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
+from mpl_toolkits import mplot3d
+import numpy as np
+import pickle
+import matplotlib.lines as mlines
+
+from astropy.table import Table
+import matplotlib.gridspec as gridspec
+
+def weighted_quantile(values, quantiles, sample_weight=None, 
+                      values_sorted=False, old_style=False):
+    """ Very close to numpy.percentile, but supports weights.
+    NOTE: quantiles should be in [0, 1]!
+    :param values: numpy.array with data
+    :param quantiles: array-like with many quantiles needed
+    :param sample_weight: array-like of the same length as `array`
+    :param values_sorted: bool, if True, then will avoid sorting of
+        initial array
+    :param old_style: if True, will correct output to be consistent
+        with numpy.percentile.
+    :return: numpy.array with computed quantiles.
+    """
+    values = np.array(values)
+    quantiles = np.array(quantiles)
+    if sample_weight is None:
+        sample_weight = np.ones(len(values))
+    sample_weight = np.array(sample_weight)
+    assert np.all(quantiles >= 0) and np.all(quantiles <= 1), \
+        'quantiles should be in [0, 1]'
+
+    if not values_sorted:
+        sorter = np.argsort(values)
+        values = values[sorter]
+        sample_weight = sample_weight[sorter]
+
+    weighted_quantiles = np.cumsum(sample_weight) - 0.5 * sample_weight
+    if old_style:
+        # To be convenient with numpy.percentile
+        weighted_quantiles -= weighted_quantiles[0]
+        weighted_quantiles /= weighted_quantiles[-1]
+    else:
+        weighted_quantiles /= np.sum(sample_weight)
+    return np.interp(quantiles, weighted_quantiles, values)
+
+def plot(plot_type,x,y=None,yerr=None,xerr=None,ax=None,x_lab='',y_lab='',fontsize=18,figsize=(12,12),
+         x_name=None,y_name=None,label_name=None,ticklabelsize=16,
+         majorticklength=7,minorticklength=3,tickwidth=2,**kwargs):
+    if ax is None and plot_type != 'joint':
+        fig=plt.figure(figsize=figsize)
+        ax=fig.gca()
+
[…]

### 2021-01-19 Paper/NatureAstronomy/manual_bibliography.tex
Updates from Overleaf

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{riess_observational_1998}
\bibinfo{author}{Riess, A.~G.} \emph{et~al.}
\newblock \bibinfo{title}{Observational {Evidence} from {Supernovae} for an
  {Accelerating} {Universe} and a {Cosmological} {Constant}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{116}}, \bibinfo{pages}{1009--1038}
  (\bibinfo{year}{1998}).
%\newblock \urlprefix\url{http://stacks.iop.org/1538-3881/116/i=3/a=1009}.

\bibitem{perlmutter_measurements_1999}
\bibinfo{author}{Perlmutter, S.} \emph{et~al.}
\newblock \bibinfo{title}{Measurements of $\Omega$ and $\Lambda$ from 42 high-redshift
  supernovae}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{517}}, \bibinfo{pages}{565--586}
  (\bibinfo{year}{1999}).

\bibitem{Riess_large_2019}
\bibinfo{author}{Riess, A.~G.}, \bibinfo{author}{Casertano, S.},
  \bibinfo{author}{Yuan, W.}, \bibinfo{author}{Macri, L.~M.} \&
  \bibinfo{author}{Scolnic, D.}
\newblock \bibinfo{title}{Large {Magellanic} {Cloud} {Cepheid} {Standards}
  {Provide} a 1\% {Foundation} for the {Determination} of the {Hubble}
  {Constant} and {Stronger} {Evidence} for {Physics} beyond Λ{CDM}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{876}}, \bibinfo{pages}{85} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab1422}.

\bibitem{amendola_cosmology_2013}
\bibinfo{author}{Amendola, L.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmology and fundamental physics with the euclid
  satellite}.
\newblock \emph{\bibinfo{journal}{Living Reviews in Relativity}}
  \textbf{\bibinfo{volume}{16}}, \bibinfo{pages}{6} (\bibinfo{year}{2013}).

\bibitem{spergel_wide_2015}
\bibinfo{author}{Spergel, D.} \emph{et~al.}
\newblock \bibinfo{title}{Wide-field {InfrarRed} survey telescope-astrophysics
  focused telescope assets {WFIRST}-{AFTA} 2015 report}.
\newblock Preprint at \url{https://arxiv.org/abs/1503.03757}
%\emph{\bibinfo{journal}{arXiv e-prints}}
%  \textbf{\bibinfo{volume}{Arxiv:1503.03757}}
(\bibinfo{year}{2015}).

\bibitem{Ivezic_lsst_2019}
\bibinfo{author}{Ivezic} \emph{et~al.}
\newblock \bibinfo{title}{{LSST}: {From} {Science} {Drivers} to {Reference}
  {Design} and {Anticipated} {Data} {Products}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{873}}, \bibinfo{pages}{111} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab042c}.

\bibitem{aghanim_planck_2018}
\bibinfo{author}{{Planck Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{Planck 2018 results. {VI}. {Cosmological}
  parameters}.
%\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
%  \textbf{\bibinfo{volume}{arXiv:1807.06209}}
Preprint at \url{https://arxiv.org/abs/1807.06209} 
(\bibinfo{year}{2018}).

\bibitem{verde_tensions_2019}
\bibinfo{author}{Verde, L.}, \bibinfo{author}{Treu, T.} \&
  \bibinfo{author}{Riess, A.~G.}
\newblock \bibinfo{title}{Tensions between the early and late {Universe}}.
\newblock \emph{\bibinfo{journal}{Nature Astronomy}}
  \textbf{\bibinfo{volume}{3}}, \bibinfo{pages}{891--895}
  (\bibinfo{year}{2019}).

\bibitem{einstein_lens_1936}
\bibinfo{author}{Einstein, A.}
\newblock \bibinfo{title}{Lens-like action of a star by the deviation of light
  in the gravitational field}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{84}},
  \bibinfo{pages}{506--507} (\bibinfo{year}{1936}).

\bibitem{refsdal_possibility_1964}
\bibinfo{author}{Refsdal, S.}
\newblock \bibinfo{title}{On the {Possibility} of {Determining} {Hubble}'s
  {Parameter} and the {Masses} of {Galaxies} from the {Gravitational} {Lens}
  {Effect}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{307--310}
  (\bibinfo{year}{1964}).
%\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/128/4/307/2601707}.

\bibitem{coe_cosmological_2009}
\bibinfo{author}{Coe, D.} \& \bibinfo{author}{Moustakas, L.~A.}
\newblock \bibinfo{title}{Cosmological Constraints from Grvitational Lens Time Delays}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{706}}, \bibinfo{pages}{45--59}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/706/1/45}.

\bibitem{linder_lensing_2011}
\bibinfo{author}{Linder, E.~V.}
\newblock \bibinfo{title}{Lensing time delays and cosmological
  complementarity}.
\newblock \emph{\bibinfo{journal}{Physical Review D}}
  \textbf{\bibinfo{volume}{84}}, \bibinfo{pages}{123529}
  (\bibinfo{year}{2011}).
%\newblock \urlprefix\url{https://link.aps.org/doi/10.1103/PhysRevD.84.123529}.

\bibitem{suyu_cosmology_2014}
\bibinfo{author}{Suyu, S.~H.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmology from Gravitational Lens Time Delays and Planck Data}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{788}}, \bibinfo{pages}{L35} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/2041-8205/788/2/L35}.

\bibitem{bonvin_cosmograil_2019}
\bibinfo{author}{Bonvin, V.} \emph{et~al.}
\newblock \bibinfo{title}{{COSMOGRAIL}: {XVIII}. Time Delays of the Quadruply  Lensed Wuasar {WFI2033}-4723}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{629}}, \bibinfo{pages}{A97} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201935921}.

\bibitem{wong_h0licow_2019}
\bibinfo{author}{Wong, K.~C.} \emph{et~al.}
\newblock \bibinfo{title}{{H0LiCOW} {XIII}. {A} 2.4\% Measurement of
  \${H}\_\{0\}\$ from Lensed Quasars: \$5.3{\textbackslash}sigma\$ Tension
  Between Early and Late-{Universe} Probes}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{accepted}}, %\bibinfo{pages}{tbd}
\newblock Preprint at \url{http://arxiv.org/abs/1907.04869}
(\bibinfo{year}{2019}).

\bibitem{suyu_cosmological_2018}
\bibinfo{author}{Suyu, S.~H.}, \bibinfo{author}{Chang, T.-C.},
  \bibinfo{author}{Courbin, F.} \& \bibinfo{author}{Okumura, T.}
\newblock \bibinfo{title}{Cosmological {distance} {indicators}}.
\newblock \emph{\bibinfo{journal}{Space Science Reviews}}
  \textbf{\bibinfo{volume}{214}}, \bibinfo{pages}{91} (\bibinfo{year}{2018}).
%\newblock \urlprefix\url{http://link.springer.com/10.1007/s11214-018-0524-3}.

\bibitem{kelly_multiple_2015}
\bibinfo{author}{Kelly, P.~L.} \emph{et~al.}
\newblock \bibinfo{title}{Multiple images of a highly magnified supernova
  formed by an early-type cluster galaxy lens}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{347}},
  \bibinfo{pages}{1123--1126} (\bibinfo{year}{2015}).
\newblock
%  \urlprefix\url{https://www.sciencemag.org/lookup/doi/10.1126/science.aaa3350}.

\bibitem{goobar_iptf16geu:_2017}
\bibinfo{author}{Goobar, A.} \emph{et~al.}
\newblock \bibinfo{title}{{iPTF16geu}: {A} multiply imaged, gravitationally
  lensed type {Ia} supernova}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{356}},
  \bibinfo{pages}{291--295} (\bibinfo{year}{2017}).
\newblock
%  \urlprefix\url{http://www.sciencemag.org/lookup/doi/10.1126/science.aal2729}.

\bibitem{kelly_sn_2016}
\bibinfo{author}{Kelly, P.~L.} \emph{et~al.}
\newblock \bibinfo{title}{SN Refsdal: Classification as a luminous and blue SN 1987A-like Type II Supernova}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{831}}, \bibinfo{pages}{205} (\bibinfo{year}{2016}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/0004-637X/831/2/205}.

\bibitem{dhawan_magnification_2019}
\bibinfo{author}{Dhawan, S.} \emph{et~al.}
\newblock \bibinfo{title}{Magnification, dust and time-delay constraints from
  the first resolved strongly lensed {Type} {Ia} supernova {iPTF16geu}}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \bibinfo{pages}{stz2965} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/advance-article/doi/10.1093/mnras/stz2965/5607803}.

\bibitem{newman_resolving_2018}
\bibinfo{author}{Newman, A.~B.}, \bibinfo{author}{Belli, S.},
  \bibinfo{author}{Ellis, R.~S.} \& \bibinfo{author}{Patel, S.~G.}
\newblock \bibinfo{title}{Resolving {Quiescent} {Galaxies} at \textit{z}$\geq$2.
  {II}. {Direct} {Measures} of {Rotational} {Support}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{862}}, \bibinfo{pages}{126} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/862/i=2/a=126?key=crossref.d984e1694ded7dbef8bab687d5b536be}.

\bibitem{ebeling_macs_2001}
\bibinfo{author}{Ebeling, H.}, \bibinfo{author}{Edge, A.~C.} \&
  \bibinfo{author}{Henry, J.~P.}
\newblock \bibinfo{title}{{MACS}: {A} quest for the most massive galaxy
  clusters in the universe}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{553}}, \bibinfo{pages}{668--676}
  (\bibinfo{year}{2001}).

\bibitem{materials_methods_2020}
\bibinfo{title}{Methods are fully described in the online Methods section}.

\bibitem{jullo_bayesian_2007}
\bibinfo{author}{Jullo, E.} \emph{et~al.}
\newblock \bibinfo{title}{A {Bayesian} approach to strong lensing modelling of
  galaxy clusters}.
\newblock \emph{\bibinfo{journal}{New Journal of Physics}}
  \textbf{\bibinfo{volume}{9}}, \bibinfo{pages}{447--447}
  (\bibinfo{year}{2007}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1367-2630/9/12/447}.

\bibitem{kneib_lenstool_2011}
\bibinfo{author}{Kneib, J.-P.} \emph{et~al.}
\newblock \bibinfo{title}{{LENSTOOL}: {A} gravitational lensing software for
  modeling mass distribution of galaxies and clusters (strong and weak regime)}
  \bibinfo{pages}{ascl:1102.004} (\bibinfo{year}{2011}).

\bibitem{woosley_type_2007}
\bibinfo{author}{Woosley, S.~E.}, \bibinfo{author}{Kasen, D.},
  \bibinfo{author}{Blinnikov, S.} \& \bibinfo{author}{Sorokina, E.}
\newblock \bibinfo{title}{Type {Ia} {Supernova} {Light} {Curves}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{662}}, \bibinfo{pages}{487--503}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://stacks.iop.org/0004-637X/662/i=1/a=487}.

\bibitem{kasen_type_2009}
\bibinfo{author}{Kasen, D.} \& \bibinfo{author}{Woosley, S.~E.}
\newblock \bibinfo{title}{Type II Supernovae: Model light curves and standard candle relationships}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{703}}, \bibinfo{pages}{2205--2216}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/703/i=2/a=2205?key=crossref.208d40b300652b1e492e00d8bcc4f81f}.

\bibitem{oguri_gravitationally_2010}
\bibinfo{author}{Oguri, M.} \& \bibinfo{author}{Marshall, P.~J.}
\newblock \bibinfo{title}{Gravitationally lensed quasars and supernovae in
  future wide-field optical imaging surveys: {Lensed} quasars and supernovae}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{405}}, \bibinfo{pages}{2579--2593}
  (\bibinfo{year}{2010}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article-lookup/doi/10.1111/j.1365-2966.2010.16639.x}.

\bibitem{goldstein_rates_2019}
\bibinfo{author}{Goldstein, D.~A.}, \bibinfo{author}{Nugent, P.~E.} \&
  \bibinfo{author}{Goobar, A.}
\newblock \bibinfo{title}{Rates and {Properties} of {Supernovae} {Strongly}
  {Gravitationally} {Lensed} by {Elliptical} {Galaxies} in {Time}-domain
  {Imaging} {Surveys}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal Supplement Series}}
  \textbf{\bibinfo{volume}{243}}, \bibinfo{pages}{6} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4365/ab1fe0}.

\bibitem{wojtak_magnified_2019}
\bibinfo{author}{Wojtak, R.}, \bibinfo{author}{Hjorth, J.} \&
  \bibinfo{author}{Gall, C.}
\newblock \bibinfo{title}{Magnified or multiply imaged? - {Search} strategies
  for gravitationally lensed supernovae in wide-field surveys}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{487}}, \bibinfo{pages}{3342--3355}
  (\bibinfo{year}{2019}).

\bibitem{gonzaga_drizzlepac_2012}
\bibinfo{author}{Gonzaga, S.} \& \bibinfo{author}{{et al.}}
\newblock \emph{\bibinfo{title}{The {DrizzlePac} handbook}}
  (\bibinfo{year}{2012}).

\bibitem{the_astropy_collaboration_astropy_2018}
\bibinfo{author}{{The Astropy Collaboration}} \emph{et~al.}
\newblock \bibinfo{title}{The {Astropy} {Project}: {Building} an {Open}-science
  {Project} and {Status} of the v2.0 {Core} {Package}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{156}}, \bibinfo{pages}{123} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-3881/aabc4f}.

\bibitem{weilbacher_data_2020}
\bibinfo{author}{Weilbacher, P.~M.} \emph{et~al.}
\newblock \bibinfo{title}{The data processing pipeline for the {MUSE}
  instrument}.
%\newblock \emph{\bibinfo{journal}{arXiv e-prints}}
%\textbf{\bibinfo{volume}{arXiv:2006.08638}}
Preprint at \url{https://arxiv.org/abs/2006.08638}
(\bibinfo{year}{2020}).

\bibitem{bacon_muse_2017}
\bibinfo{author}{Bacon, R.} \emph{et~al.}
\newblock \bibinfo{title}{The {MUSE} \textit{{Hubble}} {Ultra} {Deep} {Field}
  {Survey}: {I}. {Survey} description, data reduction, and source detection}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{608}}, \bibinfo{pages}{A1} (\bibinfo{year}{2017}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361/201730833}.

\bibitem{soto_zap_2016}
\bibinfo{author}{Soto, K.~T.}, \bibinfo{author}{Lilly, S.~J.},
  \bibinfo{author}{Bacon, R.}, \bibinfo{author}{Richard, J.} \&
  \bibinfo{author}{Conseil, S.}
\newblock \bibinfo{title}{{ZAP} - enhanced {PCA} sky subtraction for integral
  field spectroscopy}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{458}}, \bibinfo{pages}{3210--3220}
  (\bibinfo{year}{2016}).

\bibitem{piqueras_mpdaf_2019}
\bibinfo{author}{Piqueras, L.} \emph{et~al.}
\newblock \bibinfo{title}{{MPDAF} - a python package for the analysis of
  {VLT}/{MUSE} data}.
\newblock In \bibinfo{editor}{Molinaro, M.}, \bibinfo{editor}{Shortridge, K.}
  \& \bibinfo{editor}{Pasian, F.} (eds.) \emph{\bibinfo{booktitle}{Astronomical
  data analysis software and systems {XXVI}}}, vol. \bibinfo{volume}{521} of
  \emph{\bibinfo{series}{Astronomical society of the pacific conference
  series}}, \bibinfo{pages}{545} (\bibinfo{year}{2019}).

\bibitem{mahler_strong_2018}
\bibinfo{author}{Mahler, G.} \emph{et~al.}
\newblock \bibinfo{title}{Strong-lensing analysis of {A2744} with {MUSE} and
  hubble frontier fields images}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{473}}, \bibinfo{pages}{663--692}
  (\bibinfo{year}{2018}).

\bibitem{lagattuta_probing_2019}
\bibinfo{author}{Lagattuta, D.~J.} \emph{et~al.}
\newblock \bibinfo{title}{Probing {3D} structure with a large {MUSE} mosaic:
  extending the mass model of {Frontier} {Field} {Abell} 370}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{3738--3760}
  (\bibinfo{year}{2019}).

\bibitem{richard_mass_2014}
\bibinfo{author}{Richard, J.} \emph{et~al.}
\newblock \bibinfo{title}{Mass and magnification maps for the {Hubble} {Space}
  {Telescope} {Frontier} {Fields} clusters: implications for high-redshift
  studies}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{444}}, \bibinfo{pages}{268--289}
  (\bibinfo{year}{2014}).

\bibitem{richard_locuss_2010}
\bibinfo{author}{Richard, J.} \emph{et~al.}
\newblock \bibinfo{title}{{LoCuSS}: first results from strong-lensing analysis
  of 20 massive galaxy clusters at z = 0.2}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{404}}, \bibinfo{pages}{325--349}
  (\bibinfo{year}{2010}).

\bibitem{mannucci_supernova_2005}
\bibinfo{author}{Mannucci, F.} \emph{et~al.}
\newblock \bibinfo{title}{The supernova rate per unit mass}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{433}}, \bibinfo{pages}{807--814}
  (\bibinfo{year}{2005}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20041411}.

\bibitem{newman_resolving_2018-1}
\bibinfo{author}{Newman, A.~B.}, \bibinfo{author}{Belli, S.},
  \bibinfo{author}{Ellis, R.~S.} \& \bibinfo{author}{Patel, S.~G.}
\newblock \bibinfo{title}{Resolving {Quiescent} {Galaxies} at \textit{z}$\geq$2.
  {I}. {Search} for {Gravitationally} {Lensed} {Sources} and {Characterization}
  of {Their} {Structure}, {Stellar} {Populations}, and {Line} {Emission}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{862}}, \bibinfo{pages}{125} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/862/i=2/a=125?key=crossref.11a8992d65c44e536887566650da59f8}.

\bibitem{foley_classifying_2013}
\bibinfo{author}{Foley, R.~J.} \& \bibinfo{author}{Mandel, K.}
\newblock \bibinfo{title}{Classifying supernovae using only galaxy data}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{778}}, \bibinfo{pages}{167} (\bibinfo{year}{2013}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/778/i=2/a=167?key=crossref.ed447fe9ba93137547a570f6beb359f8}.

\bibitem{smartt_progenitors_2009}
\bibinfo{author}{Smartt, S.~J.}
\newblock \bibinfo{title}{Progenitors of {Core}-{Collapse} {Supernovae}}.
\newblock \emph{\bibinfo{journal}{Annual Review of Astronomy and Astrophysics}}
  \textbf{\bibinfo{volume}{47}}, \bibinfo{pages}{63--106}
  (\bibinfo{year}{2009}).
%\newblock \urlprefix\url{https://doi.org/10.1146/annurev-astro-082708-101737}.

\bibitem{li_rates_2012}
\bibinfo{author}{Li, X.}, \bibinfo{author}{Hjorth, J.} \&
  \bibinfo{author}{Richard, J.}
\newblock \bibinfo{title}{The rates and time-delay distribution of multiply
  imaged supernovae behind lensing clusters}.
\newblock \emph{\bibinfo{journal}{Journal of Cosmology and Astroparticle
  Physics}} \textbf{\bibinfo{volume}{2012}}, \bibinfo{pages}{015--015}
  (\bibinfo{year}{2012}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/1475-7516/2012/11/015}.

\bibitem{barbary_sncosmo_2016}
\bibinfo{author}{Barbary, K.} \emph{et~al.}
\newblock \bibinfo{title}{Sncosmo/{Sncosmo}: {V1}.4.0} (\bibinfo{year}{2016}).
\newblock \urlprefix\url{10.5281/zenodo.168220}.

\bibitem{rodney_type_2014}
\bibinfo{author}{Rodney, S.~A.} \emph{et~al.}
\newblock \bibinfo{title}{{Type} {Ia} {Supernova} {Rate} {Measurements} {to}
  {Redshift} 2.5 {From} {CANDELS}: {Searching} {for} {{}rompt} {Explosions} {in}
  the {Early} {Universe}}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{13} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/1538-3881/148/i=1/a=13?key=crossref.807cb4ea3e88cb99df642470efc9173f}.

\bibitem{guy_salt2:_2007}
\bibinfo{author}{Guy, J.} \emph{et~al.}
\newblock \bibinfo{title}{{SALT2}: using distant supernovae to improve the use
  of type {Ia} supernovae as distance indicators}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{466}}, \bibinfo{pages}{11--21}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20066930}.

\bibitem{pierel_extending_2018}
\bibinfo{author}{Pierel, J. D.~R.} \emph{et~al.}
\newblock \bibinfo{title}{Extending {Supernova} {Spectral} {Templates} for
  {Next}-generation {Space} {Telescope} {Observations}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{130}}, \bibinfo{pages}{114504}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/1538-3873/130/i=993/a=114504?key=crossref.44ee315a73acf8a52666778cf6cc1881}.

\bibitem{kessler_snana:_2009}
\bibinfo{author}{Kessler, R.} \emph{et~al.}
\newblock \bibinfo{title}{{SNANA}: {A} {Public} {Software} {Package} for
  {Supernova} {Analysis}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{121}}, \bibinfo{pages}{1028--1035}
  (\bibinfo{year}{2009}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/605984}.

\bibitem{frieman_sloan_2008}
\bibinfo{author}{Frieman, J.~A.} \emph{et~al.}
\newblock \bibinfo{title}{The Sloan Digital Sky Survey-II Supernova Survey: Technical Summary}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{135}}, \bibinfo{pages}{338--347}
  (\bibinfo{year}{2008}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-6256/135/1/338}.

\bibitem{sako_sloan_2008}
\bibinfo{author}{Sako, M.} \emph{et~al.}
\newblock \bibinfo{title}{The Sloan Digital Sky Survey-II Supernova Survey: Search Algorithm and Follow-up Observations}.
\newblock \emph{\bibinfo{journal}{The Astronomical Journal}}
  \textbf{\bibinfo{volume}{135}}, \bibinfo{pages}{348--373}
  (\bibinfo{year}{2008}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-6256/135/1/348}.

\bibitem{dandrea_type_2010}
\bibinfo{author}{D'Andrea, C.~B.} \emph{et~al.}
\newblock \bibinfo{title}{Type II-P Supernovae from the SDSS-II Supernova Survey and the standardized candle method}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{708}}, \bibinfo{pages}{661--674}
  (\bibinfo{year}{2010}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/708/1/661}.

\bibitem{astier_supernova_2006}
\bibinfo{author}{Astier, P.} \emph{et~al.}
\newblock \bibinfo{title}{The {Supernova} {Legacy} {Survey}: measurement of
  $\Omega_{\mathsf{M}}$,   $\Omega_{\mathsf{\Lambda}}$,
  and $w$ from the first year data set}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{447}}, \bibinfo{pages}{31--48}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{http://www.aanda.org/10.1051/0004-6361:20054185}.

\bibitem{hamuy_carnegie_2006}
\bibinfo{author}{Hamuy, M.} \emph{et~al.}
\newblock \bibinfo{title}{The {Carnegie} {Supernova} {Project}: {The}
  {Low}-{Redshift} {Survey}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{118}}, \bibinfo{pages}{2--20}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/500228}.

\bibitem{stritzinger_he-rich_2009}
\bibinfo{author}{Stritzinger, M.} \emph{et~al.}
\newblock \bibinfo{title}{The He-Rich Core-collapse Supernova 2007Y: Observations from X-ray to radio wavelengths}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{696}}, \bibinfo{pages}{713--728}
  (\bibinfo{year}{2009}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.1088/0004-637X/696/1/713}.

\bibitem{morrell_carnegie_2012}
\bibinfo{author}{Morrell, N.~I.}
\newblock \bibinfo{title}{Carnegie supernova project: {Spectroscopic}
  observations of core collapse supernovae}.
\newblock In \bibinfo{editor}{Roming, P.}, \bibinfo{editor}{Kawai, N.} \&
  \bibinfo{editor}{Pian, E.} (eds.) \emph{\bibinfo{booktitle}{Death of massive
  stars: {Supernovae} and gamma-ray bursts}}, vol. \bibinfo{volume}{279} of
  \emph{\bibinfo{series}{{IAU} symposium}}, \bibinfo{pages}{361--362}
  (\bibinfo{year}{2012}).

\bibitem{pierel_turning_2019}
\bibinfo{author}{Pierel, J. D.~R.} \& \bibinfo{author}{Rodney, S.}
\newblock \bibinfo{title}{Turning {Gravitationally} {Lensed} {Supernovae} into
  {Cosmological} {Probes}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{876}}, \bibinfo{pages}{107} (\bibinfo{year}{2019}).
\newblock
%  \urlprefix\url{https://iopscience.iop.org/article/10.3847/1538-4357/ab164a}.

\bibitem{huber_strongly_2019}
\bibinfo{author}{Huber, S.} \emph{et~al.}
\newblock \bibinfo{title}{Strongly lensed {SNe} {Ia} in the era of {LSST}:
  observing cadence for lens discoveries and time-delay measurements}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{631}}, \bibinfo{pages}{A161} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201935370}.

\bibitem{goldstein_precise_2018}
\bibinfo{author}{Goldstein, D.~A.}, \bibinfo{author}{Nugent, P.~E.},
  \bibinfo{author}{Kasen, D.~N.} \& \bibinfo{author}{Collett, T.~E.}
\newblock \bibinfo{title}{Precise {Time} {Delays} from {Strongly}
  {Gravitationally} {Lensed} {Type} {Ia} {Supernovae} with {Chromatically}
  {Microlensed} {Images}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{855}}, \bibinfo{pages}{22} (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/855/i=1/a=22?key=crossref.0c66b370adee53fbbf39e00b6f7f9f0d}.

\bibitem{foxley-marrable_impact_2018}
\bibinfo{author}{Foxley-Marrable, M.}, \bibinfo{author}{Collett, T.~E.},
  \bibinfo{author}{Vernardos, G.}, \bibinfo{author}{Goldstein, D.~A.} \&
  \bibinfo{author}{Bacon, D.}
\newblock \bibinfo{title}{The impact of microlensing on the standardization of
  strongly lensed {Type} {Ia} supernovae}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{478}}, \bibinfo{pages}{5081--5090}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/478/4/5081/5001437}.

\bibitem{bonvin_impact_2019}
\bibinfo{author}{Bonvin, V.} \emph{et~al.}
\newblock \bibinfo{title}{Impact of the {3D} source geometry on time-delay
  measurements of lensed type-{Ia} supernovae}.
\newblock \emph{\bibinfo{journal}{Astronomy \& Astrophysics}}
  \textbf{\bibinfo{volume}{621}}, \bibinfo{pages}{A55} (\bibinfo{year}{2019}).
%\newblock \urlprefix\url{https://www.aanda.org/10.1051/0004-6361/201833405}.

\bibitem{kochanek_quantitative_2004}
\bibinfo{author}{Kochanek, C.~S.}
\newblock \bibinfo{title}{Quantitative {Interpretation} of {Quasar}
  {Microlensing} {Light} {Curves}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{605}}, \bibinfo{pages}{58--77}
  (\bibinfo{year}{2004}).
%\newblock \urlprefix\url{https://iopscience.iop.org/article/10.1086/382180}.

\bibitem{vernardos_joint_2018}
\bibinfo{author}{Vernardos, G.}
\newblock \bibinfo{title}{A joint microlensing analysis of lensing mass and
  accretion disc models}.
\newblock \emph{\bibinfo{journal}{Monthly Notices of the Royal Astronomical
  Society}} \textbf{\bibinfo{volume}{480}}, \bibinfo{pages}{4675--4683}
  (\bibinfo{year}{2018}).
\newblock
%  \urlprefix\url{https://academic.oup.com/mnras/article/480/4/4675/5067321}.

\bibitem{hsiao_k_2007}
\bibinfo{author}{Hsiao, E.~Y.} \emph{et~al.}
\newblock \bibinfo{title}{\textit{{K}}-{Corrections} and {Spectral} {Templates} of {Type} {Ia} {Supernovae}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{663}}, \bibinfo{pages}{1187--1200}
  (\bibinfo{year}{2007}).
%\newblock \urlprefix\url{http://stacks.iop.org/0004-637X/663/i=2/a=1187}.

\bibitem{kessler_results_2010}
\bibinfo{author}{Kessler, R.} \emph{et~al.}
\newblock \bibinfo{title}{Results from the {Supernova} {Photometric}
  {Classification} {Challenge}}.
\newblock \emph{\bibinfo{journal}{Publications of the Astronomical Society of
  the Pacific}} \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{1415--1431}
  (\bibinfo{year}{2010}).
%\newblock \urlprefix\url{http://iopscience.iop.org/article/10.1086/657607}.

\bibitem{wang_determination_2006}
\bibinfo{author}{Wang, X.}, \bibinfo{author}{Wang, L.}, \bibinfo{author}{Pain,
  R.}, \bibinfo{author}{Zhou, X.} \& \bibinfo{author}{Li, Z.}
\newblock \bibinfo{title}{Determination of the {Hubble} {Constant}, the
  {Intrinsic} {Scatter} of {Luminosities} of {Type} {Ia} {Supernovae}, and
  {Evidence} for {Nonstandard} {Dust} in {Other} {Galaxies}}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{645}}, \bibinfo{pages}{488--505}
  (\bibinfo{year}{2006}).
%\newblock \urlprefix\url{https://iopscience.iop.org/article/10.1086/504312}.

\bibitem{mosher_cosmological_2014}
\bibinfo{author}{Mosher, J.} \emph{et~al.}
\newblock \bibinfo{title}{Cosmological parameter uncertainties from SALT-II Type Ia supernova light curve models}.
\newblock \emph{\bibinfo{journal}{The Astrophysical Journal}}
  \textbf{\bibinfo{volume}{793}}, \bibinfo{pages}{16} (\bibinfo{year}{2014}).
\newblock
%  \urlprefix\url{http://stacks.iop.org/0004-637X/793/i=1/a=16?key=crossref.a750658756be980048b20e0e45ff2129}.

\end{thebibliography}

### 2021-01-19 Paper/NatureAstronomy/main.tex

--- 2020-06-24 Paper/Science/main.tex
@@
 \documentclass[12pt]{article}
+%\documentclass[12pt]{nature}
+
+\usepackage[utf8]{inputenc}
+%\usepackage[backend=biber,style=nature,citestyle=numeric]{biblatex}
+%\usepackage{biblatex}
+%\addbibresource{zotero_references_biblatex.bib}
 
@@
 \usepackage{graphicx}
+\usepackage[draft,xcolor=usenames]{changes}
+\definechangesauthor[name=1, color=blue]{r1}
+\definechangesauthor[name=2, color=teal]{r2}
+\definechangesauthor[name=3, color=orange]{r3}
+\setauthormarkup{}
 
@@
 
-\usepackage{scicite}
+%\usepackage{scicite}
+%\usepackage{nature}
 
@@
 
-\paragraph*{One Sentence Summary:} A distant supernova has appeared as three images magnified by the gravity of a galaxy cluster, and will reappear in 20 years.
+%\paragraph*{One Sentence Summary:} A distant supernova has appeared as three images magnified by the gravity of a galaxy cluster, and will reappear in 20 years.
 
@@
   We report the discovery of a strongly-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
-This unprecedented scenario will enable a rare and highly precise measurement of the Hubble constant from a single lensed SN.
+This unprecedented scenario will enable a rare and highly precise measurement of the Hubble\added[id=r1]{-LeMa\^{i}tre} constant from a single lensed SN.
 The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACS J0138.0-2155.
@@
 
-\section*{Main Text:}
-
-Observations of Type Ia supernova (SN) explosions have played a key role in mapping the cosmic expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate\cite{riess_observational_1998,perlmutter_measurements_1999, Riess_large_2019}.
-Determining the nature of dark energy and how it may evolve over time is a primary goal for the large-scale cosmology experiments of the 2020s \cite{amendola_cosmology_2013,spergel_wide_2015,Ivezic_lsst_2019}.
-A series of recent investigations into the expansion rate of the universe (the Hubble-LeM\^aitre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background (CMB) radiation \cite{Riess_large_2019,aghanim_planck_2018}.
+%\section*{Main Text:}
+
+Observations of Type Ia supernova (SN) explosions have played a key role in mapping the cosmic expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate
+\cite{riess_observational_1998,perlmutter_measurements_1999, Riess_large_2019}.
+Determining the nature of dark energy and how it may evolve over time is a primary goal for the large-scale cosmology experiments of the 2020s
+\cite{amendola_cosmology_2013,spergel_wide_2015,Ivezic_lsst_2019}.
+A series of recent investigations into the expansion rate of the universe (the Hubble-LeMa\^itre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background (CMB) radiation \cite{Riess_large_2019,aghanim_planck_2018}.
 Resolving this tension in $H_0$ measurements may reveal new physics from the early universe, and to do so requires multiple
@@
 As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosmological_2018}.
+\added[id=r1]{A future sample with $\sim100$ well-measured lensing time delays will be a competitive tool for dark energy studies \cite{linder_lensing_2011,jee_time-delay_2016,suyu_HOLISMOKES_2020}.}
 
@@
 The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2019}.
-Here we present the discovery
+\added[id=r1]{An earlier discovery of an unusually luminous SN \cite{chornock_ps1-10afx_2013} was also shown to be a strongly-lensed SNIa,
+\cite{quimby_extraordinary_2013,quimby_detection_2014}
+though the multiple images were not resolved.}  Here we present the discovery 
 of a third lensed SN resolved into multiple images: \SNABC.
@@
 
-Future large-scale surveys such as the Vera C. Rubin Observatory 
-and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
-However, many of these lensed SN will require substantial follow-up resources to be made cosmologically useful.
-Furthermore, almost all will have significantly shorter
+\added[id=r1]{By itself, \SNABC will not be particularly powerful as a solitary cosmological probe.  However,} future large-scale surveys such as the Vera C. Rubin Observatory 
+and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes, \added[id=r1]{though the vast majority of these will be lensed by galaxy-scale deflectors}  \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
+\deleted[id=r1]{However, many of these lensed SN will require substantial follow-up resources to be made cosmologically useful.} Thus, almost all will have significantly shorter
 delays (of order 10--100 days) and therefore higher relative uncertainties than \SNABC.  Since it is the {\it fractional} time delay uncertainty that 
-propagates through to any time delay distance measurement, the extraordinarily long time delays of cluster-lensed SNe like SN Requiem can deliver significantly better time delay precision, with comparable observational cost.
-In fact, the long time baseline of lensed SN like \SNABC effectively insures that their cosmological precision is not limited by the time delay measurement errors.
-
-In Figure \ref{fig:cosmo} we illustrate the cosmological value of time delay cosmography with objects like \SNABC  by considering a small sample of 5 ``\reqlike'' SN.
+propagates through to any time delay distance measurement, the extraordinarily long time delays of cluster-lensed SNe like \SNABC can deliver significantly better time delay precision, with comparable observational cost.
+In fact, the long time baseline of lensed SN like \SNABC effectively insures that their cosmological precision is not limited by time delay measurement uncertainty.
+
+In Figure \ref{fig:cosmo} we illustrate the cosmological value of time delay cosmography with objects like \SNABC  by considering a small sample of 5 ``\reqlike'' SN\added[id=r1]{---with $<1\%$ time delay precision and the same redshift ratio.}
 For a comparison on equal footing, we evaluate equal-sized lensed SN samples 
@@
     \centering
-    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout_sn4.pdf}
+    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout_2021.pdf}
     \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4).
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
-    %Labels marked 3.1--3.4 indicate the locations of a separate  multiply-imaged [O\textsc{ii}]-emitter at $z=0.77$ used to help constrain the lensing potential. 
+    \added[id=r1]{Labels marked 3.1--3.4 indicate the locations of a separate  multiply-imaged [O\textsc{ii}]-emitter at $z=0.77$ used to help constrain the lensing potential.} 
     Panels \emph{b}--\emph{i} show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
 The three-color images are generated from the WFC3/IR filters as indicated; panels \emph{bcde} show the imaging from 2016 July where the SN was visible and \emph{fghi} show the later imaging from 2019 July where the the SN has faded away.
-Panels \emph{ei} indicate the location of the fourth image predicted to appear in $\approx$2037.
-All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.}
-
+Panels \emph{aei} indicate the location of the fourth image predicted to appear in $\approx$2037.
+All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.
+}
     \label{fig:layout}
@@
 Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
-Open markers show the observed photometry of the SN.
-Dotted vertical lines mark the lensing magnification correction, terminating in closed markers and solid bars that indicate the magnification in our preferred lens model and its systematic uncertainty, respectively.
-\emph{Right:} The evolution of a typical Type Ia SN at $z=1.95$ in observed color-brightness space is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
+\added[id=r1]{The directly observed photometry for each of the three SN images is shown as open markers.
+Vertical dotted lines show the effect of applying lens magnification corrections, with a filled grey marker indicating the corrected (demagnified) magnitude after applying our preferred lens model.
+Error bars indicate the systematic uncertainty (the range of alternative magnification corrections encompassed by lens model variations).}  \emph{Right:} The evolution of a typical Type Ia SN at $z=1.95$ in observed color-brightness space is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
 White diamonds correspond to the times labeled on the colorbar at right.
@@
 \midrule
-\textit{1}  & $99^{+27}_{-29}$ & -- & $3.9\pm0.5$ & --\\
-\textit{2} & $-19^{+21}_{-13}$ & $114^{+39}_{-42}$ & $7\pm3$ & $101\pm62$ \\
-\textit{3} & $87^{+15}_{-13}$ & $11\pm23$ & $5\pm1$ & $19\pm34$ \\
-\textit{4} & -- & -- & $0.4\pm0.2$ & $7760\pm540$\\
+\textit{1}  & $87^{+16}_{-13}$ & -- & $5\pm1$ & --\\
+\textit{2} & $-20^{+20}_{-11}$ & $106^{+25}_{-24}$ & $7\pm3$ & $82\pm62$ \\
+\textit{3} & $100^{+27}_{-31}$ & $-10\pm24$ &$3.9\pm0.5$  & $-19\pm34$ \\
+\textit{4} & -- & -- & $0.4\pm0.2$ & $7742\pm540$\\
+
+%%%^^^^^^^UPDATE UNCERTAINTIES BASED ON JR^^^^^^^^%%%%%%
 
@@
 
-%BibTeX users: After compilation, comment out the following two lines and paste in
-% the generated .bbl file. 
-%%%%%%%%%%%% Bibliography
-%\bibliography{references}
-%\bibliographystyle{Science}
-\begin{thebibliography}{10}
-
-\bibitem{riess_observational_1998}
-A.~G. Riess, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 116}, 1009
-  (1998).
-
-\bibitem{perlmutter_measurements_1999}
-S.~Perlmutter, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 517}, 565
-  (1999).
-
-\bibitem{Riess_large_2019}
-A.~G. Riess, S.~Casertano, W.~Yuan, L.~M. Macri, D.~Scolnic, {\it The
-  Astrophysical Journal\/} {\bf 876}, 85 (2019).
-
-\bibitem{amendola_cosmology_2013}
-L.~Amendola, {\it et~al.\/}, {\it Living Reviews in Relativity\/} {\bf 16}, 6
-  (2013).
-
-\bibitem{spergel_wide_2015}
-D.~Spergel, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:1503.03757}
-  (2015).
-
-\bibitem{Ivezic_lsst_2019}
-Ivezic, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 873}, 111
-  (2019).
-
-\bibitem{aghanim_planck_2018}
-{Planck Collaboration}, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf
-  arXiv:1807.06209} (2018).
-
-\bibitem{verde_tensions_2019}
-L.~Verde, T.~Treu, A.~G. Riess, {\it Nature Astronomy\/} {\bf 3}, 891 (2019).
-
-\bibitem{einstein_lens_1936}
-A.~Einstein, {\it Science\/} {\bf 84}, 506 (1936).
-
-\bibitem{refsdal_possibility_1964}
-S.~Refsdal, {\it Monthly Notices of the Royal Astronomical Society\/} {\bf
-  128}, 307 (1964).
-
-\bibitem{coe_cosmological_2009}
-D.~Coe, L.~A. Moustakas, {\it The Astrophysical Journal\/} {\bf 706}, 45
-  (2009).
-
-\bibitem{linder_lensing_2011}
-E.~V. Linder, {\it Physical Review D\/} {\bf 84}, 123529 (2011).
-
-\bibitem{suyu_cosmology_2014}
-S.~H. Suyu, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 788}, L35
-  (2014).
-
-\bibitem{bonvin_cosmograil_2019}
-V.~Bonvin, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 629}, A97
-  (2019).
-
-\bibitem{wong_h0licow_2019}
-K.~C. Wong, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:1907.04869}
-  (2019).
-
-\bibitem{suyu_cosmological_2018}
-S.~H. Suyu, T.-C. Chang, F.~Courbin, T.~Okumura, {\it Space Science Reviews\/}
-  {\bf 214}, 91 (2018).
-
-\bibitem{kelly_multiple_2015}
-P.~L. Kelly, {\it et~al.\/}, {\it Science\/} {\bf 347}, 1123 (2015).
-
-\bibitem{goobar_iptf16geu:_2017}
-A.~Goobar, {\it et~al.\/}, {\it Science\/} {\bf 356}, 291 (2017).
-
-\bibitem{kelly_sn_2016}
-P.~L. Kelly, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 831}, 205
-  (2016).
-
-\bibitem{dhawan_magnification_2019}
-S.~Dhawan, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
-  Society\/} 491, 2639 (2020).
-
-\bibitem{newman_resolving_2018}
-A.~B. Newman, S.~Belli, R.~S. Ellis, S.~G. Patel, {\it The Astrophysical
-  Journal\/} {\bf 862}, 126 (2018).
-
-\bibitem{ebeling_macs_2001}
-H.~Ebeling, A.~C. Edge, J.~P. Henry, {\it The Astrophysical Journal\/} {\bf
-  553}, 668 (2001).
-
-\bibitem{materials_methods_2020}
-Materials and methods are available as supplementary materials at the {Science}
-  website.
-
-\bibitem{jullo_bayesian_2007}
-E.~Jullo, {\it et~al.\/}, {\it New Journal of Physics\/} {\bf 9}, 447 (2007).
-
-\bibitem{kneib_lenstool_2011}
-J.-P. Kneib, {\it et~al.\/} LENSTOOL: A Gravitational Lensing Software for Modeling Mass Distribution of Galaxies and Clusters, ascl:1102.004 (2011).
-
-\bibitem{woosley_type_2007}
-S.~E. Woosley, D.~Kasen, S.~Blinnikov, E.~Sorokina, {\it The Astrophysical
-  Journal\/} {\bf 662}, 487 (2007).
-
-\bibitem{kasen_type_2009}
-D.~Kasen, S.~E. Woosley, {\it The Astrophysical Journal\/} {\bf 703}, 2205
-  (2009).
-
-\bibitem{oguri_gravitationally_2010}
-M.~Oguri, P.~J. Marshall, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 405}, 2579 (2010).
-
-\bibitem{goldstein_rates_2019}
-D.~A. Goldstein, P.~E. Nugent, A.~Goobar, {\it The Astrophysical Journal
-  Supplement Series\/} {\bf 243}, 6 (2019).
-
-\bibitem{wojtak_magnified_2019}
-R.~Wojtak, J.~Hjorth, C.~Gall, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 487}, 3342 (2019).
-
-\bibitem{wang_determination_2006}
-X.~Wang, L.~Wang, R.~Pain, X.~Zhou, Z.~Li, {\it The Astrophysical Journal\/}
-  {\bf 645}, 488 (2006).
-
-\bibitem{gonzaga_drizzlepac_2012}
-S.~Gonzaga, {et al.}, {\it The {DrizzlePac} handbook\/}, HST Data Handbook (2012).
-
-\bibitem{the_astropy_collaboration_astropy_2018}
-{The Astropy Collaboration}, {\it et~al.\/}, {\it The Astronomical Journal\/}
-  {\bf 156}, 123 (2018).
-
-\bibitem{weilbacher_data_2020}
-P.~M. Weilbacher, {\it et~al.\/}, {\it arXiv e-prints\/} {\bf arXiv:2006.08638}
-  (2020).
-
-\bibitem{bacon_muse_2017}
-R.~Bacon, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 608}, A1
-  (2017).
-
-\bibitem{soto_zap_2016}
-K.~T. Soto, S.~J. Lilly, R.~Bacon, J.~Richard, S.~Conseil, {\it Monthly Notices
-  of the Royal Astronomical Society\/} {\bf 458}, 3210 (2016).
-
-\bibitem{piqueras_mpdaf_2019}
-L.~Piqueras, {\it et~al.\/}, {\it Astronomical data analysis software and
-  systems {XXVI}\/}, M.~Molinaro, K.~Shortridge, F.~Pasian, eds. (2019), vol.
-  521 of {\it Astronomical society of the pacific conference series\/}, p. 545.
-
-\bibitem{mahler_strong_2018}
-G.~Mahler, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 473}, 663 (2018).
-
-\bibitem{lagattuta_probing_2019}
-D.~J. Lagattuta, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 485}, 3738 (2019).
-
-\bibitem{richard_mass_2014}
-J.~Richard, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 444}, 268 (2014).
-
-\bibitem{richard_locuss_2010}
-J.~Richard, {\it et~al.\/}, {\it Monthly Notices of the Royal Astronomical
-  Society\/} {\bf 404}, 325 (2010).
-
-\bibitem{mannucci_supernova_2005}
-F.~Mannucci, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 433}, 807
-  (2005).
-
-\bibitem{newman_resolving_2018-1}
-A.~B. Newman, S.~Belli, R.~S. Ellis, S.~G. Patel, {\it The Astrophysical
-  Journal\/} {\bf 862}, 125 (2018).
-
-\bibitem{foley_classifying_2013}
-R.~J. Foley, K.~Mandel, {\it The Astrophysical Journal\/} {\bf 778}, 167
-  (2013).
-
-\bibitem{smartt_progenitors_2009}
-S.~J. Smartt, {\it Annual Review of Astronomy and Astrophysics\/} {\bf 47}, 63
-  (2009).
-
-\bibitem{li_rates_2012}
-X.~Li, J.~Hjorth, J.~Richard, {\it Journal of Cosmology and Astroparticle
-  Physics\/} {\bf 2012}, 015 (2012).
-
-\bibitem{barbary_sncosmo_2016}
-K.~Barbary, {\it et~al.\/}, Sncosmo/{Sncosmo}: {V1}.4.0 (2016).
-
-\bibitem{rodney_type_2014}
-S.~A. Rodney, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 148}, 13
-  (2014).
-
-\bibitem{guy_salt2:_2007}
-J.~Guy, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 466}, 11 (2007).
-
-\bibitem{pierel_extending_2018}
-J.~D.~R. Pierel, {\it et~al.\/}, {\it Publications of the Astronomical Society
-  of the Pacific\/} {\bf 130}, 114504 (2018).
-
-\bibitem{kessler_snana:_2009}
-R.~Kessler, {\it et~al.\/}, {\it Publications of the Astronomical Society of
-  the Pacific\/} {\bf 121}, 1028 (2009).
-
-\bibitem{frieman_sloan_2008}
-J.~A. Frieman, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 135}, 338
-  (2008).
-
-\bibitem{sako_sloan_2008}
-M.~Sako, {\it et~al.\/}, {\it The Astronomical Journal\/} {\bf 135}, 348
-  (2008).
-
-\bibitem{dandrea_type_2010}
-C.~B. D'Andrea, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 708},
-  661 (2010).
-
-\bibitem{astier_supernova_2006}
-P.~Astier, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 447}, 31
-  (2006).
-
-\bibitem{hamuy_carnegie_2006}
-M.~Hamuy, {\it et~al.\/}, {\it Publications of the Astronomical Society of the
-  Pacific\/} {\bf 118}, 2 (2006).
-
-\bibitem{stritzinger_he-rich_2009}
-M.~Stritzinger, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 696},
-  713 (2009).
-
-\bibitem{morrell_carnegie_2012}
-N.~I. Morrell, {\it Death of massive stars: {Supernovae} and gamma-ray
-  bursts\/}, P.~Roming, N.~Kawai, E.~Pian, eds. (2012), vol. 279 of {\it {IAU}
-  symposium\/}, pp. 361--362.
-
-\bibitem{pierel_turning_2019}
-J.~D.~R. Pierel, S.~Rodney, {\it The Astrophysical Journal\/} {\bf 876}, 107
-  (2019).
-
-\bibitem{huber_strongly_2019}
-S.~Huber, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 631}, A161
-  (2019).
-
-\bibitem{goldstein_precise_2018}
-D.~A. Goldstein, P.~E. Nugent, D.~N. Kasen, T.~E. Collett, {\it The
-  Astrophysical Journal\/} {\bf 855}, 22 (2018).
-
-\bibitem{foxley-marrable_impact_2018}
-M.~Foxley-Marrable, T.~E. Collett, G.~Vernardos, D.~A. Goldstein, D.~Bacon,
-  {\it Monthly Notices of the Royal Astronomical Society\/} {\bf 478}, 5081
-  (2018).
-
-\bibitem{bonvin_impact_2019}
-V.~Bonvin, {\it et~al.\/}, {\it Astronomy \& Astrophysics\/} {\bf 621}, A55
-  (2019).
-
-\bibitem{kochanek_quantitative_2004}
-C.~S. Kochanek, {\it The Astrophysical Journal\/} {\bf 605}, 58 (2004).
-
-\bibitem{vernardos_joint_2018}
-G.~Vernardos, {\it Monthly Notices of the Royal Astronomical Society\/} {\bf
-  480}, 4675 (2018).
-
-\bibitem{hsiao_k_2007}
-E.~Y. Hsiao, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 663}, 1187
-  (2007).
-
-\bibitem{kessler_results_2010}
-R.~Kessler, {\it et~al.\/}, {\it Publications of the Astronomical Society of
-  the Pacific\/} {\bf 122}, 1415 (2010).
-
-\bibitem{mosher_cosmological_2014}
-J.~Mosher, {\it et~al.\/}, {\it The Astrophysical Journal\/} {\bf 793}, 16
-  (2014).
-
-\end{thebibliography}
-
-%%%%%%%%%%%% Acknowledgents
-\section*{Acknowledgments}
-
-Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).
-{\bf Funding:} Support for this work was provided by NASA through grant numbers HST-GO-15663 and HST-AR-15050 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
-under NASA contract NAS 5-26555.
-The Cosmic Dawn Center of Excellence is funded by the Danish National Research Foundation under grant No.
-140.
-This work was supported by NASA Headquarters under the NASA Future Investigators in Earth and Space Science and Technology (FINESST) award 80NSSC19K1414.
-{\bf Author Contributions:} 
-Conceptualization, S.A.R., G.B., and S.T.; Methodology, S.A.R., J.D.R.P., J.R., and K.F.O.; Investigation, G.B., J.R., S.T., M.A., and K.E.W.; Writing - Original Draft, G.B.\ and S.T.; Writing - Review \& Editing, S.A.R., G.B., J.D.R.P., J.R., S.T., K.F.O., M.A., and K.E.W.; Visualization, S.A.R., G.B., J.D.R.P., J.R., K.F.O.; Supervision, G.B., S.T., and K.E.W.; Funding Acquisition, K.E.W.
-{\bf Competing Interests:} All authors declare no competing interests.
-{\bf Data and Materials Availability:} All HST images used in this work are available from the Mikulski Archive for Space Telescopes (mast.stsci.edu).
-All VLT MUSE spectroscopic data used in this work are available from  the ESO Archive Science Portal (archive.eso.org).
-All high-level science products (photometry, lens model inputs, etc.) are available in the main text or the supplementary materials.
-All software tools used for primary analysis tasks are publicly available, as indicated in the text.
-
 %Here you should list the contents of your Supplementary Materials -- below is an example. 
@@
 \clearpage
-\section*{Supplementary materials}
-Materials and Methods\\
-Supplementary Text\\
-Figures S1 to S8\\
-Tables S1 to S7\\
-References \textit{(32-68)}
-\clearpage
-\setcounter{table}{0}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{S\arabic{figure}}
-
-\setcounter{page}{1}
-
-\section*{Supplementary Materials for}
-{\bf \large A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
-
-\author{
- Steven A. Rodney$^{1\ast}$, 
- Gabriel Brammer$^{2\ast}$,  
- Justin D.\,R.~Pierel$^{1}$, 
- Johan Richard$^{3}$, 
- Sune Toft$^{2}$,  
- Kyle F. O'Connor$^{1}$, 
- Mohammad Akhshik$^{4}$, 
- Katherine E. Whitaker$^{2,4,5}$  \\
-\normalsize{$^{1}$Department of Physics \& Astronomy, University of South Carolina,} \normalsize{ Columbia, SC 29208, USA}\\
-\normalsize{$^{2}$Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen,} \normalsize{Lyngbyvej 2, Copenhagen \O\ 2100 Denmark}\\
-\normalsize{$^{3}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
-\normalsize{$^{4}$Department of Physics, University of Connecticut,} \normalsize{Storrs, CT 06269, USA}\\
-\normalsize{$^{5}$Department of Astronomy, University of Massachusetts,} \normalsize{Amherst, MA 01003, USA}\\
-\normalsize{$^\ast$To whom correspondence should be addressed;}\\ \normalsize{E-mail:  srodney@sc.edu, gabriel.brammer@nbi.ku.dk}
-}
-
-\subsection*{This PDF file includes:}
-
-Materials and Methods\\
-Supplementary Text\\
-Figures S1 to S8\\
-Tables S1 to S7\\
-References \textit{(32-68)}
-
-\clearpage
-
-% For your review copy (i.e., the file you initially send in for
-% evaluation), you can use the {figure} environment and the
-% \includegraphics command to stream your figures into the text, placing
-% all figures at the end.  For the final, revised manuscript for
-% acceptance and production, however, PostScript or other graphics
-% should not be streamed into your compliled file.  Instead, set
-% captions as simple paragraphs (with a \noindent tag), setting them
-% off from the rest of the text with a \clearpage as shown  below, and
-% submit figures as separate files according to the Art Department's
-% instructions.
-
-\section*{Materials and Methods}
+%\section*{Supplementary materials}
+%Materials and Methods\\
+%Supplementary Text\\
+%Figures S1 to S8\\
+%Tables S1 to S7\\
+%References \textit{(32-68)}
+%\clearpage
+%\setcounter{table}{0}
+%\renewcommand{\thetable}{S\arabic{table}}
+
+%\setcounter{figure}{0}
+%\renewcommand{\thefigure}{S\arabic{figure}}
+
+%\setcounter{page}{1}
+
+%\section*{Supplementary Materials for}
+%{\bf \large A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
+
+%\author{
+% Steven A. Rodney$^{1\ast}$, 
+% Gabriel Brammer$^{2\ast}$,  
+% Justin D.\,R.~Pierel$^{1}$, 
+% Johan Richard$^{3}$, 
+% Sune Toft$^{2}$,  
+% Kyle F. O'Connor$^{1}$, 
+% Mohammad Akhshik$^{4}$, 
+% Katherine E. Whitaker$^{2,4,5}$  \\
+%\normalsize{$^{1}$Department of Physics \& Astronomy, University of South Carolina,} \normalsize{ Columbia, SC 29208, USA}\\
+%\normalsize{$^{2}$Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen,} \normalsize{Lyngbyvej 2, Copenhagen \O\ 2100 Denmark}\\
+%\normalsize{$^{3}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
+%\normalsize{$^{4}$Department of Physics, University of Connecticut,} \normalsize{Storrs, CT 06269, USA}\\
+%\normalsize{$^{5}$Department of Astronomy, University of Massachusetts,} \normalsize{Amherst, MA 01003, USA}\\
+%\normalsize{$^\ast$To whom correspondence should be addressed;}\\ \normalsize{E-mail:  srodney@sc.edu, gabriel.brammer@nbi.ku.dk}
+%}
+
+%\subsection*{This PDF file includes:}
+
+%Materials and Methods\\
+%Supplementary Text\\
+%Figures S1 to S8\\
+%Tables S1 to S7\\
+%References \textit{(32-68)}
+
+%\clearpage
+
+\section*{Methods}
 
@@
 \midrule
-SN1 & 57588.03 & F105W ($Y$) & 0.09  $\pm$ 0.02 \\
+SN1 & 57588.03 & F105W ($Y$) & 0.18  $\pm$ 0.02 \\
 SN2 & 57588.03 & F105W ($Y$) & 2.35  $\pm$ 0.02 \\
-SN3 & 57588.03 & F105W ($Y$) & 0.18  $\pm$ 0.02 \\
-SN1 & 57587.97 & F160W ($H$) & 0.61  $\pm$ 0.04 \\
+SN3 & 57588.03 & F105W ($Y$) & 0.09  $\pm$ 0.02 \\
+SN1 & 57587.97 & F160W ($H$) & 1.13  $\pm$ 0.04 \\
 SN2 & 57587.97 & F160W ($H$) & 3.57  $\pm$ 0.05 \\
-SN3 & 57587.97 & F160W ($H$) & 1.13  $\pm$ 0.04 \\
+SN3 & 57587.97 & F160W ($H$) & 0.61  $\pm$ 0.04 \\
 \midrule
-SN1 & 58677.87 & F110W ($Y$) & 0.01  $\pm$ 0.02 \\
-SN1 & 58678.93 & F140W ($JH$) & 0.02  $\pm$ 0.02 \\
-SN1 & 58683.89 & F125W ($J$) & 0.02  $\pm$ 0.03 \\
+SN3 & 58677.87 & F110W ($Y$) & 0.01  $\pm$ 0.02 \\
+SN3 & 58678.93 & F140W ($JH$) & 0.02  $\pm$ 0.02 \\
+SN3 & 58683.89 & F125W ($J$) & 0.02  $\pm$ 0.03 \\
 \end{tabular}
-\caption{Photometry of the SN in MRG0138.  The final three rows indicate ``empty'' aperture flux densities measured at the position of SN1 in the 2019 \textit{HST} visits.
+\caption{Photometry of the SN in MRG0138.  The final three rows indicate ``empty'' aperture flux densities measured at the position of SN3 in the 2019 \textit{HST} visits.
 \label{tab:photometry}}
@@
 In order to correctly estimate the magnification factors, time delays, and predict the appearance of the future images of \SNABC we need to precisely model the mass distribution in the MACSJ0138 cluster core.
-To do so we make use of the latest version of \lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and error on each parameter of the mass distribution.
+To do so we make use of the latest version of \lenstool \cite{jullo_bayesian_2007}\footnote{publicly available at \url{ https://git-cral.univ-lyon1.fr/lenstool/lenstool}}, which performs a Bayesian analysis with an MCMC sampler to estimate the best fit and uncertainty on each parameter of the mass distribution.
 
@@
      \midrule
-SN1 & 24.5100753 & $-$21.9273418 & 1.95 \\
+SN1 & 24.5151253 & $-$21.9306659 & 1.95 \\
 SN2 & 24.5123198 & $-$21.9297875 & 1.95 \\
-SN3 & 24.5151253 & $-$21.9306659 & 1.95 \\
+SN3 & 24.5100753 & $-$21.9273418 & 1.95 \\
      \midrule
@@
     \begin{tabular}{c|c|c|c|c|c|c|c|}
-    Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $\sigma$ & $r_{\rm core}$ & $r_{\rm cut}$ \\
-    & [arcsec] & [arcsec] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
+%\replaced[id=r1]{Potential \& $\Delta$R.A. \& $\Delta$Dec. & $e$ \& $\theta$ & $\sigma$ & $r_{\rm core}$ \& $r_{\rm cut}$ \\}
+{Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $r_{\rm core}$ & $r_{\rm cut}$ & $\sigma$ \\}
+%\replaced[id=r1]{ 
+%& [arcsec] & [arcsec] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
+ & [arcsec] & [arcsec] & & [deg] & [kpc] & [kpc] & [km\ $s^{-1}$] \\%}
 \hline
@@
 \hline 
-SN1 & 01:38:02.42     & $-$21:55:38.47         & 3.9$\pm$0.5   &   --- \\
-SN2 & 01:38:02.96     & $-$21:55:47.26         & 7$\pm$3     & 101$\pm62$ \\
-SN3 & 01:38:03.63     & $-$21:55:50.38         & 5$\pm$1     &  19$\pm34$\\
-SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7760$\pm$540\\
+SN1 & 01:38:03.63     & $-$21:55:50.38         & 5$\pm$1     &  ---\\
+SN2 & 01:38:02.96     & $-$21:55:47.26         & 7$\pm$3     & 82$\pm62$ \\
+SN3 & 01:38:02.42     & $-$21:55:38.47         & 3.9$\pm$0.5   &   -19$\pm34$ \\
+SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7742$\pm$540\\
 %SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
@@
 We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
-Multiplying by the prior probabilities derived from host galaxy properties, we finally derive the probability that the SN is of Type Ia as $p(Ia)=0.95$, 0.98, and 0.92 from the three SN images SN1, SN2 and SN3, respectively.
+\added[id=r3]{Note that in this case there is no need to apply a cut to the simulated sample to account for detectability, because the $5\sigma$ limiting magnitude of our HST observations is 26.5 AB mag, and after accounting for magnification of $\sim$1.5 mag (Table~\ref{tab:massmodel}) this becomes $m_{lim}\sim28$ mag.
+This means that all the points shown in Fig.~\ref{fig:colormag_classification_supplement} (and therefore all simulated SN entering our classification counts) would be easily detectable in our HST imaging.}  Multiplying by the prior probabilities derived from host galaxy properties, we finally derive the probability that the SN is of Type Ia as $p(Ia)=0.92$, 0.98, and 0.95 from the three SN images SN1, SN2 and SN3, respectively.
 Row c of Table~\ref{tab:classification} reports the mean of our three classification probabilities for each sub-class.
@@
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/snRequiem_stardust_classify_alltypes.pdf}
-    \caption{Maximum likelihood light curve fits for each of the three primary SN sub-classes (Type Ia, Ib/c, and II).
-The observed photometry, shown as black diamonds, has been corrected for magnification and shifted in time using the preferred \lenstool model E.
-In both panels the first data point is SN image 2, followed by image 1 and image 3.
+%    \includegraphics[width=\textwidth]{Paper/Figures/snRequiem_stardust_classify_alltypes.pdf}
+\vspace{0pt} \includegraphics[width=0.63\textwidth]{Paper/Figures/lightcurves_NSAMPLES.pdf} 
+\vspace{0pt} \includegraphics[width=0.36\textwidth]{Paper/Figures/colorcurves_NSAMPLES.pdf}
+    \caption{
+    \replaced[id=r2]{A representative set of light curve and color curve models from the STARDUST2 classification algorithm.
+Panels on the left and center columns show  F105W and F160W, respectively, plotting the model light curves in black and photometry as red markers.
+The right-most column shows the F105W-F160W color curves and color data.}{Maximum likelihood light curve fits for each of the three primary SN sub-classes (Type Ia, Ib/c, and II).
+} All data points
+    as shown have been corrected for magnification and shifted in time using the preferred \lenstool model E.
 Plotted error bars include the measurement uncertainty and the lens modeling magnification uncertainty.
-The best-fitting Type Ia, Ib/c and II light curves are shown as solid, dashed, and dotted lines, respectively.
+In all panels the first data point is SN image 2, followed by image 1 and image 3.
+\replaced[id=r2]{In each panel the black curves show 200 SN light curve models drawn at random from the nested sampling sequence of the STARDUST2 (sncosmo) classification.
+    %The distribution of light curve and color curve shapes illustrates the exploration of the multi-dimensional parameter space executed by the nested sampling algorithm as it measures the likelihood for each SN class by comparison with the observed data.
+    }{The best-fitting Type Ia, Ib/c and II light curves are shown as solid, dashed, and dotted lines, respectively.}
     \label{fig:classification_lightcurves}
@@
 The SNTD package employs a nested sampling algorithm within three separate methods to measure time delays, and is designed to fully utilize the information present in SN light curve templates \cite{hsiao_k_2007,guy_salt2:_2007,kessler_results_2010,pierel_extending_2018} to reduce the impacts of microlensing and make more accurate measurements.
-We use the "color" method present in SNTD, which attempts to reconstruct the intrinsic color curve using the SALT2 model as a template \cite{guy_salt2:_2007}.
+We use the ``color'' method present in SNTD, which attempts to reconstruct the intrinsic color curve using the SALT2 model as a template \cite{guy_salt2:_2007}.
 This method fits the age of each image simultaneously, while also varying the SN model parameters.
@@
 from SNTD for the SALT2 SN model parameters and the measured ages for each image are shown in Figure \ref{fig:corner_cfit}.
-The measured colors intersect the model at two distinct locations for images 1 and 2 of \SNABC, meaning there are two plausible ages---resulting in a double peaked posterior distribution (Fig.
+The measured colors intersect the model at two distinct locations for images 2 and 3 of \SNABC, meaning there are two plausible ages---resulting in a double peaked posterior distribution (Fig.
 \ref{fig:corner_cfit}).
@@
 The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D.
-We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=7.25\pm0.07, \ Z_E=7.00\pm0.06$).}
+We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=-7.25\pm0.07, \ Z_E=-   7.00\pm0.06$).}
 \end{table}
 
-\section*{Supplementary Text}
+%\section*{Supplementary Text}
 
@@
 
-The final posterior distributions for images 1 and 2 are extremely bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (Fig.
+The final posterior distributions for images 2 and 3 are extremely bi-modal due to a degeneracy that cannot be broken by single epoch photometry, corresponding to a double-peaked intrinsic luminosity posterior for \SNABC (Fig.
 \ref{fig:corner_combined}).
@@
 
-%\clearpage
+\clearpage
+
+%Using Biblatex for the bibliography
+%\printbibliography
+
+%Using bibtex for the bibliography:
 %\section*{References}
+\bibliographystyle{naturemag}
+%\bibliography{zotero_references}
+\bibliography{references}
+
+{\bf Data Availability Statement:} All HST images used in this work are available from the Mikulski Archive for Space Telescopes (mast.stsci.edu).
+All VLT MUSE spectroscopic data used in this work are available from  the ESO Archive Science Portal (archive.eso.org).
+The authors declare that all other data supporting the findings of this study (photometry, lens model inputs, etc.) are available within the paper and its supplementary information files.
+All software tools used for primary analysis tasks are publicly available, as indicated in the text.
+
+%%%%%%%%%%%% Acknowledgents
+\section*{Acknowledgments}
+
+Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).
+{\bf Funding:} Support for this work was provided by NASA through grant numbers HST-GO-15663 and HST-AR-15050 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
+under NASA contract NAS 5-26555.
+The Cosmic Dawn Center of Excellence is funded by the Danish National Research Foundation under grant No.
+140.
+This work was supported by NASA Headquarters under the NASA Future Investigators in Earth and Space Science and Technology (FINESST) award 80NSSC19K1414.
+
+{\bf Author Contributions:} 
+Conceptualization, S.A.R., G.B., and S.T.; Methodology, S.A.R., J.D.R.P., J.R., and K.F.O.; Investigation, G.B., J.R., S.T., M.A., and K.E.W.; Writing - Original Draft, G.B.\ and S.T.; Writing - Review \& Editing, S.A.R., G.B., J.D.R.P., J.R., S.T., K.F.O., M.A., and K.E.W.; Visualization, S.A.R., G.B., J.D.R.P., J.R., K.F.O.; Supervision, G.B., S.T., and K.E.W.; Funding Acquisition, K.E.W.
+
+{\bf Competing Interests:} All authors declare no competing interests.
 

### 2021-03-28 Paper/ResponseToReferees/response_coverletter.tex
Resubmitted

\documentclass[11pt]{article}
%\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage{soul}
%\usepackage{graphicx}
%\usepackage{lineno}
%\linenumbers

%\usepackage{hyperref}
%\usepackage{booktabs}

%\usepackage{amssymb}
\usepackage{xspace}
%\usepackage{graphicx}
%\usepackage{todonotes}

%\usepackage{geometry}

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

%\definechangesauthor[name=1, color=blue]{r1}
%\definechangesauthor[name=2, color=teal]{r2}
%\definechangesauthor[name=3, color=orange]{r3}
%\definechangesauthor[name=4, color=violet]{ed}

\begin{document}

\noindent \today\\[2em]
Marios Karouzos, Senior Editor\\
Nature Astronomy\\

\bigskip

\noindent Dear Dr. Karouzos, \\

Please accept our heartfelt thanks for allowing us to resubmit this manuscript after such a long delay.  This past year has been challenging in many ways, and we are deeply appreciative that you have held the door open for us this long.  We are all still very excited by the discovery presented here, and feel it will be well received in the community.

We provide two updated versions of the manuscript.  The ``changetext'' version includes line numbers and colored text, showing changes since the original submission.  The ``revised'' version is just the current manuscript text, without showing changes.  Our estimate of the relevant sizes in the revised document are:

\begin{itemize}
    \item Main Text : 2009 words.
    \item First Paragraph : 204 words.
    \item Main text contains 3 figures and 1 table.
    \item Figure 1 legend : 195 words
    \item Figure 2 legend : 283 words
    \item Figure 3 legend : 122 words
    \item Table 1 legend : 30 words
    \item Methods Text :  4124 words.
    \item The Methods section contains 6 tables and 10 figures.
    \item Figure and Table legends in Methods and Supplementary Material are all $<350$ words.  
    \item Figures in the manuscript are shown at their estimated final size.
    \item Total size of the revised main text document is 2.5 MB.
    \item Total size of the Methods+Supplementary+References is 8.5 MB
\end{itemize}

Our point-by-point response to the referees is provided as a separate document.  There are 4 versions: one for each referee with their comments alone, and one that includes all comments together. In addition, we have made adjustments for style, following your guidance.  Where appropriate, these changes are highlighted with purple text in the changetext manuscript.  We have:

\begin{itemize}
\item{re-worded the first paragraph to follow the guidelines you provided.  We believe it now conforms to the Nature Astronomy style, and it is now 200 words according to our count;}
\item{%You encouraged us to archive the data for this manuscript in an accessible, persistent repository. We have 
prepared a github repository (currently private) with all of the code used to construct the key figures in the paper, along with data tables recording the SN photometry.  We will change  this repository to public upon acceptance of the manuscript and include a link in the final published article;}
\item{adjusted figure legends to ensure that they provide a brief description of the figure and the symbols used, within 350 words, including definitions of any error bars employed in the figures;}
\item{adjusted the reference list to keep it at 30 references in the main text;}
\item{added a statement about the corresponding author for data requests, and ensured that we have a statement of author contributions.}
\end{itemize}

Please express our sincere gratitude to the referees for their helpful comments and extraordinary patience.

\bigskip

\noindent Warm Regards,\\
\smallskip
Steve Rodney, on behalf of co-authors

\end{document}

### 2021-03-28 Paper/ResponseToReferees/response_to_referees.tex
Resubmitted

\documentclass[11pt]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{lineno}
%\linenumbers

\usepackage{hyperref}
\usepackage{booktabs}

%\usepackage{amssymb}
\usepackage{xspace}
\usepackage{graphicx}
%\usepackage{todonotes}
\usepackage{ifthen}

\usepackage{geometry}

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

% Remove the "Contents" label from the Table of Contents
\makeatletter
\renewcommand\tableofcontents{%
    \@starttoc{toc}%
}
\makeatother

\begin{document}

\newif\ifone
\newif\iftwo
\newif\ifthree
\newif\ifhlt

\onetrue % Response to referee 1
\onefalse
\twotrue % response to referee 2
\twofalse
\threetrue % response to referee 3
%\threefalse
%\hlttrue  % Highlighting page number checks
\hltfalse

\ifone
\newcommand{\one}[2]{\textbf{\textcolor{blue}{1: #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\one}[2]{}
\fi

\iftwo
\newcommand{\two}[2]{\textbf{\textcolor{teal}{2: #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\two}[2]{}
\fi

\ifthree
\newcommand{\three}[2]{\textbf{\textcolor{Maroon}{3: #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\three}[2]{}
\fi

\ifhlt
\newcommand{\hlt}[1]{\hl{#1}}
\else
\newcommand{\hlt}[1]{{#1}}
\fi

\begin{center}
\textbf{\Large{Response to Referees}}\\
\smallskip
\today
\end{center} 
\medskip

%\title{Response to Referees}
%\maketitle
%\vspace{-5mm}

We would first like to convey to the referees the same sentiment that we have expressed to the editor: we are sincerely grateful that you are willing to still consider this manuscript after such an extraordinarily long delay.  This past year has been challenging in many ways, and we are deeply appreciative of your openness to review this resubmission.

The comments from all three referees were very constructive.  Many required significant thought and effort to respond to, and we feel that the paper has improved in the process.  We do hope that the referees will agree, and look forward to learning what you think of the updated manuscript.

Our point-by-point responses are presented below. In this document we have grouped the responses by topic and area of the manuscript, so that referees can see responses to similar concerns in context.   We have color-coded each referee's comments, matching the colors used in the changetext version of the manuscript, as follows:

\begin{itemize}
\item \textbf{\textcolor{blue}{Items from Referee \#1 in blue.}}
\item \textbf{\textcolor{teal}{Items from Referee \#2 in teal.}}
\item \textbf{\textcolor{Maroon}{Items from Referee \#3 in maroon.}}
\end{itemize}

After each item we provide our response in black text.  Page references and line numbers refer to the lines in the ``changetext'' version of the manuscript.

We have provided our response to editorial suggestions in a separate cover letter, but the referees should note that we have re-worded the first paragraph to follow the guidelines provided by the editor, and we have removed some references as we added new ones, in order to keep to the guidelines.  All changes made in response to editorial comments are  \textbf{\textcolor{violet}{in purple text}} in the changetext document.

The sections of this response are as follows: \\
\bigskip

\tableofcontents

\clearpage

\section{Overall Significance}

\one{The authors have discovered a unique and interesting gravitational lens system whose predictions of a future event, if correct, could help put constraints on some of the cosmological parameters. The manuscript, generally, reads well. The reasons to publish this in Nature Astronomy are not obvious though. The authors make a good case that the transient source is a lensed SN of type 1a and since this is not still confirmed, one cannot rule out the possibility that it may be of a different type. In any case, there have been other lensed SN Ia detections (e.g. Quimby et al. 2014, Goobar et al. 2017) although not with long time delays. Furthermore, had this been the analysis of their model predicted event, it would be a first such analysis, of high significance and relevance to the wider community and thus, suitable for Nature Astronomy.\\ 
In light of these statements, could the authors justify the suitability of their choice of journal in a few sentences ?}
{Our perspective is that articles published in Nature Astronomy should be broad and significant: of interest to a broad range of astronomers, and presenting significant new discoveries or theoretical models.
\begin{itemize}
\item On breadth, this touches on a wide range of subjects astronomy—gravitational lensing, transient surveys, SN science, cosmology, and galaxy evolution.  The breadth is also highlighted by its relevance for the Rubin Observatory and Roman Space Telescope. 
\item  As for the significance, we believe that this discovery will be important in supporting the role of cluster-scale lensing for future SN time delay cosmography programs.  When review articles are written in a decade, we expect this transient will be listed alongside SN Refsdal as a trailblazer for the use of cluster-lensed SNe in cosmology.
\end{itemize}
As you will see in further responses below, even though SN Refsdal was lensed by a galaxy cluster, since its discovery in 2015 the vast majority of the literature on lensed SN has focused on the prospects for building cosmological samples from galaxy-lensed SNIa like SN 2016geu. Furthermore, SN Refsdal required dozens of HST orbits over several years of monitoring and follow-up. With SN Requiem we are demonstrating that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed SNe. This event is ready and waiting for the final time-delay measurements with just two epochs of imaging. The long time baseline virtually ensures that this event will deliver a time delay measurement with sub-percent precision, making this class of lensed SN a very low-cost but high-value target population.}

\one{The authors make an important point about the utility of cluster scale lenses with long time delays for cosmology given that most lenses will be at galaxy scales with short time delays and affected by microlensing. Why do the authors think that the VRO survey won't find cluster scale lensed SNe ? Assuming that they can be found, the projected constraints in Fig. 3 may then be biased corresponding to the VRO sample, at least. Similar revision for RST may be required too.
}{This is a very valid point, and we've attempted to clarify this in the text on \hlt{page 7 (blue text, line 134-135).} In brief, the VRO and Roman lensed SN samples will indeed include cluster-lensed SNe, but almost all previous analyses of these surveys have been limited to galaxy-scale lenses.\\
For brevity, we did not expand on the literature context in the text, but we will here. :\\
- Oguri \& Marshall 2010 did not consider clusters. They were limited only to elliptical galaxy lenses (which they assessed would make up $>80\%$ of all lensed transients in modern wide-field surveys.)\\
- Goldstein \& Nugent 2017, Goldstein et al. 2019 and Wojtak et al. 2019 were also all limited to elliptical galaxy lenses.\\
- Pierel et al. 2021 analyzed the Roman Space Telescope, considering only galaxy-scale lenses.\\
- Petrushevska et al. 2018 and Petrushevska 2020 have addressed cluster-lensed SNe, but they have explicitly limited those analyses to time delays $<5$ years, because of the JWST lifetime.  Note that we have added these references in the ``Future Discoveries" discussion \hlt{in the Supplemental Note, p 42-43)}.}

\one{On a related point, it is unclear what kind of lenses were used for the simulations of VRO and RST survey samples and what properties are considered when the authors simulated ``AT 2016tbd-like" ? The text suggests something regarding the ratio of the source redshift to lens redshift but what about other parameters such as the lens mass scales, redshift range, time delays ? How do they compare with the J0138 lens?}{The simulated ``AT 2016tbd-like" sample is constructed to mimic the time delay and redshift properties of the discovered object. That is, we have assumed a redshift ratio that matches the observed redshift ratio of SN AT 2016tbd, and we have assumed that the time delay can be measured to $<1\%$ precision, as would be the case for other cluster-scale lenses with decade-long lensing time delays.  This has been clarified in the text \hlt{(page 7, blue text, lines 148-149)}}

\one{What is going to be the significance of the analysis of this system in 2037, assuming many more lensed SNe are likely to be found by planned and future surveys? Note that it is unlikely we will have only about 5 systems with long time delays in the next 17 years. A sentence on this point needs to be added.}{
We do not expect that this system alone will stand out as a singularly important system in 2037, in the same way that one of the Type Ia SNe like SN 1991T or SN 1991bg was not particularly important in and of itself after a decade. As with those seminal Type Ia discoveries, the value of this system will be that it provides a benchmark for a class of objects that can collectively be important for lensed time delay cosmology. A sentence reflecting this has been added \hlt{(page 7, lines 131-132)}}

\two{On a more general note, it would be surprising to most if 20 years from now, with the slew of ground and space-based cosmology surveys in the pipeline, current day precision estimates of the Hubble constant and the Dark Energy equation of state parameters are a relevant point of comparison. Thus, it is hard to get excited about potentially(!) getting a precise time-delay estimate 17 years from now.}{

This is fair enough.  However, you could also ask how many in the cosmological community would have predicted in the year 2000 that a tension in the measurement of $H_0$ would be a hot topic in 2020?

We don't really know what is coming 10 or 20 years from now, but the strength of the dark energy enterprise is in the many complementary methods we have available.      Anticipating this precise time delay in 17 years should motivate us to continue building the tools to make cluster-lensed SNe a more fully developed part of that cosmology toolkit.
}

\section{Supernova Classification}

\one{Fig. 2 Right panel: There's no comment about the fact that the best-model-predicted-unlensed magnitudes of images 1-3 are above the curve showing the evolution.}{
\textit{Note that this figure has been reconstructed, so the panel referenced is now panel (c)}\\
A number of effects could account for this, though we would caution readers not to over-interpret the limited data (granting that we ourselves are doing everything we can to squeeze reasonable inferences out of these few data points).    We have added a brief comment in the text addressing this (page 5, blue text, lines 89-93). \\
  For the interested referee, we elaborate:\\
- The well-known mass sheet degeneracy (MSD) is one plausible explanation, in which an intervening mass sheet between the observer and the lens can systematically shift the absolute magnifications of all background sources, without altering their relative magnifications, or the apparent positions of the multiple images (Falco, Gorenstein \& Shapiro 1985).   Note that the MSD would also not impact the time delay predictions or observations.  More general related degeneracies can have similar systematic effects (Schneider \& Sluse 2014).   Impacts of these degeneracies can be mitigated by including many multiply imaged systems at different redshifts as input constraints for the lens models, and including spatially resolved kinematics of the lensing system (e.g. Birrer et al. 2016, Shajib et al. 2019).\\
- If the points had landed below the curve in the right side of Fig 2, then this source would have looked more consistent with the CC SN population.  Invoking the MSD or a similar degeneracy might then have been an important consideration in evaluating the classification of the source.  However, since the points fall above the line (brighter than expected), this makes the source even less likely to be a CC SN (one would need to invoke an even stronger mass sheet effect to bring those points into the CC region of the diagram. \\
- The key takeaway we would like readers to get from that panel of the figure is that the three points follow the trend that would be expected for a Type Ia SN evolving over time.  They are consistent with the curve, and the offset could reasonably be explained by a well-known lensing effect.}

\bigskip
\textit{Several comments from referee 2 raise concerns related to the classification reported in the Table S6 and Figure S2. \hlt{(NOTE: Table S6 is now Table 7 on p.23.   Fig. S2 is now Fig. 6 on p.24)}}
\medskip

\two{Issue \#1: Classification\\
It is of course painful that the late discovery of the 2016 transient, a presumed supernova explosion, prohibits spectroscopic identification and photometric follow-up which would have allowed a proper classification of the transient, as well as establishing accurate times for a later time-delay measurement.\\\\
The authors have tried very hard to overcome these shortcomings by using both the properties of the presumed host galaxy at z=1.95 as well as the HST NIR imaging in two bands from 2016, when three images of the transient were detected. However, while certainly plausible, I find that the authors fail to present a clear case for the ``90\%" confidence of this being a Type Ia supernova. Figure 2 in the main journal article is what the authors have chosen to demonstrate this. I find this figure quite hard to read and interpret I can agree that it shows that a SNIa classification is acceptable, while I cannot really tell if other classifications are significantly worse. This becomes even more problematic while looking at Fig. S2, where I find it quite unlikely that the authors can make claim that the dotted line (SNII) is a worse statistical fit than the solid line (SNIa).}{
The referees have identified a clear failing in the presentation of this photometric SN classification.  As previously constructed, Fig 6 (formerly S2) was visually misleading, because the light curve models shown were the maximum-likelihood fits.  As such, they were only showing a goodness-of-fit, not a true posterior probability.    As previously noted in the text of the supplemental materials: \\\\
``This figure shows that the limited photometric data can be reasonably well fit by at least one model from any of these three sub-classes. However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types than for the Type Ia class."\\\\
When computing a full posterior probability, the STARDUST2 algorithm computes the likelihood over a wide range of CC SN models (light curve templates) and model parameters (time of peak, luminosity, host galaxy dust extinction).   The total Type Ia classification likelihood is also computed by marginalizing over a wide range of light curve parameters for the SALT2 model (t0, x0, x1, c).   Therefore the previous Figure S2 was not very informative, because it only showed that any of these SN sub-classes could provide a good fit to the data with at least 1 set of parameters.\\\\
We have now provided a new figure 6 that shows a representative set of light curves and F105W-F160W color curves from the STARDUST2/sncosmo nested sampling chains.   This shows that although there are a few examples of Type Ib/c or Type II models that can fit these data with a low $\chi^2$, there is a much greater density of Type Ia instances that do as well or better.   The net effect is that the Type Ia likelihood distribution has a broad plateau of high likelihood across parameter space, while the CC distributions have a few spikes with a much wider region of low likelihood.  Multiplying each of these likelihood landscapes by the host galaxy priors serves to further enhance the Type Ia posterior probability relative to the collective Core Collapse posterior.  
}

\two{Moreover, when it comes to all the non-Ia supernovae alternatives, the authors are no longer dealing with ``standard candles". Thus, while the SED templates used produce some sort of generic behavior for the bulk of core-collapse supernovae subtypes, individual light curves observed in the local universe show a great deal of diversity within the same sub-type classification, rendering a classification based on such limited data and strong assumptions very doubtful.}{
It is certainly true that we should not take the limited set of CC SN SED templates as fully representative of the CC SN subtypes.  This is exactly why we begin our classification by comparing the photometry against a smoothed representation of the entire population for each subtype, in color-magnitude space (Fig 2a, and again in Fig 4 in the Methods).   In these figures, the gaps in the SN template library are smoothed over by random sampling and removal of the time dimension.  We can already see that the three observed data points are much more consistent with the red ``Type Ia" cloud than either of the CC SN clouds.   Combining this ``birds eye view" with the more granular light-curve and color-curve view in the revised Figure 6, we believe that we've now given solid visual support for the quantitative classification probabilities reported in the text. \\\\
We do acknowledge that this methodology is imperfect, especially when applied at high redshift where the SN populations may have systematic differences due to demographic evolution.    However, this approach is not dissimilar to the classification used for other SN at similar redshift and with similarly limited photometric information.   For example, see: \\
\url{https://ui.adsabs.harvard.edu/abs/2018ApJ...866...65R/abstract}\\
\url{https://ui.adsabs.harvard.edu/abs/2018MNRAS.479.3563F/abstract}\\
\url{https://ui.adsabs.harvard.edu/abs/2013ApJ...768..166J/abstract}
}

\two{Furthermore, the identification makes use of the LENSTOOL estimates of the time-delays to spread the measured photometry in time. Examination of table S7 with the 5 lensing models shows dramatic differences in establishing the relative age of the SN images at the time of observations.}{
It is very true, as Referee \#2 points out, that all of this photometric classification is strongly conditional on both the presumptions of SN population correlations with host galaxy properties, and on the adoption of magnification corrections from the lens model.  Please note, however, that the classification of this source as a likely Type Ia SN does not rely strongly on the lens-model-predicted time delays.  The classification information summarized in Figure 2 reflects the classification result of p(Ia)=0.95 that appears as row (c) in Table 7.   This was made without including any time delay correction.   As shown in Figure 2b, the color-magnitude data alone is suggestive of a time delay of ~100 days between image 2 and images 1+3, if this is a Type Ia SN.  We feel that the overall Type Ia classification inference is strengthened by the fact that the lens model independently (and in a blinded analysis) predicted roughly that same time delay.\\ \\
When we do include the lens model time delay to put the three points together as a single light curve for classification, we find an almost identical classification probability:  p(Ia)=0.94, reported in row (d) on Table 7.   This reinforces the fact that the lens model time delay is not introducing new information that is essential to the classification. \\\\
 If any of these priors are changed (by future observations or new lens modeling) then the classification should be updated accordingly, as a good Bayesian does.   We have attempted to include appropriate caveats throughout the text, though most of these are in the supplemental material.   Although we prefer to be quantitative when presenting results, we acknowledge that the subtleties of classification are elided by the headline statement in the abstract of ``>90\% probabibilty".    To make the reader more immediately aware of the limitations of the classification evidence, we have changed this to a ``likely" classification, which is a little squishy, but certainly encompasses the range of 60-95\% classification probabilities presented in Table 7.     When we present the classification in the main text we have also added a statement to point out that we are proceeding with the assumption that this object is a Type Ia SN, but if future observations show it to be a CC SN, much of the same analysis can be repeated, simply using a different light curve model  \hlt{(page 6, line 114)}.   As long as the ages of the first three SN images  can be constrained to within $\pm$300 days (not a high bar), the time delay measurements will have better than 4\% precision and be subdominant in the error budget of any cosmological inference.}

\two{While the nature of the host galaxy is suggestive of a SNIa host in the local universe, however, it is hard to quantify the applicability of this inference at redshift 2.}{
It is true that there are not enough SN detections at z$\sim$2 for us to rely only on a purely empirical approach to correlating SN class with host galaxy properties.  However, for this host we have not only the observables (luminosity, color) but we also know something about the physical properties of the galaxy (mass and star formation rate).   We can therefore use a correlation to the SN population that is strongly physically motivated: the progenitors of CC SNe are more massive than Type Ia SN progenitors, so when a galaxy has an older stellar population we should expect that it will preferentially host Type Ia SNe over CC SNe.  \\\\
In Table 7 we have presented both of these possible host-based classifications.   Row (a) shows that we infer p(Ia)=0.75 when considering the host galaxy's bulk observed properties ($M_K$ and $B-K$).   This is the inference that should be treated as most suspicious when translated to z$\sim$2.    Row (b), however, uses instead the inferred mass and star formation rate of the host galaxy, which gives us the more solid footing of a physically-motivated association to SN class. 
\\\\
You may be concerned that at high redshift we should even be suspicious of the correlation of stellar population properties with SN rates and subtypes.   To address this concern, we would refer the reader to Rubin, Hayden et al 2018 and  Meyers et al 2012, two studies from the Supernova Cosmology Project that examined this question in some detail, for SN host galaxies that are quite similar to the one presented here.   Those authors consistently found that the host galaxy physical properties remain a reliable indicator for SN Ia classification even at z>1.5. 
\\\\
In our analysis we adopt the physically-motivated host galaxy classification (row b of Table 7) as the prior for all subsequent classification probabilities. 
\\\\
\url{https://ui.adsabs.harvard.edu/abs/2012ApJ...750....1M}\\
\url{https://ui.adsabs.harvard.edu/abs/2018ApJ...866...65R}
}

\one{ For the color-mag calculation of the host galaxy, which image was considered and what was the magnification factor used?}{
\textit{NOTE: this is referring to the method ``a'' in \hlt{Table 7 (formerly table S6).}}

In the text we have specified that

``We adopt a lensing magnification correction using LENSTOOL model E to get MK. The B-K color is not affected by the foreground lens.''

We used image 2 and a flux-weighted mean magnification for the galaxy, which is now reported in the new \hlt{Table 7 on page 23}, part of the newly-added subsection on Comparison to Previous Lens Modeling. We verified that using either of the other host galaxy images instead does not impact the results. The text on \hlt{page 22, lines 311-314} has been updated to clarify this.
}

\two{There is one extra test the authors could try, to leave no stone unturned. The Spitzer observations from Oct 2016 could potentially have been sensitive to the restframe J-band second maximum for a SNIa at z=1.95. It would be interesting to see if these observations have any constraining power or not.}{

Great suggestion.  We evaluated the Oct 2016 Spitzer observations in IRAC CH1 and CH2.  The best chance for a detection or constraint would be for image 2, the brightest and the one at the earliest  phase.  At the time of the IRAC observations, the image 2 phase would be $\sim$67 days after peak brightness, and we would expect it to have AB magnitudes  26.1  in both Ch1 and Ch2.   Unfortunately, this is several magnitudes fainter than the 1-$\sigma$ noise floor of about 23 to 23.5 AB mags for those IRAC bands.  So we do not have any constraining power from those Spitzer observations. }

\subsection{Figure 2}

\one{Fig. 2 Caption: Sentence about open/closed markers and dotted/solid bars is confusing. Use simpler sentences.}{
The caption has been updated to be more clear.}

\three{Figure 2 (left) and Figure S1: The caption of Figure 2 states that the simulated SNe had their color-magnitude sampled uniformly in time. Does this mean that the authors simulated 10,000 different SNe, then sampled a random time on each SNe's light curve once? Does this method account for the limiting magnitude of the observed data, which might cause a bias toward certain regions in color-magnitude space (i.e. certain SNe might only be detectable at certain points in their light curve)?}{
Yes, the referee's understanding of the sampling method for this figure is exactly correct.

The point regarding limiting magnitudes has been addressed with new text in the Methods section \hlt{(maroon text, page 25, lines 343-347):}

``Note that in this case there is no need to apply a cut to the simulated sample to account for detectability, because the 5$\sigma$ limiting magnitude of our HST observations is 26.5 AB mag, and after accounting for magnification of $\sim$1.5 mag (Table 5) this becomes $m_{lim}\sim28$ mag. This means that all the points shown in Fig. 4 (and therefore all simulated SN entering our classification counts) would be easily detectable in our HST imaging.''   
}

\three{The ``stellar-population-based host galaxy classification'' prior presumably accounts for the expected rates of the different SNe types, and is reflected in the top and right panels of Figure S1, but this doesn't seem to come across in Figure 2 (left). This could potentially be misleading, as a casual reader might look at the left panel of Figure 2 and think that an SN Ib/c isn't all that inconsistent with the data, but the prior effectively rules it out. Maybe some additional text in the caption, or some indication of the priors in the figure itself would be useful.}{
We have updated Figure 2 to include a new sub-panel (b) that shows the distribution of our SN simulation in color space, after applying the host galaxy priors (as was previously reflected in the Methods \hlt{Figure 6, formerly Fig. S1).}  The caption  of Fig. 2 also more clearly explains how the host galaxy stellar population properties that were used here.
}

\three{Figure 2 and Figure S1: Do the filled points represent the median magnitude of the images after the magnification correction? It's not clear why the solid vertical line (representing the magnification uncertainty) only extends below the filled points and not in both directions.}{
Yes, the filled points represent the magnification-corrected magnitudes.  We have attempted to make this more clear with labels in the figure, and words in the caption of Figure 2 and the text.    Given the limited space available in the main text, we have opted to keep the discussion of the asymmetric error bars in the Methods section \hlt{(maroon text, lines 265-268 on p.18-19; and see also the green text, lines 339-341 on p.25)}}

\section{Time Delay}

\one{An uncertainty of 1.5-2 yrs in the predicted event is still fairly large for the follow-up observations to ensure that the 4th image is observed at the right time. How practically feasible is it going to be to be able to follow-up and detect the SN right when it goes off?}{
This is indeed a concern.  We hope that future observations of the lensing cluster (e.g. with JWST) will provide more lens modeling constraints.   The significant redshift of the SN and the associated cosmological time dilation is also an advantage for a future monitoring campaign.  We have laid out the reasoning for this in a new subsection ``Future Observations" note in the supplemental material \hlt{(page 41-42)}}

\two{Issue \#2: time-delay\\\\
As already pointed out above, the classification can be questioned. Even assuming it is right, the authors go on to make unsubstantiated claims on how well the light curve parameters are measured, including the time of maximum, needed to measure time delay. }{
We will do our best to more clearly substantiate our results here.  Additionally, we are using open-source code, and publishing all of the measurements used in this analysis, so we hope that a reader who is still skeptical can proceed with their own analysis if needed.  }

\two{First of all, they seem to set x1=0 in the SALT2 fit, without proper motivation. }{
The referee has raised a reasonable point that we did not explain the handling of the SALT2  x1 parameter in great detail.    If you allow x1 to float, there is no useful constraint on it, because it is quite degenerate with the time delay between the images, which is of course a free parameter in all the fits.    Because of this, in the fiducial analysis we opted to fix x1=0 throughout the time delay fitting process.    We have also tried fixing x1 to other values from -1 to +1, and the time delay results change by less than 5 days  for both the color curve and light curve fitting, which is well within all error bars.  We argue that it is justifiable to fix x1, since we expect that a full light curve of the fourth SN image will provide a tight constraint on x1, which can then be propagated back into the fitting of the SN images 1-3.   The text has been updated to explain this more clearly \hlt{(green text in the Methods, page 28-29, lines 401-410).}
}

\two{Then, they claim that they constrain the SALT “c” parameter to an accuracy of just 0.05 mag. This is hard to believe, as such good accuracy is among the best that has been achieved in SNIa cosmology based on far better data-sets. }{
It is certainly reasonable for Referee \#2 to be surprised by the precision of this constraint on the SALT2 ``c" parameter.   As we investigated this, we discovered that there was a book-keeping error in our analysis code which was indirectly related to this: we were using the wrong column from our photometry table (aperture flux instead of PSF fitting flux, but without additional uncertainty for the aperture correction).  Correcting this led to a revision of the overall constraint on SALT2 c.  We now report this as  $c=0.04^{+0.05}_{-0.07}$.    In spite of this slightly larger uncertainty,  the referee's concern should still apply.

There are two components that lead to this unexpectedly precise measurement:

\begin{enumerate}
\item{The photometry is uncharacteristically good, especially for the brightest image (SN image 2).  This image has an AB magnitude of 23 in F105W (Y band) and 23.8 in F160W (H band) (see Table 3).  It was observed with a full 2 HST orbits of exposure time ($\sim$1.5 hours) over those two bandpasses.  The vast majority of Type Ia SNe in the literature do not have HST photometry at all, and this may be among a very few SN to get such an investment of exposure time on a single epoch at this magnitude.    The HST WFC3-IR ETC estimates that the S/N for a point source at this magnitude and exposure time should be  S/N$\sim$200 in F105W and  S/N$\sim$125 in F160W.   Our photometry measured S/N = 173 for F105W and S/N=71 for F160W (the difference attributable to the elevated background noise due to the cluster light or the use of a ``pseudo-template" as described in the Methods).}
\item{These three SN images happen to be almost optimally placed to provide a tight collective constraint on the SALT2 c parameter.   If we consider each observed image separately, we can accommodate the observed F105W-F160W color with a wide range of SALT2 c values, simply by adjusting the assumed phase (time since peak brightness) of the SN for that image.   This is shown in Fig~\ref{fig:salt2c_vs_phase} (here in the referee report, not in the paper), where each image traces out a curve in the parameter space of ``SALT2-c vs observer-frame phase".   The width of each curve shows the $\pm1\sigma$ spread in the c parameter due to the photometric uncertainty on the observed F105W-F160W color.    If we only had images 1 and 3, then we would have very weak constraints on the color parameter c, because the curves overlap.  Similarly, if we only had image 2 alone, without an independent constraint on the phase, then we would have a weak constraint on c.   In this case it just happens that there is only a small range of c values that can accommodate \textit{both} image 2 and images 1+3 in this parameter space.  The dashed lines show this range, measured here as c=0.02$\pm$0.09, which is consistent with the constraint we get from the more complete and rigorous light curve fitting procedure described in the text.   Note that this serendipitous arrangement also helps to simultaneously constrain the phase of each of  image, as shown in the supplementary text.}
\end{enumerate}

Another way to see this is to look at the F105W-F160W color curve in Figure 11.  Changing the SALT2 c parameter would shift the grey curve up or down.  Adjusting the relative phase for each image can shift the points left or right.  Since the points happen to sit near the extrema of the color curve, there is not much room for changes in either c or t0.

In summary, we agree that the color constraint is unusual, but find it is explainable given the unusual photometric precision and the lucky complementarity of the three time-delayed images.
}

\iftwo
\begin{figure}
    \centering
\includegraphics[width=0.7\textwidth]{Paper/ResponseToReferees/snrequiem_color_constraints.png}
    \caption{The SALT2-color vs. Observer-frame Phase. The serindipitous positioning of the three SN images is highly effective for a joint constraint on SALT2 c.  This figure is for illustrative purposes only---meaning that we did not use this construction for placing constraints on the SN color or phase. }
    \label{fig:salt2c_vs_phase}
\end{figure}
\clearpage
\else
\fi

\two{The waters turn even muddier when looking at Fig. S6 showing the bimodal nature of the fits, rendering the quoted SN ages, and especially their uncertainties, hard to defend. E.g., the central value for the quoted ages of Images 1 and 2 seem to be sitting at a local minimum of their probability distribution. If I have misunderstood this, others may as well. Thus, a clarification is needed.}{

Yes, the referee is highlighting here an issue of presentation that we wrestled with.  We were torn about how to present the interpretation of these bimodal distributions.  We expect that future observations of the final appearance of the SN will provide better constraints on the intrinsic light curve shape, which would collapse those distributions to one mode or the other.  Therefore, the expected final  precision of each parameter would be accurately represented by picking a single peak from the distribution. However, there is no good way to collapse the degeneracy in advance.    We opted for a concise presentation of the uncertainty, though it was somewhat muddy.

Happily, this problem has resolved itself.  After correcting the book-keeping error on the photometry described above (using the wrong flux column), we have re-run the time delay fitting with SNTD and find that the posterior distributions are significantly  less bimodal.   \hlt{Figures 9 and 11} now show these corrected  distributions.  As you can see from our combined constraints in the updated Figure 11 on \hlt{p.36},
the 50th percentile is no longer at a local minimum for any parameter. We have opted therefore to still use the 16th and 84th percentiles to report the uncertainties in the text. }

\two{Issue \#3: The big picture, precision\\\\
Figure 3 in the paper, and the text that goes with it, argues for the competitiveness of events like AT2016tbd (assuming 4 more are found) as precision tools for cosmology. This is a bit of a stretch. First of all, the time scales involved, decades(!), hardly argues in favor of this being a very competitive probe. It is not even clear what instruments will be around to measure the light curve of fourth de-magnified image of AT2016tbd, and get a spectrum to finally settle on the classification. Furthermore, it is clearly not so that a 1\% uncertainty on time-delay (which is small enough for the lensing model considered) require AT216tbd like systems, with two decades between multiple images. The median uncertainty on the light curve peak MJD of the Pantheon compilation of SNIa used in cosmology is under 0.3 days, indicating that systems with time-delays of $>$50 days are already at that level of accuracy, if a SN cosmology type of light curve sampling is performed.}{

The referee's skepticism is understandable, but we feel that this essentially boils down to a cost/benefit analysis.  SN Requiem represents a class of objects that is not currently getting much consideration in cosmological projections (indeed, we have been guilty of overlooking cluster-lensed SNe ourselves—Pierel et al. 2021).   In this section of the paper we are not arguing that pursuit of other cosmological probes should be abandoned, but rather that cluster-lensed SNe should be included in the conversation.   For example, suppose that a future Roman Space Telescope GO program is approved, with fields that include strong-lensing clusters (someone will surely write that proposal).  This paper should help make the case for that GO program to use a cadenced observing strategy to enable detection of more AT 2016tbd-like events.

The source-to-lens redshift ratio is another aspect of AT 2016tbd-like events that makes them interesting as additions to the cosmological toolkit.  As shown in Fig. 3, the contours in cosmological parameter space are highly complementary with other lensed SN time delays, due primarily to the unusually high redshift ratio of a typical cluster lens relative to galaxy-scale lenses.

Regarding the future observations of AT 2016tbd, we have complete confidence that there will be suitable observatories available for follow-up.  Even if there is no space telescope for high-resolution imaging to capture the light curve, we can count on the availability of ground-based AO imaging with NIR detectors in the 2030's and beyond.  Furthermore, the ground-based ELTs will be excellent for spectroscopic classification.  High S/N spectroscopy can even be used to measure lensed SN time delays (Johansson et al. 2021, Bayer et al. 2021).

Regarding the precision of other lensed SN time delay measurements:  unfortunately the precision on the time of peak measurement from the Pantheon sample is not representative of what we can expect from lensed SNe.   For light curves from ground-based observatories like LSST, most lensed SNe will have blended PSFs from multiple overlapping SN images.  One must also consider microlensing effects that perturb a lensed SN light curve (and are more problematic for galaxy-lensed SNe than cluster-lensed events like AT 2016tbd).    All analyses to date that have incorporated some of these complications have found that there is a floor of about +- 3 days, even for very high-quality light curves such as those expected from the Roman Space Telescope (Huber+ 2019, Pierel+ 2021).    As an absolute floor, one could look to the analysis of Goldstein et al. 2018, which found that microlensing of galaxy-lensed LSST SNe leads to a minimum uncertainty of 1\% to 4\% on the time delay, though this analysis assumed 45 observations with an HST-like system delivering  ``infinite signal-to-noise, with a uniform temporal spacing, spanning the light curve."

\noindent\url{https://ui.adsabs.harvard.edu/abs/2021MNRAS.502..510J}\\
\url{https://ui.adsabs.harvard.edu/abs/2021arXiv210106229B}\\
\url{https://ui.adsabs.harvard.edu/abs/2019A\%26A...631A.161H}\\
\url{https://ui.adsabs.harvard.edu/abs/2018ApJ...855...22G}
}

\one{It should be noted that images 1 and 3 are minima which are less susceptible to high deviations owing to microlensing compared to image 2 which is a saddle. }{

We have added this point in the \hlt{blue text on page 29, lines 425-426.}\\

Under our assumption that this SN is of Type Ia, we constrain the age of the SN at image 2 to be at or before peak brightness. This age is well within the projected ``achromatic phase'' of microlensing ($\sim$3 rest frame weeks after explosion), so our use of the SALT2 color curve to constrain the time delay for image 2 will be minimally impacted by microlensing.   If the magnitude of image 2 was significantly biased by microlensing, then we would expect the light-curve-based time delay estimate to be significantly different from the color-curve-based time delay estimate.  The fact that these two methods agree does reinforce the hypothesis that there are no extreme microlensing impacts on the SN images. }

\section{Lens Modeling}

\one{Table 1: What do the errors on magnification correspond to in Table 1?}
{ The magnifications listed in Table 1 are derived from the lens modeling.   As with the components of the mass model, the magnification uncertainties are derived from the MCMC models by sampling their posterior probability distribution (see the Lens Modeling section of the supplementary materials).   For a detailed analysis of magnification uncertainties in the LENSTOOL modeling framework, we would refer the reader to the original LENSTOOL paper (Jullo et al. 2007).\\ \url{https://iopscience.iop.org/article/10.1088/1367-2630/9/12/447}}

\one{Why are the absolute errors so small for SN images 1 and 4?}{
\textit{Note: after adjusting the labeling of the SN images to match Newman et al. 2018, the previous image 1 is now image 3.  So this comment refers to the lens model predictions for the magnifications of SN images 3 and 4, reported in Table 1 as 3.9$\pm$0.5 and 0.4$\pm$0.2, respectively.}\\
These represent the uncertainty from the final lens model, E, and give the formal 16-84\% confidence interval of the distribution of magnifications derived from the MCMC sampling done by LENSTOOL.  They are therefore statistical uncertainties only, and do not reflect possible systematics related to choices in the setup of the lens model.  Newman et al. 2018 explored systematic uncertainties for the magnifications of this MRG0138 cluster by constructing variants of their LENSTOOL model.  Those authors found systematic uncertainties of 30\% to 43\%.    We have similarly explored variations in the LENSTOOL modeling (models A through E, as described in the Lens Modeling section in the Methods addendum).  The range of magnifications across these five model variants can is reflected in the magnitude uncertainties shown in Figure 2 
(and again in \hlt{Figure 6} in the Methods section).   When classifying the transient, we have used the full range of magnification uncertainties across all 5 lens model variants—so we are in fact using an estimate of the systematic uncertainties for the SN analysis.   
These last points were not clear in the originally submitted text, so we have added text to clarify \hlt{(green text, page 25, lines 339-341).}}

\one{Please add predictions for image 5 in the table. }{

This refers to \hlt{Table 1, now on page 12}
We have updated Table 1 to show the lens model E magnification (basically $<0.01$ in all models) and time delay predictions for SN image 5.}

\one{Do the authors understand why the time delays are so poorly constrained?}{
The lens model has poor constraints for the time delays primarily because of the limited number of physical constraints in the immediate vicinity of the transient source.   For MACS J0138 we have three multiply-imaged systems to use.  For comparison, the lens models of the cluster MACS J1149 that were used to make time delay predictions for SN Refsdal began with 10 multiply-imaged galaxies, and were updated to include 30 individual knots within the face-on spiral that was the SN Refsdal host galaxy (Treu et al. 2016).   We can not hope that MACS J0138 will ever yield quite that richness of lens model constraints, but it could certainly be improved in coming years.   This is addressed in our new note in the supplemental note ``Future observations" \hlt{(p.41-42).}
}

\one{Couldn't the relative magnifications of the SN1-3 be used to get more accurate predictions for the time delay? In fact, one may even want to go with the assumption that the transient is truly a SN1a and make use of the absolute magnifications to better constrain the lens model and see how the time delay predictions are affected.}{
It would indeed be interesting to incorporate magnifications as constraints, though this would be at the cost of a fully blinded analysis, which is methodologically valuable.    An example of using the magnification of lens-magnified Type Ia SN to test lens models was presented in Rodney et al. 2015 (\url{https://ui.adsabs.harvard.edu/abs/2015ApJ...811...70R/abstract}).   With a full light curve of the lensed SN from the fourth image (c.\,2037), one could derive a measurement of the peak apparent magnitude in the B band, $m_B$.  Then one could use the collection of non-magnified Type Ia SNe at similar redshifts to provide a prediction for what is the ``expected" peak magnitude, thus delivering a measure of the lensing magnification for AT 2016tbd that is largely free of cosmological assumptions (see Rodney+ 2015 for details).   This, however, will be limited in the near term by the dearth of well-measured Type Ia SNe at $z\sim2$.   By 2037 we can expect that the $z\sim2$ SNIa sample will be substantially expanded by, for example, the Roman space telescope survey, so this kind of analysis should in fact be possible.   The new ``Future Observations" supplementary note discusses this  possibility \hlt{(pages 41-42)}}

\one{Cluster lenses are better for cosmology because they produce longer time delays but they also have more complex mass distribution and tend to have relatively massive structures in the line-of-sight which can affect the observables (e.g. see the spread in the SN Refsdal predictions of magnification vs time delay in Kelly et al. 2016). These caveats need to be mentioned and that different challenges exist at both galaxy and cluster-scales. }{

We absolutely agree that cluster lens modeling is a very different beast than galaxy-scale lens modeling, and both have distinct challenges.   We have updated the text to more clearly acknowledge this, and also took the opportunity to highlight the value of cluster lens modeling as a means for testing systematics. \hlt{ (blue text, page 7, lines 142-146)}
}

\one{ The radial magnification of image 4 and the position of the image 5 are not included as data constraints which is probably going to affect the constraints on the density profile and as a result magnification along with the time delays. Why are these constraints not taken into account?}{

The Lenstool code is not structured to allow the use of observed fluxes as a constraint when using image plane optimization.   It can only be done when using source plane optimization.   We find the image plane optimization is more robust here compared to source plane optimization because it deals better with actual positional uncertainties.

We recognize that additional lens modeling of this cluster could use alternate approaches that may be informative, and may improve on our model predictions.  We hope that this work will encourage such efforts.  }

\one{  Newman et al. have used pixel data as constraints from images 1-3 and attempted sophisticated modelling of the lens. The model predicted images 4 and 5 can be compared with the data in their paper. How does the preferred model E compare with that of Newman et al. e.g. predicted magnifications of H1-H3 from their rough Sersic models? Does the preferred model predict the location of Image 5 correctly ? }{

This is a very good suggestion to provide a more explicit comparison to the Newman et al. (hereafter N18) model predictions.   We have added a new Supplementary Note \hlt{(p.39-40)} that compares our lens model E against the N18 lens modeling methodology and magnification predictions.
This is referenced in the lens modeling discussion on \hlt{p.21 (lines 278-281)}.

The new \hlt{Supplementary Table 1 on p.39} shows that our magnification predictions are fully consistent with the N18 values, when comparing the flux ratios averaged over each galaxy image profile.    Our model E does yield systematically lower magnification predictions compared to the N18 model.   This is consistent with our own estimate of lens modeling systematics (our lens model variants A-D also yield higher magnifications than model E).    We note that slightly higher magnifications would in fact result in a more “normal” SNIa absolute luminosity. 
}

\one{Table S4: The velocity dispersions for the BCG and other components in the table look unrealistically small. My assumption is that PIE parameters are not too different from the SIE model. How could this produce such a large image separation in the lensed images?  Also, the rcore for the DM component is too big compared to the rcut. These parameters look very strange. One cannot just rely on Bayesian evidence.}{
\textit{(Note: this is now \hlt{Table 5 on p.19})}\\

Thank you for noticing this.  We made a mistake when converting that table into Latex.  We mixed up the ordering of columns between $r_{cut}$, $r_{core}$, and $\sigma$.  This resolves the issues the referee pointed out, and it is now corrected in the resubmitted manuscript.}

\one{ Isn't there any measurement of the stellar velocity dispersion of the BCG which could constrain sigma in the model instead of keeping it free ?}{
At the referee's suggestion, we have measured the velocity dispersion of the BCG from our MUSE data, finding it to be 390$\pm$10 km s$^{-1}$. We now report this measurement in the Methods section, \hlt{blue text, page 15, lines 211-214}.

We explored the effect of including this in model E, but we did not develop a complete new model with this additional constraint.  At this point, such a model would not be blind, and therefore would require a separate discussion in the paper to describe its impact on the SN classification and time delay.  This would be difficult to do within the limits of a Nature Astronomy letter.

Though we prefer to restrict ourselves to the blind model E in this paper, future work on this cluster could and should incorporate the measured BCG velocity dispersion. With a preliminary extension of model E we have explored what the impact will be, and find it will likely be within the range of our current systematic uncertainty estimates.  See the new Supplementary Note on Future Lens Modeling \hlt{(blue text, p.40-41)}
}

\one{Since only the positions of the lensed images are used as constraints, the mass model possibly doesn't have many degrees of freedom. }{
This is a reasonable point, and certainly argues for the value of future lens modeling work on this cluster. The Newman et al. lens modeling did include pixel-level constraints, and we are encouraged that our model predictions for the magnifications are very consistent with that work (see the new Lens Model Comparison section in the Methods). We feel that the mass model is sufficiently well-constrained for the purposes of this paper (classification and preliminary predictions). To actually use this SN for cosmology, a revised lens model will be warranted (and there is plenty of time to build that model!). We anticipate future lens models will leverage all of the pixel-level data from Newman et al. 2018, along with new data that we are publishing in this paper: positions and magnitudes of the SN and the measured velocity dispersion of the BCG. To aid in comparison of those future lens models with our predictions, we are publishing the pixel-by-pixel source model and residuals from our preferred lens model (model E).}

\one{Many of the model E parameters are fixed a priori which are probably coming from the previous models (i.e. A-D). If yes, then the best fit parameters of model E are not independent of the previous models and one cannot use the Bayesian evidence to decide which of these models are preferred. How were the model E parameters fixed a priori? }{
To fix the model E parameters {\it a priori}, we did not take values from the previous model fit and hold them constant.  Rather, we used the result of the previous model as a guide to choose {\it which} parameters should be fixed in order to get a useful improvement with the next model.  We then used observed information to set the actual a priori constraints.   This is admittedly a subtle point, and does somewhat cloud the interpretation of the Bayesian evidence analysis.  As we've revised this document, we find that the Bayesian evidence discussion is not essential to the main conclusions of the paper, and have simply removed it. 
}

\three{Page 6: The authors quote a 5\% uncertainty from lens modeling, with the potential to improve to 2\% precision with improved lensing constraints. Is this just from statistical uncertainty? What about potential systematics? In the lensed quasar community, there has been quite a lot of recent debate about systematics arising from mass profiles (see e.g., Blum+2020, Kochanek 2020a,b, Birrer+2020), and I would suspect that clusters, being more complex, would have similar issues. Also, what about potential line-of-sight effects (e.g., external convergence)}{

We agree that there is good reason to be cautious when using cluster lens models for predicting time delays or magnifications at specific locations.  Most public lens models on well-studied clusters were not designed for time delay cosmography.   Because of this, the scatter in predictions from such lens models should not necessarily be taken as an indication of the true systematic uncertainty from a model that is well constrained and designed for the task.  As an example, the most effective models designed for predicting the time delays of SN Refsdal are already able to deliver uncertainties of $<$7\% in a fully blind analysis.

It’s true that there are known parameter degeneracies in lens modeling that could contribute a systematic error term on the order of 10\%.  However, work such as Birrer et al. 2016,2020 and Birrer \& Treu 2020 propose methods to significantly reduce these impacts by way of high-quality velocity dispersion measurements and a hierarchical Bayesian modeling methodology.   Line-of-sight effects may be mitigated by 3D and multi-plane lens modeling (e.g., McCully et al. 2014, Chirivi et al. 2018, Raney et al. 2020, Buckley-Greer et al. 2020).

We believe that further progress on these methods alone may be sufficient to limit the total lens modeling uncertainty to $\sim$5\%.  Finally, under the assumption of the SN being of Type Ia we expect high-quality spectroscopy and photometry for the final image to provide additional constraints to guard against lens modeling systematics.

Even if our prognosis for more precise and robust cluster lens models proves overly optimistic, we would argue that cluster-lensed SN are still valuable in time delay cosmography.  The systematic biases of cluster lens models will always be very different from those of galaxy scale lens modeling.   The vast majority of time delay cosmography constraints will likely come from quasars lensed by galaxy-scale lenses.   As we have attempted to show in Figure 3,  just a handful of cluster-lensed SNe with precision comparable to SN Requiem will be valuable for validating the full time delay sample.
\noindent\url{https://ui.adsabs.harvard.edu/abs/2014MNRAS.443.3631M}\\
\url{https://ui.adsabs.harvard.edu/abs/2018A\%26A...614A...8C}\\
\url{https://ui.adsabs.harvard.edu/abs/2020MNRAS.492..503R}\\
\url{https://ui.adsabs.harvard.edu/abs/2020MNRAS.498.3241B}\\
}

\three{Lens Modeling section: How many individual cluster galaxies are included in the lens model? It might be useful to include a figure similar to Figure 1, indicating the location of the mass components (pointing out the four galaxies that are individually optimized), as well as the multiply-imaged features that constrain the model.}{
There are 32 individual cluster galaxies included in the lens model. Including the BCG, three perturbers, and the main cluster potential, there are 37 components in total for lens model E.  We have added a sentence in the text and a figure to show them \hlt{(p 17 lines 236-237 and Fig 4)}
}

\three{Lens Modeling section: Could the authors include a figure showing the ``reproduced" arc morphology with model E and the two Sersic sources? It's difficult to evaluate this statement without seeing the reconstructed image.}{
We have produced this figure and included it in the Methods section \hlt{(Fig 5 on p 20, referenced on page 19, line 272)}
}

\section{Other Miscellaneous Comments}

\one{Abstract says ``Hubble constant''. Add ``LeMaitre'' too.}{Done (but now in the second paragraph due to rewording of the ``abstract'' to fit Nat.Astro. style)}

\one{Add Quimby et al. 2014 reference as it claimed to have a lensed SN Ia.}{Done}

\one{In Fig. 1 or in a new figure, identify the measured image positions of source at $z=0.766$ (3.1-3.4), H1-4 and SN1-4 along with the predictions of model E.}{Fig 1 now includes the locations of the multiply-imaged galaxy system 3.1-3.4}

\three{Figure 1: It would be helpful if this figure indicated the locations of the multiply-imaged features used to constrain the lens model (the ones listed in Table S3). The text states that the ``central light peak'' of the SN host galaxy is used - presumably this is the brightest pixel at the center of each galaxy image? The images of the background galaxy at z=0.766 should be indicated as well (was the central light peak also used)?}{
Fig 1 now includes the locations of the multiply-imaged galaxy system 3.1-3.4.

The ``central light peak''  refers to the centroid position of each galaxy image, determined from the source extraction algorithm applied on the HST F105W imaging.  We have clarified this in the main text \hlt{(maroon text, page 5, line 84)}.}

\one{Fig. 3 Caption: Dashed lines are too close together and almost appear as solid lines unless seen at a highly zoomed version. White marker is transparent which appears colored due to multiple overlapping colored contours. Making it black would help.}{We have updated the figure as suggested.}

\two{ Can the authors please enlighten the readers as to what the expected rate of discoveries may be?}{

We have added a few paragraphs discussing expected rates into the new Supplementary Note section on  Future Discoveries \hlt{(green text, page 42)}.   We note, however, that the published work on this is quite limited, and we hope this paper will encourage more  effort in this direction.    The rate estimates we have cited are based on a small number of lensing clusters, and for various methodological reasons should be seen as lower limits on the expected rates.   Extrapolating these (crudely) over the next 10-15 years, we anticipate at least 10 detections each from the LSST and Roman surveys.    A more accurate estimation would include a much more complete census of lensing clusters, along with lens models to predict magnifications and time delays, and measurements of star formation and stellar mass in lensed galaxies to predict the SN explosion rate.   This is a substantial undertaking, which we would prefer to leave for future work. }

\one{Fig S3 and S5 Captions: Typo in ``image 1 (upper right)''. It will be upper left.}{
Corrected.  (These are now \hlt{Figure 8 on p 33 and Figure 10 on p. 35)}}

\one{Table S3: ID 3.1-3.4 are not identified in the image of the lens system. Could the authors point these out in Fig. 1 or show in supplementary figures?}{
Done.  Figure 1 now includes labels for images 3.1-3.4}

\one{Image order is strange. They don't seem to be ordered by apparent magnitude, time delay or magnification. Couldn't the authors keep the same numbering order as Newman et al.? It creates unnecessary confusion otherwise.}{
We have corrected this by swapping the labels for SN images 1 and 3 throughout—in figures, tables and text.   Perhaps the long delay in responding to the referee's report will mean that you've conveniently forgotten which image was which, and the swap will not be confusing. }

\one{Page 4 says 2037 +/- 1.5 whereas everywhere else the error is given as 2 yrs.}{Corrected.}

\three{Table S7: The quantities in the table should have uncertainties associated with them.}{
Corrected.  \hlt{(this is now Table 6 on p.19)}}

\two{To summarize: I am charmed by the beautiful discovery. However, I find that the current manuscript makes unnecessary claims on the cosmological implications. I don’t think these are necessary to publish a discovery paper on this rare phenomenon.}{

We appreciate your enthusiasm for the discovery itself.   Our long delay in this response notwithstanding, we are also still charmed by it.    We hope that our response and the improvements in the text spurred by your comments will persuade you that the cosmological discussion is worthy of inclusion.}

\end{document}

### 2021-05-21 Analysis/mrg/fig1.py
update fig1

@@ -72,15 +72,16 @@ def rgb():
     
     xy = np.cast[int](np.round(wcs.all_world2pix(coo['ra'], coo['dec'], 0))).T
     
-    for i in [4,5,6,7]:
+    if 0:
+        for i in [4,5,6,7]:
         
-        xi, yi = xy[i]
-        slx = slice(xi-N, xi+N)
-        sly = slice(yi-N, yi+N)
+            xi, yi = xy[i]
+            slx = slice(xi-N, xi+N)
+            sly = slice(yi-N, yi+N)
         
-        _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
+            _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
 
-        _rgb = auto_script.field_rgb(root=root, filters=['f110w','f125w','f140w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', rgb_scl=[1.06,1,1.02], suffix='.off{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
+            _rgb = auto_script.field_rgb(root=root, filters=['f110w','f125w','f140w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', rgb_scl=[1.06,1,1.02], suffix='.off{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
         
     
     import matplotlib.pyplot as plt
@@ -133,6 +134,7 @@ def rgb():
     labels = 'bcdefghijk'
     
     iters = [6,5,4]
+    iters = [4,5,6]
     if ny == 4:
         iters += [7]
         
@@ -202,7 +204,7 @@ def rgb():
             a.plot(xreg, yreg, color=colors[7])
         
     gs.tight_layout(fig, pad=0.1)
[…]

### 2021-05-21 Paper/ResponseToReferees/response_to_referees2.tex

\documentclass[11pt]{article}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{soul}
\usepackage{graphicx}
\usepackage{lineno}
%\linenumbers

\usepackage{hyperref}
\usepackage{booktabs}

%\usepackage{amssymb}
\usepackage{xspace}
\usepackage{graphicx}
%\usepackage{todonotes}
\usepackage{ifthen}

\usepackage{geometry}

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

% Remove the "Contents" label from the Table of Contents
\makeatletter
\renewcommand\tableofcontents{%
    \@starttoc{toc}%
}
\makeatother

\begin{document}

\newif\ifone
\newif\iftwo
\newif\ifthree
\newif\ifed
\newif\ifhlt

\onetrue % Response to referee 1
%\onefalse
\twotrue % response to referee 2
%\twofalse
\threetrue % response to referee 3
%\threefalse
\hlttrue  % Highlighting page number checks
%\hltfalse

\ifone
\newcommand{\one}[2]{\textbf{\textcolor{blue}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\one}[2]{}
\fi

\iftwo
\newcommand{\two}[2]{\textbf{\textcolor{teal}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\two}[2]{}
\fi

\ifthree
\newcommand{\three}[2]{\textbf{\textcolor{Maroon}{ #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\three}[2]{}
\fi

\ifed
\newcommand{\ed}[2]{\textbf{\textcolor{DarkOrchid}{Ed: #1}}\\ \linebreak {#2}\\\noindent\rule{\textwidth}{1pt}\bigskip}
\else
\newcommand{\ed}[2]{}
\fi

\ifhlt
\newcommand{\hlt}[1]{\hl{#1}}
\else
\newcommand{\hlt}[1]{{#1}}
\fi

\begin{center}
\textbf{\Large{Response to Referees}}\\
\smallskip
\today
\end{center} 
\medskip

Our point-by-point responses are presented below. In this document we have grouped the responses by reviewer.   We have color-coded each referee's comments, matching the colors used in the changetext version of the manuscript, as follows:

\begin{itemize}
\item \textbf{\textcolor{blue}{Items from Referee \#1 in blue.}}
\item \textbf{\textcolor{teal}{Items from Referee \#2 in teal.}}
\item \textbf{\textcolor{Maroon}{Items from Referee \#3 in maroon.}}
\end{itemize}

\pagebreak

\ed{As you will note, there is still a range of different opinions regarding your paper. Referee \#1 has some remaining minor concerns, however it their comments to the editor express concern about the dependence of your results on the lens modelling and how that dependence might compromise the confidence and universality of your results.\\ \smallskip\\
More seriously, referee \#2 is still questioning the relevance of your results in the context of precisions cosmology. Particularly, while they find your analysis interesting, they disagree that the proposed method is a valid tool for precision cosmology for the next 10 years.\\ \smallskip\\
Combined with the comments of referee \#1, I think it will be important to try and more accurately reflect the applicability, relevance and robustness of your method. One way to proceed would be to follow the suggestions of referee \#2 and significantly tone down your claims regarding precision cosmology and instead focus on the uniqueness of this system more generally.\\ \smallskip\\
Given the current set of reports, it will be important to convince referee \#2 if we are to consider your manuscript for publication.
}{}

\clearpage

\section{Reviewer 1 (Comments for the Author):}

\one{The authors have incorporated most of the previous comments. I have a few more comments (in no particular order) after which the manuscript could be considered for publication.\\ 
\linebreak
1. The authors have made use of positional data constraints alone, have not used data constraints from images 4-5 and have assumed one specific lens density profile in this analysis. All of these are known to affect the main predictions which are the magnifications and time delays. This is still a point of concern. The current uncertainties do not account for that. Therefore, the readers need to be sufficiently warned about the biases and uncertainties, as a result of the above. This could be done by quantifying the uncertainties to the extent possible or by adding cautionary statements in the main text and also in the abstract, at minimum.
}{
We do not disagree with the sentiment of the referee on this point.  Systematic lens modeling uncertainties are absolutely an essential component for understanding how seriously to take the conclusions about the SN classification and time delay estimation presented here.
In this work we have focused on presenting the analysis using only truly {\it blind} lens models, developed without knowing the impact of lens modeling choices on the SN classification or time delay. As a result, we acknowledge that we have only a limited window on potential systematic biases.

A rigorous quantification of MACS J0138 lens modeling uncertainties would be valuable, but it is a significant undertaking.  Ideally it would involve multiple lens modeling teams using different software tools and modeling methodologies (e.g., as has been done with MACS J1149 for SN Refsdal, or with the Frontier Fields simulated cluster lens modeling challenge of Meneghetti et al. 2017).   We feel this is beyond the scope of this work, so we've attempted to address the referee's concern with appropriate caveats throughout.  These are necessarily brief in the abstract \hlt{(blue text, lines 18-20)} and main text \hlt{(lines 84-86)}, but are expanded upon in the methods \hlt{(lines 343-346)}, and supplemental materials \hlt{(lines 514-521)}.
}

\one{2. Fig. 5 shows model-predicted images of the host galaxy for images 1-3 but not for images 4 and 5 which can be quite important in deciding the robustness of the model E.}{
  (note that this is now Fig 4)\\  
\textcolor{red}{TODO: Johan will add this to the figure}\\

We have added this to Figure 5.  \textcolor{red}{TODO: add some comments here and in the supplemental text about how well images 4 and 5 are reproduced.  If appropriate, we could note that Newman+ 2018 said ``We note that the radial images 4 and 5 were not used to constrain the model except via their approximate positions, so a close match to their detailed structure is not expected.''
}}

\one{3. Some of the best model parameters reported in Table 5 still look odd. For example, a velocity dispersion of 700 km/s for the BCG seems unrealistic.}{  
\textbf{\textcolor{red}{Johan: please review and edit as needed}}\\

This is certainly a fair point.  In the main text the new sentence at \hlt{lines 87-89} now indicates that we did not include stellar kinematics constraints. In the first resubmission we added a paragraph to the ``Future Lens Modeling'' section \hlt{(p.39)} about the BCG velocity dispersion measurement and its implications for lens modeling. We have added a new sentence in that section \hlt{(lines 540-541)} to highlight that our adopted value for the BCG velocity dispersion is at odds with our measurement from the VLT data ($390\pm10$ km/s).   
As described there, we have chosen to limit the main conclusions of this paper to only the blind models, and therefore did not develop a new lens model that incorporates the measured BCG velocity dispersion.  We look forward to exploring that in future work.
}

\one{4. Model predicted magnification ratios and measured magnification ratios (image2 to image1) are not consistent.}{
We are unsure of exactly what the referee is referring to here.   If this refers to the magnification ratios of the SN images, then there is a misunderstanding, because we have not attempted to measure any SN magnification ratios.  Given the limited data,  only the color-curve fitting method can be used to measure SN lensing properties independently of the lens model.  The SN color curves are insensitive to "macro-lensing" magnification, so we can't measure $\mu$ ratios from them.  For all other SN fitting, we adopt the magnifications from the lens model, as described in the Methods.\\

This comment may instead refer to the host galaxy image magnifications, as reported in Supplementary Table 1.  This may again be a misunderstanding.  The values in that table are all predicted magnifications, either from our lens model (columns 2-4) or from the Newman+ 2018 model (column 5).  As described in the Supplementary Note text, the relevant comparison here is from column 4 ($\mu_{gal,avg}$) against column 5 ($\mu_{N18,gal,avg}$).   The $\mu$ ratios (and the individual $\mu$ values) are fully consistent between those two models.
}

\one{5. Table 1 and Table 6 have duplicate information. Authors could merge them.}{
Thank you for the suggestion.  We've merged them. \\
\textcolor{red}{Johan:  can you give the predicted RA, Dec coordinates for image SN5?}
}

\one{6. The authors mention that systematic uncertainties are accounted for in the magnification uncertainties. However, these do not include biases due to the assumption of the density profile which can strongly affect magnifications. This should be clearly mentioned.}{
This is now addressed directly in the main text \hlt{(lines 84-86)}, the methods \hlt{(lines 343-346)}, and supplemental materials \hlt{(lines 514-521)}.

\textcolor{red}{Johan?  can you recommend a good reference to cite for this?
   Maybe Birrer et al 2020?  (that's more about the mass-sheet transform though)}
}

\clearpage
\section{Reviewer 2 (Comments for the Author):}

\two{While authors have improved the manuscript in many ways, and I am still in favor of having the discovery reported in Nature Astronomy, my main concern with respect to precision cosmology persists. As indicated in their Fig 3, the limiting factor in time-delay cosmography is the lens model (in their case 2 or 5\% uncertainty assumed). Thus, the current emphasis on the power of waiting for 20 years to maybe catch a SN image that would allow for, potentially, a sub percent time delay measurement seems rather misplaced.\\
The system of AT 2016tbd, as pretty as it is, it does not have any more power in measuring the Hubble constant than any other system with just $\sim$100 days time-delay and 1-2 days accuracy. As long as Fig 3 remains in the manuscript, I cannot recommend publication. It just is not relevant and gives the wrong impression.}{

We will concede this point.  It is certainly true that the 20-year timeline makes any cosmological forecasting highly speculative.  It is also of course true that any lensed SN with a $\sim$100-day time-delay measured with a precision of 1-2 days will be equivalent to a long-delay system like this one. It may be that we diverge from the referee primarily on the question of how many lensed SN like that could be observed in the coming decade, and at what cost.  Evaluating that (and doing a more rigorous cosmological analysis) is beyond the scope of this discovery paper---and we appreciate that Reviewer \#2 does agree with us on that.

We have removed Figure 3 (the projected cosmological contours) and the related discussion from the main text.  In its place, we've added a paragraph that introduces a little of the ``cost/benefit analysis'' discussion, comparing the observational cost of SN Refsdal against AT 2016tbd \hlt{(lines 151-157)}.  We also added a few sentences discussing the cosmological utility of cluster-lensed SN systems more generally, which also addresses a request from Referee \#3 \hlt{(red text, lines 163-167)}.
}

\subsection{Some minor points:}

\two{Abstract:
``Achieving these cosmological goals requires many more lensed supernova discoveries and more efficient observational follow-up.''
\linebreak
I think the authors are getting ahead of themselves, “more” here is quite premature, as they have not described what there is yet.}{
Fair enough.  We've removed ``more'' from the abstract.}

\two{``This object demonstrates that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed supernovae.''
\linebreak
I do not quite get the “minimal” part here. It would be a major effort for a space mission to hunt for the 4:th image over 4 years!}{For simplicity, we've removed this statement, but we'll also take a moment to explain: This statement was intended to refer to the fact that when the time delay is long enough, the SN measurements can be anchored at either end by just a few observations, making the whole time-delay measurement less expensive.  
We've added some text in the supplemental note on Future Observations that we hope will clarify our intended meaning \hlt{(lines 578-587)}.  In the previous resubmission we did also include a discussion of the observational cost for a monitoring campaign to catch the reappearance \hlt{(lines 557-566).}
}

\two{Introduction:
While describing the H0 tension, the authors should certainly clarify that the community is also engaged in exploring potential systematic effects behind the tension.}{
 Certainly.  We have added a few sentences \hlt{(teal text, lines 32-34)}, but have kept the Verde+ 2019 reference. It is a conference proceeding, and a little old in this fast-moving field, but its one of the few that presents the search for systematic biases and the hunt for new physics with some balance.
}

\two{I also wonder why Ref [12] is singled out here. It certainly was not the first, see e.g., \href{https://ui.adsabs.harvard.edu/abs/2002A\%26A...393...25G/abstract}{2002A\&A,393,25}
(and there may be others, I have not made an exhaustive search).}{
This is a very fair point.  We had been trying to finesse the 30-reference Nature Astronomy limit by identifying appropriate references that can do ``double duty.''  In an earlier draft we were applying Ref [12] (Coe \& Moustakas 2009) both in the introduction and in the description of future cosmological constrains (the former Figure 3).

To replace that reference, we have settled on Holz 2001 as the first to explicitly connect time delay cosmography with measurement of {\em dark energy parameters}.  One could certainly argue for inclusion of others, but we are right against the limit. 
}

\clearpage

\section{Reviewer 3 (Comments for the Author):}

\three{I thank the authors for addressing my initial comments, along with those from the other referees. I am satisfied with the changes they have made to the paper, and recommend it for publication. I do have a few very minor comments that the authors may wish to take under advisement before submitting the final version.\\
---\\
Page 3 (2nd paragraph): The time-delay cosmography method has now been applied to seven lensed quasars (see Millon et al. 2020, Birrer et al. 2020).}{
Corrected.
}

\three{Page 7: In their response to my initial comments, the authors acknowledge that lens model systematics may limit the uncertainties, but argue that this method is valuable regardless. I agree with this assessment, but the paper text doesn't really acknowledge this, and presents the 5\%/2\% values as if those are expected uncertainties from current/future samples. I think there should be some additional text here so as not to present an overly optimistic picture of future constraints.}{
This section has been removed, as Reviewer \#2 strongly objected to the cosmological forecasting section.  With the 5\%/2\% values no longer referenced, we have instead included an abbreviated version of our prior response to Reviewer \#3 on this point, in the new maroon text \hlt{(lines 166-170).}
}

\three{Figure 1: The tick marks seem to have disappeared from this figure.}{
Slippery little ticks. We have corrected the figure.

\textcolor{blue}{Gabe: can you redo this fig with ticks?}
}

\three{Figure 3: The left and right columns are labeled "FlatwCDM" and "Flatw0waCDM", respectively, but aren't the same cosmologies being presented in both cases? It's not entirely clear that you need to label the top row, as these have fixed w0 and wa, and thus are essentially flat LCDM. Shouldn't the top row be labeled "Flat LCDM" and the bottom panels be labeled "Flatw0waCDM"?}{
This figure was removed, responding to the strong concerns of Reviewer \#2.

Though the point is moot, this was due to an error on our part (a misplacement of the w0,wa labeling text)  and our mistake in not explaining clearly enough how the simulations fixed the ``true'' dark energy equation of state values while nevertheless allowing them as free parameters. 
}

\three{Figure 5: The contours in the first column are a bit difficult to see, particularly the orange ones. I would recommend that the authors try to find some colors/linestyles to make these more apparent.}{
\textcolor{blue}{Johan: can you fix, please?}
}

\three{Time Delay Estimation (page 27), 2nd paragraph: I'm not familiar with SALT2 or how these light curve fittings are performed, but I take it that the "stretch" parameter x1 is some parameter of the model light curve that affects its shape, which the authors set to x1 = 0. They state that fixing it to other values from $-1 < x_1 < 1$ results in a change in the time delay by less than five days. Is this explicitly included in the time delay uncertainties provided? Granted, this would not change the results substantially, but it would be good to know for completeness.}{
The referee has a correct understanding of our procedure.   We did not include the variation of a fixed x1 value in the reported time delay uncertainties.  We have now explicitly stated this in the Methods \hlt{(lines 416-418).}  It is effectively a (small) systematic uncertainty now, and we anticipate that it will be substantially reduced with any future analysis. As we noted in the previous response: \\
``we expect that a full light curve of the fourth SN image will provide a tight constraint on x1, which can then be propagated back into the fitting of the SN images 1-3.''\\
}

\end{document}

### 2021-05-21 Paper/NatureAstronomy/main_resubmission1.tex

--- 2021-01-19 Paper/NatureAstronomy/main.tex
@@
 \usepackage[utf8]{inputenc}
-%\usepackage[backend=biber,style=nature,citestyle=numeric]{biblatex}
-%\usepackage{biblatex}
-%\addbibresource{zotero_references_biblatex.bib}
-
-%extra packages added during drafting, remove for submission
+
+% Required packages
+\usepackage{caption}
 \usepackage{hyperref}
 \usepackage{booktabs}
-
-%\usepackage{amssymb}
 \usepackage{xspace}
 \usepackage{graphicx}
-\usepackage[draft,xcolor=usenames]{changes}
+
+%extra packages added during drafting, remove for submission
+\usepackage{lineno}
+
+%%%  SELECT DRAFT VERSION (CHANGETEXT) OR FINAL 
+%\usepackage[draft,xcolor=dvipsnames]{changes}
+%\linenumbers
+\usepackage[final,xcolor=dvipsnames]{changes}
+
 \definechangesauthor[name=1, color=blue]{r1}
 \definechangesauthor[name=2, color=teal]{r2}
-\definechangesauthor[name=3, color=orange]{r3}
+\definechangesauthor[name=3, color=Maroon]{r3}
+\definechangesauthor[name=4, color=violet]{ed}
 \setauthormarkup{}
@@
 \def\SNABC{AT 2016tbd\xspace}
-%\def\SNABC{SN Requiem\xspace}
-%\def\reqlike{Requiem-like\xspace}
 \def\reqlike{16tbd-like\xspace}
@@
 
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-%\usepackage{scicite}
 %\usepackage{nature}
-
 \usepackage{times}
-
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
 
@@
 %The next command sets up an environment for the abstract to your paper.
-
 \newenvironment{sciabstract}{%
@@
 % Include your paper's title here
-
 \title{A Gravitationally Lensed Supernova with an Observable Two-Decade Time Delay}
@@
  Steven A. Rodney$^{1\ast}$, 
- Gabriel Brammer$^{2\ast}$,  
+ Gabriel Brammer$^{2,3\ast}$,  
  Justin D.\,R.~Pierel$^{1}$,\\ 
- Johan Richard$^{3}$, 
- Sune Toft$^{2}$,\\  
+ Johan Richard$^{4}$, 
+ Sune Toft$^{2,3}$,\\  
  Kyle F. O'Connor$^{1}$, 
- Mohammad Akhshik$^{4}$, 
- Katherine E. Whitaker$^{2,4,5}$  
+ Mohammad Akhshik$^{5}$, 
+ Katherine E. Whitaker$^{6,2}$  
 \\
+
 \normalsize{$^{1}$Department of Physics \& Astronomy, University of South Carolina,}\\ \normalsize{ Columbia, SC 29208, USA}\\
-\normalsize{$^{2}$Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen,}\\ \normalsize{Lyngbyvej 2, Copenhagen \O\ 2100 Denmark}\\
-\normalsize{$^{3}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon}\\ \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
-\normalsize{$^{4}$Department of Physics, University of Connecticut,}\\ \normalsize{Storrs, CT 06269, USA}\\
-\normalsize{$^{5}$Department of Astronomy, University of Massachusetts,}\\ \normalsize{Amherst, MA 01003, USA}\\
+\normalsize{$^{2}$Cosmic Dawn Center (DAWN), Copenhagen Denmark}\\
+\normalsize{$^{3}$Niels Bohr Institute, University of Copenhagen, Jagtvej 128, Copenhagen, Denmark}\\
+\normalsize{$^{4}$Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon}\\ \normalsize{UMR5574, F-69230, Saint-Genis-Laval, France}\\
+\normalsize{$^{5}$Department of Physics, University of Connecticut,}\\ \normalsize{Storrs, CT 06269, USA}\\
+\normalsize{$^{6}$Department of Astronomy, University of Massachusetts,}\\ \normalsize{Amherst, MA 01003, USA}\\
 \normalsize{$^\ast$To whom correspondence should be addressed;}\\ \normalsize{E-mail:  srodney@sc.edu, gabriel.brammer@nbi.ku.dk}
@@
 % Place your abstract within the special {sciabstract} environment.
-
+\clearpage
 \begin{sciabstract}
 
+\replaced[id=ed]{
+When the light from a distant stellar explosion passes very near to a foreground galaxy or cluster, gravitational lensing can cause it to appear as multiple images on the sky.
+Such strongly-lensed supernovae can be used to constrain the cosmic expansion rate \cite{refsdal_possibility_1964} and dark energy models \cite{treu_time_2016}.
+Achieving these cosmological goals requires many more lensed supernova discoveries and more efficient observational follow-up.
+Here we report the discovery of a multiply-imaged supernova that will enable a time delay measurement with an uncertainty of $<1\%$.
+It appeared in an evolved galaxy at $z=1.95$, gravitationally lensed by a massive foreground galaxy cluster.
+It is likely a Type Ia supernova---the explosion of a low-mass stellar remnant, whose light curve can be used to measure cosmic distances.
+In archival Hubble Space Telescope imaging, three lensed images of the supernova are detected with relative time delays of $<$200 days.
+We predict a fourth image will appear close to the cluster core in the year 2037$\pm$2.
+Observation and modeling of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline.
+This object demonstrates that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed supernovae.}{
   We report the discovery of a strongly-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
@@
 This is the most distant multiply-imaged supernova yet discovered.
-We classify the supernova as a Type Ia with {$>90\%$} probability based on archival imaging observations from the \textit{Hubble Space Telescope}.
+We classify the supernova as \added[id=r2]{most likely} a Type Ia \deleted[id=r2]{with {$>90\%$} probability} based on archival imaging observations from the \textit{Hubble Space Telescope}.
 Three lensed images of the SN are detected with relative time delays of $<$200 days, and we predict that a fourth image in the component closest to the cluster core will appear in the year 2037$\pm$2.
 Observing the light curve of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline.
-
+}
 \end{sciabstract}
@@
 Observations of Type Ia supernova (SN) explosions have played a key role in mapping the cosmic expansion history, and led to the discovery of dark energy that now appears to be driving an accelerating cosmic expansion rate
-\cite{riess_observational_1998,perlmutter_measurements_1999, Riess_large_2019}.
+\cite{riess_observational_1998,perlmutter_measurements_1999} %Riess_large_2019}.  
 Determining the nature of dark energy and how it may evolve over time is a primary goal for the large-scale cosmology experiments of the 2020s
 \cite{amendola_cosmology_2013,spergel_wide_2015,Ivezic_lsst_2019}.
-A series of recent investigations into the expansion rate of the universe (the Hubble-LeMa\^itre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background (CMB) radiation \cite{Riess_large_2019,aghanim_planck_2018}.
+\deleted[id=ed]{A series of} Recent investigations into the expansion rate of the universe (the Hubble-LeMa\^itre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background \deleted[id=ed]{(CMB)} radiation \cite{Riess_large_2019,aghanim_planck_2018}.
 Resolving this tension in $H_0$ measurements may reveal new physics from the early universe, and to do so requires multiple
@@
 %the expansion rate of the universe, 
-$H_0$  and the dark energy equation-of-state, $w$ \cite{refsdal_possibility_1964,coe_cosmological_2009,linder_lensing_2011}.
+$H_0$ \cite{refsdal_possibility_1964} and the dark energy equation-of-state, $w$ \cite{coe_cosmological_2009}.%,linder_lensing_2011}.
 In recent years this method has been successfully applied to lensed
-quasars \cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, with six high-precision measurements to date \cite{wong_h0licow_2019}.
+quasars %cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, 
+with six high-precision measurements to date \cite{wong_h0licow_2019}.
 As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosmological_2018}.
-\added[id=r1]{A future sample with $\sim100$ well-measured lensing time delays will be a competitive tool for dark energy studies \cite{linder_lensing_2011,jee_time-delay_2016,suyu_HOLISMOKES_2020}.}
+\added[id=r1]{A future sample with $\sim100$ well-measured lensing time delays will be a competitive tool for dark energy studies \cite{treu_time_2016}.}
+%\cite{linder_lensing_2011,jee_time-delay_2016,suyu_HOLISMOKES_2020}.}
 
@@
 Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---in contrast to the stochastic variation of quasars.
-However, despite the promise of lensed SN time delay cosmography as a cosmological distance probe, to date, there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
+However, \deleted[id=ed]{despite the promise of lensed SN time delay cosmography as a cosmological distance probe,} to date there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
 The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_sn_2016}.
 The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2019}.
-\added[id=r1]{An earlier discovery of an unusually luminous SN \cite{chornock_ps1-10afx_2013} was also shown to be a strongly-lensed SNIa,
-\cite{quimby_extraordinary_2013,quimby_detection_2014}
+\added[id=r1]{An earlier discovery of an unusually luminous SN \cite{chornock_ps1-10afx_2013} was also shown to be a strongly-lensed SNIa,  \cite{quimby_detection_2014} %quimby_extraordinary_2013,
 though the multiple images were not resolved.}  Here we present the discovery 
@@
 MRG-M0138 is quadruply lensed by a foreground galaxy cluster at $z=0.338$.  
-During analysis of REQUIEM observations obtained 13--14 July 2019 \cite{materials_methods_2020} we discovered three point 
-sources that were present in archival HST images from 18--19 July 2016, part of the program 
-that first confirmed the MRG-M0138 galaxy as a strongly-lensed object (HST-GO-14496; PI:Newman). 
+During analysis of REQUIEM observations obtained 13--14 July 2019
+%\cite{materials_methods_2020} 
+we discovered three point 
+sources that were present in archival HST images from 18--19 July 2016, part of the program (HST-GO-14496; PI:Newman)
+that first confirmed the MRG-M0138 galaxy as a strongly-lensed object 
+\added[id=ed]{(Methods: Observations)}. 
 Each point source is within 5 arcseconds of one of the four MRG-M0138 images.  None of the
@@
 the point sources are multiple images of a single astrophysical 
-transient in MRG-M0138, most likely a SN \cite{materials_methods_2020}.  
+transient in MRG-M0138, most likely a SN. %\cite{materials_methods_2020}.  
 %The official designation for this multiply-imaged astrophysical transient is \TNSname. 
@@
 
-To construct a lens model for the MACS J0138.0-2155 cluster we use the \lenstool software \cite{jullo_bayesian_2007,kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster-scale and multiple galaxy-scale potentials \cite{materials_methods_2020}.
+To construct a lens model for the MACS J0138.0-2155 cluster we use the \lenstool software \cite{jullo_bayesian_2007,kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster-scale and multiple galaxy-scale potentials
+\added[id=ed]{(Methods: Lens Modeling)}.
+%\cite{materials_methods_2020}.  
 To avoid unintended bias, we kept the lens model development completely separate from the analysis of the SN.
-Only upon independent completion of both were the results combined for the analysis described here.
-The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the central light peak and the SN location in each image) as well as a multiply-imaged background
-galaxy at $z=0.766$, both having secure spectroscopic redshifts \cite{materials_methods_2020}.  
+Only upon \deleted[id=ed]{independent} completion of both were the results combined for the analysis described here.
+The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the \replaced[id=r3]{galaxy's centroid position }{central light peak} and the SN location in each image) as well as a multiply-imaged background
+galaxy at $z=0.766$, both having secure spectroscopic redshifts
+\added[id=ed]{(Methods: Observations)}.
+%\cite{materials_methods_2020}.  
 From this model we derive estimates for the lensing magnification and time delay of each of the SN images, including the predicted fourth image (Table \ref{tab:time_delays}).
-The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$1.5, demagnified with $\mu=0.4\pm0.2$.
-The predicted location for this future image is $\alpha=01:38:04.15,\delta=-21:55:24.659$.
-A fifth image will also appear at date later still, located near the center of the cluster and much more significantly demagnified, so it will not be easily observable.
+The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$\replaced[id=r1]{2}{1.5}, demagnified with $\mu=0.4\pm0.2$.
+The predicted location for this future image is $\alpha=$01:38:04.15, $\delta=-$21:55:24.659.
+A fifth image will also appear at a still later date, located near the center of the cluster and much more significantly demagnified, so it will not be easily observable.
+\added[id=r1]{We anticipate that future lens modeling of the cluster may improve on these predictions} \added[id=ed]{(Supplementary Note: Future Work}).
 
@@
 we need to estimate the age of each SN image, which in turn constrains the lensing time delays. For this
-goal, it is necessary to have a firm determination of the transient’s class.
+goal, it is helpful to have a firm determination of the transient’s class.
 Expected time delays and magnifications from the lens model exclude any of the various rapidly evolving and low-luminosity stellar transient classes, strongly suggesting that it is a SN.
@@
 unlikely to retain any significant population of high-mass stars \cite{newman_resolving_2018}.
-Based on observed properties of the host galaxy alone, we find a 62-75\% probability that \SNABC is a Type Ia SN \cite{materials_methods_2020}.
+Based on observed properties of the host galaxy alone, we find a 62-75\% probability that \SNABC is a Type Ia SN.
 Adopting the lens model magnifications for the three observed SN images (Table \ref{tab:time_delays}) we can locate each SN image in color-magnitude space (Fig.
 \ref{fig:class}).
-This provides more classification leverage, yielding p(Ia)=95\% \cite{materials_methods_2020}.
-By also including the model-predicted time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=94\% \cite{materials_methods_2020}.
-An improved classification can be achieved with spectroscopy and multi-band photometry upon arrival of the fourth image.
-
-The color of a SNIa evolves substantially over its lifetime as the photosphere expands and cools, revealing different layers of the expanding shell and driving episodes of recombination \cite{woosley_type_2007,kasen_type_2009}.
-Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model \cite{materials_methods_2020}.
-Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table \ref{tab:time_delays} \cite{materials_methods_2020}.
+\replaced[id=r1]{After magnification correction, all three images are still brighter than expected for a Type Ia SN, which may indicate that a lens-modeling degeneracy is at play \cite{falco_model-dependent_1985, schneider_source-position_2014}.
+Nevertheless, the magnification-corrected \SNABC data are more consistent with the Type Ia population than any CC SN sub-class (Fig.~\ref{fig:class}a,b), and demonstrate the expected evolution of a Type Ia SN color and brightness over $\sim 100$ days (Fig.~\ref{fig:class}c).}{This provides more classification leverage, yielding p(Ia)=95\%.}
+By also including the model-predicted time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=94\% 
+\added[id=ed]{(Methods: Classification)}.
+%\cite{materials_methods_2020}. 
+\replaced[id=r2]{An improved classification can be achieved }{These final classifications are strongly conditional on the priors, and we look forward to an improved classification} with spectroscopy and multi-band photometry upon arrival of the fourth image.
+\added[id=r2]{For the remainder of this analysis, we proceed under the assumption that \SNABC is indeed a Type Ia SN---though the subsequent analysis could be revised to achieve similar results with a different underlying SN model.}
+
+The color of a SNIa evolves substantially over its lifetime as the photosphere expands and cools, revealing different layers of the expanding shell and driving episodes of recombination \cite{kasen_type_2009}.
+%woosley_type_2007
+Since the phenomenon of gravitational lensing in general is achromatic, this color evolution makes it possible to derive an age constraint that is largely independent of the lens model.
+%\cite{materials_methods_2020}.
+Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table \ref{tab:time_delays}
+\added[id=ed]{(Methods: Time Delay)}.
+%\cite{materials_methods_2020}. 
 Remarkably, the ages of image 1 and 3 are constrained to better than $\pm$20 days, despite having only a single epoch of photometric data.    These uncertainties may be 
 further reduced when the future fourth image is observed with high-precision, multi-epoch photometry.
-Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images, and break remaining parameter degeneracies (see supplemental materials).
-
-\added[id=r1]{By itself, \SNABC will not be particularly powerful as a solitary cosmological probe.  However,} future large-scale surveys such as the Vera C. Rubin Observatory 
-and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes, \added[id=r1]{though the vast majority of these will be lensed by galaxy-scale deflectors}  \cite{oguri_gravitationally_2010,goldstein_rates_2019,wojtak_magnified_2019}.
+Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images, and break remaining parameter degeneracies.
+%\added[id=ed]{(Supplementary Note: Future Observations)}.
+
+\added[id=r1]{As with any single time-delay system, \SNABC will not be particularly powerful as a solitary cosmological probe.
+However,} future large-scale surveys such as the Vera C.
+Rubin Observatory
+and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes, \added[id=r1]{though the vast majority of these will be lensed by galaxy-scale deflectors \cite{oguri_gravitationally_2010,  goldstein_rates_2019, pierel_projected_2020}.} %wojtak_magnified_2019,
 \deleted[id=r1]{However, many of these lensed SN will require substantial follow-up resources to be made cosmologically useful.} Thus, almost all will have significantly shorter 
@@
 In fact, the long time baseline of lensed SN like \SNABC effectively insures that their cosmological precision is not limited by time delay measurement uncertainty.
+\added[id=r1]{Cluster-scale lenses are more complex than galaxy-scale lenses, but they generally have ``independent'' measurements of the magnification from several multiply-imaged systems in the same field.
+As such, they can provide a valuable check on systematics related to specific lens modeling software, microlensing variation, and more.}
 
@@
 
-To achieve these cosmological constraints in practice, such a sample could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered.
+To achieve these cosmological constraints in practice, such a sample could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered
+\added[id=ed]{(Supplementary Note: Future Work}).
+%\cite{materials_methods_2020}.  
 As \SNABC shows, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.  
@@
     \centering
-    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout_2021.pdf}
+    \includegraphics[draft=False,width=0.9\textwidth]{Paper/Figures/fig1_layout.pdf}
     \caption{Overview of the MACSJ0138 cluster field and the locations of the \SNABC images  (SN1--3) and its multiply-imaged host galaxy (H1--4).
@@
 The three-color images are generated from the WFC3/IR filters as indicated; panels \emph{bcde} show the imaging from 2016 July where the SN was visible and \emph{fghi} show the later imaging from 2019 July where the the SN has faded away.
-Panels \emph{aei} indicate the location of the fourth image predicted to appear in $\approx$2037.
+Panels \emph{aei} indicate the location of the fourth image predicted to appear in $\approx$2037 \added[id=r3]{and panel \emph{a} shows the final and highly demagnified fifth image (``SN5'')}.
 All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.
@@
 \end{figure*}
+
 \clearpage
@@
   \centering
-    \includegraphics[draft=False, width=\textwidth]{Paper/Figures/classification_contours_timeline.pdf}
-    \caption{Classification information for SN Requiem based on its position in color-magnitude space.
-\emph{Left:} Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green), drawn to enclose 68\% (interior solid lines) and 95\% (exterior shaded regions) of each SN population.
+    \includegraphics[draft=False, width=\textwidth]{Paper/Figures/snRequiem_classcontours_timeline_hist.png}
+    \caption{Classification information for \SNABC based on its position in color-magnitude space. \replaced[id=r3]{(a)}{\emph{Left:}} 
+    \added[id=r1]{The observed photometry for the three SN images is shown as open markers.
+Vertical dotted lines show the lens magnification corrections using our preferred lens model, with a filled grey marker indicating the corrected (demagnified) magnitude.
+Error bars indicate the observational and systematic uncertainty, including the range of alternative magnification corrections encompassed by lens model variations.}
+    Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green), drawn \replaced[id=r3]{with two contour levels enclosing }{to enclose} 68\% \deleted[id=r3]{(interior solid lines)} and 95\% \deleted[id=r3]{(exterior shaded regions)} of each SN population.
 Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
-\added[id=r1]{The directly observed photometry for each of the three SN images is shown as open markers.
-Vertical dotted lines show the effect of applying lens magnification corrections, with a filled grey marker indicating the corrected (demagnified) magnitude after applying our preferred lens model.
-Error bars indicate the systematic uncertainty (the range of alternative magnification corrections encompassed by lens model variations).}  \emph{Right:} The evolution of a typical Type Ia SN at $z=1.95$ in observed color-brightness space is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
-White diamonds correspond to the times labeled on the colorbar at right.
-Grey shading shows the typical range of luminosities observed for the Type Ia SN population in the nearby universe \cite{wang_determination_2006}.
+    \replaced[id=r3]{(b)}{\emph{Right:}} \added[id=r3]{Marginalized distributions along the color dimension for the three SN sub-classes (using the same color scheme).
+The simulated populations have been scaled according to the expected explosion rates in the SN host galaxy, based on its stellar population properties.
+Open markers show the observed colors again.}
+    \added[id=r3]{(c) Zoomed-in view of the color-mag space marked by the grey box in panel a.}
+    The evolution of a typical Type Ia SN at $z=1.95$ \deleted[id=r3]{in observed color-brightness space} is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
+White diamonds correspond to the times labeled on the colorbar \replaced[id=r3]{below}{at right}.
+Grey shading shows the typical range of luminosities \added[id=r3]{and colors} observed for the Type Ia SN population in the nearby universe.
+%\cite{wang_determination_2006}.
+    \added[id=r2]{Although the magnification-corrected data are brighter than expected for most SNIa, they are consistent both with the overall SNIa population, and with the SNIa color-mag vs time curve.
+}
     %An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
@@
     The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation-of-state parameters ($w_0, w_a$).
-Dashed lines and the white marker show the input values (upper right of the top panels) that were used for this simulation.
+Dashed lines and the \replaced[id=r3]{black}{white} marker show the input values (upper right of the top panels) that were used for this simulation.
 Contours show the 1$\sigma$ confidence region for a projected sample of 5 lensed SNIa time delays from the Rubin Observatory (blue) and the Roman Space Telescope (red) compared to 5 events like \SNABC (black).
@@
 \midrule
-\textit{1}  & $87^{+16}_{-13}$ & -- & $5\pm1$ & --\\
-\textit{2} & $-20^{+20}_{-11}$ & $106^{+25}_{-24}$ & $7\pm3$ & $82\pm62$ \\
-\textit{3} & $100^{+27}_{-31}$ & $-10\pm24$ &$3.9\pm0.5$  & $-19\pm34$ \\
+\textit{1}  & $92^{+21}_{-19}$ & -- & $5\pm1$ & --\\
+\textit{2} & $-24^{+16}_{-7}$ & $114^{+28}_{-31}$ & $7\pm3$ & $82\pm62$ \\
+\textit{3} & $107^{+26}_{-21}$ & $-17^{+19}_{-16}$ &$3.9\pm0.5$  & $-19\pm34$ \\
 \textit{4} & -- & -- & $0.4\pm0.2$ & $7742\pm540$\\
+\textit{5} & -- & -- & $<0.01$ & $9463\pm770$\\
 
@@
 \caption{\label{tab:time_delays}Time Delays.  The combination of the models for the light curve evolution and the lens time delays implies a date of $2037\pm2$ for the peak brightness of Image 4.}
+%\todo[inline]{Note: updated to include image 5}.}
 \end{table}
+
+\clearpage
 
@@
 
-\clearpage
 %\section*{Supplementary materials}
@@
 %\clearpage
+%\end{document}
 
@@
 
-\subsection*{Observations of the SN and Lensing System}
+\subsection*{Observations} % of the SN and Lensing System}
 
@@
 
-\subsection*{VLT Spectroscopy}
+\subsubsection*{VLT Spectroscopy}
 \label{sec:vltmuse}
@@
 Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.766$.
+\added[id=r1]{Finally, we have measured the velocity dispersion of the BCG to be 390$\pm$10 km s$^{-1}$.
+This measurement was not available for use in our blind lens modeling, but could provide a useful constraint for future lens model improvements (Supplemental Note: Future Work).}
 
 \subsection*{Lens Modeling}
-%\todo[inline]{Fill in details of lens models here.}
 
@@
 We add a single galaxy-scale halo on each cluster member, where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15\,kpc).
-Cluster members were identified by the combination of red sequence selection (based on the F814W$-$F160W color) and MUSE spectroscopy.
+\added[id=r3]{Figure~\ref{fig:model_components} shows the locations of all components of the cluster model, including 32 cluster members (yellow ellipses).} Cluster members were identified by the combination of red sequence selection (based on the F814W$-$F160W color) and MUSE spectroscopy.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth]{Paper/Figures/fig4_lensmodel_layout.pdf}
+    \caption{\added[id=r3]{
+    The elements of the MRG0138 cluster lens model.
+The model comprises 37 potentials in total: the BCG (red), 32 cluster members (yellow), three perturbers (cyan), and the main cluster potential (pink).
+Labeled $\times$ symbols indicate the positions of the SN, host, and one additional multiply-imaged galaxy with a secure redshift used as model constraints (Table~\ref{tab:mulimages}).
+The filters used to generate the color image are as in Fig.~\ref{fig:layout}, and tick marks are separated by 10 arcsec.
+    } }
+    \label{fig:model_components}
+\end{figure}
 
@@
 The final model, and the one selected as the preferred model prior to unblinding, is model E, which includes all four perturbers described above, and includes the additional background object at $z=0.7663$.
-
-The final \lenstool model E reproduces all multiple systems with an RMS of 0.15\arcsec.
-We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs.
-This model is then used to predict the magnification and time delays for the 3 observed images of \SNABC, as well as the location of the fourth  image, which is still to appear.
-The actual 1$\sigma$ uncertainty on this location is the ellipse overlayed on top of the bottom cutouts in Fig.~\ref{fig:layout}.
-As the lens model reproduces the location of the SN images within a small uncertainty, these predictions are computed with \lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position.
-We summarise these predictions in Table \ref{tab:snpred}.
+\added[id=r3]{Note that all of the lens model variants A-D would give a slightly larger magnification for all  three SN images.
+This means that our estimated systematic uncertainties are one-sided, as can be seen on Fig.~\ref{fig:class} and Fig.~\ref{fig:colormag_classification_supplement}.}
 
@@
     \begin{tabular}{c|c|c|c|c|c|c|c|}
-%\replaced[id=r1]{Potential \& $\Delta$R.A. \& $\Delta$Dec. & $e$ \& $\theta$ & $\sigma$ & $r_{\rm core}$ \& $r_{\rm cut}$ \\}
-{Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $r_{\rm core}$ & $r_{\rm cut}$ & $\sigma$ \\}
-%\replaced[id=r1]{ 
-%& [arcsec] & [arcsec] & & [deg] & [km\ $s^{-1}$] & [kpc] & [kpc] \\
- & [arcsec] & [arcsec] & & [deg] & [kpc] & [kpc] & [km\ $s^{-1}$] \\%}
-\hline
-Cluster-DM & $ -0.7^{+  0.4}_{ -0.4}$ & $ -1.2^{+  0.4}_{ -0.4}$ & $ 0.81^{+ 0.02}_{-0.13}$ & $114.9^{+  2.0}_{ -4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
-BCG            & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $136^{+42}_{-32}$ & $[0.15]$ & $700^{+52}_{-57}$ \\
-P1             & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[25]$            & $[0.15]$ & $152^{+30}_{-57}$ \\
-P2             & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[12]$            & $[0.15]$ & $23^{+111}_{-29}$ \\
-P3             & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[6]$             & $[0.15]$ & $110^{+35}_{-32}$ \\
-L$^{*}$ galaxy &           &           &          &           & $[45]$            & $[0.15]$ & $[158]$\\            
-%BCG & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$ & $700^{+52}_{-57}$ \\
-%P1 & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$ & $152^{+30}_{-57}$ \\
-%P2 & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$ & $23^{+111}_{-29}$ \\
-%P3 & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$ & $110^{+35}_{-32}$ \\
-%L$^{*}$ galaxy &  & & & & $[0.15]$ & $[45]$ & $[158]$\\
-\hline
+    Potential & $\Delta$R.A. & $\Delta$Dec. & $e$ & $\theta$ & $r_{\rm core}$ & $r_{\rm cut}$ & $\sigma$ \\
+                  & [arcsec] & [arcsec] & & [deg] & [kpc] & [kpc] & [km\ $s^{-1}$] \\
+\midrule
+Cluster-DM & $ -0.7^{+0.4}_{-0.4}$ & $ -1.2^{+0.4}_{-0.4}$ & $ 0.81^{+0.02}_{-0.13}$ & $114.9^{+2.0}_{-4.1}$ & $31^{+13}_{-12}$ & $[1000]$ & $446^{+52}_{-70}$ \\
+BCG            & $[  0.1]$ & $[ -0.1]$ & $[0.52]$ & $[-41.1]$ & $[0.15]$ & $136^{+42}_{-32}$  & $700^{+52}_{-57}$ \\
+P1             & $[ 19.2]$ & $[-13.5]$ & $[0.49]$ & $[ 86.2]$ & $[0.15]$ & $[25]$            &  $152^{+30}_{-57}$ \\
+P2             & $[ -5.0]$ & $[  6.9]$ & $[0.06]$ & $[  4.4]$ & $[0.15]$ & $[12]$            &  $23^{+111}_{-29}$ \\
+P3             & $[ -0.8]$ & $[-16.7]$ & $[0.24]$ & $[-63.1]$ & $[0.15]$ & $[6]$             &  $110^{+35}_{-32}$ \\
+L$^{*}$ galaxy &           &           &          &           & $[0.15]$ & $[45]$            & $[158]$\\
     \end{tabular}
@@
 and $\Delta$Dec.), dPIE shape (ellipticity and orientation), velocity dispersion, core and cut radius.
-The final row
-    is the generic galaxy mass at the characteristic luminosity L$^*$, which is scaled to match each of cluster member galaxies.
+The final row  is the generic galaxy mass at the characteristic luminosity L$^*$, which is scaled to match each of cluster member galaxies.
 Parameters in square brackets are fixed {\it a priori} in the final model (version E).
@@
 SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7742$\pm$540\\
-%SN.1 & & & 3.907$\pm$0.534 &   0.0 \\
-%SN.2 & & & 7.381$\pm$3.044 & 101.4$\pm62$ \\
-%SN.3 & & & 5.020$\pm$1.217 &  19.3$\pm34$\\
-%SN.4 & -5.22$\pm$0.36 &6.99$\pm$0.43 & 0.377$\pm$0.187 & 7761.0$\pm$541\\
-%SN.5 & & & & \\
 \hline 
@@
 
-\subsection*{Classification as a SN}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.75\textwidth]{Paper/Figures/host_image1_resid.pdf}\\
+    \includegraphics[width=0.75\textwidth]{Paper/Figures/host_image2_resid.pdf}\\
+    \includegraphics[width=0.75\textwidth]{Paper/Figures/host_image3_resid.pdf}
+    \caption{\added[id=r3]{Comparison of the SN host galaxy against a simulation using lens model E.
+North is up and East is left.
+Image 1.1 is shown in the top row, 1.2 in the middle, and 1.3 in the bottom.
+The left column (panels a,d,g) shows each observed image in the F160W bandpass, with a scale bar indicating 1 arcsecond.
+The central column (b,e,h) shows a simulated galaxy profile generated using lens model E, with a sum of two Sersic  profiles to represent the background galaxy.
+The last column (c,f,i) shows the residuals (observed-model).
+    Overlaid contours in the first column show the profile of the observed data (green) and the model (orange).
+    Some residual flux is apparent in the difference images, but the overall shape of each image is well matched by the simulated profile and the distortions introduced by lens model E.}
+    }
+    \label{fig:host_model_residuals}
+\end{figure}
+
+The final \lenstool model E reproduces all multiple systems with an RMS of 0.15\arcsec.
+We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs\added[id=r3]{, as shown in Figure~\ref{fig:host_model_residuals}}.
+This model is then used to predict the magnification and time delays for the 3 observed images of \SNABC, as well as the location of the fourth  image, which is still to appear.
+The actual 1$\sigma$ uncertainty on this location is the ellipse overlayed on top of the bottom cutouts in Fig.~\ref{fig:layout}.
+As the lens model reproduces the location of the SN images within a small uncertainty, these predictions are computed with \lenstool using the barycenter of all source positions corresponding to images SN.1, SN.2 and SN.3 as the same reference source position.
+We summarise these predictions in Table \ref{tab:snpred}.
+\added[id=r1]{Comparing our lens modeling to the previous  model of this cluster from \cite{newman_resolving_2018}, we find that the magnification estimates are broadly consistent, though systematically lower (Supplementary Note: Comparison to Previous Lens Modeling).}
+
+%\added[id=r1]{
+
+\subsection*{Classification}
+
 The lens modeled time delays between the images are $\sim100$ observer-frame days, 
@@
 
-\subsection*{SN Sub-Classification Based on Host Galaxy}
+\subsubsection*{SN Sub-Classification Based on Host Galaxy}
 With this transient identified as a SN, we now seek to identify the most likely SN type, under the assumption that it belongs to one of the three most common sub-classes (Ia, II, Ib/c).
@@
 derive a $75\%$ probability that \SNABC is of Type Ia (row a of Table \ref{tab:classification}).
+\added[id=r1]{
+We used host galaxy image 2 for this purpose, with the flux-weighted harmonic mean magnification $\mu=8.3$ to derive $M_K$ (see Table~\ref{tab:mu_comparison}).
+We also evaluated the other host galaxy images and found no change in the resulting SN classification probability.}
 
@@
 
-\subsection*{SN Sub-Classification Based on SN Photometry}
+\subsubsection*{SN Sub-Classification Based on SN Photometry}
 
@@
 Open markers show the observed photometry of the SN.
-Dotted vertical lines mark the magnification correction based on \lenstool model E, terminating in closed markers with error bars that show the magnitude uncertainty.
-Horizontal error bars in the upper panel indicate the observed uncertainty in
+Dotted vertical lines mark the magnification correction based on \lenstool model E.
+\added[id=r2]{Closed markers show the resulting magnification-corrected photometry, with asymmetric error bars reflecting the systematic uncertainty derived from the five lens model variants.}  Horizontal error bars in the upper panel indicate the observed uncertainty in
     the SN color (not affected by lensing).
@@
 The width of this sampling region is set to 3 times the observed color uncertainty, and the height is equal to the lens-modeling magnification uncertainty.
-We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
+\added[id=r2]{The $\mu$ uncertainty used here includes an estimate of the systematic uncertainty for each SN image, derived from the spread of magnifications across lens model variants (similar to the methodology of \cite{newman_resolving_2018}).}  We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
 \added[id=r3]{Note that in this case there is no need to apply a cut to the simulated sample to account for detectability, because the $5\sigma$ limiting magnitude of our HST observations is 26.5 AB mag, and after accounting for magnification of $\sim$1.5 mag (Table~\ref{tab:massmodel}) this becomes $m_{lim}\sim28$ mag.
@@
 With {\tt STARDUST2} we use a nested sampling algorithm to measure likelihoods over the SN simulation parameter space.
-Figure~\ref{fig:classification_lightcurves} shows the magnification- and time-delay-corrected photometry of \SNABC and the {\tt STARDUST2} maximum likelihood light curve fits from each of the three SN sub-classes considered (Ia, II, Ib/c).
+Figure~\ref{fig:classification_lightcurves} shows the magnification- and time-delay-corrected photometry of \SNABC and \replaced[id=r2]{a random sampling of light curve models from the {\tt sncosmo} nested sampling algorithm employed by {\tt STARDUST2}}{the {\tt STARDUST2} maximum likelihood light curve fits from each of the three SN sub-classes considered (Ia, II, Ib/c).}
+\added[id=r2]{Nested sampling is a Monte Carlo method that traverses the likelihood space in a manner that samples the Bayesian likelihood \cite{skilling_nested_2004}.
+These sample light curves and color curves therefore give a visual representation of how well each SN sub-class (Ia, II, Ib/c) can match the observed data.}
 This figure shows that the limited photometric data can be reasonably well fit by at least one model from any of these three sub-classes. 
-However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types than for the Type Ia class.
+\added[id=r2]{The density of curves in the top panels demonstrates that the SNIa model is consistently a good match to the data.} However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types.
+\deleted[id=r2]{than for the Type Ia class.}
 To compute the posterior probability distribution we adopt priors for each of the three SN classes, again using the classification probabilities derived from the \SNABC host galaxy stellar population properties (row b of Table~\ref{tab:classification}).
@@
 Plotted error bars include the measurement uncertainty and the lens modeling magnification uncertainty.
-In all panels the first data point is SN image 2, followed by image 1 and image 3.
+\added[id=r2]{Data points in the right column also include this magnification uncertainty, even though cluster-scale lensing is achromatic, because the {\tt STARDUST2} analysis was done on the light curve data, not the color data directly.} In all panels the first data point is SN image 2, followed by image 1 and image 3.
 \replaced[id=r2]{In each panel the black curves show 200 SN light curve models drawn at random from the nested sampling sequence of the STARDUST2 (sncosmo) classification.
@@
 
-\subsection*{Measuring the Age of the SN for each Image}
+%\subsection*{Measuring the Age of the SN for each Image}
+\subsection*{Time Delay Estimation}
+
 We constrain the relative time delays of \SNABC by using two separate methods to estimate the age of the SN at each image during the single observed epoch.
@@
 Each of these images stems from the same SN explosion, so the difference between the measured age of each image is also a measure of the relative time delay.
+
+\added[id=r2]{
+In all of the light curve fitting exercises described below, we also fix the SALT2 ``stretch'' parameter at $x_1=0$.
+This parameter defines the shape of the SN Ia light curve (the rate of decline in brightness).
+If we  allow $x_1$ to be a free parameter, there is no useful constraint on it.
+It is highly degenerate with the time delay between the images, which is of course a free parameter in all the fits.
+As a check, we have also tried fixing $x_1$ to other values from $-1$ to $+1$, and the time delay results change by less than 5 days, which is well within all error bars.   
+Fixing $x_1$ in this way is comparable to the analysis that will be possible in the 2030s when the fourth SN image is observed.
+We expect that a SALT2 fit to a well-sampled light curve from the fourth image will provide a tight constraint on $x_1$.
+That measured $x_1$ will then be propagated back as a fixed parameter (with small uncertainty) into revised fitting of the SN images 1-3.
+}
 
@@
 While such extreme microlensing could alter the results for images 1 and 3, it would not alter the measurement of image 2 as it is likely in the achromatic phase.
+\added[id=r1]{Fortuitously, images 1 and 3 are minima, which are less susceptible to high deviations owing to microlensing when compared to image 2, which is a saddle.}
 
@@
 This means we are finding a single set of SN model parameters to describe the intrinsic photometric evolution of the SN, and also finding the age (time from peak brightness) for each of the three images.
+%\added[id=r2]{For this method we fix the SALT2 stretch parameter at $x_1$=0.
+In the SALT2 formalism, the stretch parameter does not affect the color of the SN, so any choice of $x_1$ would be acceptable.
+}
 
@@
 
-After repeating this process for each of the five lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
+%\replaced[id=r1]{After repeating this process for each of the five lens models, we compare the Bayesian Evidence of each fit and determine model E to be the preferred lens model.}
+\deleted[id=r1]{After repeating this process for each of the five lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
 Using a coarse sampling we find significant preference for models C and E over models A,B, and D (at $>3\sigma$), but no significant difference between models C and E (Table \ref{tab:model_evidence}).
@@
 This was also the model selected as the optimal lens model before unblinding, so we have reinforced the justification to adopt model E as our preferred model.
+}
 
@@
 
-\begin{table}[ht]
-\begin{tabular}{crrrrrrr}
-
-    \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
-\midrule
-\textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
-\textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
-\textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
-\textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
-\textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7760&$-6.95\pm0.2$ \\
-\end{tabular}
-\caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work.
+% \begin{table}[ht]
+% \begin{tabular}{crrrrrrr}
+
+%     \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
+% \midrule
+% \textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
+% \textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
+% \textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
+% \textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
+% \textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7760&$-6.95\pm0.2$ \\
+% \end{tabular}
+% \caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work.
 The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D.
 We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=-7.25\pm0.07, \ Z_E=-   7.00\pm0.06$).}
-\end{table}
+% \end{table}
 
@@
 
+% updated to SNTD fits and new fluxes
 \begin{figure*}
@@
     \includegraphics[width=0.49\textwidth]{Paper/Figures/colorcurve_image3.pdf}
-    \caption{Color-based age constraints for \SNABC image 1 (upper right), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Color Curve Age Constraints} section.
+    \caption{Color-based age constraints for \SNABC image 1 (upper \replaced[id=r1]{left}{right}), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Color Curve Age Constraints} section.
 The upper panel of each figure shows the posterior for the age of each image from SNTD, using a prior on the SALT2 color parameter (c) based on known population characteristics of SNIa.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/corner_color_curve_fit_with_c_prior_labels.pdf}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/corner_color_curve_fit_with_c_prior_labels}
 %    corner_color_curve_fit_with_c_prior.pdf}
@@
     \includegraphics[width=0.49\textwidth]{Paper/Figures/lightcurve_image3.pdf}
-    \caption{Light-curve-based age constraints for \SNABC image 1 (upper right), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Light Curve Age Constraints} section.
+    \caption{Light-curve-based age constraints for \SNABC image 1 (upper \replaced[id=r1]{left}{right}), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Light Curve Age Constraints} section.
 The upper panel in each figure shows the posterior distributions from SNTD for the age of each image that is independent of the lens model (magenta, figure \ref{fig:colorcurves}), using lens model E (light blue), and the combination of both methods (orange).
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelH_color_corner_labels.pdf}
+    \includegraphics[width=0.9\textwidth]{Paper/Figures/lc_modelE_color_corner_labels}
     \caption{The marginalized and joint posterior distributions for the final age constraints measured in this analysis.
@@
 \end{figure*}
-
+% updated to SNTD fits and new fluxes
 \begin{figure}[htp]
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/full_lightcurve.pdf}
+    \includegraphics[width=0.6\textwidth]{Paper/Figures/full_lightcurve.pdf}
     \caption{\label{fig:full_lightcurve}The reconstructed light curve for \SNABC.
@@
 \end{figure}
+% updated to SNTD fits and new fluxes
 \begin{figure}[hbp]
     \centering
-    \includegraphics[width=\textwidth]{Paper/Figures/full_colorcurve_total.pdf}
+    \includegraphics[width=0.6\textwidth]{Paper/Figures/full_colorcurve_total.pdf}
     \caption{\label{fig:full_colorcurve} The reconstructed color curve for \SNABC, using best-fit lensing parameters.
@@
 
+\section*{Supplementary Material}
+
+\subsection*{Supplementary Note: Comparison to Previous Lens Modeling}
+
+\added[id=r1]{
+Ref \cite{newman_resolving_2018} (hereafter N18) provides a detailed analysis of this cluster, including sophisticated modeling of the lens.
+The N18 lens modeling also uses \lenstool, but has several important differences.
+Most notably, N18 uses source-plane instead of image-plane optimization, incorporates pixel-level data as constraints, and provides source-plane reconstructions of the lensed galaxy that we identify as the SN host.
+For this work, we find the \lenstool image-plane optimisation to be more robust because it deals better with actual positional uncertainties.
+We did not incorporate pixel-level flux data, because the \lenstool code can only use observed fluxes when doing source plane optimisation.
+}
+
+\setcounter{table}{0} %\renewcommand{\thetable}{\arabic{figure}}
+\begin{table}[tbp]
+    \captionsetup{name={Supplementary Table}}
+    \centering
+    \begin{tabular}{crrrrr}
+    Image     & $\langle$ $\mu_{\rm SN}$ $\rangle$ & $\mu_{\rm opt,SN}$ & $\mu_{\rm opt,gal.pk.}$ & $\mu_{\rm gal.avg.}$ & $\mu_{\rm N18,gal.avg.}$\\
+\hline 
+        1 & 3.9$\pm$0.5 &  6.7 & 4.35 & 10.0 & 12.5$\pm$5.4 \\
+        2 & 7.4$\pm$3   & 15.2 &  6.9 &  8.3 & 10.3$\pm$3.1 \\
+        3 & 5$\pm$1     &  4.3 & 3.64 &  4.2 & 4.9$\pm$1.6 \\
+    \end{tabular}
+    \caption{
+    \added[id=r1]{Comparison of magnification predictions with the N18 lens model.}
+    }
+    \label{tab:mu_comparison}
+\end{table}
+
+\added[id=r1]{
+Table~\ref{tab:mu_comparison} shows the magnification values predicted by our lens model E in comparison to the values reported in N18. 
+Column 2 repeats the magnifications given in the main text and Table~\ref{tab:massmodel}, which are the expectation values from the $\mu$ distributions generated by the \lenstool MCMC sampling over model parameter space.
+Column 3 gives the ``optimized'' magnification, which is the $\mu$ value returned by the single model instance that has the minimum $\chi^2$ value (note that this may be significantly different from the peak of the $\mu$ distribution, as for image 2 in particular).
+Both of these are magnifications for the location of each SN image.
+The fourth and fifth columns give magnification predictions for the SN host galaxy.
+Column 4 reports the minimum-$\chi^2$ magnification at the peak of the surface brightness profile for each galaxy image.
+Column 5 reports the
+ratio of the total flux to source flux of the host galaxy, which is effectively a flux-weighted harmonic mean of the magnification factors across each galaxy image.
+This last value is the most appropriate for comparison to the values of N18 (given in Column 6), which are computed in a similar way.
+The uncertainties from N18 reflect an estimate of systematic uncertainties, derived from lens modeling variants.
+
+From the last two columns of Table~\ref{tab:mu_comparison} we see that our preferred lens model E magnifications are within 1$\sigma$ of the N18 model, though our predictions are systematically lower by about 20\%.
+This agrees with the assessment of systematic uncertainties from our lens model variants discussed above, which are also shown as the asymmetric error bars on the SN magnitudes in Figure~\ref{fig:class}.
+As seen in Figure~\ref{fig:class}c, a larger magnification value would make the SN {\it more} consistent with the expected luminosity of a Type Ia SN at this redshift---though it would also make it more consistent with some CC SN light curves, likely making the classification somewhat more ambiguous.
+We expect that new lens modeling of this cluster with alternate software and different choices of constraints will also be informative, and may improve on our model predictions.  
+Both the N18 modeling and the construction of lens model E and our model variants are constructed blind (without knowledge of the SN magnitudes).
+Future lens modeling could incorporate the measured magnitudes as constraints, potentially yielding a more robust prediction of the time delay for the fourth image.
+We hope that the discovery of \SNABC  will encourage such efforts.
+}
+
+\subsection*{Supplementary Note: Future Work}
+
+\subsubsection*{Future Lens Modeling}
+\added[id=r1]{
+The uncertainty in the predicted time delay from the lens model presented here is $\pm$540 days (in the observer frame).
+Are there improvements to the lens modeling that could tighten this prediction?
+
+Our lens modeling did not make use of the velocity dispersion of the BCG, measured as 390$\pm$10 km s$^{-1}$ from our MUSE data.
+We did not have this measurement available prior to unblinding, and thus we have restricted ourselves to only consider fully blind lens models in this paper.
+However, future analyses could incorporate the BCG velocity dispersion and here we speculate about the impact.
+With a preliminary extension of model E we find that the time delay predictions would likely shift by $<$15 days, and the predicted magnifications for SN images 1-3 would likely be larger by as much as $\sim$2.5$\times$.
+This is within the range of our systematic uncertainty estimates based on lens models A-E.
+We therefore expect that inclusion of the BCG velocity dispersion will not significantly impact the SN classification or time delay conclusions, but may improve the accuracy and precision of the time delay estimate for image SN4.
+
+One may anticipate that future observations of the lensing cluster (e.g.
+with JWST) will provide more lens modeling constraints, potentially including the discovery of new multiply-imaged systems and new redshift measurements.
+These would substantially improve the lens model time delay predictions.
+Application of different lens modeling approaches could also provide some added confidence that there are not systematic biases in the lens model time delay prediction.
+}
+
+\subsubsection*{Future Observations}
+\added[id=r1]{
+Though the $\pm540$ day time delay uncertainty is small relative to the baseline of $>7000$ days, it nevertheless represents a long period over which the field would need to be monitored for the reappearance.
+Is it feasible to expect future observations to catch the reappearance of \SNABC close to peak brightness?
+Even if the time delay uncertainty remains on the order of $\pm1$ year, it would still be reasonable to execute a follow up campaign with a cadence of approximately 2 months.
+Since the SN is at a redshift of $z=1.95$, a span of, say, 50 days in the observer frame is 17 days in the rest frame, comparable to the rise-time of a Type Ia SN.
+Thus, it is reasonable to expect that a relatively inexpensive monitoring campaign would be able to catch the return appearance of \SNABC at or before peak brightness, ensuring a well-sampled light curve for the final SN image.
+
+If future follow-up observations are successful in capturing the full light curve of the final fourth image, then future lens modeling could also incorporate measured SN magnifications as constraints.
+Measured magnifications from lensed Type Ia SNe have been used to test lens models at both the cluster and galaxy scale \cite{nordin_lensed_2014, rodney_illuminating_2015, dhawan_magnification_2020}.
+The addition of astrometric constraints for the fourth image could also significantly improve the time delay predictions for a lens model \cite{birrer_astrometric_2019}---and this could be done even with a fully blinded analysis.
+Measurement of the magnification for a lensed Type Ia SN can be done without adopting strong priors from a cosmological model \cite{patel_three_2014}, meaning that one can avoid a circular constraint when the \SNABC time delay is then used for cosmology.
+}
+
+\subsubsection*{Future Discoveries}
+\added[id=r2]{
+In addition to follow-up observations of \SNABC, we may also hope for more discoveries of similar cluster-lensed SNe with long time delays.
+The expected rate for such events is still highly uncertain, and published rate estimates to date can only be taken as extreme lower limits for the expected yield from future sky surveys \cite{riehm_near-ir_2011,li_rates_2012,petrushevska_searching_2018,petrushevska_strongly_2020}.
+All of these past analyses have been
+limited to $\leq 5$ well-studied galaxy clusters.  Furthermore, they have only examined the set of {\it already known} multiply-imaged galaxies, and have 
+explicitly predicted only the rate of events that would have a time delay of $<$5 years.
+With these caveats, the predicted lower limits are of order 1 SN detection per year per cluster, for a deep survey with a detection limit of 27 AB mag \cite{li_rates_2012}.
+At the $5\sigma$ limits of the Rubin Observatory ($i\sim23.4$ AB mag), the lower limit on that rate is reduced by about a factor of ten \cite{petrushevska_strongly_2020}.
+
+It is treacherous to extend these estimates to the larger population of all galaxy clusters that will be regularly observed by future wide-field surveys.
+Nevertheless, let us make a crude extrapolation to motivate future work.
+Consider the 1-year 2000 deg$^2$ High Latitude Survey (HLS) from the Roman Space Telescope \cite{spergel_wide_2015, troxel_synthetic_2021}, and let us conservatively apply the rate of
+$\sim$1~SN yr$^{-1}$ cluster$^{-1}$ to only the $\sim$10 most massive clusters in the HLS area.
+This still predicts at least 10 cluster-lensed SN detections, which is comparable to the few dozen galaxy-lensed SNe expected from the Roman SN cosmology survey \cite{pierel_projected_2020}.
+Similarly, if we apply the 10$\times$ lower rate for the Rubin Observatory to the most massive clusters in the LSST survey area, we would anticipate at least $\sim$10 detections over the 10-year survey.
+
+We hope that the discovery of \SNABC will motivate an improvement over this very rough estimation of future rates.
+This would require a more complete census of lensing clusters, along with lens models to predict magnifications and time delays, and measurements of star formation and stellar mass in lensed galaxies to predict the SN explosion rates.
+}
+
+\clearpage
+
 %Using Biblatex for the bibliography
@@
 
+Correspondence and requests for materials may be addressed to S.R. (\href{mailto:srodney@sc.edu}{srodney@sc.edu}).
+
 %%%%%%%%%%%% Acknowledgents
@@
 Based on observations made with the NASA/ESA Hubble Space Telescope, obtained from the data archive at the Space Telescope Science Institute, and on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 0103.A-0777(A).
-{\bf Funding:} Support for this work was provided by NASA through grant numbers HST-GO-15663 and HST-AR-15050 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
+{\bf Funding:} Support for this work was provided by NASA through grant numbers HST-GO-14622, HST-GO-15663 and HST-AR-15050 from the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc.
 under NASA contract NAS 5-26555.
@@
 140.
-This work was supported by NASA Headquarters under the NASA Future Investigators in Earth and Space Science and Technology (FINESST) award 80NSSC19K1414.
+M.A.\ and J.D.R.P.\ were supported by NASA Headquarters under the NASA Future Investigators in Earth and Space Science and Technology (FINESST) awards 80NSSC19K1414 and 80NSSC19K1418, respectively.
+K.E.W.\ wishes to acknowledge funding from the Alfred P.
+Sloan Foundation.
 
 {\bf Author Contributions:} 
-Conceptualization, S.A.R., G.B., and S.T.; Methodology, S.A.R., J.D.R.P., J.R., and K.F.O.; Investigation, G.B., J.R., S.T., M.A., and K.E.W.; Writing - Original Draft, G.B.\ and S.T.; Writing - Review \& Editing, S.A.R., G.B., J.D.R.P., J.R., S.T., K.F.O., M.A., and K.E.W.; Visualization, S.A.R., G.B., J.D.R.P., J.R., K.F.O.; Supervision, G.B., S.T., and K.E.W.; Funding Acquisition, K.E.W.
+Conceptualization, S.A.R., G.B., and S.T.; Methodology, S.A.R., J.D.R.P., J.R., and K.F.O.; Investigation, G.B., J.R., S.T., M.A., and K.E.W.; Writing - Original Draft, G.B.\ and S.T.; Writing - Review \& Editing, S.A.R., G.B., J.D.R.P., J.R., S.T., K.F.O., M.A., and K.E.W.; Visualization, S.A.R., G.B., J.D.R.P., J.R., K.F.O.; Supervision, S.A.R., G.B., S.T., and K.E.W.; Funding Acquisition, M.A.\ \& K.E.W.
 

### 2021-05-21 Paper/NatureAstronomy/main_resubmission2.tex

--- 2021-05-21 Paper/NatureAstronomy/main_resubmission1.tex
@@
 \usepackage{graphicx}
+\usepackage{threeparttable}
 
@@
 %%%  SELECT DRAFT VERSION (CHANGETEXT) OR FINAL 
-%\usepackage[draft,xcolor=dvipsnames]{changes}
-%\linenumbers
-\usepackage[final,xcolor=dvipsnames]{changes}
+\usepackage[draft,xcolor=dvipsnames]{changes}
+\linenumbers
+%\usepackage[final,xcolor=dvipsnames]{changes}
 
@@
 
-\replaced[id=ed]{
   When the light from a distant stellar explosion passes very near to a foreground galaxy or cluster, gravitational lensing can cause it to appear as multiple images on the sky.
 Such strongly-lensed supernovae can be used to constrain the cosmic expansion rate \cite{refsdal_possibility_1964} and dark energy models \cite{treu_time_2016}.
-Achieving these cosmological goals requires many more lensed supernova discoveries and more efficient observational follow-up.
-Here we report the discovery of a multiply-imaged supernova that will enable a time delay measurement with an uncertainty of $<1\%$.
+Achieving these cosmological goals \replaced[id=r2]{will require many lensed supernovae with precise time delay measurements.}{requires many more lensed supernova discoveries suitable for precise time delay measurement.}   Here we report the discovery of a multiply-imaged supernova that will enable a time delay measurement with an uncertainty of $<1\%$.
 It appeared in an evolved galaxy at $z=1.95$, gravitationally lensed by a massive foreground galaxy cluster.
@@
 We predict a fourth image will appear close to the cluster core in the year 2037$\pm$2.
-Observation and modeling of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline.
-This object demonstrates that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed supernovae.}{
-  We report the discovery of a strongly-lensed supernova (SN) explosion that will enable a time delay measurement with an uncertainty of $<1\%$.
-This unprecedented scenario will enable a rare and highly precise measurement of the Hubble\added[id=r1]{-LeMa\^{i}tre} constant from a single lensed SN.
-The SN is in an evolved galaxy at $z=1.95$, gravitationally lensed by the massive foreground galaxy cluster MACS J0138.0-2155.
-This is the most distant multiply-imaged supernova yet discovered.
-We classify the supernova as \added[id=r2]{most likely} a Type Ia \deleted[id=r2]{with {$>90\%$} probability} based on archival imaging observations from the \textit{Hubble Space Telescope}.
-Three lensed images of the SN are detected with relative time delays of $<$200 days, and we predict that a fourth image in the component closest to the cluster core will appear in the year 2037$\pm$2.
-Observing the light curve of that future image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline.
-}
+\added[id=r1]{The SN classification and the predicted reappearance time could be improved with further lens modeling and a comprehensive analysis of systematic uncertainties.}  
+  Observation \replaced[id=r1]{of the fourth }{and modeling of that future} image could provide a time delay precision of $\approx 7$ days over an extraordinary 20 year baseline. 
+  \deleted[id=r2]{ This object demonstrates that cosmologically useful time delays can be measured with minimal observational cost using cluster-lensed supernovae.}
+
 \end{sciabstract}
@@
 \cite{amendola_cosmology_2013,spergel_wide_2015,Ivezic_lsst_2019}.
-\deleted[id=ed]{A series of} Recent investigations into the expansion rate of the universe (the Hubble-LeMa\^itre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background \deleted[id=ed]{(CMB)} radiation \cite{Riess_large_2019,aghanim_planck_2018}.
+ Recent investigations into the expansion rate of the universe (the Hubble-LeMa\^itre constant; $H_0$) have found that measurements from the local universe are significantly different from the value inferred from measurement of the cosmic microwave background radiation \cite{Riess_large_2019,aghanim_planck_2018}.
+\replaced[id=r2]{
+ The community is actively attempting to resolve this tension in $H_0$ measurements by mitigating systematic uncertainties  or revealing new physics from the early universe \cite{verde_tensions_2019}.
+Either resolution will require multiple independent cosmological probes.}{
 Resolving this tension in $H_0$ measurements may reveal new physics from the early universe, and to do so requires multiple 
-independent cosmological probes \cite{verde_tensions_2019}.
+independent cosmological probes.}
 
@@
 %the expansion rate of the universe, 
-$H_0$ \cite{refsdal_possibility_1964} and the dark energy equation-of-state, $w$ \cite{coe_cosmological_2009}.%,linder_lensing_2011}.
+$H_0$ \cite{refsdal_possibility_1964} and the dark energy equation-of-state, $w$ \cite{holz_seeing_2001}. 
 In recent years this method has been successfully applied to lensed
 quasars %cite{suyu_cosmology_2014,bonvin_cosmograil_2019}, 
-with six high-precision measurements to date \cite{wong_h0licow_2019}.
+with \replaced[id=r3]{seven}{six} high-precision measurements to date \replaced[id=r3]{\cite{wong_h0licow_2019}}{\cite{birrer_tdcosmo_2020}}.
 As this sample of time delay lenses grows to several dozen, it is expected to deliver a measurement of $H_0$ with 1\% precision \cite{suyu_cosmological_2018}.
-\added[id=r1]{A future sample with $\sim100$ well-measured lensing time delays will be a competitive tool for dark energy studies \cite{treu_time_2016}.}
+A future sample with $\sim100$ well-measured lensing time delays will be a competitive tool for dark energy studies \cite{treu_time_2016}.
 %\cite{linder_lensing_2011,jee_time-delay_2016,suyu_HOLISMOKES_2020}.}
 
-Gravitationally lensed SN with multiple images present an attractive new addition to this field.
-Most notably, SN exhibit relatively simple photometric behavior, with well-understood light curve shapes and colors---in contrast to the stochastic variation of quasars.
-However, \deleted[id=ed]{despite the promise of lensed SN time delay cosmography as a cosmological distance probe,} to date there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
+Gravitationally lensed SN with multiple images 
+\replaced[id=r2]{could become an important part of this time-delay cosmology sample that will develop over the next 10-20 years.}{
+present an attractive new addition to this field. Most notably, SN exhibit}
+\added[id=r2]{Lensed SN are attractive for this purpose because they have} relatively simple photometric behavior, with well-understood light curve shapes and colors---in contrast to the stochastic variation of quasars.
+However,  to date there have been only two lensed SN observed with multiple images \cite{kelly_multiple_2015,goobar_iptf16geu:_2017}.
 The first, {\it SN Refsdal}, was a peculiar Type II SN whose image with the longest delay was missed \cite{kelly_sn_2016}.
 The second, {\it SN 2016geu}, was a Type Ia SN with short delays that make high precision time delay measurements impossible \cite{dhawan_magnification_2019}.
-\added[id=r1]{An earlier discovery of an unusually luminous SN \cite{chornock_ps1-10afx_2013} was also shown to be a strongly-lensed SNIa,  \cite{quimby_detection_2014} %quimby_extraordinary_2013,
-though the multiple images were not resolved.}  Here we present the discovery 
+An earlier discovery of an unusually luminous SN \cite{chornock_ps1-10afx_2013} was also shown to be a strongly-lensed SNIa,  \cite{quimby_detection_2014} %quimby_extraordinary_2013,
+though the multiple images were not resolved.  
+Here we present the discovery 
 of a third lensed SN resolved into multiple images: \SNABC.
@@
 that first confirmed the MRG-M0138 galaxy as a strongly-lensed object 
-\added[id=ed]{(Methods: Observations)}. 
+(Methods: Observations). 
 Each point source is within 5 arcseconds of one of the four MRG-M0138 images.  None of the
@@
 To construct a lens model for the MACS J0138.0-2155 cluster we use the \lenstool software \cite{jullo_bayesian_2007,kneib_lenstool_2011} to model the mass distribution in the cluster core as the combination of a cluster-scale and multiple galaxy-scale potentials
-\added[id=ed]{(Methods: Lens Modeling)}.
+(Methods: Lens Modeling).
 %\cite{materials_methods_2020}.  
 To avoid unintended bias, we kept the lens model development completely separate from the analysis of the SN.
-Only upon \deleted[id=ed]{independent} completion of both were the results combined for the analysis described here.
-The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the \replaced[id=r3]{galaxy's centroid position }{central light peak} and the SN location in each image) as well as a multiply-imaged background
+Only upon  completion of both were the results combined for the analysis described here.
+The input model constraints are the positions and redshifts of the MRG-M0138 galaxy at $z=1.95$ (both the galaxy's centroid position and the SN location in each image) as well as a multiply-imaged background
 galaxy at $z=0.766$, both having secure spectroscopic redshifts
-\added[id=ed]{(Methods: Observations)}.
+(Methods: Observations).
 %\cite{materials_methods_2020}.  
 From this model we derive estimates for the lensing magnification and time delay of each of the SN images, including the predicted fourth image (Table \ref{tab:time_delays}).
-The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$\replaced[id=r1]{2}{1.5}, demagnified with $\mu=0.4\pm0.2$.
+The lensing model predicts that the SN should appear in the fourth MRG-M0138 image in the year 2037$\pm$2, demagnified with $\mu=0.4\pm0.2$.
 The predicted location for this future image is $\alpha=$01:38:04.15, $\delta=-$21:55:24.659.
 A fifth image will also appear at a still later date, located near the center of the cluster and much more significantly demagnified, so it will not be easily observable.
-\added[id=r1]{We anticipate that future lens modeling of the cluster may improve on these predictions} \added[id=ed]{(Supplementary Note: Future Work}).
+We anticipate that future lens modeling of the cluster may improve on these predictions (Supplementary Note: Future Work).
+\added[id=r1]{For example,
+our analysis adopted only a single form for the density profiles, and did not incorporate constraints from stellar kinematics or pixel-level surface brightness data from the multiply-imaged systems.}
 
@@
 \ref{fig:class}).
-\replaced[id=r1]{After magnification correction, all three images are still brighter than expected for a Type Ia SN, which may indicate that a lens-modeling degeneracy is at play \cite{falco_model-dependent_1985, schneider_source-position_2014}.
-Nevertheless, the magnification-corrected \SNABC data are more consistent with the Type Ia population than any CC SN sub-class (Fig.~\ref{fig:class}a,b), and demonstrate the expected evolution of a Type Ia SN color and brightness over $\sim 100$ days (Fig.~\ref{fig:class}c).}{This provides more classification leverage, yielding p(Ia)=95\%.}
+After magnification correction, all three images are still brighter than expected for a Type Ia SN, which may indicate that a lens-modeling degeneracy is at play \cite{falco_model-dependent_1985, schneider_source-position_2014}.
+Nevertheless, the magnification-corrected \SNABC data are more consistent with the Type Ia population than any CC SN sub-class (Fig.~\ref{fig:class}a,b), and demonstrate the expected evolution of a Type Ia SN color and brightness over $\sim 100$ days (Fig.~\ref{fig:class}c).
 By also including the model-predicted time delays, we can treat the three SN images effectively as three points on a common SN light curve, and we find p(Ia)=94\% 
-\added[id=ed]{(Methods: Classification)}.
+(Methods: Classification).
 %\cite{materials_methods_2020}. 
-\replaced[id=r2]{An improved classification can be achieved }{These final classifications are strongly conditional on the priors, and we look forward to an improved classification} with spectroscopy and multi-band photometry upon arrival of the fourth image.
-\added[id=r2]{For the remainder of this analysis, we proceed under the assumption that \SNABC is indeed a Type Ia SN---though the subsequent analysis could be revised to achieve similar results with a different underlying SN model.}
+An improved classification can be achieved  with spectroscopy and multi-band photometry upon arrival of the fourth image.
+For the remainder of this analysis, we proceed under the assumption that \SNABC is indeed a Type Ia SN---though the subsequent analysis could be revised to achieve similar results with a different underlying SN model.
 
@@
 Combining this information with magnification constraints from the lens modeling helps break parameter degeneracies, yielding the measured delays in Table \ref{tab:time_delays}
-\added[id=ed]{(Methods: Time Delay)}.
+(Methods: Time Delay).
 %\cite{materials_methods_2020}. 
@@
 Such a light curve will pin down the intrinsic SN light curve parameters that are shared by all images, and break remaining parameter degeneracies.
-%\added[id=ed]{(Supplementary Note: Future Observations)}.
-
-\added[id=r1]{As with any single time-delay system, \SNABC will not be particularly powerful as a solitary cosmological probe.
-However,} future large-scale surveys such as the Vera C.
-Rubin Observatory
-and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes, \added[id=r1]{though the vast majority of these will be lensed by galaxy-scale deflectors \cite{oguri_gravitationally_2010,  goldstein_rates_2019, pierel_projected_2020}.} %wojtak_magnified_2019,
-\deleted[id=r1]{However, many of these lensed SN will require substantial follow-up resources to be made cosmologically useful.} Thus, almost all will have significantly shorter 
+%(Supplementary Note: Future Observations).
+
+As with any single time-delay system, \SNABC will not be particularly powerful as a solitary cosmological probe.  However, future large-scale surveys such as the Vera C. Rubin Observatory 
+and the Nancy Grace Roman Space Telescope will observe dozens to hundreds of lensed SN over their mission lifetimes, though the vast majority of these will be lensed by galaxy-scale deflectors \cite{oguri_gravitationally_2010,  goldstein_rates_2019, pierel_projected_2020}.
+%wojtak_magnified_2019,
+ Thus, almost all will have significantly shorter 
 delays (of order 10--100 days) and therefore higher relative uncertainties than \SNABC.  Since it is the {\it fractional} time delay uncertainty that 
@@
 In fact, the long time baseline of lensed SN like \SNABC effectively insures that their cosmological precision is not limited by time delay measurement uncertainty.
-\added[id=r1]{Cluster-scale lenses are more complex than galaxy-scale lenses, but they generally have ``independent'' measurements of the magnification from several multiply-imaged systems in the same field.
-As such, they can provide a valuable check on systematics related to specific lens modeling software, microlensing variation, and more.}
-
-In Figure \ref{fig:cosmo} we illustrate the cosmological value of time delay cosmography with objects like \SNABC  by considering a small sample of 5 ``\reqlike'' SN\added[id=r1]{---with $<1\%$ time delay precision and the same redshift ratio.}
+Cluster-scale lenses are more complex than galaxy-scale lenses, but they generally have ``independent'' measurements of the magnification from several multiply-imaged systems in the same field.
+As such, they can provide a valuable check on systematics related to specific lens modeling software, microlensing variation, and more.
+
+\deleted{In Figure \ref{fig:cosmo} we illustrate the cosmological value of time delay cosmography with objects like \SNABC  by considering a small sample of 5 ``\reqlike'' SN---with $<1\%$ time delay precision and the same redshift ratio.
 For a comparison on equal footing, we evaluate equal-sized lensed SN samples 
@@
 Because of the unusually large redshift ratio of \SNABC, the constraints
-from the \reqlike sample are nicely complementary to the low-$z$ Rubin Observatory and high-$z$ Roman Space Telescope samples. 
-Furthermore, when we assume that the lens modeling uncertainty is equal for each sample (amounting to a 5\% uncertainty in each time delay distance), the \reqlike sample has leverage that is comparable to the same number of lensed SN from the wide-field surveys.
-However, if we improve  the lensing constraints to 2\% precision, the \reqlike contours tighten dramatically, reflecting the fact that these long-time-baseline events are limited only by the lens modeling uncertainty.
-
-To achieve these cosmological constraints in practice, such a sample could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered
-\added[id=ed]{(Supplementary Note: Future Work}).
-%\cite{materials_methods_2020}.  
-As \SNABC shows, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.  
-%After that, all we need is patience.
+from the \SNABC-like sample are nicely complementary to the low-$z$ Rubin Observatory and high-$z$ Roman Space Telescope samples. 
+Furthermore, when we assume that the lens modeling uncertainty is equal for each sample (amounting to a 5\% uncertainty in each time delay distance), the \SNABC-like sample has leverage that is comparable to the same number of lensed SN from the wide-field surveys.
+However, if we improve  the lensing constraints to 2\% precision, the \SNABC-like contours tighten dramatically, reflecting the fact that these long-time-baseline events are limited only by the lens modeling uncertainty.}
+
+\added[id=r2]{
+The first multiply-imaged SN discovery, SN Refsdal, has shown that time delay cosmography with a cluster-lensed SN is viable \cite{rodney_sn_2016,kelly_deja_2016}.
+However, the observing campaign for SN Refsdal was extraordinary, deploying more than 75 HST orbits over three years.
+Significant observational investment has been required for high-precision time delay measurement of lensed quasars, such as decade-long programs \cite{millon_cosmograil_2020} or daily monitoring for high-cadence light curves \cite{millon_tdcosmo_2020}.
+In the case of \SNABC it will be possible to achieve similar time delay precision over the 20-year baseline with just a single imaging epoch as the anchor point.
+}
+
+\replaced[id=r2]{A sample of \SNABC-like events}{To achieve these cosmological constraints in practice, such a sample} could be developed with regular monitoring of cluster-scale lenses, partnered with modest follow-up to characterize any lensed SN discovered
+(Supplementary Note: Future Work).
+\deleted[id=r2]{As \SNABC shows, even a single epoch of photometric data at the time of detection may be sufficient to provide the necessary anchor point for this promising cosmological tool.
+}  \added[id=r3]{ Even with a concerted effort to discover  cluster-lensed SN, the vast majority of time delay cosmography constraints will always come from  quasars and SN lensed by {\em galaxy}-scale lenses.
+The systematic biases of cluster lens models are very different from those of galaxy scale lens modeling, so systems like \SNABC can be an asset for validating time delay cosmology systematics.
+%We leave a detailed exploration of the cosmological impact of this and other cluster-lensed SN to future work. 
+}
 
@@
 The wide-field view in $a)$ is 40\arcsec\ on a side with ticks indicating 10\arcsec\ intervals.
-    \added[id=r1]{Labels marked 3.1--3.4 indicate the locations of a separate  multiply-imaged [O\textsc{ii}]-emitter at $z=0.77$ used to help constrain the lensing potential.} 
+    Labels marked 3.1--3.4 indicate the locations of a separate  multiply-imaged [O\textsc{ii}]-emitter at $z=0.77$ used to help constrain the lensing potential. 
     Panels \emph{b}--\emph{i} show 4\arcsec\ cutouts around the lensed SN images with 1\arcsec\ ticks.
 The three-color images are generated from the WFC3/IR filters as indicated; panels \emph{bcde} show the imaging from 2016 July where the SN was visible and \emph{fghi} show the later imaging from 2019 July where the the SN has faded away.
-Panels \emph{aei} indicate the location of the fourth image predicted to appear in $\approx$2037 \added[id=r3]{and panel \emph{a} shows the final and highly demagnified fifth image (``SN5'')}.
+Panels \emph{aei} indicate the location of the fourth image predicted to appear in $\approx$2037 and panel \emph{a} shows the final and highly demagnified fifth image (``SN5'').
 All panels use the late-epoch F125W imaging for the green channel; nevertheless, it is immediately clear that the SN2 image is substantially bluer than the other two, which helps to constrain the relative age of each SN image and the transient classification as a likely Type Ia supernova explosion.
@@
     \includegraphics[draft=False, width=\textwidth]{Paper/Figures/snRequiem_classcontours_timeline_hist.png}
-    \caption{Classification information for \SNABC based on its position in color-magnitude space. \replaced[id=r3]{(a)}{\emph{Left:}} 
-    \added[id=r1]{The observed photometry for the three SN images is shown as open markers.
+    \caption{Classification information for \SNABC based on its position in color-magnitude space. (a) 
+    The observed photometry for the three SN images is shown as open markers.
 Vertical dotted lines show the lens magnification corrections using our preferred lens model, with a filled grey marker indicating the corrected (demagnified) magnitude.
-Error bars indicate the observational and systematic uncertainty, including the range of alternative magnification corrections encompassed by lens model variations.}
-    Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green), drawn \replaced[id=r3]{with two contour levels enclosing }{to enclose} 68\% \deleted[id=r3]{(interior solid lines)} and 95\% \deleted[id=r3]{(exterior shaded regions)} of each SN population.
+Error bars indicate the observational and systematic uncertainty, including the range of alternative magnification corrections encompassed by lens model variations.
+    Contours show the population distributions for normal SNe of Type Ia (red), Type Ib/Ic (gold), and Type II (green), drawn with two contour levels enclosing 68\%  and 95\%  of each SN population.
 Each SN sub-class was simulated at $z=1.95$, and samples from their expected light curves were drawn uniformly in time.
-    \replaced[id=r3]{(b)}{\emph{Right:}} \added[id=r3]{Marginalized distributions along the color dimension for the three SN sub-classes (using the same color scheme).
+    (b) Marginalized distributions along the color dimension for the three SN sub-classes (using the same color scheme).
 The simulated populations have been scaled according to the expected explosion rates in the SN host galaxy, based on its stellar population properties.
-Open markers show the observed colors again.}
-    \added[id=r3]{(c) Zoomed-in view of the color-mag space marked by the grey box in panel a.}
-    The evolution of a typical Type Ia SN at $z=1.95$ \deleted[id=r3]{in observed color-brightness space} is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
-White diamonds correspond to the times labeled on the colorbar \replaced[id=r3]{below}{at right}.
-Grey shading shows the typical range of luminosities \added[id=r3]{and colors} observed for the Type Ia SN population in the nearby universe.
+Open markers show the observed colors again.
+    (c) Zoomed-in view of the color-mag space marked by the grey box in panel a.
+    The evolution of a typical Type Ia SN at $z=1.95$  is shown by a colored line, with the line color indicating SN age in observer-frame days relative to peak brightness.
+White diamonds correspond to the times labeled on the colorbar below.
+Grey shading shows the typical range of luminosities and colors observed for the Type Ia SN population in the nearby universe.
 %\cite{wang_determination_2006}.
-    \added[id=r2]{Although the magnification-corrected data are brighter than expected for most SNIa, they are consistent both with the overall SNIa population, and with the SNIa color-mag vs time curve.
-}
+    Although the magnification-corrected data are brighter than expected for most SNIa, they are consistent both with the overall SNIa population, and with the SNIa color-mag vs time curve.  
     %An interactive 3-D version of this figure is available online at \href{https://plot.ly/~jpierel/6}{https://plot.ly/~jpierel/6}
@@
 
-\clearpage
-\begin{figure}
-    \centering
-    \includegraphics[draft=False,trim={2cm, 3cm, 3cm, 4cm},clip,width=\textwidth]{Paper/Figures/snrequiem_hw_w0wa_apples_to_lsst_ngrst_4panel.pdf}
-    \caption{  
-    The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation-of-state parameters ($w_0, w_a$).
-Dashed lines and the \replaced[id=r3]{black}{white} marker show the input values (upper right of the top panels) that were used for this simulation.
+%%% FIGURE 3 REMOVED 
+%\clearpage
+%\begin{figure}
+%    \centering
+%    \includegraphics[draft=False,trim={2cm, 3cm, 3cm, 4cm},clip,width=\textwidth]{Paper/Figures/snrequiem_hw_w0wa_apples_to_lsst_ngrst_4panel.pdf}
+%    \caption{  
+%    The sensitivity of \SNABC to the expansion rate of the universe ($H_0$) and dark energy equation-of-state parameters ($w_0, w_a$).
+Dashed lines and the black marker show the input values (upper right of the top panels) that were used for this simulation.
 Contours show the 1$\sigma$ confidence region for a projected sample of 5 lensed SNIa time delays from the Rubin Observatory (blue) and the Roman Space Telescope (red) compared to 5 events like \SNABC (black).
 The left and right columns assume a 5\% and 2\% contribution to the distance uncertainty from modeling the lens potential, respectively.
-    In order to isolate the plotted parameters, all contours are constructed assuming perfect knowledge of the cosmological parameters that are not shown. 
-    }
-    \label{fig:cosmo}
-\end{figure}
+%    In order to isolate the plotted parameters, all contours are constructed assuming perfect knowledge of the cosmological parameters that are not shown. 
+%    }
+%    \label{fig:cosmo}
+%\end{figure}
 
@@
 
-\begin{table}
-\centering
-\begin{tabular}{crc|cc}
-    \multicolumn{1}{c}{}&
-    \multicolumn{2}{c}{\textbf{Inferred from Photometry}}&\multicolumn{2}{c}{\textbf{Lens Model Predictions}}\\
-    %\multicolumn{1}{c}{}&\multicolumn{1}{c}{}\\
-    \multicolumn{1}{c}{\textbf{Image}} &\multicolumn{1}{c}{\textbf{Age}} &\multicolumn{1}{c}{$\mathbf{t_i-t_1}$}&\multicolumn{1}{c}{$\mathbf{\mu}$}
-    &\multicolumn{1}{c}{$\mathbf{t_i-t_1}$}\\
-
+\begin{table}[tb]
+    \caption{\label{tab:time_delays} SN lensing observables.} 
+    \centering
+\begin{threeparttable}
+    \begin{tabular}{cccllcc}
+    Image     & R.A.\tnote{a} & Dec.\tnote{a} & 
+    Age\tnote{b} &  $\Delta t_{\rm obs}$\tnote{c} 
+    & $\Delta t_{\rm pred}$\tnote{c} 
+    & $\mu_{\rm pred}$ \\
+    & & & [days] & [days] & [days] &  \\
+%\hline \\[4pt]
 \midrule
-\textit{1}  & $92^{+21}_{-19}$ & -- & $5\pm1$ & --\\
-\textit{2} & $-24^{+16}_{-7}$ & $114^{+28}_{-31}$ & $7\pm3$ & $82\pm62$ \\
-\textit{3} & $107^{+26}_{-21}$ & $-17^{+19}_{-16}$ &$3.9\pm0.5$  & $-19\pm34$ \\
-\textit{4} & -- & -- & $0.4\pm0.2$ & $7742\pm540$\\
-\textit{5} & -- & -- & $<0.01$ & $9463\pm770$\\
+SN1 & 01:38:03.63     & $-$21:55:50.38        & $92^{+21}_{-19}$  & ---- & --- & 5$\pm$1 \\[4pt]
+SN2 & 01:38:02.96     & $-$21:55:47.26        & $-24^{+16}_{-7}$  & $114^{+28}_{-31}$ & $82\pm62$  & $7\pm3$ \\[4pt]
+SN3 & 01:38:02.42     & $-$21:55:38.47        & $107^{+26}_{-21}$ & $-17^{+19}_{-16}$ & $-19\pm34$ & $3.9\pm0.5$  \\[4pt]
+SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 &  --- & --- & $7742\pm540$\tnote{d} & $0.4\pm0.2$ \\[4pt]
+SN5 &                    &                    & --- & --- & $9463\pm770$\tnote{d} & $<0.01$\\
+\hline 
+\end{tabular}
+
+\begin{tablenotes}    
+    \item[a]{Coordinates are given in the J2000 reference frame, as measured for images 1--3 and as predicted for image 4.  Uncertainties in the predicted position of image 4 are in arcseconds.}
+    \item[b]{The measured age of each SN image is the number of days relative to peak brightness, in observer-frame days. A negative value means the image was observed prior to peak brightness.  }
+    \item[$\dagger$]{Time delays are reported relative to SN1.}
+    \item[$\ddag$]{The combination of the models for the light curve evolution and the lens time delays implies a date of $2037\pm2$ for the peak brightness of Image 4 and 2042$\pm$4 for Image 5 (which will likely be undetectable).}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+%\begin{table}
+%\centering
+%\begin{tabular}{crc|cc}
+
+%\midrule
+%\textit{1}  & 
+%\textit{2} &
+%\textit{3} & \\
+%\textit{4} 
+%
 
@@
 %\textit{4} &-- \ \ \ \ \ \ \ \ \ &-- \ \ \ \ \ \ \ \ \ &1.137&5980.4\\
-\end{tabular}
-\caption{\label{tab:time_delays}Time Delays.  The combination of the models for the light curve evolution and the lens time delays implies a date of $2037\pm2$ for the peak brightness of Image 4.}
+%\end{tabular}
+
 %\todo[inline]{Note: updated to include image 5}.}
-\end{table}
+%\end{table}
 
@@
 Apart from the lensed quiescent galaxy, we measured spectroscopic redshifts for cluster members and one ring-like background galaxy north of the BCG at $z=0.766$.
-\added[id=r1]{Finally, we have measured the velocity dispersion of the BCG to be 390$\pm$10 km s$^{-1}$.
-This measurement was not available for use in our blind lens modeling, but could provide a useful constraint for future lens model improvements (Supplemental Note: Future Work).}
+Finally, we have measured the velocity dispersion of the BCG to be 390$\pm$10 km s$^{-1}$.
+This measurement was not available for use in our blind lens modeling, but could provide a useful constraint for future lens model improvements (Supplemental Note: Future Work).
 
@@
 We add a single galaxy-scale halo on each cluster member, where the shape parameters (halo center, ellipticity) are fixed to their measured HST morphology and their core radius is negligible (fixed at 0.15\,kpc).
-\added[id=r3]{Figure~\ref{fig:model_components} shows the locations of all components of the cluster model, including 32 cluster members (yellow ellipses).} Cluster members were identified by the combination of red sequence selection (based on the F814W$-$F160W color) and MUSE spectroscopy.
+Figure~\ref{fig:model_components} shows the locations of all components of the cluster model, including 32 cluster members (yellow ellipses).
+Cluster members were identified by the combination of red sequence selection (based on the F814W$-$F160W color) and MUSE spectroscopy.
 
@@
     \includegraphics[width=0.8\textwidth]{Paper/Figures/fig4_lensmodel_layout.pdf}
-    \caption{\added[id=r3]{
+    \caption{
     The elements of the MRG0138 cluster lens model.
@@
 The filters used to generate the color image are as in Fig.~\ref{fig:layout}, and tick marks are separated by 10 arcsec.
-    } }
+    }
     \label{fig:model_components}
@@
 The final model, and the one selected as the preferred model prior to unblinding, is model E, which includes all four perturbers described above, and includes the additional background object at $z=0.7663$.
-\added[id=r3]{Note that all of the lens model variants A-D would give a slightly larger magnification for all  three SN images.
-This means that our estimated systematic uncertainties are one-sided, as can be seen on Fig.~\ref{fig:class} and Fig.~\ref{fig:colormag_classification_supplement}.}
+Note that all of the lens model variants A-D would give a slightly larger magnification for all  three SN images.
+This means that our estimated systematic uncertainties are one-sided, as can be seen on Fig.~\ref{fig:class} and Fig.~\ref{fig:colormag_classification_supplement}.
 
@@
 
-\begin{table}[tb]
-    \centering
-    \begin{tabular}{c|l|l|c|c|}
-    Image     & R.A. & Dec. & $\mu$ & $\Delta t$ \\
-    & & & & [days] \\
-\hline 
-SN1 & 01:38:03.63     & $-$21:55:50.38         & 5$\pm$1     &  ---\\
-SN2 & 01:38:02.96     & $-$21:55:47.26         & 7$\pm$3     & 82$\pm62$ \\
-SN3 & 01:38:02.42     & $-$21:55:38.47         & 3.9$\pm$0.5   &   -19$\pm34$ \\
-SN4 & 01:38:04.15$\pm$0.36 & $-$21:55:24.73$\pm$0.43 & 0.4$\pm$0.2 & 7742$\pm$540\\
-\hline 
-\end{tabular}
-    \caption{Magnifications and time delays predicted by the lens model at the location of each supernova image.
-Coordinates are given in the J2000 reference frame, as measured for images 1--3 and as predicted for image 4.
-Uncertainties in the predicted position of image 4 are in arcseconds.
-Time delays are reported relative to SN1.}
-    \label{tab:snpred}
-\end{table}
-
 \begin{figure}
@@
     \includegraphics[width=0.75\textwidth]{Paper/Figures/host_image3_resid.pdf}
-    \caption{\added[id=r3]{Comparison of the SN host galaxy against a simulation using lens model E.
+    \caption{Comparison of the SN host galaxy against a simulation using lens model E.
 North is up and East is left.
@@
     Overlaid contours in the first column show the profile of the observed data (green) and the model (orange).
-    Some residual flux is apparent in the difference images, but the overall shape of each image is well matched by the simulated profile and the distortions introduced by lens model E.}
+    Some residual flux is apparent in the difference images, but the overall shape of each image is well matched by the simulated profile and the distortions introduced by lens model E.
     }
@@
 The final \lenstool model E reproduces all multiple systems with an RMS of 0.15\arcsec.
-We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs\added[id=r3]{, as shown in Figure~\ref{fig:host_model_residuals}}.
+We also simulated the overall shape of the quiescent galaxy using the sum of two Sersic profiles, and check from the HST residuals that they reproduce the pixel-to-pixel morphology of the arcs, as shown in Figure~\ref{fig:host_model_residuals}.
 This model is then used to predict the magnification and time delays for the 3 observed images of \SNABC, as well as the location of the fourth  image, which is still to appear.
@@
 We summarise these predictions in Table \ref{tab:snpred}.
-\added[id=r1]{Comparing our lens modeling to the previous  model of this cluster from \cite{newman_resolving_2018}, we find that the magnification estimates are broadly consistent, though systematically lower (Supplementary Note: Comparison to Previous Lens Modeling).}
-
-%\added[id=r1]{
+Comparing our lens modeling to the previous  model of this cluster from \cite{newman_resolving_2018}, we find that the magnification estimates are broadly consistent, though systematically lower (Supplementary Note: Comparison to Previous Lens Modeling).
 
@@
 derive a $75\%$ probability that \SNABC is of Type Ia (row a of Table \ref{tab:classification}).
-\added[id=r1]{
 We used host galaxy image 2 for this purpose, with the flux-weighted harmonic mean magnification $\mu=8.3$ to derive $M_K$ (see Table~\ref{tab:mu_comparison}).
-We also evaluated the other host galaxy images and found no change in the resulting SN classification probability.}
+We also evaluated the other host galaxy images and found no change in the resulting SN classification probability.
 
@@
 Dotted vertical lines mark the magnification correction based on \lenstool model E.
-\added[id=r2]{Closed markers show the resulting magnification-corrected photometry, with asymmetric error bars reflecting the systematic uncertainty derived from the five lens model variants.}  Horizontal error bars in the upper panel indicate the observed uncertainty in
+Closed markers show the resulting magnification-corrected photometry, with asymmetric error bars reflecting the systematic uncertainty derived from the five lens model variants.
+Horizontal error bars in the upper panel indicate the observed uncertainty in
     the SN color (not affected by lensing).
@@
 The width of this sampling region is set to 3 times the observed color uncertainty, and the height is equal to the lens-modeling magnification uncertainty.
-\added[id=r2]{The $\mu$ uncertainty used here includes an estimate of the systematic uncertainty for each SN image, derived from the spread of magnifications across lens model variants (similar to the methodology of \cite{newman_resolving_2018}).}  We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
-\added[id=r3]{Note that in this case there is no need to apply a cut to the simulated sample to account for detectability, because the $5\sigma$ limiting magnitude of our HST observations is 26.5 AB mag, and after accounting for magnification of $\sim$1.5 mag (Table~\ref{tab:massmodel}) this becomes $m_{lim}\sim28$ mag.
-This means that all the points shown in Fig.~\ref{fig:colormag_classification_supplement} (and therefore all simulated SN entering our classification counts) would be easily detectable in our HST imaging.}  Multiplying by the prior probabilities derived from host galaxy properties, we finally derive the probability that the SN is of Type Ia as $p(Ia)=0.92$, 0.98, and 0.95 from the three SN images SN1, SN2 and SN3, respectively.
+The $\mu$ uncertainty used here includes an estimate of the systematic uncertainty for each SN image, derived from the spread of magnifications across lens model variants (similar to the methodology of \cite{newman_resolving_2018}).
+\added[id=r1]{
+Note, however, that the lens model variations evaluated here  do not vary the assumption of the density profile, which can strongly affect magnifications (for further discussion of this issue, see the Supplementary Note on comparison to prior lens models).
+}
+We take the number of simulated SN for each type as an estimate of the likelihood that \SNABC belongs to that class.
+Note that in this case there is no need to apply a cut to the simulated sample to account for detectability, because the $5\sigma$ limiting magnitude of our HST observations is 26.5 AB mag, and after accounting for magnification of $\sim$1.5 mag (Table~\ref{tab:massmodel}) this becomes $m_{lim}\sim28$ mag.
+This means that all the points shown in Fig.~\ref{fig:colormag_classification_supplement} (and therefore all simulated SN entering our classification counts) would be easily detectable in our HST imaging.
+Multiplying by the prior probabilities derived from host galaxy properties, we finally derive the probability that the SN is of Type Ia as $p(Ia)=0.92$, 0.98, and 0.95 from the three SN images SN1, SN2 and SN3, respectively.
 Row c of Table~\ref{tab:classification} reports the mean of our three classification probabilities for each sub-class.
@@
 With {\tt STARDUST2} we use a nested sampling algorithm to measure likelihoods over the SN simulation parameter space.
-Figure~\ref{fig:classification_lightcurves} shows the magnification- and time-delay-corrected photometry of \SNABC and \replaced[id=r2]{a random sampling of light curve models from the {\tt sncosmo} nested sampling algorithm employed by {\tt STARDUST2}}{the {\tt STARDUST2} maximum likelihood light curve fits from each of the three SN sub-classes considered (Ia, II, Ib/c).}
-\added[id=r2]{Nested sampling is a Monte Carlo method that traverses the likelihood space in a manner that samples the Bayesian likelihood \cite{skilling_nested_2004}.
-These sample light curves and color curves therefore give a visual representation of how well each SN sub-class (Ia, II, Ib/c) can match the observed data.}
+Figure~\ref{fig:classification_lightcurves} shows the magnification- and time-delay-corrected photometry of \SNABC and a random sampling of light curve models from the {\tt sncosmo} nested sampling algorithm employed by {\tt STARDUST2}.
+Nested sampling is a Monte Carlo method that traverses the likelihood space in a manner that samples the Bayesian likelihood \cite{skilling_nested_2004}.
+These sample light curves and color curves therefore give a visual representation of how well each SN sub-class (Ia, II, Ib/c) can match the observed data.
 This figure shows that the limited photometric data can be reasonably well fit by at least one model from any of these three sub-classes. 
-\added[id=r2]{The density of curves in the top panels demonstrates that the SNIa model is consistently a good match to the data.} However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types.
-\deleted[id=r2]{than for the Type Ia class.}
+The density of curves in the top panels demonstrates that the SNIa model is consistently a good match to the data.
+However, the range of model parameters that allow such a fit to the data is much more limited for the heterogeneous CCSN types.
 To compute the posterior probability distribution we adopt priors for each of the three SN classes, again using the classification probabilities derived from the \SNABC host galaxy stellar population properties (row b of Table~\ref{tab:classification}).
@@
     \caption{
-    \replaced[id=r2]{A representative set of light curve and color curve models from the STARDUST2 classification algorithm.
+    A representative set of light curve and color curve models from the STARDUST2 classification algorithm.
 Panels on the left and center columns show  F105W and F160W, respectively, plotting the model light curves in black and photometry as red markers.
-The right-most column shows the F105W-F160W color curves and color data.}{Maximum likelihood light curve fits for each of the three primary SN sub-classes (Type Ia, Ib/c, and II).
-} All data points
+The right-most column shows the F105W-F160W color curves and color data.
+All data points
     as shown have been corrected for magnification and shifted in time using the preferred \lenstool model E.
 Plotted error bars include the measurement uncertainty and the lens modeling magnification uncertainty.
-\added[id=r2]{Data points in the right column also include this magnification uncertainty, even though cluster-scale lensing is achromatic, because the {\tt STARDUST2} analysis was done on the light curve data, not the color data directly.} In all panels the first data point is SN image 2, followed by image 1 and image 3.
-\replaced[id=r2]{In each panel the black curves show 200 SN light curve models drawn at random from the nested sampling sequence of the STARDUST2 (sncosmo) classification.
-    %The distribution of light curve and color curve shapes illustrates the exploration of the multi-dimensional parameter space executed by the nested sampling algorithm as it measures the likelihood for each SN class by comparison with the observed data.
-    }{The best-fitting Type Ia, Ib/c and II light curves are shown as solid, dashed, and dotted lines, respectively.}
+Data points in the right column also include this magnification uncertainty, even though cluster-scale lensing is achromatic, because the {\tt STARDUST2} analysis was done on the light curve data, not the color data directly.
+In all panels the first data point is SN image 2, followed by image 1 and image 3.
+In each panel the black curves show 200 SN light curve models drawn at random from the nested sampling sequence of the STARDUST2 (sncosmo) classification.
     \label{fig:classification_lightcurves}
@@
 
-\added[id=r2]{
 In all of the light curve fitting exercises described below, we also fix the SALT2 ``stretch'' parameter at $x_1=0$.
@@
 That measured $x_1$ will then be propagated back as a fixed parameter (with small uncertainty) into revised fitting of the SN images 1-3.
-}
+\added[id=r3]{Because of this, we do not incorporate the $\pm$5 day systematic uncertainty in the time-delay errors reported in Table~\ref{tab:time_delays}.}
 
@@
 While such extreme microlensing could alter the results for images 1 and 3, it would not alter the measurement of image 2 as it is likely in the achromatic phase.
-\added[id=r1]{Fortuitously, images 1 and 3 are minima, which are less susceptible to high deviations owing to microlensing when compared to image 2, which is a saddle.}
+Fortuitously, images 1 and 3 are minima, which are less susceptible to high deviations owing to microlensing when compared to image 2, which is a saddle.
 
@@
 This means we are finding a single set of SN model parameters to describe the intrinsic photometric evolution of the SN, and also finding the age (time from peak brightness) for each of the three images.
-%\added[id=r2]{For this method we fix the SALT2 stretch parameter at $x_1$=0.
-In the SALT2 formalism, the stretch parameter does not affect the color of the SN, so any choice of $x_1$ would be acceptable.
-}
+%For this method we fix the SALT2 stretch parameter at $x_1$=0. In the SALT2 formalism, the stretch parameter does not affect the color of the SN, so any choice of $x_1$ would be acceptable.
 
@@
 
-%\replaced[id=r1]{After repeating this process for each of the five lens models, we compare the Bayesian Evidence of each fit and determine model E to be the preferred lens model.}
-\deleted[id=r1]{After repeating this process for each of the five lens models, we use the Bayesian Evidence to determine a preferred lens model (Table \ref{tab:model_evidence}).
-Using a coarse sampling we find significant preference for models C and E over models A,B, and D (at $>3\sigma$), but no significant difference between models C and E (Table \ref{tab:model_evidence}).
-Using a finer sampling for these two models, we find that there is preference for model E over model C (at $\sim3.6\sigma$).
-This was also the model selected as the optimal lens model before unblinding, so we have reinforced the justification to adopt model E as our preferred model.
-}
-
-%Figure \ref{fig:corner_modelE} shows our final constraints on the age of each SN image based on these simultaneous light curve fits to the magnification-corrected fluxes in F105W and F160W.
-
 As our final method to incorporate the color and brightness information together, we use the color-based posterior probability distributions (Fig. \ref{fig:corner_cfit}) as the prior for 
@@
 The joint posterior distributions from this method are shown in Figure \ref{fig:corner_combined}.
-%As expected, these match very closely with the two-band light-curve-based fitting (Fig. \ref{fig:corner_modelE}).
-
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=0.45\textwidth]{Images/lightcurve_image2.pdf}
-%     \caption{Light-curve-based age constraints for \SNABC image 2, using the methodology outlined in section \ref{s:lightcurves}.
-The upper panel shows the posterior distributions from SNTD for the age of image 2 from section \ref{s:colorcurves} (magenta), section \ref{s:lightcurves} (light blue), and the combination of both methods (orange).
-The grey shaded region covers the 68\% confidence interval of the best-fit SALT2 light curve, with the median model shown as a solid line.
-The orange shaded region shows the 1$\sigma$ range of the measured (lens-model-corrected, see table \ref{tab:time_delays}) F160W magnitude, which corresponds to a V band magnitude in the rest-frame.
-}
-%     \label{fig:lightcurve2}
-% \end{figure}
-
-% \begin{table}[ht]
-% \begin{tabular}{crrrrrrr}
-
-%     \multicolumn{1}{c}{Model} &\multicolumn{1}{c}{$\mu_1$} & \multicolumn{1}{c}{$\mu_2$} &\multicolumn{1}{c}{$\mu_3$} &\multicolumn{1}{c}{$t_2-t_1$} & \multicolumn{1}{c}{$t_3-t_1$}& \multicolumn{1}{c}{$t_4-t_1$} & \multicolumn{1}{c}{Bayesian Evidence}\\
-% \midrule
-% \textit{A} & 6.324 & 9.526 & 6.879 & 180.3 & 82.7&7402.8&$-10.98\pm0.28$ \\
-% \textit{B} & 6.281 & 9.923 & 7.472 & 184.4 & 85.3&7034.9&$-10.21\pm0.27$ \\
-% \textit{C} &8.942  & 18.48 & 13.257 & 103.6 & 50.2&5876.8&$-6.91\pm0.22$ \\
-% \textit{D} & 8.699 & 18.069 & 12.719 & 108.3 & 53.7&6020.5&$-7.78\pm0.24$ \\
-% \textit{E} & 3.907 & 7.381 & 5.020 & 101.4 & 19.3&7760&$-6.95\pm0.2$ \\
-% \end{tabular}
-% \caption{\label{tab:model_evidence}Predicted lensing observables and Bayesian evidence for the five lens model variants investigated in this work.
-The Bayesian evidences in the final column are calculated by comparison to the observed photometry, using a coarse (100 live points) nested sampling fit, which helps identify models C and E as preferred over A,B, and D.
-We then implement a finer nested sampling fit (1,000 live points), and find that in fact model E is preferred at $>3\sigma$ ($Z_C=-7.25\pm0.07, \ Z_E=-   7.00\pm0.06$).}
-% \end{table}
-
-%\section*{Supplementary Text}
 
@@
     \includegraphics[width=0.49\textwidth]{Paper/Figures/colorcurve_image3.pdf}
-    \caption{Color-based age constraints for \SNABC image 1 (upper \replaced[id=r1]{left}{right}), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Color Curve Age Constraints} section.
+    \caption{Color-based age constraints for \SNABC image 1 (upper left), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Color Curve Age Constraints} section.
 The upper panel of each figure shows the posterior for the age of each image from SNTD, using a prior on the SALT2 color parameter (c) based on known population characteristics of SNIa.
@@
     \includegraphics[width=0.49\textwidth]{Paper/Figures/lightcurve_image3.pdf}
-    \caption{Light-curve-based age constraints for \SNABC image 1 (upper \replaced[id=r1]{left}{right}), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Light Curve Age Constraints} section.
+    \caption{Light-curve-based age constraints for \SNABC image 1 (upper left), image 2 (upper right), and image 3 (bottom center), using the methodology outlined in the \textit{Light Curve Age Constraints} section.
 The upper panel in each figure shows the posterior distributions from SNTD for the age of each image that is independent of the lens model (magenta, figure \ref{fig:colorcurves}), using lens model E (light blue), and the combination of both methods (orange).
@@
 
-\added[id=r1]{
 Ref \cite{newman_resolving_2018} (hereafter N18) provides a detailed analysis of this cluster, including sophisticated modeling of the lens.
@@
 We did not incorporate pixel-level flux data, because the \lenstool code can only use observed fluxes when doing source plane optimisation.
-}
 
@@
     \caption{
-    \added[id=r1]{Comparison of magnification predictions with the N18 lens model.}
+    Comparison of magnification predictions with the N18 lens model.
     }
@@
 
-\added[id=r1]{
 Table~\ref{tab:mu_comparison} shows the magnification values predicted by our lens model E in comparison to the values reported in N18. 
@@
 As seen in Figure~\ref{fig:class}c, a larger magnification value would make the SN {\it more} consistent with the expected luminosity of a Type Ia SN at this redshift---though it would also make it more consistent with some CC SN light curves, likely making the classification somewhat more ambiguous.
+
+\added[id=r1]{It is important to note that both the N18 models and all of the model variants explored here adopted 
+dual pseudo-isothermal elliptical (dPIE)  distributions as the density profile for all lensing components.
+It is well-documented that the choice of the density profile can strongly affect the inferred magnifications and time delays in a strong lensing system.
+This is therefore another potential source of systematic uncertainty that should be explored in future lens modeling.
+If alternate density profiles result in significant changes to the model-predicted magnfications for the SN images, that could in principle change the conclusions about SN classification and age constraints described here.
+}
+
 We expect that new lens modeling of this cluster with alternate software and different choices of constraints will also be informative, and may improve on our model predictions.  
@@
 We hope that the discovery of \SNABC  will encourage such efforts.
-}
 
@@
 \subsubsection*{Future Lens Modeling}
-\added[id=r1]{
+
 The uncertainty in the predicted time delay from the lens model presented here is $\pm$540 days (in the observer frame).
@@
 We did not have this measurement available prior to unblinding, and thus we have restricted ourselves to only consider fully blind lens models in this paper.
-However, future analyses could incorporate the BCG velocity dispersion and here we speculate about the impact.
+However, \added[id=r1]{we note that this measured value is very discrepant with the best-fit value of 700 km s$^{-1}$ from our preferred lens model, variant E (see Table~\ref{tab:massmodel}).}  Future analyses could incorporate the BCG velocity dispersion and here we speculate about the impact \added[id=r1]{this would have}.
+
 With a preliminary extension of model E we find that the time delay predictions would likely shift by $<$15 days, and the predicted magnifications for SN images 1-3 would likely be larger by as much as $\sim$2.5$\times$.
@@
 Application of different lens modeling approaches could also provide some added confidence that there are not systematic biases in the lens model time delay prediction.
-}
 
 \subsubsection*{Future Observations}
-\added[id=r1]{
+
 Though the $\pm540$ day time delay uncertainty is small relative to the baseline of $>7000$ days, it nevertheless represents a long period over which the field would need to be monitored for the reappearance.
@@
 Measurement of the magnification for a lensed Type Ia SN can be done without adopting strong priors from a cosmological model \cite{patel_three_2014}, meaning that one can avoid a circular constraint when the \SNABC time delay is then used for cosmology.
-}
 
 \subsubsection*{Future Discoveries}
-\added[id=r2]{
+
 In addition to follow-up observations of \SNABC, we may also hope for more discoveries of similar cluster-lensed SNe with long time delays.
+\added[id=r2]{A primary motivation for pursuing such events is that they can be a relatively low-cost tool for time delay cosmography.
+As \SNABC shows, when the time delay is longer than a few years, the time delay measurement can be anchored at either end by just a few epochs of imaging.
+If similar events are detected while the SN is still observable, one could collect a well-sampled light curve for an early and bright image using ground-based telescopes.
+After waiting through the decade-long delay, the SN's reappearance can be captured with a relatively low-cost monitoring campaign.
+A full light curve of the final image would not be needed.
+For example, with \SNABC even if the time delay is measured to only $\pm$150 days, that would be a 2\% time-delay measurement, meaning it is lens-model-limited for cosmological inferences.}
+
 The expected rate for such events is still highly uncertain, and published rate estimates to date can only be taken as extreme lower limits for the expected yield from future sky surveys \cite{riehm_near-ir_2011,li_rates_2012,petrushevska_searching_2018,petrushevska_strongly_2020}.
@@
 Similarly, if we apply the 10$\times$ lower rate for the Rubin Observatory to the most massive clusters in the LSST survey area, we would anticipate at least $\sim$10 detections over the 10-year survey.
+\added[id=r2]{This discovery rate from wide-field surveys could be enhanced with dedicated ground-based cluster surveys.
+\cite{stanishev_near-ir_2009,goobar_near-ir_2009,riehm_near-ir_2011}
+}
 
@@
 This would require a more complete census of lensing clusters, along with lens models to predict magnifications and time delays, and measurements of star formation and stellar mass in lensed galaxies to predict the SN explosion rates.
-}
 

### 2021-05-21 Analysis/mrg/fig1_SRmods.py
resubmission stuff

@@ -1,0 +1,121 @@
+"""
+Discovery figure, Fig. 1
+"""
+from astropy.table import Table
+
+def rgb():
+    
+    from grizli.pipeline import auto_script
+    from mastquery import overlaps
+    import astropy.io.fits as pyfits
+    import astropy.wcs as pywcs
+    import numpy as np      
+    
+    root = 'j013804m2156'
+
+    x0, y0= 2465, 1740
+    
+    NY = 200
+    NX = 200
+
+    slx = slice(x0-NX, x0+NX)
+    sly = slice(y0-NY, y0+NY)
+    
+    mi = -0.01
+    
+    si = 4.8
+    
+    _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si))
+
+    _rgb = auto_script.field_rgb(root=root, filters=['f110w','f125w','f140w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', rgb_scl=[1.06,1,1.02], suffix='.off', rgb_min=mi, tick_interval=10, xsize=si, output_dpi=int(2*NX/si))
+    
+    im = pyfits.open(f'{root}-f160w_drz_sci.fits')
+    wcs = pywcs.WCS(im[0].header, relax=True)
+    wsl = wcs.slice((sly, slx))
+    
+    coo = Table.read('coords.txt', format='ascii.commented_header')
+    N, inter = 10, 0.5
+    
+    N, inter = 20, 1.0
+    
+    xy = np.cast[int](np.round(wcs.all_world2pix(coo['ra'], coo['dec'], 0))).T
+    
+    for i in [4,5,6]:
+        
+        xi, yi = xy[i]
+        slx = slice(xi-N, xi+N)
+        sly = slice(yi-N, yi+N)
+        
+        _rgb = auto_script.field_rgb(root=root, filters=['f105w','f125w','f160w'], HOME_PATH=None, xyslice=(slx, sly), show_ir=False, add_labels=False, output_format='png', suffix='.on{0}'.format(coo['label'][i]), rgb_min=mi, tick_interval=inter, xsize=si/3.)
+
[…]

### 2021-05-21 Analysis/mrg/fig1.py
shift labels

@@ -42,11 +42,7 @@ def rgb():
     import numpy as np      
     
     from grizli import utils
-<<<<<<< HEAD
-=======
-
     plt.rcParams.update({'font.size':10})
->>>>>>> 8dafb3ee4ba770e7c3cd5c2541a900edcc2f58e2
     
     root = 'j013804m2156'
 
@@ -91,9 +87,9 @@ def rgb():
           
     
     # Label offsets
-    #      H1  H2 H3   H4 SN3 SN2  SN1  SN4   SN5 3.1 3.2 3.3 3.4
-    dx = [-30, 10, 0, -28,  0, 5,  -28, -27] + [0, 0, 0, -18, 0]
-    dy = [-8, 14, 10,  0,  10, 10, -15,  10] + [15, 15, 15, 0, 0]
+    #      H1  H2   H3   H4 SN3 SN2  SN1  SN4   SN5 3.1 3.2 3.3 3.4
+    dx = [-20, 10, -25, -28,-10, 5,  -40, -34] + [0, 0, 0, -18, 0]
+    dy = [ 13, 20,   10,  0,  10, 10, -15, 10] + [15, 15, 15, 0, 0]
         
     ny = 3
     ny = 4
@@ -133,7 +129,8 @@ def rgb():
         else:
             fs = 11
             
-        ax.text(xyi[i][0]+dx[i], sh[0]-xyi[i][1]+dy[i], coo['label'][i], ha='center', va='top',
+        ax.text(xyi[i][0]+dx[i], sh[0]-xyi[i][1]+dy[i], coo['label'][i], 
+                ha='center', va='top',
                 color=colors[i], fontsize=fs)
     
     labels = 'bcdefghijk'
